### 2022-02-08 _targets.Rmd
reproducible pipeline example

---
title: "Target Markdown"
output: html_document
---

```{r setup, include = FALSE}
here::set_here()
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")

# load libraries for targets notebook
library(targets)
library(tidyverse, quietly = TRUE)

# clean knitting history
tar_unscript()
```

```{targets example-globals, tar_globals = TRUE}
options(tidyverse.quiet = TRUE)

# load libraries for make
tar_option_set(packages = c("tidyverse", "quanteda"))

# read custom functions
lapply(list.files(here::here("R"), full.names = TRUE), source)
```

# Data import

```{targets texts, tar_simple = TRUE}
read_csv2(here::here("data_core_pubs_trim.csv"))
```

# Text pre-processing

```{targets}
list(
    tar_target(corpus,
               extract_corpus(texts)),
    tar_target(tokens,
               process_tokens(corpus, texts))
)
```

# Check results

```{r}
tar_read(tokens)
```

etc... rinse and repeat

### 2022-02-08 R/extract_corpus.R

@@ -1,0 +1,7 @@
+extract_corpus <- function(texts) {
+    
+    texts %>% 
+        pull(pubs_title) %>% 
+        tolower()
+    
+}

### 2022-02-08 R/process_tokens.R

@@ -1,0 +1,23 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param corpus
+#' @return
+#' @author hlageek
+#' @export
+process_tokens <- function(corpus, texts) {
+
+    tokens <-  tokens(corpus, what = "word", 
+                      remove_numbers = F, remove_punct = T,
+                      remove_symbols = F)
+    tokens <-  tokens_wordstem(tokens, language="english")
+    stopwords("english")
+    sw = unique(c( quanteda::stopwords("english"),"also","e.g", "can","includ","said","first","wherein","other","made","make", "later",  "copyright", "fig", "figur", "tabl", "description", "describ"))
+    tokens =  tokens_select(tokens, sw,  selection = "remove")
+    
+    names(tokens) = texts$ID_core_pubs
+
+    tokens
+}

### 2022-02-08 R/create_dfm.R
add create_dfm()

@@ -1,0 +1,17 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param tokens
+#' @return
+#' @author hlageek
+#' @export
+create_dfm <- function(tokens_input) {
+
+    
+    tokens.dfm <- quanteda::dfm(tokens_input, tolower = FALSE)
+    
+    dfm_trim(tokens.dfm, min_termfreq = 10, termfreq_type="count")
+
+}

### 2022-05-05 _targets.Rmd
add create_dfm()
targets

@@
 ---
+
+# Set up targets environment
+
+Here we run necessary code for `targets` setup.
 
@@
 library(targets)
-library(tidyverse, quietly = TRUE)
+library(dplyr, quietly = TRUE)
 
@@
 
+# Dependencies
+
+Here, we load packages and custom functions required in the pipeline.
+
 ```{targets example-globals, tar_globals = TRUE}
@@
 # load libraries for make
-tar_option_set(packages = c("tidyverse", "quanteda"))
+tar_option_set(packages = c("dplyr",
+                            "tidyr",
+                            "purrr",
+                            "readr",
+                            "quanteda",
+                            "igraph",
+                            "DiagrammeR",
+                            "tibble",
+                            "stringr",
+                            "topicmodels",
+                            "ggplot2",
+                            "scales",
+                            "ldatuning",
+                            "quanteda",
+                            "data.table",
+                            "tidytext",
+                            "tm"
+                            ))
 
@@
 
-```{targets texts, tar_simple = TRUE}
-read_csv2(here::here("data_core_pubs_trim.csv"))
-```
+```{targets data_import}
+list(
 
-# Text pre-processing
+    tar_target(one_author,
+               read.csv2(here::here("data", "raw", "Binter_pubs.csv")),
+               format = "qs"),
+    tar_target(two_authors, read.csv2(here::here("data", "raw", "Binter_Kvapilova_pubs.csv")),
+               format = "qs")
 
-```{targets}
-list(
-    tar_target(corpus,
-               extract_corpus(texts)),
-    tar_target(tokens,
-               process_tokens(corpus, texts))
 )
@@
 
-# Check results
+# Coauthorship network
+
+```{targets network}
+
+list(
+
+    tar_target(edgelist,
+               make_edgelist(one_author),
+                format = "qs"),
+    tar_target(graph, igraph::graph_from_data_frame(edgelist, directed = FALSE) )
+
+)
+
+```
+
+# Topic model
+
+```{targets topic_model}
+list(
+
+   tar_target(topic_model, 
+              make_topic_model(two_authors),
+               format = "qs")
+
+)
+```
+
+# Researcher independence indicator (RII) part 1 - eigenvector centrality
+
+```{targets RII1}
+
+list(
+
+    tar_target(eigen_centr,
+               calc_eigen_centr(graph), 
+               format = "qs")
+
+)
+
+```
+
+# Researcher independence indicator (RII) part 2 - clustering coefficient
+
+```{targets RII2}
+
+list(
+
+    tar_target(clustering,
+               calc_clustering(graph), 
+               format = "qs")
+
+)
+
+```
+
+# Researcher independence indicator (RII) part 3 - independent publications
+
+```{targets RII3}
+
+list(
+
+    tar_target(ind_pubs,
+               calc_ind_pubs(one_author), 
+               format = "qs")
+
+)
+
+```
+
+# Researcher independence indicator (RII) part 4 - independent topics
+
+```{targets RII4}
+
+list(
+
+    tar_target(ind_topics,
+               calc_ind_topics(topic_model, two_authors), 
+               format = "qs")
+
+)
+
+```
+
+# Researcher independence indicator (RII) part 4 - independent topics: alternative way via cosine similarity
+
+```{targets RII4_2}
+
+list(
+
+    tar_target(ind_topics_cs,
+               calc_cos_sim(topic_model, two_authors), 
+               format = "qs")
+
+)
+
+```
+
+# Final indicator
 
 ```{r}
-tar_read(tokens)
+
+```
+# Article
+
+```{targets article}
+list(
+    tarchetypes::tar_render(article, here::here("Rmd", "article.Rmd"))
+)
+
 ```

### 2022-05-12 _targets.Rmd
targets update

@@
                             "tidytext",
-                            "tm"
+                            "tm",
+                            "httr",
+                            "rjson",
+                            "keyring",
+                            "RSQLite",
+                            "DBI"
                             ))
@@
 
-    tar_target(one_author,
-               read.csv2(here::here("data", "raw", "Binter_pubs.csv")),
+    # tar_target(one_author,
+    #           read.csv2(here::here("data", "raw",    #"Binter_pubs.csv")),
+ #              format = "qs"),
+      tar_target(ids, read.csv2(here::here("data", "raw", "supervisors.csv")),
               format = "qs"),
-    tar_target(two_authors, read.csv2(here::here("data", "raw", "Binter_Kvapilova_pubs.csv")),
+    tar_target(db_path,
+           here::here("data", "raw", "czech_sci_db.sqlite")),
+    tar_target(all_pubs,
+           get_all_pubs(db_path, ids), 
+              format = "qs")
+
+)
+```
+
+# Topic model
+
+```{targets topic_model}
+list(
+
+   tar_target(topic_model, 
+              make_topic_model(all_pubs),
                format = "qs")
@@
 
-```
-
-# Topic model
-
-```{targets topic_model}
-list(
-
-   tar_target(topic_model, 
-              make_topic_model(two_authors),
-               format = "qs")
-
-)
 ```

### 2022-05-12 R/api_import_fc.R

@@ -1,0 +1,36 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param ids
+#' @return
+#' @author fatal: unable to access 'C:/Users/David Jank?/Documents/.config/git/config': Invalid argument
+#' @export
+api_import_fc <- function(ids) {
+  result_df <- tibble()
+
+  for (i in seq_along(ids$vedidk_core_researcher)[1:3]) { # tady bych mel idealne dat vsechny ids do jednoho vektoru a vyhodit z nich duplikovane
+
+    vedidk <- ids$vedidk_core_researcher[i]
+    body1 <- list(token = keyring::key_get("riv"), 
+                  oblast = "riv", 
+                  rezim = "filtr-detail", 
+                  "tv-identifikator" = vedidk)
+    result <- httr::POST(url = "https://api.isvavai.cz/api.php", 
+                         body = body1, 
+                         encode = c("form"))
+
+    dataAsRawjson <- httr::content(result, as = "text")
+    dataAsjson <- jsonlite::fromJSON(dataAsRawjson, flatten = TRUE)
+    # as_tibble(dataAsjson[[1]][1])
+    # dataAsjson[["hlavicka"]][["zprava"]] #najit sloupce ktere chci z toho vytahat a pouzit
+    # [1] "IP adresa požadavku není uvedena v seznamu povolených adres" --> tohle je problem, zkontrolovat doma
+
+    temp_df <- as_tibble(dataAsjson[[1]])
+    temp_df$my_id <- vedidk
+    result_df <- bind_rows(result_df, temp_df)
+    # result_df[i] <- as_tibble(dataAsjson[[1]][1]) - v pripade ze bych to chtel jako list (pak musim zmenit typ toho result_df)
+    Sys.sleep(0.5)
+  }
+}

### 2022-05-12 R/calc_cos_sim.R

@@ -1,0 +1,28 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param topic_model
+#' @return
+#' @author fatal: unable to access 'C:/Users/David Jank?/Documents/.config/git/config': Invalid argument
+#' @export
+calc_cos_sim <- function(topic_model, two_authors) {
+
+    topic_model <- as.matrix(topic_model) 
+    cosine_matrix <- lsa::cosine(topic_model) %>% 
+        as.data.frame() %>% 
+        rownames_to_column("Kód.výsledku") %>% 
+        as.data.table() 
+    
+       
+    finaldata <- merge.data.table(two_authors, cosine_matrix, by.y = "Kód.výsledku", by.x = "Kód.výsledku", all = TRUE) #tady páruju ty datasety
+    
+    finaldata <- filter(finaldata, !duplicated(finaldata$Kód.výsledku))
+    
+    finaldata <- filter(finaldata, str_detect(finaldata$list, "Binter")) #v tenhle moment mi to hází 21 výsledků i když původne mel mit Binter jen 20, tak nevím co s tim
+    
+    finaldata$avg <- rowMeans(finaldata[ ,84:140]) #tady jsem si ale musel manualne najit poradi sloupců -> melo by to jit nějak vic automatizovane 
+    
+    mean(finaldata$avg, na.rm = TRUE)
+}

### 2022-05-12 R/calc_ind_pubs.R

@@ -1,0 +1,16 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param one_author
+#' @return
+#' @author fatal: unable to access 'C:/Users/David Jank?/Documents/.config/git/config': Invalid argument
+#' @export
+calc_ind_pubs <- function(one_author) {
+
+    ind_pubs <- filter(one_author, !str_detect(one_author$list, "Klapilová, Kateřina"))
+    
+    rpubs = nrow(ind_pubs)/nrow(one_author)
+
+}

### 2022-05-12 R/calc_ind_topics.R

@@ -1,0 +1,60 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param topic_model
+#' @return
+#' @author fatal: unable to access 'C:/Users/David Jank?/Documents/.config/git/config': Invalid argument
+#' @export
+calc_ind_topics <- function(topic_model, two_authors) {
+
+    all_pubs <- as_tibble(t(topic_model)) %>% #in this step, the identificators of pubs gets deleted and substituted with numbers
+        rownames_to_column("pub_id") %>% 
+        mutate(pub_id = as.integer(pub_id)) %>% 
+        left_join(two_authors %>% 
+                      select(pub_id = ID_core_pubs, list)) #this should be matched with "Kód.výstupu" not ID_core_ 
+    
+    
+    all_pubs <- mutate(all_pubs, str_detect(all_pubs$list, "Binter"))
+    
+    all_pubs <- mutate(all_pubs, str_detect(all_pubs$list, "Klapilová"))
+    
+   # colnames(all_pubs) <- paste0("topic_", colnames(topics))
+    
+    #tahle funkce říká: pokud v daném tématu nemá sledovaný výzkumník ani jednu publikaci s loadingem  více než 0,1, pak mi vytiskni "0", pokud má alespoň jednu, ale zároveň i jeho supervisors má alsepoň jednu, tak mi vytiskni "2", a pokud má alespoň jednu ale supervisor nemá žádnou, tak vytiskni "1". Takhle funkce bohužel není škálovatelná, takže se bude muset přepsat.   
+    topics$topic_one <- if(sum(ifelse(data[1,1:20]>0.1, 1, 0))<1){print("0")
+    } else if(sum(ifelse(data[1,21:77]>0.1, 1, 0))>1){print("2")
+    } else {
+        print("1")
+    }
+    
+    topics$topic_two <- if(sum(ifelse(data[2,1:20]>0.1, 1, 0))<1){print("0")
+    } else if(sum(ifelse(data[2,21:77]>0.1, 1, 0))>1){print("2")
+    } else {
+        print("1")
+    }
+    
+    topics$topic_three <- if(sum(ifelse(data[3,1:20]>0.1, 1, 0))<1){print("0")
+    } else if(sum(ifelse(data[3,21:77]>0.1, 1, 0))>1){print("2")
[…]

### 2022-05-12 R/data_download.R

@@ -1,0 +1,14 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+
+#' @return
+#' @author fatal: unable to access 'C:/Users/David Jank?/Documents/.config/git/config': Invalid argument
+#' @export
+data_download <- function() {
+
+  NULL
+
+}

### 2022-05-12 R/get_all_pubs.R

@@ -1,0 +1,122 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param db_path
+#' @param ids
+#' @return
+#' @author fatal: unable to access 'C:/Users/David Jank?/Documents/.config/git/config': Invalid argument
+#' @export
+get_all_pubs <- function(db_path, ids) {
+
+    con <-  DBI::dbConnect(RSQLite::SQLite(), db_path)
+    on.exit(DBI::dbDisconnect(con))
+    
+    DBI::dbListTables(con)
+    
+    ids_complete <- as_tibble(ids) %>% 
+        filter(!is.na(vedoucí.vedidk)) %>% 
+        filter(!is.na(vedidk_core_researcher))
+    
+    ids_complete_vector <- cbind(ids_complete$vedidk_core_researcher, ids_complete$vedoucí.vedidk) %>% 
+        as_tibble() %>% 
+        as_vector() 
+    
+    ids_complete_col <- bind_rows(as_tibble(ids_complete$vedidk_core_researcher), as_tibble(ids_complete$vedoucí.vedidk))
+    
+    comb_vedidk_pubids <- DBI::dbReadTable(con, "authors_by_pubs") %>% 
+        select(vedidk, id_unique) %>% 
+        filter(vedidk %in% ids_complete_vector) %>% 
+        distinct() %>% 
+        as_tibble()
+    
+    # comb_vedidk_pubids <- DBI::dbReadTable(con, "authors_by_pubs") %>%
+    #     filter(vedidk == .env$vedidk) %>%
+    #     select(vedidk, id_unique) %>%
+    #     distinct() %>%
+    #     as_tibble()
+    
+    
+    # comb_pubids_kod <- DBI::dbReadTable(con, "riv_unique_ids") %>% #colnames()
+    #     filter(id_unique %in% comb_vedidk_pubids$id_unique) %>% 
+    #     distinct() %>% 
+    #     as_tibble()
+    
+    filtered_pubs <- DBI::dbReadTable(con, "riv_disc") %>%  #colnames()  
+        select(id_unique, pub_type) %>% 
+        filter(id_unique %in% comb_vedidk_pubids$id_unique) %>% 
+        filter(pub_type %in% c("J","B","C","D")) %>% 
+        as_tibble() 
+  
+    # this filtered out all non-publication outputs, n=4676
+    
+    text_pubs <- DBI::dbReadTable(con, "riv_text") %>% #colnames()
[…]

### 2022-05-12 R/make_edgelist.R

@@ -1,0 +1,36 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param one_author
+#' @return
+#' @author fatal: unable to access 'C:/Users/David Jank?/Documents/.config/git/config': Invalid argument
+#' @export
+make_edgelist <- function(one_author) {
+
+   
+    split_authors <- strsplit(as.character(one_author$list), ':')
+    
+    dat <- enframe(split_authors) %>% unnest(cols = "value")
+    
+    dat %>% group_by(name) %>% 
+        right_join(dat, by = "name") %>% 
+        filter(value.x != value.y) %>% 
+        mutate(from = pmin(value.x, value.y),
+               to = pmax(value.x, value.y)) %>% 
+        select(pub_id = name, from, to) %>% 
+        distinct() %>% 
+        ungroup() %>% 
+        
+        mutate(from = tolower(stringi::stri_trans_general(from, "latin-ascii")),
+               to = tolower(stringi::stri_trans_general(to, "latin-ascii"))) %>% 
+        mutate(from = str_trim(str_replace(from, "(.*), (.?){1}.*", "\\1\\2")),
+               to = str_trim(str_replace(to, "(.*), (.?){1}.*", "\\1\\2"))) %>% 
+        
+        relocate(pub_id, .after = last_col()) %>% 
+        group_by(from, to) %>% 
+        count(name = "weight") %>% 
+        ungroup()
+    
+}

### 2022-05-12 network_analysis.R

@@ -309,7 +309,7 @@ rm(topics)
 all_pubs <- as_tibble(t(data)) %>% 
     rownames_to_column("pub_id") %>% 
     mutate(pub_id = as.integer(pub_id)) %>% 
-    left_join(two_auth %>% 
+    left_join(two_authors %>% 
                    select(pub_id = ID_core_pubs, list)) 
 
 

### 2022-05-12 _targets.Rmd
pipline iteration done

@@
  #              format = "qs"),
-      tar_target(ids, read.csv2(here::here("data", "raw", "supervisors.csv")),
+      tar_target(ids, read.csv2(here::here("data", "raw", "supervisors.csv"), nrows = 20),
               format = "qs"),
+      tar_target(ids_complete, create_ids_complete(ids),
+              format = "qs"),
+    tar_target(ids_complete_vector,
+               make_ids_complete_vector(ids)),
     tar_target(db_path,
@@
            get_all_pubs(db_path, ids), 
-              format = "qs")
+              format = "qs"),
+    tar_target(one_author,
+           read_one_author(db_path, ids_complete_vector), 
+              format = "qs", pattern = map(ids_complete_vector), iteration = "list")
 
@@
 
-   tar_target(topic_model, 
-              make_topic_model(all_pubs),
-               format = "qs")
+   tar_target(topic_model_input,
+              make_topic_model_input(all_pubs),
+                format = "qs") #,
+   # --> fce find k 
+   # tar_target(topic_model,
+   #            make_topic_model(topic_model_input),
+   #             format = "qs")
 
@@
                make_edgelist(one_author),
-                format = "qs"),
-    tar_target(graph, igraph::graph_from_data_frame(edgelist, directed = FALSE) )
+                format = "qs", pattern = map(one_author), iteration = "list"),
+    tar_target(graph, igraph::graph_from_data_frame(edgelist, directed = FALSE), pattern = map(edgelist), iteration = "list")
 
@@
     tar_target(eigen_centr,
-               calc_eigen_centr(graph), 
-               format = "qs")
+               calc_eigen_centr(graph, ids_complete, one_author, db_path),
+               format = "qs", pattern = map(graph, one_author), iteration = "list")
 
@@
 
-    tar_target(clustering,
-               calc_clustering(graph), 
-               format = "qs")
-
+    # tar_target(clustering,
+    #            calc_clustering(graph), 
+    #            format = "qs")
+    # 
 )
@@
 
-    tar_target(ind_pubs,
-               calc_ind_pubs(one_author), 
-               format = "qs")
-
+    # tar_target(ind_pubs,
+    #            calc_ind_pubs(one_author), 
+    #            format = "qs")
+    # 
 )
@@
 
-    tar_target(ind_topics,
-               calc_ind_topics(topic_model, two_authors), 
-               format = "qs")
+    # tar_target(ind_topics,
+    #            calc_ind_topics(topic_model, two_authors), 
+    #            format = "qs")
 
@@
 
-    tar_target(ind_topics_cs,
-               calc_cos_sim(topic_model, two_authors), 
-               format = "qs")
-
+    # tar_target(ind_topics_cs,
+    #            calc_cos_sim(topic_model, two_authors), 
+    #            format = "qs")
+    # 
 )
@@
 
-```{r}
+```{targets final}
+
+list(
+
+    tar_target(final_data,
+               calc_final_data(eigen_centr, clustering = NULL, ind_topics = NULL, ind_pubs = NULL),
+               format = "qs")
+
+)
 

### 2022-05-12 R/calc_eigen_centr.R

@@ -7,7 +7,7 @@
 #' @return
 #' @author fatal: unable to access 'C:/Users/David Jank?/Documents/.config/git/config': Invalid argument
 #' @export
-calc_eigen_centr <- function(graph) {
+calc_eigen_centr <- function(graph, ids_complete, one_author, db_path) {
 
     ecentr <- eigen_centrality(
         graph,
@@ -19,10 +19,36 @@ calc_eigen_centr <- function(graph) {
     
     centr <- enframe(ecentr$vector, name = "author", value = "eigen_ctr")
     
+    vedidk_researcher <- one_author %>% 
+        pull(vedidk) %>% 
+        unique()
+    
+    sup_vector <- ids_complete %>% 
+            filter(vedidk_core_researcher == vedidk_researcher) %>% 
+            pull(vedoucí.vedidk)
+        
+    con <-  DBI::dbConnect(RSQLite::SQLite(), db_path)
+    on.exit(DBI::dbDisconnect(con))
+    
+   a <- DBI::dbReadTable(con, "authors_by_pubs") %>% #colnames()
+        filter(vedidk == sup_vector) %>% 
+        select(id_helper) %>% 
+        count(id_helper) %>% 
+        filter(n == max(n)) %>% 
+        slice_sample(n=1) %>% 
+        pull(id_helper)
+    
     sup <- centr %>% 
-        filter(author=="klapilovak")
+               filter(author == a) %>% 
+        pull(eigen_ctr)
+    
+    table <- tibble(vedidk = vedidk_researcher, eig = sup)
     
     
-    sup$eigen_ctr
+    # access ïds_complete -> take the vedidk_core_researcher of the given 
+    # current research -> match it with the vedouci.vedidk na stejnem radku 
+    # --> vezmi ten vedidk vedouciho, jdi do databaze "authors by pubs" a 
+    # match it with the id_helper of a given person
+    
 
 }

### 2022-05-12 R/calc_final_data.R

@@ -1,0 +1,33 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param eigen_centr
+#' @param clustering
+#' @param ind_topics
+#' @param ind_pubs
+#' @return
+#' @author fatal: unable to access 'C:/Users/David Jank?/Documents/.config/git/config': Invalid argument
+#' @export
+calc_final_data <- function(eigen_centr, clustering = NULL, ind_topics = NULL, ind_pubs = NULL) {
+# 
+#     vedidk_researcher <- one_author %>% 
+#         map("vedidk") %>% 
+#         unlist() %>% 
+#         unique() 
+    
+    
+  # final_data <- tibble(vedidk = vedidk_researcher, 
+  #                      eigen_centr = unlist(eigen_centr), 
+  #                      # clustering = unlist(clustering),
+  #                      # ind_pubs = unlist(ind_pubs),
+  #                      # ind_topics = unlist(ind_topics)
+  #                      ) 
+      
+
+    bind_rows(eigen_centr)
+    
+    # left_join(eigen_centr, eigen_centr, by = "vedidk")
+
+}

### 2022-05-12 R/create_ids_complete.R

@@ -1,0 +1,17 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+
+#' @return
+#' @author fatal: unable to access 'C:/Users/David Jank?/Documents/.config/git/config': Invalid argument
+#' @export
+create_ids_complete <- function(ids) {
+
+    ids_complete <- as_tibble(ids) %>% 
+        select(vedidk_core_researcher, vedoucí.vedidk) %>% 
+        filter(!is.na(vedoucí.vedidk)) %>% 
+        filter(!is.na(vedidk_core_researcher)) 
+
+}

### 2022-05-12 R/get_all_pubs.R

@@ -59,40 +59,41 @@ get_all_pubs <- function(db_path, ids) {
         filter(!is.na(abstract_eng)) %>% 
         as_tibble() 
     
-    #interestingly, we lost 778 (2.7 %) publications in this step, not sure why. Also, many of the remaining publications seem to have missing abstracts or keywords. Analysis of the 778 missing cases below:
     ## we decided to only include papers with full abstracts = 27134 pubs 
     
-    disc_pubs_missing <- DBI::dbReadTable(con, "riv_disc") %>%  #colnames()  
-        filter(id_unique %in% comb_vedidk_pubids$id_unique) %>% 
-        filter(pub_type %in% c("J","B","C","D")) %>% 
-        filter(!id_unique %in% text_pubs$id_unique) %>% 
-        as_tibble() 
+    #interestingly, we lost 778 (2.7 %) publications in this step, not sure why. Also, many of the remaining publications seem to have missing abstracts or keywords. Analysis of the 778 missing cases below:
     
-    text_pubs_missing <- DBI::dbReadTable(con, "riv_text") %>% #colnames()
-        select(id_unique, title_eng, abstract_eng, keywords) %>% 
-        filter(id_unique %in% disc_pubs_missing$id_unique) %>% 
-        filter(!duplicated(id_unique)) %>% 
-        as_tibble() 
-    
-    kod_pubs_missing <- DBI::dbReadTable(con, "riv_unique_ids") %>% #colnames()
-             filter(id_unique %in% disc_pubs_missing$id_unique) %>% 
-             distinct() %>% 
-             as_tibble()
-    
-    year_pubs_missing <- DBI::dbReadTable(con, "riv_details") %>% #colnames()
-        filter(kod %in% kod_pubs_missing$kod) %>% 
-        distinct() %>% 
-        as_tibble()
-    
-    wos_pubs_missing <- DBI::dbReadTable(con, "riv_wos_scopus") %>% #colnames()
-        filter(id_unique %in% disc_pubs_missing$id_unique) %>% 
-        distinct() %>% 
-        as_tibble()
-    
-    authors_pubs_missing <- DBI::dbReadTable(con, "authors_by_pubs") %>% #colnames()
-        filter(id_unique %in% disc_pubs_missing$id_unique) %>% 
-        distinct() %>% 
-        as_tibble()
[…]

### 2022-05-12 R/make_edgelist.R

@@ -10,23 +10,23 @@
 make_edgelist <- function(one_author) {
 
    
-    split_authors <- strsplit(as.character(one_author$list), ':')
+    # split_authors <- strsplit(as.character(one_author$list), ':')
+    # 
+    # dat <- enframe(split_authors) %>% unnest(cols = "value")
     
-    dat <- enframe(split_authors) %>% unnest(cols = "value")
-    
-    dat %>% group_by(name) %>% 
-        right_join(dat, by = "name") %>% 
-        filter(value.x != value.y) %>% 
-        mutate(from = pmin(value.x, value.y),
-               to = pmax(value.x, value.y)) %>% 
-        select(pub_id = name, from, to) %>% 
+        one_author %>% group_by(id_unique) %>% 
+        right_join(one_author, by = "id_unique") %>% 
+        filter(id_helper.x != id_helper.y) %>% 
+        mutate(from = pmin(id_helper.x, id_helper.y),
+               to = pmax(id_helper.x, id_helper.y)) %>% 
+        select(pub_id = id_unique, from, to) %>% 
         distinct() %>% 
-        ungroup() %>% 
+        # ungroup() %>% 
         
-        mutate(from = tolower(stringi::stri_trans_general(from, "latin-ascii")),
-               to = tolower(stringi::stri_trans_general(to, "latin-ascii"))) %>% 
-        mutate(from = str_trim(str_replace(from, "(.*), (.?){1}.*", "\\1\\2")),
-               to = str_trim(str_replace(to, "(.*), (.?){1}.*", "\\1\\2"))) %>% 
+        # mutate(from = tolower(stringi::stri_trans_general(from, "latin-ascii")),
+        #        to = tolower(stringi::stri_trans_general(to, "latin-ascii"))) %>% 
+        # mutate(from = str_trim(str_replace(from, "(.*), (.?){1}.*", "\\1\\2")),
+        #        to = str_trim(str_replace(to, "(.*), (.?){1}.*", "\\1\\2"))) %>% 
         
         relocate(pub_id, .after = last_col()) %>% 
         group_by(from, to) %>% 

### 2022-05-23 _targets.Rmd
whole pipeline finalized, changed the way of calculating "one_author" target to allow for faster and smoother compute

@@
                             "tm",
-                            "httr",
-                            "rjson",
-                            "keyring",
                             "RSQLite",
@@
     tar_target(ids_complete_vector,
-               make_ids_complete_vector(ids)),
+               make_ids_complete_vector(ids_complete)),
     tar_target(db_path,
@@
     tar_target(all_pubs,
-           get_all_pubs(db_path, ids), 
+           get_all_pubs(db_path, ids_complete), 
               format = "qs"),
     tar_target(one_author,
-           read_one_author(db_path, ids_complete_vector), 
+           read_one_author(db_path, ids_complete_vector, ids_complete), 
               format = "qs", pattern = map(ids_complete_vector), iteration = "list")
@@
    tar_target(topic_model_input,
-              make_topic_model_input(all_pubs),
-                format = "qs") #,
-   # --> fce find k 
+              make_topic_model_input(all_pubs)) #,
+
+    # tar_target(topic_number,
+    #           find_topic_number(topic_model_input),
+    #             format = "qs") #, 
     # tar_target(topic_model,
@@
 
-    # tar_target(clustering,
-    #            calc_clustering(graph), 
-    #            format = "qs")
+     tar_target(clustering,
+                calc_clustering(graph, ids_complete, one_author, db_path),
+               format = "qs", pattern = map(graph, one_author), iteration = "list") 
+    #            
     # 
@@
 
-    # tar_target(ind_pubs,
-    #            calc_ind_pubs(one_author), 
-    #            format = "qs")
-    # 
+     tar_target(ind_pubs,
+                calc_ind_pubs(one_author, ids_complete, db_path), 
+                format = "qs", pattern = map(one_author),                  iteration = "list")
+
 )
@@
 
-    # tar_target(ind_topics,
-    #            calc_ind_topics(topic_model, two_authors), 
-    #            format = "qs")
+     tar_target(ind_topics,
+                calc_ind_topics(topic_model = NULL, one_author, ids_complete, db_path), 
+                format = "qs", pattern = map(one_author), iteration = "list")
 
@@
     tar_target(final_data,
-               calc_final_data(eigen_centr, clustering = NULL, ind_topics = NULL, ind_pubs = NULL),
-               format = "qs")
+               calc_final_data(eigen_centr, clustering, ind_topics, ind_pubs),
+               format = "qs") #,
+     # tar_target(testing,
+     #           just_test(eigen_centr, clustering, ind_topics = NULL, ind_pubs = NULL),
+     #           format = "qs")
 

### 2022-05-23 R/calc_clustering.R

@@ -7,16 +7,44 @@
 #' @return
 #' @author fatal: unable to access 'C:/Users/David Jank?/Documents/.config/git/config': Invalid argument
 #' @export
-calc_clustering <- function(graph) {
+calc_clustering <- function(graph, ids_complete, one_author, db_path) {
 
+   
+        
+     vedidk_researcher <- one_author %>% 
+         pull(vedidk) %>% 
+         unique()
+     
+     b <- one_author %>% 
+         pull(vedouci) %>% 
+         unique()
+     
+    # sup_vector <- ids_complete %>% 
+    #     filter(vedidk_core_researcher == vedidk_researcher) %>% 
+    #     pull(vedoucí.vedidk)
+    # 
+    # con <-  DBI::dbConnect(RSQLite::SQLite(), db_path)
+    # on.exit(DBI::dbDisconnect(con))
+    # 
+    # b <- DBI::dbReadTable(con, "authors_by_pubs") %>% #colnames()
+    #     filter(vedidk == sup_vector) %>% 
+    #     select(id_helper) %>% 
+    #     count(id_helper) %>% 
+    #     filter(n == max(n)) %>% 
+    #     slice_sample(n=1) %>% 
+    #     pull(id_helper)
+    
     clustering <-
         transitivity(
             graph,
             type = c("local"),
-            vids = which(V(graph)$name == "klapilovak"),
+            vids = which(V(graph)$name == b),
             weights = E(graph)$weight,
             isolates = c("NaN", "zero")
         )
+    
+    table <- tibble(vedidk = vedidk_researcher, clustr = clustering)
+    
     
 
 }

### 2022-05-23 R/calc_eigen_centr.R

@@ -23,32 +23,32 @@ calc_eigen_centr <- function(graph, ids_complete, one_author, db_path) {
         pull(vedidk) %>% 
         unique()
     
-    sup_vector <- ids_complete %>% 
-            filter(vedidk_core_researcher == vedidk_researcher) %>% 
-            pull(vedoucí.vedidk)
-        
-    con <-  DBI::dbConnect(RSQLite::SQLite(), db_path)
-    on.exit(DBI::dbDisconnect(con))
+    a <- one_author %>% 
+        pull(vedouci) %>% 
+        unique()
     
-   a <- DBI::dbReadTable(con, "authors_by_pubs") %>% #colnames()
-        filter(vedidk == sup_vector) %>% 
-        select(id_helper) %>% 
-        count(id_helper) %>% 
-        filter(n == max(n)) %>% 
-        slice_sample(n=1) %>% 
-        pull(id_helper)
+   #  sup_vector <- ids_complete %>% 
+   #          filter(vedidk_core_researcher == vedidk_researcher) %>% 
+   #          pull(vedoucí.vedidk)
+   #      
+   #  con <-  DBI::dbConnect(RSQLite::SQLite(), db_path)
+   #  on.exit(DBI::dbDisconnect(con))
+   #  
+   # a <- DBI::dbReadTable(con, "authors_by_pubs") %>% #colnames()
+   #      filter(vedidk == sup_vector) %>% 
+   #      select(id_helper) %>% 
+   #      count(id_helper) %>% 
+   #      filter(n == max(n)) %>% 
+   #      slice_sample(n=1) %>% 
+   #      pull(id_helper)
+    
+    
     
     sup <- centr %>% 
                filter(author == a) %>% 
         pull(eigen_ctr)
     
     table <- tibble(vedidk = vedidk_researcher, eig = sup)
-    
-    
-    # access ïds_complete -> take the vedidk_core_researcher of the given 
-    # current research -> match it with the vedouci.vedidk na stejnem radku 
-    # --> vezmi ten vedidk vedouciho, jdi do databaze "authors by pubs" a 
-    # match it with the id_helper of a given person
     
 
 }

### 2022-05-23 R/calc_final_data.R

@@ -10,7 +10,7 @@
 #' @return
 #' @author fatal: unable to access 'C:/Users/David Jank?/Documents/.config/git/config': Invalid argument
 #' @export
-calc_final_data <- function(eigen_centr, clustering = NULL, ind_topics = NULL, ind_pubs = NULL) {
+calc_final_data <- function(eigen_centr, clustering, ind_topics, ind_pubs) {
 # 
 #     vedidk_researcher <- one_author %>% 
 #         map("vedidk") %>% 
@@ -26,8 +26,12 @@ calc_final_data <- function(eigen_centr, clustering = NULL, ind_topics = NULL, i
   #                      ) 
       
 
-    bind_rows(eigen_centr)
+    a <- left_join(bind_rows(eigen_centr), bind_rows(clustering), by = "vedidk")
+    b <- left_join(bind_rows(a), bind_rows(ind_pubs), by = "vedidk")        
+    c <- left_join(bind_rows(b), bind_rows(ind_topics), by = "vedidk")    
     
-    # left_join(eigen_centr, eigen_centr, by = "vedidk")
-
+    c$RII <- ((1-c$eig)+c$clustr+c$ind_pubs+c$ind_topics*2)/4
+    
+    c
+    
 }

### 2022-05-23 R/calc_ind_pubs.R

@@ -7,10 +7,46 @@
 #' @return
 #' @author fatal: unable to access 'C:/Users/David Jank?/Documents/.config/git/config': Invalid argument
 #' @export
-calc_ind_pubs <- function(one_author) {
+calc_ind_pubs <- function(one_author, ids_complete, db_path) {
 
-    ind_pubs <- filter(one_author, !str_detect(one_author$list, "Klapilová, Kateřina"))
+    #hledani jmena vedouciho
+    vedidk_researcher <- one_author %>% 
+        pull(vedidk) %>% 
+        unique()
     
-    rpubs = nrow(ind_pubs)/nrow(one_author)
-
+    c <- one_author %>% 
+        pull(vedouci) %>% 
+        unique()
+    
+    # sup_vector <- ids_complete %>% 
+    #     filter(vedidk_core_researcher == vedidk_researcher) %>% 
+    #     pull(vedoucí.vedidk)
+    # 
+    # con <-  DBI::dbConnect(RSQLite::SQLite(), db_path)
+    # on.exit(DBI::dbDisconnect(con))
+    # 
+    # c <- DBI::dbReadTable(con, "authors_by_pubs") %>% #colnames()
+    #     filter(vedidk == sup_vector) %>% 
+    #     select(id_helper) %>% 
+    #     count(id_helper) %>% 
+    #     filter(n == max(n)) %>% 
+    #     slice_sample(n=1) %>% 
+    #     pull(id_helper)
+    
+    all_pubs_author <- one_author %>% 
+        select(id_unique) %>% 
+        distinct()
+    
+    sup_pubs <- one_author %>% 
+        filter(id_helper == c) %>% 
+        select(id_unique)
+    
+    ind_pubs <- anti_join(all_pubs_author, sup_pubs)
+       
+    rpubs = nrow(ind_pubs)/nrow(all_pubs_author)
+    
+    table <- tibble(vedidk = vedidk_researcher, ind_pubs = rpubs)
+    
+    # e <- anti_join(one_author[[1]], sup_pubs, by = "id_unique")
+    
 }

### 2022-05-23 R/get_all_pubs.R

@@ -8,22 +8,19 @@
 #' @return
 #' @author fatal: unable to access 'C:/Users/David Jank?/Documents/.config/git/config': Invalid argument
 #' @export
-get_all_pubs <- function(db_path, ids) {
+get_all_pubs <- function(db_path, ids_complete) {
 
     con <-  DBI::dbConnect(RSQLite::SQLite(), db_path)
     on.exit(DBI::dbDisconnect(con))
     
     DBI::dbListTables(con)
     
-    ids_complete <- as_tibble(ids) %>% 
-        filter(!is.na(vedoucí.vedidk)) %>% 
-        filter(!is.na(vedidk_core_researcher))
     
     ids_complete_vector <- cbind(ids_complete$vedidk_core_researcher, ids_complete$vedoucí.vedidk) %>% 
         as_tibble() %>% 
         as_vector() 
     
-    ids_complete_col <- bind_rows(as_tibble(ids_complete$vedidk_core_researcher), as_tibble(ids_complete$vedoucí.vedidk))
+    # ids_complete_col <- bind_rows(as_tibble(ids_complete$vedidk_core_researcher), as_tibble(ids_complete$vedoucí.vedidk))
     
     comb_vedidk_pubids <- DBI::dbReadTable(con, "authors_by_pubs") %>% 
         select(vedidk, id_unique) %>% 

### 2022-05-23 R/make_topic_model.R

@@ -9,26 +9,20 @@
 #' @export
 make_topic_model <- function(topic_model_input) {
 
-    result <- FindTopicsNumber(
-        topic_model_input,
-        topics = c(30, 100, 200, 300, 500, 1000),
-        metrics = c("Griffiths2004", "CaoJuan2009", "Deveaud2014"),
-        method = "Gibbs",
-        control = list(seed = 77),
-        mc.cores = parallel::detectCores()-1,
-        verbose = TRUE
-    )
     
-    FindTopicsNumber_plot(result)
+    dfm <- dfm[which(rowSums(dfm) > 0),]
+    topic_model_input <- convert(dfm,to="topicmodels")
+    # dim(topic_model_input)
+    lda.model <- LDA(topic_model_input,k = 60, control = list(seed = 123),alpha = 0.1, beta = 0.01 , verbose=1) 
     
-    dfm = dfm[which(rowSums(dfm) > 0),]
-    dtm = convert(dfm,to="topicmodels")
-    dim(dtm)
-    lda.model = LDA(dtm,k = 10, control = list(seed = 123),alpha = 0.1, beta = 0.01 , verbose=1) 
-    
-    lda.matrix = posterior(lda.model,dfm)$topics
+    lda.matrix <- posterior(lda.model,dfm)$topics
     dim(lda.matrix) 
     
     data <- as_tibble(t(lda.matrix))
 
-}
+    # write.csv2(data, file = here::here("data", "derived", "topic_model_matrix.csv"))
+    # write_excel_csv2(data, here("data", "derived", "tmm.csv"), na = "NA")
+    # save(lda.matrix, file = paste(here("data", "derived", c("topic_dist.Rdata")), sep=""))
+
+}    
+    

### 2022-05-23 R/read_one_author.R

@@ -8,7 +8,7 @@
 #' @return
 #' @author fatal: unable to access 'C:/Users/David Jank?/Documents/.config/git/config': Invalid argument
 #' @export
-read_one_author <- function(db_path, ids_complete_vector) {
+read_one_author <- function(db_path, ids_complete_vector, ids_complete) {
 
   con <-  DBI::dbConnect(RSQLite::SQLite(), db_path)
   on.exit(DBI::dbDisconnect(con))
@@ -22,12 +22,33 @@ read_one_author <- function(db_path, ids_complete_vector) {
       select(vedidk, id_unique) %>% 
       distinct() %>% 
       as_tibble()
-  
+ 
+ # mozna by bylo fajn v tomto kroku vyselektovat vsechny nepublikacni vystupy, protoze ty jsou asi defaultne zapocitane:
+     one_vedidk_filtered_pubs <- DBI::dbReadTable(con, "riv_disc") %>%  #colnames()
+     select(id_unique, pub_type) %>%
+     filter(id_unique %in% one_vedidk_pubids$id_unique) %>%
+     filter(pub_type %in% c("J","B","C","D")) %>%
+     as_tibble()
+     
+ 
+    sup_vector <- ids_complete %>% 
+        filter(vedidk_core_researcher == ids_complete_vector) %>% 
+        pull(vedoucí.vedidk) 
+    
+    sup_name <- DBI::dbReadTable(con, "authors_by_pubs") %>% #colnames()
+        filter(vedidk == sup_vector) %>% 
+        select(id_helper) %>% 
+        count(id_helper) %>% 
+        filter(n == max(n)) %>% 
+        slice_sample(n=1) %>% 
+        pull(id_helper)
+ 
   one_vedidk_coauthors <- DBI::dbReadTable(con, "authors_by_pubs") %>% # colnames()
       select(id_unique, id_helper) %>% 
-      filter(id_unique %in% one_vedidk_pubids$id_unique) %>% 
+      filter(id_unique %in% one_vedidk_filtered_pubs$id_unique) %>% 
       distinct() %>%
       mutate(vedidk = ids_complete_vector) %>% 
+      mutate(vedouci = sup_name) %>% 
       as_tibble()
   
   ####

### 2022-05-27 _targets.Rmd
filtering out diplicate vedidks of researchers who received 2 grants (keeping only the record of the first one) -> this is in create_ids_complete function
...and duplicate vedidks of supervisors who supervised more than one grant recipients -> this is in make_ids_complete_vector function, which is also used in get_all_pubs function

@@
      # tar_target(testing,
-     #           just_test(eigen_centr, clustering, ind_topics = NULL, ind_pubs = NULL),
+     #           just_test(db_path),
      #           format = "qs")

### 2022-05-27 R/create_ids_complete.R

@@ -10,8 +10,18 @@
 create_ids_complete <- function(ids) {
 
     ids_complete <- as_tibble(ids) %>% 
-        select(vedidk_core_researcher, vedoucí.vedidk) %>% 
+        select(vedidk_core_researcher, vedoucí.vedidk, grant_start_year) %>% 
         filter(!is.na(vedoucí.vedidk)) %>% 
-        filter(!is.na(vedidk_core_researcher)) 
+        filter(!is.na(vedidk_core_researcher))
+        
+    #these row below are new - their point is to filter the cases of researchers who received 2 grants, such that only the record of receving the first grant will remain
+    
+    ids_complete$grant_start_year <- substring(ids_complete$grant_start_year, 7)  
+    ids_complete $grant_start_year <- as.numeric(ids_complete$grant_start_year)
+    
+    ids_complete <- ids_complete %>% 
+        group_by(vedidk_core_researcher) %>% 
+        slice(which.min(grant_start_year)) %>% 
+        ungroup()
 
 }

### 2022-05-27 R/get_all_pubs.R

@@ -18,7 +18,10 @@ get_all_pubs <- function(db_path, ids_complete) {
     
     ids_complete_vector <- cbind(ids_complete$vedidk_core_researcher, ids_complete$vedoucí.vedidk) %>% 
         as_tibble() %>% 
-        as_vector() 
+        as_vector() %>% 
+        as_tibble() %>% #from here below it was added - I should check that it does change any further results 
+        distinct() %>% #here
+        as_vector()  #here
     
     # ids_complete_col <- bind_rows(as_tibble(ids_complete$vedidk_core_researcher), as_tibble(ids_complete$vedoucí.vedidk))
     

### 2022-05-27 R/just_test.R

@@ -10,8 +10,7 @@
 #' @return
 #' @author fatal: unable to access 'C:/Users/David Jank?/Documents/.config/git/config': Invalid argument
 #' @export
-just_test <- function(eigen_centr, clustering, ind_topics = NULL, ind_pubs =
-                      NULL) {
+just_test <- function(db_path) {
 
    # aa <- one_author[[4]] %>% group_by(id_unique) %>% 
    #      right_join(one_author[[4]], by = "id_unique") %>% 
@@ -57,6 +56,7 @@ just_test <- function(eigen_centr, clustering, ind_topics = NULL, ind_pubs =
      
      all_researchers_vector <- ids_complete$vedidk_core_researcher %>% 
          as_tibble() %>% 
+         distinct() %>% #this was added - I should check that it does change any further results 
          as_vector() 
      
      all_researchers_pubids <- DBI::dbReadTable(con, "authors_by_pubs") %>% 
@@ -83,9 +83,20 @@ just_test <- function(eigen_centr, clustering, ind_topics = NULL, ind_pubs =
      all_researchers_pubs <- all_researchers_pubids %>% 
          group_by(vedidk) %>% 
          count(name = "weight") %>% 
-         ungroup() #this will generate only 239 vedidks, not 248 entered in the all_researchers_vector, which is 4 % 
+         ungroup() #this will generate only 239 vedidks, not 248 entered in the all_researchers_vector, which is 4 % --> explained by duplicates in vedidks (people who received 2 grants)
      
-         
+     
+     #important things that I need to work on further
+     
+     ids_complete$vedidk_core_researcher <- as.character(ids_complete$vedidk_core_researcher)
+     
+     missing_researchers <- anti_join(ids_complete, all_researchers_pubs, by = c("vedidk_core_researcher" = "vedidk"))
+     
+     ids_complete_duplicated <- ids_complete %>% 
+         filter(duplicated(vedidk_core_researcher))  #I should filter out the double vedidks at the beginning (i.e. from the ids_complete dataset) and only include the earlier one (i.e. the date of the first grant, not the second)
+     
+     
+     
      all_researchers_pubs <- all_researchers_pubs %>% 
          filter(vedidk != 4427920)    #one vedidk had over 800 publications, which seemed unrealistic, so I deleted it
      
[…]

### 2022-08-22 _targets.Rmd
Added disciplines to grant recipients

@@
  #              format = "qs"),
-      tar_target(ids, read.csv2(here::here("data", "raw", "supervisors.csv"), nrows = 20),
+     tar_target(ids_path, here::here("data", "raw", "supervisors.csv"), format = "file"),
+     tar_target(ids, read.csv2(ids_path, nrows = 20),
               format = "qs"),

### 2022-08-22 R/create_ids_complete.R

@@ -10,18 +10,100 @@
 create_ids_complete <- function(ids) {
 
     ids_complete <- as_tibble(ids) %>% 
-        select(vedidk_core_researcher, vedoucí.vedidk, grant_start_year) %>% 
+        select(vedidk_core_researcher, vedoucí.vedidk) %>% 
         filter(!is.na(vedoucí.vedidk)) %>% 
         filter(!is.na(vedidk_core_researcher))
         
-    #these row below are new - their point is to filter the cases of researchers who received 2 grants, such that only the record of receving the first grant will remain
+    #adding info about discipline (based on which disciplinary committee evaluated the grant) and year the grant project started
+    con <-  DBI::dbConnect(RSQLite::SQLite(), db_path)
+    on.exit(DBI::dbDisconnect(con))
     
-    ids_complete$grant_start_year <- substring(ids_complete$grant_start_year, 7)  
-    ids_complete$grant_start_year <- as.numeric(ids_complete$grant_start_year)
+    DBI::dbListTables(con)
+    
+    GJ <- DBI::dbReadTable(con, "cep_details") %>%
+        filter(program_kod == "GJ") %>% 
+        select(kod, disc, ford, year_start) %>% 
+        tidyr::unite(disc_ford, c(disc, ford), na.rm = TRUE) %>%
+        as_tibble
+    
+   
+    GJ$disc_ford[GJ$disc_ford %in% c("BA", "BB")] <- 10100 #BD
+    GJ$disc_ford[GJ$disc_ford %in% c("IN", "BC", "BD", "AF")] <- 10200
+    GJ$disc_ford[GJ$disc_ford %in% c("BE", "BM", "BF", "BG", "BK", "BL", "BH", "BI","BN")] <- 10300
+    GJ$disc_ford[GJ$disc_ford %in% c("CC", "CA", "CH", "CF", "CD", "CG", "CB")] <- 10400
+    GJ$disc_ford[GJ$disc_ford %in% c("DA", "DB", "DC", "DE", "DG", "DO", "DK", "DL", "DM", "DI", "DJ")] <- 10500
[…]

### 2022-08-22 R/read_one_author.R

@@ -24,12 +24,16 @@ read_one_author <- function(db_path, ids_complete_vector, ids_complete) {
       as_tibble()
  
  # mozna by bylo fajn v tomto kroku vyselektovat vsechny nepublikacni vystupy, protoze ty jsou asi defaultne zapocitane:
+ ## 
      one_vedidk_filtered_pubs <- DBI::dbReadTable(con, "riv_disc") %>%  #colnames()
-     select(id_unique, pub_type) %>%
+     select(id_unique, pub_type, disc, ford) %>%
      filter(id_unique %in% one_vedidk_pubids$id_unique) %>%
      filter(pub_type %in% c("J","B","C","D")) %>%
      as_tibble()
-     
+
+#tabulka nahoře obsahuje obor každé z publikací daného autora, a proto by šlo z ní vypočítat majoritní disciplínu daného autora. K tomu by bylo potřeba:
+#     1) přeložit disciplíny z roku dřívějšího než 2018 do klasifikace ford a 2) udělat nějaký algoritmus který by to agregoval a vytáhl z toho disciplinaritu daného autora - například vzít modus disciplín
+#     3)  tohle by se pak dalo vytisknout do proměnné "discipline" (podobně jako je proměnná sup_name) a tu pak přidat do tabulky níže tí že odstraníme #před mutate)
  
     sup_vector <- ids_complete %>% 
         filter(vedidk_core_researcher == ids_complete_vector) %>% 
@@ -49,7 +53,10 @@ read_one_author <- function(db_path, ids_complete_vector, ids_complete) {
       distinct() %>%
       mutate(vedidk = ids_complete_vector) %>% 
       mutate(vedouci = sup_name) %>% 
+      #mutate(discipline = discipline)
       as_tibble()
+  
+  one_vedidk_coauthors <- left_join(one_vedidk_coauthors, one_vedidk_filtered_pubs, by = )
   
   ####
   

### 2022-08-24 _targets.Rmd
Further updates in Propensity score matching script (added new variable of "interdisciplinarity/specialisation" and "career age of receving first grant". Futher, all edidks that were not paired with any supervisor vedidk were deleted from the treatment sample

--- 2022-05-27 _targets.Rmd
@@
 
-    # tar_target(one_author,
-    #           read.csv2(here::here("data", "raw",    #"Binter_pubs.csv")),
- #              format = "qs"),
-      tar_target(ids, read.csv2(here::here("data", "raw", "supervisors.csv"), nrows = 20),
+     tar_target(ids_path, here::here("data", "raw", "supervisors.csv"), format = "file"),
+     tar_target(ids, read.csv2(ids_path, nrows = 20),
               format = "qs"),

### 2022-08-24 propensity_score_matching.R

@@ -145,7 +145,8 @@ discipline_data <- left_join(discipline_pubs_short, n_pubs_filtered, by = "id_un
 discipline_data$disc_ford <- as.character(discipline_data$disc_ford)
 
 
-count(discipline_data$disc_ford) #test showed I ned to look closer to things that contain D and F and perhaps J and then perhaps delete all the letters
+count(discipline_data$disc_ford) 
+
 
 disciplines <- discipline_data %>% 
     select(disc_ford, vedidk) %>% 
@@ -164,8 +165,37 @@ count(disciplines$disc_ford)
 
 ### it would be cool to now count how many/what proportion of publications each author has within their "primary discipline" vs in other disciplines
 
+##interdisciplinarity / specialisation
 
-##calculating intervention
+interdisc <- discipline_data %>% 
+    dplyr::select(disc_ford, vedidk) %>% 
+    filter(!is.na(disc_ford)) %>% 
+    filter(vedidk %in% n_pubs_count$vedidk) 
+
+interdisc <- left_join(interdisc, disciplines, by = "vedidk", suffix = c("_pub", "_main"))
+
+interdisc_final <- interdisc %>%  
+      group_by(vedidk) %>% 
+      filter(disc_ford_pub != disc_ford_main) %>% 
+      dplyr::count(name = "interdisc") %>% 
+      ungroup() 
+
+interdisc_final <- left_join(n_pubs_count, interdisc_final, by = "vedidk")
+
+interdisc_final$interdisc <- replace_na(interdisc_final$interdisc, "0")
+
+interdisc_final$interdisc <- as.numeric(interdisc_final$interdisc)
+
+
+interdisc_final <- interdisc_final %>% 
+    mutate(interdisc_proportion = interdisc/freq*100)
+
+plot(hist(interdisc_final$interdisc_proportion))
+
+sum(interdisc_final$interdisc_proportion == 0)
+
+
+##calculating intervention group
 
 GJ <- DBI::dbReadTable(con, "cep_details") %>%
     filter(program_kod == "GJ") %>% 
@@ -199,7 +229,63 @@ treatment_data <- n_pubs_count %>%
 count(treatment_data$treatment) #this shows that it matched only 329 out of 356 treatment vedidks -> not sure why?
 
 
-##calculating whether they have received any grant //in some time period// - maybe first (career) year of receving their grant?
[…]

### 2022-09-02 _targets.Rmd
slightly changed pipeline to accomodate propensity score matching

@@
                             "RSQLite",
-                            "DBI"
+                            "DBI",
+                            "MatchIt",
+                            "plyr"
                             ))
@@
     tar_target(db_path,
-           here::here("data", "raw", "czech_sci_db.sqlite")),
+           here::here("data", "raw", "czech_sci_db.sqlite"))#,
+    # tar_target(all_pubs,
+    #        get_all_pubs(db_path, ids_complete), 
+    #           format = "qs"),
+    # tar_target(one_author,
+    #        read_one_author(db_path, ids_complete_vector, ids_complete), 
+    #           format = "qs", pattern = map(ids_complete_vector), iteration = "list")
+    # 
+)
+```
+
+# Matching and data preparation
+
+```{targets matching_preparation}
+list(
+
+     tar_target(matching, match(db_path, ids)
+                format = "qs"),
+     #at this point, I will need to manually search for the supervisors of the control group researchers and upload their vedidks into new ids file
      tar_target(all_pubs,
-           get_all_pubs(db_path, ids_complete), 
+           get_all_pubs(db_path, matching, ids_complete), 
               format = "qs"),

### 2022-09-02 R/match.R

@@ -1,0 +1,432 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param db_path
+#' @param ids
+#' @return
+#' @author fatal: unable to access 'C:/Users/David Jank?/Documents/.config/git/config': Invalid argument
+#' @export
+match <- function(db_path, ids) {
+
+    con <-  DBI::dbConnect(RSQLite::SQLite(), db_path)
+    on.exit(DBI::dbDisconnect(con))
+    
+    DBI::dbListTables(con)
+    
+    # setting up the set of all authors
+    
+    all_auth <- DBI::dbReadTable(con, "authors_by_pubs") %>% #colnames()
+        select(vedidk) %>% 
+        distinct() %>% 
+        as_tibble()
+    
+    ## number of pubs per researcher (mainly for cleaning the extreme low and high values)
+    
+    ### first selecting only specific types of publications - this appear to be working, but suggests that all pubs in this brach of the database are of the tzpes that I am looking for, which is a bit weird
+    n_pubs_types <- DBI::dbReadTable(con, "riv_disc") %>%  #colnames()  
+        select(id_unique, pub_type) %>% 
+        filter(pub_type %in% c("J","B","C","D")) %>% 
+        as_tibble() 
+    
+    n_pubs_filtered <- DBI::dbReadTable(con, "authors_by_pubs") %>% 
+        select(vedidk, id_unique) %>% 
+        filter(id_unique %in% n_pubs_types$id_unique) %>% #it doesn't really matter whether I use this filter or not - it always come with the same result which is weird
+        distinct() %>% 
+        as_tibble()
+    
+    n_pubs_count <- plyr::count(n_pubs_filtered, vars = "vedidk") %>% 
+        filter(freq > 4) %>%  #filtering out all authors with less than 4 publications
+        as_tibble
+    
+    sum(n_pubs_count$freq>400) #139 authors have more than 400 publications -> should I delete them too?
+    
+    
+    # graph_all_researchers <- ggplot(data=n_pubs_count, aes(x = reorder(vedidk, -freq), y=freq)) +
[…]

### 2022-09-02 _targets.Rmd
edited pipeline

@@
               format = "qs"),
-      tar_target(ids_complete, create_ids_complete(ids),
+     tar_target(db_path,
+           here::here("data", "raw", "czech_sci_db.sqlite")),
+      tar_target(ids_complete, create_ids_complete(ids, db_path),
               format = "qs"),
     tar_target(ids_complete_vector,
-               make_ids_complete_vector(ids_complete)),
-    tar_target(db_path,
-           here::here("data", "raw", "czech_sci_db.sqlite"))#,
+               make_ids_complete_vector(ids_complete))#,
+
     # tar_target(all_pubs,
@@
 
-     tar_target(matching, match(db_path, ids)
+     tar_target(matching, match(db_path, ids),
                 format = "qs"),
      #at this point, I will need to manually search for the supervisors of the control group researchers and upload their vedidks into new ids file
+     tar_target(ids_full_vector,
+               make_ids_full_vector(matching)),
      tar_target(all_pubs,
@@
     tar_target(one_author,
-           read_one_author(db_path, ids_complete_vector, ids_complete), 
-              format = "qs", pattern = map(ids_complete_vector), iteration = "list")
+           read_one_author(db_path, ids_complete_vector, ids_complete, matching, ids_full_vector), 
+              format = "qs", pattern = map(head(ids_full_vector,3)), iteration = "list")
 
@@
     tar_target(final_data,
-               calc_final_data(eigen_centr, clustering, ind_topics, ind_pubs),
+               calc_final_data(eigen_centr, clustering, ind_topics, ind_pubs, matching),
                format = "qs") #,

### 2022-09-02 R/calc_final_data.R

@@ -10,7 +10,7 @@
 #' @return
 #' @author fatal: unable to access 'C:/Users/David Jank?/Documents/.config/git/config': Invalid argument
 #' @export
-calc_final_data <- function(eigen_centr, clustering, ind_topics, ind_pubs) {
+calc_final_data <- function(eigen_centr, clustering, ind_topics, ind_pubs, matching) {
 # 
 #     vedidk_researcher <- one_author %>% 
 #         map("vedidk") %>% 
@@ -26,13 +26,22 @@ calc_final_data <- function(eigen_centr, clustering, ind_topics, ind_pubs) {
   #                      ) 
       
 
-    a <- right_join(bind_rows(eigen_centr), bind_rows(clustering), by = "vedidk")
-    b <- right_join(bind_rows(a), bind_rows(ind_pubs), by = "vedidk")        
-    c <- right_join(bind_rows(b), bind_rows(ind_topics), by = "vedidk")    
+    matching <- left_join(matching, bind_rows(eigen_centr), by = "vedidk")
+    matching <- left_join(matching, bind_rows(clustering), by = "vedidk")                
+    matching <- left_join(matching, bind_rows(ind_pubs), by = "vedidk")                
+    matching <- left_join(matching, bind_rows(ind_topics), by = "vedidk")                
+    matching$RII <- ((1-c$eig)+c$clustr+c$ind_pubs+c$ind_topics*2)/4
     
-    c$RII <- ((1-c$eig)+c$clustr+c$ind_pubs+c$ind_topics*2)/4
+        
+    # a <- right_join(bind_rows(eigen_centr), bind_rows(clustering), by = "vedidk")
+    # b <- right_join(bind_rows(a), bind_rows(ind_pubs), by = "vedidk")        
+    # c <- right_join(bind_rows(b), bind_rows(ind_topics), by = "vedidk")    
+    # 
+    # c$RII <- ((1-c$eig)+c$clustr+c$ind_pubs+c$ind_topics*2)/4
+    # 
+    # c
     
-    c
+    
     # write.csv2(final_data, here::here("data", "derived", "final_indicators.csv"), na = "NA")
     # readr::write_excel_csv2(final_data, here::here("data", "derived", "final_indicators.csv"), na = "NA")
 }

### 2022-09-02 R/get_all_pubs.R

@@ -8,7 +8,7 @@
 #' @return
 #' @author fatal: unable to access 'C:/Users/David Jank?/Documents/.config/git/config': Invalid argument
 #' @export
-get_all_pubs <- function(db_path, ids_complete) {
+get_all_pubs <- function(db_path, matching, ids_complete) {
 
     con <-  DBI::dbConnect(RSQLite::SQLite(), db_path)
     on.exit(DBI::dbDisconnect(con))

### 2022-09-02 R/make_ids_full_vector.R

@@ -1,0 +1,19 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param matching
+#' @return
+#' @author fatal: unable to access 'C:/Users/David Jank?/Documents/.config/git/config': Invalid argument
+#' @export
+make_ids_full_vector <- function(matching) {
+
+    ids_full_vector <- matching$vedidk %>% 
+        as_tibble() %>% 
+        as_vector() %>% 
+        as_tibble() %>% #from here below it was added - I should check that it does change any further results 
+        distinct() %>% #here
+        as_vector()  #here
+
+}

### 2022-09-02 R/match.R

@@ -226,10 +226,28 @@ match <- function(db_path, ids) {
         filter(!is.na(vedidk)) 
     # This show that although the database could find 845 distinct pairs of Junior grant code and vedidk, only in 356 cases there were actual vedidks, which means that in 845-356=489 cases there were pairs of existing code but missing vedidk 
     
+    treatment_refined <- left_join(treatment_refined, GJ, by = "kod")
+    
+    treatment_refined$year_start <- ifelse(nchar(treatment_refined$year_start, type = "chars", allowNA = FALSE, keepNA = NA)>4, substring(treatment_refined$year_start, 7), treatment_refined$year_start)
+    
+    treatment_refined$year_start <- as.numeric(treatment_refined$year_start)
+    
+    tr <- treatment_refined %>%  #z tohoto plyne že všech 356 kódů je unikátních, tzn nikde tam nejsou 2 vedidky napsané na jednom grantu
+        select(vedidk) %>%
+        distinct()
+    
+    treatment_refined <-  treatment_refined %>% 
+        group_by(vedidk) %>% 
+        slice(which.min(year_start)) %>% 
+        ungroup()
+    #tímto krokem vyfiltruju pryč vedidky, které dostly více juniorských grantů a vezmu v potaz jen jejich první grant (celkem se to týká 7 lidí)
+    
     treatment_data <- n_pubs_count %>% 
         select(vedidk) %>% 
         mutate(treatment = ifelse(vedidk %in% treatment_refined$vedidk, 1, 0)) %>% 
+        mutate(treatment_year = ifelse(vedidk %in% treatment_refined$vedidk, treatment_refined$year_start, NA)) %>% 
         as_tibble()
+    #?v tomto kroku z původních 349 unique treatment vedidků zbyde jen 329. Když místo n_pubs_count použiju dataset all_auth jako výchozí (což v praxi znamená, že vezmu v potaz i autory, kteří mají méně něž 5 publikací), tak mi to i tak klesne na 343, což nevím proč se děje  
     
     plyr::count(treatment_data$treatment) #this shows that it matched only 329 out of 356 treatment vedidks -> not sure why?
     
@@ -301,8 +319,10 @@ match <- function(db_path, ids) {
     final_data <- left_join(final_data, disciplines, by = "vedidk")
     final_data <- left_join(final_data, n_pubs_count, by = "vedidk")
     
+    final_data$treatment_year <- NULL
+    
     ##excluding rows with missing values
[…]

### 2022-09-02 R/read_one_author.R

@@ -8,7 +8,7 @@
 #' @return
 #' @author fatal: unable to access 'C:/Users/David Jank?/Documents/.config/git/config': Invalid argument
 #' @export
-read_one_author <- function(db_path, ids_complete_vector, ids_complete) {
+read_one_author <- function(db_path, ids_complete_vector, ids_complete, matching, ids_full_vector) {
 
   con <-  DBI::dbConnect(RSQLite::SQLite(), db_path)
   on.exit(DBI::dbDisconnect(con))
@@ -16,21 +16,33 @@ read_one_author <- function(db_path, ids_complete_vector, ids_complete) {
   DBI::dbListTables(con)
   
 
- 
- one_vedidk_pubids <- DBI::dbReadTable(con, "authors_by_pubs") %>% #colnames()
-      filter(vedidk == ids_complete_vector) %>% 
+  one_vedidk_pubids <- DBI::dbReadTable(con, "authors_by_pubs") %>% #colnames()
+      filter(vedidk == ids_full_vector) %>% 
       select(vedidk, id_unique) %>% 
       distinct() %>% 
       as_tibble()
+  
+ matching <- matching %>%    # tohle asi bude dělat problémy když se tam budou opakovat vedidky, a oni se opakují -> nevím jak to vyřešit - ledaže bych měl nějaké pořadí toho vektoru a pracoval s tím pořadím
+     filter(vedidk == ids_full_vector)
+ 
+ #  saving just for case that something goes bad and I will need to return to this / this is the last version that worked
+ # one_vedidk_pubids <- DBI::dbReadTable(con, "authors_by_pubs") %>% #colnames()
+ #      filter(vedidk == ids_complete_vector) %>% 
+ #      select(vedidk, id_unique) %>% 
+ #      distinct() %>% 
+ #      as_tibble()
  
  # mozna by bylo fajn v tomto kroku vyselektovat vsechny nepublikacni vystupy, protoze ty jsou asi defaultne zapocitane:
  ## 
-     one_vedidk_filtered_pubs <- DBI::dbReadTable(con, "riv_disc") %>%  #colnames()
-     select(id_unique, pub_type, disc, ford) %>%
+     one_vedidk_filtered_pubs <- DBI::dbReadTable(con, "riv_disc") %>%  # colnames()
+     select(id_unique, pub_type, disc, ford, year) %>%
      filter(id_unique %in% one_vedidk_pubids$id_unique) %>%
      filter(pub_type %in% c("J","B","C","D")) %>%
[…]

### 2022-09-12 _targets.Rmd
changed pipeline - mapping now within all_authors function

@@
               format = "qs"),
-    tar_target(one_author,
-           read_one_author(db_path, ids_complete_vector, ids_complete, matching, ids_full_vector), 
-              format = "qs", pattern = map(head(ids_full_vector,3)), iteration = "list")
+    # tar_target(one_author,
+           # read_one_author(db_path, ids_complete_vector, ids_complete, matching, ids_full_vector), 
+           #    format = "qs", pattern = map(head(ids_full_vector,3)), iteration = "list"),
+    tar_target(all_authors,
+           read_all_authors(db_path, ids_complete_vector, ids_complete, matching, ids_full_vector), 
+              format = "qs")
 

### 2022-09-12 R/read_one_author.R

@@ -8,7 +8,7 @@
 #' @return
 #' @author fatal: unable to access 'C:/Users/David Jank?/Documents/.config/git/config': Invalid argument
 #' @export
-read_one_author <- function(db_path, ids_complete_vector, ids_complete, matching, ids_full_vector) {
+read_one_author <- function(db_path, ids_complete_vector, ids_complete, matching, ids_full_vector, intervention_year, timing) {
 
   con <-  DBI::dbConnect(RSQLite::SQLite(), db_path)
   on.exit(DBI::dbDisconnect(con))
@@ -22,9 +22,9 @@ read_one_author <- function(db_path, ids_complete_vector, ids_complete, matching
       distinct() %>% 
       as_tibble()
   
- matching <- matching %>%    # tohle asi bude dělat problémy když se tam budou opakovat vedidky, a oni se opakují -> nevím jak to vyřešit - ledaže bych měl nějaké pořadí toho vektoru a pracoval s tím pořadím
-     filter(vedidk == ids_full_vector)
- 
+ # matching <- matching %>%    # tohle asi bude dělat problémy když se tam budou opakovat vedidky, a oni se opakují -> nevím jak to vyřešit - ledaže bych měl nějaké pořadí toho vektoru a pracoval s tím pořadím
+ #     filter(vedidk == ids_full_vector)
+ # 
  #  saving just for case that something goes bad and I will need to return to this / this is the last version that worked
  # one_vedidk_pubids <- DBI::dbReadTable(con, "authors_by_pubs") %>% #colnames()
  #      filter(vedidk == ids_complete_vector) %>% 
@@ -38,7 +38,11 @@ read_one_author <- function(db_path, ids_complete_vector, ids_complete, matching
      select(id_unique, pub_type, disc, ford, year) %>%
      filter(id_unique %in% one_vedidk_pubids$id_unique) %>%
      filter(pub_type %in% c("J","B","C","D")) %>%
-     purrr::when(matching$independence_timing == "before_intervention" ~ filter(., year <= matching$treatment_year), ~ filter(., year >= matching$treatment_year)) %>% 
+         left_join(one_vedidk_pubids) %>% 
+         inner_join(matching %>% select(vedidk, treatment_year, independence_timing)) %>% 
+         filter(treatment_year == intervention_year, independence_timing == timing) %>% 
[…]

### 2022-10-06 _targets.Rmd
changed macthing algorithm, added gender and impacted pubs

--- 2022-09-02 _targets.Rmd
@@
               format = "qs"),
+     tar_target(gender, read.delim(here::here("data", "raw", "names4api_tagged.tsv")),
+              format = "qs"),
      tar_target(db_path,
@@
 
-     tar_target(matching, match(db_path, ids),
+     tar_target(matching, match(db_path, ids, gender),
                 format = "qs"),

### 2022-10-06 R/match.R

@@ -8,7 +8,7 @@
 #' @return
 #' @author fatal: unable to access 'C:/Users/David Jank?/Documents/.config/git/config': Invalid argument
 #' @export
-match <- function(db_path, ids) {
+match <- function(db_path, ids, gender) {
 
     con <-  DBI::dbConnect(RSQLite::SQLite(), db_path)
     on.exit(DBI::dbDisconnect(con))
@@ -18,64 +18,127 @@ match <- function(db_path, ids) {
     # setting up the set of all authors
     
     all_auth <- DBI::dbReadTable(con, "authors_by_pubs") %>% #colnames()
-        select(vedidk) %>% 
+        select(vedidk, id_unique) %>% 
         distinct() %>% 
         as_tibble()
     
-    ## number of pubs per researcher (mainly for cleaning the extreme low and high values)
+    # # org affiliation
+    # 
+    # auth_affiliation <- DBI::dbReadTable(con, "riv_details") %>% 
+    #     select(kod, id_organization)
     
-    ### first selecting only specific types of publications - this appear to be working, but suggests that all pubs in this brach of the database are of the tzpes that I am looking for, which is a bit weird
-    n_pubs_types <- DBI::dbReadTable(con, "riv_disc") %>%  #colnames()  
-        select(id_unique, pub_type) %>% 
-        filter(pub_type %in% c("J","B","C","D")) %>% 
+    ##grants starting 2015
+    #number of all publications up to 2014 (ie the year when the grant was awarded
+    
+    
+    n_pubs_types2014 <- DBI::dbReadTable(con, "riv_disc") %>%  #colnames()  
+        dplyr::select(id_unique, pub_type, year) %>% 
+        filter(pub_type %in% c("J","B","C","D")) %>%
+        filter(year < 2014) %>% 
         as_tibble() 
     
-    n_pubs_filtered <- DBI::dbReadTable(con, "authors_by_pubs") %>% 
-        select(vedidk, id_unique) %>% 
-        filter(id_unique %in% n_pubs_types$id_unique) %>% #it doesn't really matter whether I use this filter or not - it always come with the same result which is weird
+    n_pubs_filtered2014 <- DBI::dbReadTable(con, "authors_by_pubs") %>% 
+        dplyr::select(vedidk, id_unique) %>% 
[…]

### 2022-10-06 R/read_all_authors.R

@@ -15,16 +15,13 @@ read_all_authors <- function(db_path, ids_complete_vector, ids_complete,
                              matching, ids_full_vector) {
 
 matching <- as_tibble(matching)
-l <- list(a = matching$vedidk, b = matching$treatment_year, c = matching$independence_timing)
-
-l <- list(a = x, b = y, c = z)
-pmap(l, function(c, b, a) (a + c) * b)
+l <- list(ids_full_vector = matching$vedidk, intervention_year = matching$treatment_year, timing = matching$independence_timing)
 
 
 new <-  head(matching) %>% 
         select(vedidk, treatment_year, independence_timing) %>% 
-        mutate(pub_table = purrr::pmap(list(vedidk, treatment_year, independence_timing), 
-                                       read_one_author(db_path, ids_complete_vector, ids_complete, matching, ids_full_vector = vedidk, intervention_year = treatment_year, timing = independence_timing)))
+        mutate(pub_table = purrr::pmap(.l = list(vedidk, treatment_year, independence_timing),
+                                       .f = read_one_author(db_path, ids_complete_vector, ids_complete, matching, vedidk, treatment_year, independence_timing)))
 
 # intervention_year = treatment_year, timing = independence_timing
 #     ids_full_vector = vedidk)

### 2022-10-12 _targets.Rmd
rozbite targets ale updatovana pipelina

--- 2022-09-02 _targets.Rmd
@@
      tar_target(ids_path, here::here("data", "raw", "supervisors.csv"), format = "file"),
-     tar_target(ids, read.csv2(ids_path, nrows = 20),
+     tar_target(ids, read.csv2(ids_path),
               format = "qs"),
+     tar_target(gender_path, here::here("data", "raw", "names4api_tagged.tsv"), format = "file"),
+     tar_target(gender, read.delim(gender_path), format = "qs"),
+     # tar_target(gender, read.delim(here::here("data", "raw", "names4api_tagged.tsv")),
+     #          format = "qs"),
       tar_target(db_path,
@@
     tar_target(ids_complete_vector,
-               make_ids_complete_vector(ids_complete))#,
+               make_ids_complete_vector(ids_complete))
 
@@
     #        read_one_author(db_path, ids_complete_vector, ids_complete), 
-    #           format = "qs", pattern = map(ids_complete_vector), iteration = "list")
+    #           format = "qs")
     # 
@@
 
-     tar_target(matching, match(db_path, ids),
-                format = "qs"),
+     # tar_target(matching, match(db_path, ids, gender),
+     #            format = "qs"),
+     # tar_target(sup_path, here::here("data", "raw", "supervisors_control.csv"), format = "file"),
+     # tar_target(sup_control, read.csv2(sup_path),
+     #          format = "qs"),
+     # tar_target(sup_control, read.csv2(here::here("data", "raw", "supervisors_control.csv")),
+     #          format = "qs"),
+     # tar_target(final_data, refine_data(matching, db_path, ids, sup_control),
+     #            format = "qs"),
      #at this point, I will need to manually search for the supervisors of the control group researchers and upload their vedidks into new ids file
-     tar_target(ids_full_vector,
-               make_ids_full_vector(matching)),
-     tar_target(all_pubs,
-           get_all_pubs(db_path, matching, ids_complete), 
-              format = "qs"),
-    tar_target(one_author,
-           read_one_author(db_path, ids_complete_vector, ids_complete, matching, ids_full_vector), 
-              format = "qs", pattern = map(head(ids_full_vector,3)), iteration = "list")
+     # tar_target(ids_full_vector,
+     #           make_ids_full_vector(matching)),
+    #  tar_target(all_pubs,
+    #        get_all_pubs(db_path, matching, ids_complete), 
+    #           format = "qs"),
+    # tar_target(all_authors,
+    #        read_all_authors(db_path, ids_complete_vector, ids_complete, matching, ids_full_vector), 
+    #           format = "qs")
 
@@
 
-   tar_target(topic_model_input,
-              make_topic_model_input(all_pubs)) #,
-
-    # tar_target(topic_number,
-    #           find_topic_number(topic_model_input),
-    #             format = "qs") #, 
-    # tar_target(topic_model,
-    #            make_topic_model(topic_model_input),
-    #             format = "qs")
+   # tar_target(topic_model_input,
+   #            make_topic_model_input(all_pubs)) #,
+   #                            
+   #  # tar_target(topic_number,
+   #  #           find_topic_number(topic_model_input),
+   #  #             format = "qs") #, 
+   #  # tar_target(topic_model,
+   #  #            make_topic_model(topic_model_input),
+   #  #             format = "qs")
 
@@
 
-    tar_target(edgelist,
-               make_edgelist(one_author),
-                format = "qs", pattern = map(one_author), iteration = "list"),
-    tar_target(graph, igraph::graph_from_data_frame(edgelist, directed = FALSE), pattern = map(edgelist), iteration = "list")
+    # tar_target(edgelist,
+    #            make_edgelist(one_author),
+    #             format = "qs", pattern = map(one_author), iteration = "list"),
+    # tar_target(graph, igraph::graph_from_data_frame(edgelist, directed = FALSE), pattern = map(edgelist), iteration = "list")
 
@@
 
-    tar_target(eigen_centr,
-               calc_eigen_centr(graph, ids_complete, one_author, db_path),
-               format = "qs", pattern = map(graph, one_author), iteration = "list")
-
+    # tar_target(eigen_centr,
+    #            calc_eigen_centr(graph, ids_complete, one_author, db_path),
+    #            format = "qs", pattern = map(graph, one_author), iteration = "list")
+    # 
 )
@@
 
-     tar_target(clustering,
-                calc_clustering(graph, ids_complete, one_author, db_path),
-               format = "qs", pattern = map(graph, one_author), iteration = "list") 
-    #            
-    # 
+    #  tar_target(clustering,
+    #             calc_clustering(graph, ids_complete, one_author, db_path),
+    #            format = "qs", pattern = map(graph, one_author), iteration = "list") 
+    # #            
+    # # 
 )
@@
 
-     tar_target(ind_pubs,
-                calc_ind_pubs(one_author, ids_complete, db_path), 
-                format = "qs", pattern = map(one_author),                  iteration = "list")
-
+     # tar_target(ind_pubs,
+     #            calc_ind_pubs(one_author, ids_complete, db_path), 
+     #            format = "qs", pattern = map(one_author),                  iteration = "list")
+     # 
 )
@@
 
-     tar_target(ind_topics,
-                calc_ind_topics(topic_model = NULL, one_author, ids_complete, db_path), 
-                format = "qs", pattern = map(one_author), iteration = "list")
-
+     # tar_target(ind_topics,
+     #            calc_ind_topics(topic_model = NULL, one_author, ids_complete, db_path), 
+     #            format = "qs", pattern = map(one_author), iteration = "list")
+     # 
 )
@@
 
-    tar_target(final_data,
-               calc_final_data(eigen_centr, clustering, ind_topics, ind_pubs, matching),
-               format = "qs") #,
-     # tar_target(testing,
-     #           just_test(db_path),
-     #           format = "qs")
-
+    # tar_target(final_data,
+    #            calc_final_data(eigen_centr, clustering, ind_topics, ind_pubs, matching),
+    #            format = "qs") #,
+    #  # tar_target(testing,
+    #  #           just_test(db_path),
+    #  #           format = "qs")
+    # 
 )

### 2022-10-12 R/match.R

@@ -62,7 +62,7 @@ match <- function(db_path, ids, gender) {
     n_pubs_ws2014 <- plyr::count(n_pubs_ws2014, vars = "vedidk") %>% 
         as_tibble()
     
-    n_pubs_ws2014 <- rename( n_pubs_ws2014, ws_pubs = freq)
+    n_pubs_ws2014 <- rename(n_pubs_ws2014, ws_pubs = freq)
     
     
     #gender
@@ -428,9 +428,9 @@ match <- function(db_path, ids, gender) {
     
     matched_data2015 <- match.data(out2015) # this actually spits out exactly the list of treated nad mtached untreated people in a way that I can easily use it!
     
-    table(matched_data2015$disc_ford, by = matched_data2015$treatment)
+    # table(matched_data2015$disc_ford, by = matched_data2015$treatment)
     
-    summary(out2015)
+    # summary(out2015)
     
     
     m <- out2015[["match.matrix"]]%>% 
@@ -470,9 +470,9 @@ match <- function(db_path, ids, gender) {
     
     matched_data_funded2015 <- match.data(out_funded2015) # this actually spits out exactly the list of treated nad mtached untreated people in a way that I can easily use it!
     
-    table(matched_data_funded2015$disc_ford, by = matched_data_funded2015$treatment)
+    # table(matched_data_funded2015$disc_ford, by = matched_data_funded2015$treatment)
     
-    summary(out_funded2015)
+    # summary(out_funded2015)
     
     
     m <- out_funded2015[["match.matrix"]]%>% 
@@ -526,15 +526,7 @@ match <- function(db_path, ids, gender) {
     
     
     
-    ## 2) decide whether to join "unfunded" and "funded" tables right here (after each year) or only after the very end
     
-    
-    
-    ##potential problem - in the original Matching dataset, there was 48 juniors with treatment year 2015, whereas here are only 38 -> it could be because during the process the researchers with negative career age were deleted (in the step "career age") and some of it will also be because there porbably were some missing values -> e,g, in the "calculating treatment group" step we had 40 in treatment group and in the matching itself there were only 38
-    
-   
-    
-    ##co dal:   3) přidat další proměnné které jsou důležité - gender, instituce, peer review papery, atd... 4) vyrobit 2 kontrolni skupiny - jednu s fundingem a druhou bez 
     
     
     
[…]

### 2022-10-12 R/refine_data.R

@@ -1,0 +1,37 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param matching
+#' @param db_path
+#' @param ids
+#' @param sup_control
+#' @return
+#' @author fatal: unable to access 'C:/Users/David Jank?/Documents/.config/git/config': Invalid argument
+#' @export
+refine_data <- function(matching, db_path, ids, sup_control) {
+
+    ids_refined <- ids %>%
+        select(vedoucí.vedidk, vedidk_core_researcher) %>%
+        filter(!is.na(vedoucí.vedidk)) %>%
+        filter(!is.na(vedidk_core_researcher)) %>%
+        distinct()
+
+    ids_refined$vedidk_core_researcher <- as.character(ids_refined$vedidk_core_researcher)
+    ids_refined <- rename(ids_refined, sup_vedidk = vedoucí.vedidk)
+    ids_refined <- rename(ids_refined, vedidk = vedidk_core_researcher)
+
+    sup_control <- sup_control %>%
+        select(vedidk, sup_vedidk) %>%
+        distinct()
+
+    sup_control$vedidk <- as.character(sup_control$vedidk)
+
+    sup_complete <- rbind2(ids_refined, sup_control)
+
+    complete_data <- left_join(matching, sup_complete, by = "vedidk")
+    
+    
+
+}

### 2022-11-22 _targets.Rmd
problem with function all_authors when run via targets: when the output of the function is zero (which in some cases is), targets signposts error saying "replacement has 1 row, data has 0"

@@
      tar_target(ids_path, here::here("data", "raw", "supervisors.csv"), format = "file"),
-     tar_target(ids, read.csv2(ids_path),
-              format = "qs"),
+     tar_target(ids, read.csv2(ids_path)),
      tar_target(gender_path, here::here("data", "raw", "names4api_tagged.tsv"), format = "file"),
-     tar_target(gender, read.delim(gender_path), format = "qs"),
+     tar_target(gender, read.delim(gender_path)),
      # tar_target(gender, read.delim(here::here("data", "raw", "names4api_tagged.tsv")),
@@
            here::here("data", "raw", "czech_sci_db.sqlite")),
-      tar_target(ids_complete, create_ids_complete(ids, db_path),
-              format = "qs"),
+      tar_target(ids_complete, create_ids_complete(ids, db_path)),
     tar_target(ids_complete_vector,
@@
 
-     # tar_target(matching, match(db_path, ids, gender),
-     #            format = "qs"),
-     # tar_target(sup_path, here::here("data", "raw", "supervisors_control.csv"), format = "file"),
-     # tar_target(sup_control, read.csv2(sup_path),
-     #          format = "qs"),
+      tar_target(matching, match(db_path, ids, gender)),
+      tar_target(sup_path, here::here("data", "raw", "supervisors_control.csv"), format = "file"),
+      tar_target(sup_control, read.csv2(sup_path)),
+
      # tar_target(sup_control, read.csv2(here::here("data", "raw", "supervisors_control.csv")),
      #          format = "qs"),
-     # tar_target(final_data, refine_data(matching, db_path, ids, sup_control),
-     #            format = "qs"),
+      tar_target(final_data, refine_data(matching, db_path, ids, sup_control)),
+
      #at this point, I will need to manually search for the supervisors of the control group researchers and upload their vedidks into new ids file
-     # tar_target(ids_full_vector,
-     #           make_ids_full_vector(matching)),
+     tar_target(ids_full_vector,
+               make_ids_full_vector(matching)),
     #  tar_target(all_pubs,
@@
     #           format = "qs"),
-    # tar_target(all_authors,
-    #        read_all_authors(db_path, ids_complete_vector, ids_complete, matching, ids_full_vector), 
-    #           format = "qs")
+    tar_target(all_authors,
+           read_all_authors(db_path, ids_complete_vector, ids_complete, matching, ids_full_vector))
 
@@
 list(
-    tarchetypes::tar_render(article, here::here("Rmd", "article.Rmd"))
+    # tarchetypes::tar_render(article, here::here("Rmd", "article.Rmd"))
 )

### 2022-11-22 R/refine_data.R

@@ -19,8 +19,8 @@ refine_data <- function(matching, db_path, ids, sup_control) {
         distinct()
 
     ids_refined$vedidk_core_researcher <- as.character(ids_refined$vedidk_core_researcher)
-    ids_refined <- rename(ids_refined, sup_vedidk = vedoucí.vedidk)
-    ids_refined <- rename(ids_refined, vedidk = vedidk_core_researcher)
+    ids_refined <- dplyr::rename(ids_refined, sup_vedidk = vedoucí.vedidk)
+    ids_refined <- dplyr::rename(ids_refined, vedidk = vedidk_core_researcher)
 
     sup_control <- sup_control %>%
         select(vedidk, sup_vedidk) %>%
@@ -28,7 +28,34 @@ refine_data <- function(matching, db_path, ids, sup_control) {
 
     sup_control$vedidk <- as.character(sup_control$vedidk)
 
-    sup_complete <- rbind2(ids_refined, sup_control)
+    sup_complete <- rbind2(ids_refined, sup_control) %>% 
+        filter(!is.na(sup_vedidk))
+    
+    # sup_vector <- sup_complete %>%
+    #         filter(vedidk_core_researcher %in% ids_complete_vector) %>%
+    #         pull(vedoucí.vedidk)
+
+    con <-  DBI::dbConnect(RSQLite::SQLite(), db_path)
+    on.exit(DBI::dbDisconnect(con))
+    
+   sup_name <- DBI::dbReadTable(con, "authors_by_pubs") %>% #colnames()
+        filter(vedidk %in% sup_complete$sup_vedidk) %>%
+        dplyr::select(id_helper, vedidk) %>%
+        group_by(vedidk) %>% 
+        dplyr::count(id_helper) %>%
+        filter(n == max(n)) %>%
+        slice_sample(n=1) %>%
+        ungroup() %>% 
+        dplyr::select(!n)
+    
+    sup_name <- dplyr::rename(sup_name, sup_name = id_helper)
+   
+    sup_complete$sup_vedidk <- as.character(sup_complete$sup_vedidk)
+    
+    sup_complete <- left_join(sup_complete, sup_name, by = c("sup_vedidk" = "vedidk"))
+    
+   
+    
 
     complete_data <- left_join(matching, sup_complete, by = "vedidk")
     

### 2022-11-23 _targets.Rmd
pipeline adapted, but doesnt run via targets because it gets stuck on all_authors becuase there are empty fields

@@
     tar_target(all_authors,
-           read_all_authors(db_path, ids_complete_vector, ids_complete, matching, ids_full_vector))
+           read_all_authors(db_path, ids_complete_vector, ids_complete, final_data, ids_full_vector))
 
@@
     # tar_target(graph, igraph::graph_from_data_frame(edgelist, directed = FALSE), pattern = map(edgelist), iteration = "list")
+    tar_target(coauthorship,
+               make_network(all_authors)),
+
+     tar_target(coauthorship_graph,
+               make_graph(all_authors))
 
@@
     # 
+     tar_target(eigen_centrality,
+               comp_eigen_centr(coauthorship_graph))
+
 )
@@
     # #
+
+    tar_target(cluster,
+                comp_clustering(eigen_centrality))
+
 )
@@
      # 
+     tar_target(independent_pubs,
+                comp_ind_pubs(cluster))
 )
@@
      # 
+    tar_target(independent_topics,
+                comp_ind_topics(independent_pubs))
 )
@@
     #  #           format = "qs")
-    # 
+
+    tar_target(full_indicator,
+               calc_full_indicator(independent_topics),
+
 )

### 2022-11-23 R/calc_clustering.R

@@ -7,18 +7,20 @@
 #' @return
 #' @author fatal: unable to access 'C:/Users/David Jank?/Documents/.config/git/config': Invalid argument
 #' @export
-calc_clustering <- function(graph, ids_complete, one_author, db_path) {
+calc_clustering <- function(graph, one_author) {
 
    
-        
-     vedidk_researcher <- one_author %>% 
-         pull(vedidk) %>% 
-         unique()
+     #    
+     # vedidk_researcher <- one_author %>% 
+     #     pull(vedidk) %>% 
+     #     unique()
+     # 
+     # b <- one_author %>% 
+     #     pull(vedouci) %>% 
+     #     unique()
      
-     b <- one_author %>% 
-         pull(vedouci) %>% 
-         unique()
-     
+    
+
     # sup_vector <- ids_complete %>% 
     #     filter(vedidk_core_researcher == vedidk_researcher) %>% 
     #     pull(vedoucí.vedidk)
@@ -34,16 +36,18 @@ calc_clustering <- function(graph, ids_complete, one_author, db_path) {
     #     slice_sample(n=1) %>% 
     #     pull(id_helper)
     
+    b <- one_author
+    
     clustering <-
-        transitivity(
+        igraph::transitivity(
             graph,
             type = c("local"),
-            vids = which(V(graph)$name == b),
-            weights = E(graph)$weight,
+            vids = which(igraph::V(graph)$name == b),
+            weights = igraph::E(graph)$weight,
             isolates = c("NaN", "zero")
         )
     
-    table <- tibble(vedidk = vedidk_researcher, clustr = clustering)
+    # table <- tibble(vedidk = vedidk_researcher, clustr = clustering)
     
     
 

### 2022-11-23 R/calc_eigen_centr.R

@@ -7,25 +7,28 @@
 #' @return
 #' @author fatal: unable to access 'C:/Users/David Jank?/Documents/.config/git/config': Invalid argument
 #' @export
-calc_eigen_centr <- function(graph, ids_complete, one_author, db_path) {
+calc_eigen_centr <- function(graph, one_author, db_path) {
 
-    ecentr <- eigen_centrality(
+    ecentr <- igraph::eigen_centrality(
         graph,
         directed = FALSE,
         scale = TRUE,
-        weights = E(graph)$weight,
-        options = arpack_defaults
+        weights = igraph::E(graph)$weight,
+        # options = arpack_defaults
     )
     
-    centr <- enframe(ecentr$vector, name = "author", value = "eigen_ctr")
+    centr <- tibble::enframe(ecentr$vector, name = "author", value = "eigen_ctr")
     
-    vedidk_researcher <- one_author %>% 
-        pull(vedidk) %>% 
-        unique()
+    # vedidk_researcher <- one_author %>% 
+    #     pull(vedidk) %>% 
+    #     unique()
     
-    a <- one_author %>% 
-        pull(vedouci) %>% 
-        unique()
+    # a <- one_author %>% 
+    #     pull(sup_name) %>% 
+    #     unique()
+    # 
+    
+    a <- one_author
     
    #  sup_vector <- ids_complete %>% 
    #          filter(vedidk_core_researcher == vedidk_researcher) %>% 
@@ -48,7 +51,7 @@ calc_eigen_centr <- function(graph, ids_complete, one_author, db_path) {
                filter(author == a) %>% 
         pull(eigen_ctr)
     
-    table <- tibble(vedidk = vedidk_researcher, eig = sup)
+    # table <- tibble(vedidk = vedidk_researcher, eig = sup)
     
 
 }

### 2022-11-23 R/calc_full_indicator.R

@@ -1,0 +1,29 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param independent_topics
+#' @return
+#' @author fatal: unable to access 'C:/Users/David Jank?/Documents/.config/git/config': Invalid argument
+#' @export
+calc_full_indicator <- function(independent_topics) {
+ 
+               
+    independent_topics$eig_centr <- ifelse(independent_topics$eig_centr == "numeric(0)", NA, independent_topics$eig_centr)
+    
+    independent_topics$RII <- ((1-independent_topics$eig_centr)+independent_topics$clustr+independent_topics$ind_pubs+independent_topics$ind_topics*2)/4
+    
+        
+    # a <- right_join(bind_rows(eigen_centr), bind_rows(clustering), by = "vedidk")
+    # b <- right_join(bind_rows(a), bind_rows(ind_pubs), by = "vedidk")        
+    # c <- right_join(bind_rows(b), bind_rows(ind_topics), by = "vedidk")    
+    # 
+    # c$RII <- ((1-c$eig)+c$clustr+c$ind_pubs+c$ind_topics*2)/4
+    # 
+    # c
+    
+    
+    # write.csv2(final_data, here::here("data", "derived", "final_indicators.csv"), na = "NA")
+    # readr::write_excel_csv2(final_data, here::here("data", "derived", "final_indicators.csv"), na = "NA")
+}

### 2022-11-23 R/calc_ind_topics.R

@@ -7,7 +7,7 @@
 #' @return
 #' @author fatal: unable to access 'C:/Users/David Jank?/Documents/.config/git/config': Invalid argument
 #' @export
-calc_ind_topics <- function(topic_model = NULL, one_author, ids_complete, db_path) {
+calc_ind_topics <- function(topic_model = NULL, one_author, db_path, sup_vedidk) {
 
     topic_model <- read.csv2(here::here("data", "derived", "tmm.csv"))
     
@@ -27,7 +27,7 @@ calc_ind_topics <- function(topic_model = NULL, one_author, ids_complete, db_pat
     
     author_pubs_topics <- as_tibble(cbind(id_unique = names(topic_model), t(topic_model))) 
        
-    author_pubs_tp <- semi_join(author_pubs_topics, all_pubs_author) 
+    author_pubs_tp <- semi_join(author_pubs_topics, all_pubs_author, by = "id_unique") 
 
     author_pubs_tp <-  as_tibble(author_pubs_tp) %>% 
         tibble::column_to_rownames("id_unique")
@@ -42,26 +42,28 @@ calc_ind_topics <- function(topic_model = NULL, one_author, ids_complete, db_pat
     
     #spočítat poměrné zastoupení každého tématu ve vzorku publikací vedouciho daneho vyzkumnika
    
-    vedidk_researcher <- one_author %>% 
-        pull(vedidk) %>% 
-        unique()
-    
-    sup_vector <- ids_complete %>% 
-        filter(vedidk_core_researcher == vedidk_researcher) %>% 
-        pull(vedoucí.vedidk)
+        # vedidk_researcher <- one_author %>% 
+        #     pull(vedidk) %>% 
+        #     unique()
+        # 
+        # sup_vector <- ids_complete %>% 
+        #     filter(vedidk_core_researcher == vedidk_researcher) %>% 
+        #     pull(vedoucí.vedidk)
+            
+    sup_vedidk <- sup_vedidk
     
     con <-  DBI::dbConnect(RSQLite::SQLite(), db_path)
     on.exit(DBI::dbDisconnect(con))
     
     sup_pubids <- DBI::dbReadTable(con, "authors_by_pubs") %>% #colnames()
-        filter(vedidk == sup_vector) %>% 
+        filter(vedidk == sup_vedidk) %>% 
         select(id_unique) %>% 
         distinct() %>% 
         as_tibble()
     
[…]

### 2022-11-23 R/comp_ind_pubs.R

@@ -1,0 +1,24 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param clustr
+#' @param 
+#' @return
+#' @author fatal: unable to access 'C:/Users/David Jank?/Documents/.config/git/config': Invalid argument
+#' @export
+comp_ind_pubs <- function(clustr) {
+
+
+independent_pubs <-  clustering %>% 
+                        mutate(ind_pubs = purrr::pmap(.l = list(pub_table, sup_name),
+                                   .f = function(first, second){
+                                       calc_ind_pubs(one_author = first, sup_name = second)
+                                   } ))
+
+
+
+
+
+    }

### 2022-11-23 R/comp_ind_topics.R

@@ -1,0 +1,22 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param independent_pubs
+#' @param 
+#' @return
+#' @author fatal: unable to access 'C:/Users/David Jank?/Documents/.config/git/config': Invalid argument
+#' @export
+independent_topics <- function(independent_pubs) {
+
+
+independent_topics <-  independent_pubs %>% 
+                        mutate(ind_topics = purrr::pmap(.l = list(pub_table, sup_vedidk),
+                                   .f = function(first, second){
+                                       calc_ind_topics(topic_model = NULL, db_path, 
+                                                       one_author = first, sup_vedidk = second)
+                                   } ))
+
+
+    }

### 2022-11-23 R/find_topic_number.R

@@ -1,0 +1,25 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param topic_model_input
+#' @return
+#' @author fatal: unable to access 'C:/Users/David Jank?/Documents/.config/git/config': Invalid argument
+#' @export
+find_topic_number <- function(topic_model_input) {
+
+    result <- FindTopicsNumber(
+        topic_model_input,
+        topics = c(15, 30, 100),
+        metrics = c("Griffiths2004", "CaoJuan2009", "Deveaud2014"),
+        method = "Gibbs",
+        control = list(seed = 77),
+        mc.cores = parallel::detectCores()-1,
+        verbose = TRUE
+    )
+    
+    FindTopicsNumber_plot(result)
+    
+
+}

### 2022-11-23 R/make_edgelist.R

@@ -14,6 +14,18 @@ make_edgelist <- function(one_author) {
     # 
     # dat <- enframe(split_authors) %>% unnest(cols = "value")
     
+    # testing:
+    # a <- new[3,] %>% 
+    #     tidyr::unnest(pub_table, names_repair = "minimal") 
+    # 
+    # a[,1:3] <- NULL
+    # 
+    # 
+    # 
+    # b <- a %>% 
+    
+    
+    
         one_author %>% group_by(id_unique) %>% 
         right_join(one_author, by = "id_unique") %>% 
         filter(id_helper.x != id_helper.y) %>% 

### 2022-11-23 R/read_all_authors.R

@@ -6,20 +6,20 @@
 #' @param db_path
 #' @param ids_complete_vector
 #' @param ids_complete
-#' @param matching
+#' @param final_data
 #' @param ids_full_vector
 #' @return
 #' @author fatal: unable to access 'C:/Users/David Jank?/Documents/.config/git/config': Invalid argument
 #' @export
 read_all_authors <- function(db_path, ids_complete_vector, ids_complete,
-                             matching, ids_full_vector) {
+                             final_data, ids_full_vector) {
 
-matching <- as_tibble(matching)
+matching <- as_tibble(final_data)
 # l <- list(ids_full_vector = matching$vedidk, intervention_year = matching$treatment_year, timing = matching$independence_timing)
 
 
 new <-  head(matching) %>% 
-        dplyr::select(vedidk, treatment_year, independence_timing) %>% 
+        dplyr::select(vedidk, treatment_year, independence_timing, sup_name, sup_vedidk) %>% 
         mutate(pub_table = purrr::pmap(.l = list(vedidk, treatment_year, independence_timing),
                                        .f = function(first, second, third){
                                            read_one_author(db_path, ids_complete_vector, ids_complete, matching, 

### 2023-04-14 _targets.Rmd
...

@@
       tar_target(matching, match(db_path, ids, gender)),
-      tar_target(sup_path, here::here("data", "raw", "supervisors_control.csv"), format = "file"),
+      tar_target(sup_path, here::here("data", "raw", "supervisors_control_final.csv"), format = "file"),
       tar_target(sup_control, read.csv2(sup_path)),
@@
     tar_target(full_indicator,
-               calc_full_indicator(independent_topics),
+               calc_full_indicator(independent_topics))
 

### 2023-04-14 _targets.Rmd
engine

--- 2022-11-23 _targets.Rmd
@@
 
-```{targets example-globals, tar_globals = TRUE}
+```{r, engine="targets", example-globals, tar_globals = TRUE}
 options(tidyverse.quiet = TRUE)
@@
 
-```{targets data_import}
+```{r, engine="targets", data_import}
 list(
@@
 
-```{targets matching_preparation}
+```{r, engine="targets", matching_preparation}
 list(
@@
 
-```{targets topic_model}
+```{r, engine="targets", topic_model}
 list(
@@
 
-```{targets network}
+```{r, engine="targets", network}
 
@@
 
-```{targets RII1}
+```{r, engine="targets", RII1}
 
@@
 
-```{targets RII2}
+```{r, engine="targets", RII2}
 
@@
 
-```{targets RII3}
+```{r, engine="targets", RII3}
 
@@
 
-```{targets RII4}
+```{r, engine="targets", RII4}
 
@@
 
-```{targets RII4_2}
+```{r, engine="targets", RII4_2}
 
@@
 
-```{targets final}
+```{r, engine="targets", final}
 
@@
     tar_target(full_indicator,
-               calc_full_indicator(independent_topics),
-
+               calc_full_indicator(independent_topics)
+    )
                )

### 2023-04-14 _targets.Rmd

@@
     tar_target(full_indicator,
-               calc_full_indicator(independent_topics)
-    )
+               calc_full_indicator(independent_topics))
+
 )

### 2023-04-14 _targets.Rmd
...

--- 2023-04-14 _targets.Rmd
@@
                             "DBI",
-                            "MatchIt",
-                            "plyr"
+                            "MatchIt"
                             ))

### 2023-04-14 R/comp_ind_pubs.R
small changes

@@ -8,10 +8,10 @@
 #' @return
 #' @author fatal: unable to access 'C:/Users/David Jank?/Documents/.config/git/config': Invalid argument
 #' @export
-comp_ind_pubs <- function(clustr) {
+comp_ind_pubs <- function(cluster) {
 
 
-independent_pubs <-  clustering %>% 
+independent_pubs <-  cluster %>% 
                         mutate(ind_pubs = purrr::pmap(.l = list(pub_table, sup_name),
                                    .f = function(first, second){
                                        calc_ind_pubs(one_author = first, sup_name = second)

### 2023-04-14 _targets.Rmd
small changes
small edits

@@
                             "DBI",
-                            "MatchIt"
+                            "MatchIt",
+                            "qs"
                             ))
@@
                make_ids_full_vector(matching)),
-    #  tar_target(all_pubs,
-    #        get_all_pubs(db_path, matching, ids_complete), 
-    #           format = "qs"),
+     tar_target(all_pubs,
+           get_all_pubs(db_path, final_data)),
     tar_target(all_authors,
@@
 
-   # tar_target(topic_model_input,
-   #            make_topic_model_input(all_pubs)) #,
-   #                            
-   #  # tar_target(topic_number,
-   #  #           find_topic_number(topic_model_input),
-   #  #             format = "qs") #, 
-   #  # tar_target(topic_model,
-   #  #            make_topic_model(topic_model_input),
-   #  #             format = "qs")
+   tar_target(topic_model_input,
+              make_topic_model_input(all_pubs)),
+
+    tar_target(topic_number,
+              find_topic_number(topic_model_input),
+                format = "qs"),
+    tar_target(topic_model,
+               make_topic_model(topic_model_input),
+                format = "qs")
 
@@
      tar_target(coauthorship_graph,
-               make_graph(all_authors))
+               make_graph(coauthorship))
 

### 2023-04-14 R/comp_ind_topics.R

@@ -14,7 +14,7 @@ independent_topics <- function(independent_pubs) {
 independent_topics <-  independent_pubs %>% 
                         mutate(ind_topics = purrr::pmap(.l = list(pub_table, sup_vedidk),
                                    .f = function(first, second){
-                                       calc_ind_topics(topic_model = NULL, db_path, 
+                                       calc_ind_topics(topic_model, db_path, 
                                                        one_author = first, sup_vedidk = second)
                                    } ))
 

### 2023-04-14 R/find_topic_number.R

@@ -13,13 +13,13 @@ find_topic_number <- function(topic_model_input) {
         topic_model_input,
         topics = c(15, 30, 100),
         metrics = c("Griffiths2004", "CaoJuan2009", "Deveaud2014"),
-        method = "Gibbs",
+        method = "Gibbs",                         #rozhodnout se jestli použít VEM nebo Gibbs
         control = list(seed = 77),
         mc.cores = parallel::detectCores()-1,
         verbose = TRUE
     )
     
-    FindTopicsNumber_plot(result)
+    # FindTopicsNumber_plot(result)
     
 
 }

### 2023-04-14 R/make_topic_model.R

@@ -10,10 +10,18 @@
 make_topic_model <- function(topic_model_input) {
 
     
-    dfm <- dfm[which(rowSums(dfm) > 0),]
-    topic_model_input <- convert(dfm,to="topicmodels")
-    # dim(topic_model_input)
-    lda.model <- LDA(topic_model_input,k = 60, control = list(seed = 123),alpha = 0.1, beta = 0.01 , verbose=1) 
+    # s <- result %>% 
+    #     filter(Griffiths2004 == max(Griffiths2004), CaoJuan2009 == min(CaoJuan2009), Deveaud2014 == min(Deveaud2014)) %>% 
+    #     pull(topics)
+    # 
+    s <- topic_model_input %>% 
+        filter(Griffiths2004 == max(Griffiths2004)) %>% 
+        pull(topics)
+    
+    # dfm <- dfm[which(rowSums(dfm) > 0),]    podívat se proč jsem tady tenhle řádek a ten pod tím měl --> nějak to nedává smysl, mělo by to být spíš v topic model input nebo v tom kroku předtím
+    # topic_model_input <- convert(dfm,to="topicmodels")
+    # # dim(topic_model_input)
+    lda.model <- LDA(topic_model_input,k = s, control = list(seed = 123),alpha = 0.1, beta = 0.01 , verbose=1) 
     
     lda.matrix <- posterior(lda.model,dfm)$topics
     dim(lda.matrix) 

### 2023-04-26 _targets.Rmd
updated topic model, still need to work on Full_indicator as NAs there create problems + should also look at comp_ind_topics as it seems to generate only NaNs

@@
     tar_target(topic_model,
-               make_topic_model(topic_model_input),
+               make_topic_model(topic_model_input, topic_number),
                 format = "qs")
@@
     tar_target(independent_topics,
-                comp_ind_topics(independent_pubs))
+                comp_ind_topics(independent_pubs, topic_model, db_path))
 )

### 2023-04-26 R/calc_full_indicator.R

@@ -10,7 +10,13 @@
 calc_full_indicator <- function(independent_topics) {
  
                
-    independent_topics$eig_centr <- ifelse(independent_topics$eig_centr == "numeric(0)", NA, independent_topics$eig_centr)
+    # independent_topics <- independent_topics %>% 
+    #     mutate_all(~ ifelse(. == "numeric(0)", NA, .))
+   
+    independent_topics <- independent_topics %>% 
+        mutate_all(~ na_if(., "numeric(0)"))
+    
+    # independent_topics <- na.omit(independent_topics)
     
     independent_topics$RII <- ((1-independent_topics$eig_centr)+independent_topics$clustr+independent_topics$ind_pubs+independent_topics$ind_topics*2)/4
     

### 2023-04-26 R/find_topic_number.R

@@ -9,8 +9,12 @@
 #' @export
 find_topic_number <- function(topic_model_input) {
 
+    
+    dtm <- convert(topic_model_input,to="topicmodels")
+    # dim(dtm)
+    
     result <- FindTopicsNumber(
-        topic_model_input,
+        dtm,
         topics = c(15, 30, 100),
         metrics = c("Griffiths2004", "CaoJuan2009", "Deveaud2014"),
         method = "Gibbs",                         #rozhodnout se jestli použít VEM nebo Gibbs

### 2023-04-26 R/make_topic_model.R

@@ -7,23 +7,23 @@
 #' @return
 #' @author fatal: unable to access 'C:/Users/David Jank?/Documents/.config/git/config': Invalid argument
 #' @export
-make_topic_model <- function(topic_model_input) {
+make_topic_model <- function(topic_model_input, topic_number) {
 
     
-    # s <- result %>% 
+    # s <- topic_number %>% 
     #     filter(Griffiths2004 == max(Griffiths2004), CaoJuan2009 == min(CaoJuan2009), Deveaud2014 == min(Deveaud2014)) %>% 
     #     pull(topics)
     # 
-    s <- topic_model_input %>% 
-        filter(Griffiths2004 == max(Griffiths2004)) %>% 
+    # 
+    s <- topic_number %>%
+        filter(Griffiths2004 == max(Griffiths2004)) %>%
         pull(topics)
     
-    # dfm <- dfm[which(rowSums(dfm) > 0),]    podívat se proč jsem tady tenhle řádek a ten pod tím měl --> nějak to nedává smysl, mělo by to být spíš v topic model input nebo v tom kroku předtím
-    # topic_model_input <- convert(dfm,to="topicmodels")
-    # # dim(topic_model_input)
-    lda.model <- LDA(topic_model_input,k = s, control = list(seed = 123),alpha = 0.1, beta = 0.01 , verbose=1) 
+    dtm <- convert(topic_model_input,to="topicmodels")
+  
+    lda.model <- LDA(dtm,k = s, control = list(seed = 123),alpha = 0.1, beta = 0.01 , verbose=1) 
     
-    lda.matrix <- posterior(lda.model,dfm)$topics
+    lda.matrix <- posterior(lda.model,topic_model_input)$topics
     dim(lda.matrix) 
     
     data <- as_tibble(t(lda.matrix))

### 2023-04-26 network_analysis.R

@@ -141,6 +141,7 @@ rpubs = nrow(ind_pubs)/nrow(oneauth)
 ##ideálně by se dopic model mel dělat ze všech publikací všech autorů a jejich vedoucích a pak az z toho kompletního modelu tahat ta témata
 ###je potreba pracovat s unikatnima publikacema --> takze jeste chybi krok ktery protridi vsechny publikace autora a vedouciho a vyhodi ty ktere jsou stejne
 
+##guide example: https://bixuansunphd.com/N-R_tutorial.html#overview 
 
 library(data.table)
 require(data.table)

### 2023-04-27 _targets.Rmd
dd

@@
     tar_target(all_authors,
-           read_all_authors(db_path, ids_complete_vector, ids_complete, final_data, ids_full_vector))
-
+           read_all_authors(db_path, ids_complete_vector, ids_complete, final_data, ids_full_vector)),
+     tar_target(random_pubs,
+           get_random_pubs(db_path))
 )

### 2023-04-27 R/calc_ind_topics.R

@@ -13,7 +13,12 @@ calc_ind_topics <- function(topic_model, one_author, db_path, sup_vedidk) {
     
     # topic_model_2 <- load(paste(here::here("data", c("derivedtopic_dist.Rdata"))))
     
+    #for debugging: this is easy method how to call nested table:
+    # one_author <- as_tibble(do.call(cbind, independent_pubs$pub_table[4]))
+    
+    
     # names(topic_model)=substring(names(topic_model),2)
+    
     
     #spočítat poměrné zastoupení každého tématu v celém vzorku
      topic_model$topic_means <- rowMeans(topic_model)

### 2023-04-27 R/read_one_author.R

@@ -80,7 +80,7 @@ read_one_author <- function(db_path, ids_complete_vector, ids_complete, matching
   
   if(nrow(one_vedidk_coauthors)==0){tibble(id_unique = NA, id_helper = NA, year = NA, vedidk = NA, treatment_year = NA, independence_timing = NA)}else(one_vedidk_coauthors)
   
-  ####
+  #####
   
   # sup_vector <- ids_complete$vedoucí.vedidk %>% 
   #     as_tibble() %>% 

### 2023-04-27 _targets.Rmd
new topic model implemented

@@
    tar_target(topic_model_input,
-              make_topic_model_input(all_pubs)),
-
+              make_topic_model_input(random_pubs)),
    tar_target(topic_number,
@@
                 format = "qs"),
+   tar_target(topic_model_original,
+               make_topic_model(topic_model_input, topic_number),
+                format = "qs"),
+   tar_target(topic_model_input_addition,
+              make_topic_model_input_addition(all_pubs)),
    tar_target(topic_model,
-               make_topic_model(topic_model_input, topic_number),
+               make_topic_model_addition(topic_model_input_addition, topic_model_original),
                 format = "qs")

### 2023-04-27 R/make_topic_model.R

@@ -23,10 +23,12 @@ make_topic_model <- function(topic_model_input, topic_number) {
   
     lda.model <- LDA(dtm,k = s, control = list(seed = 123),alpha = 0.1, beta = 0.01 , verbose=1) 
     
-    lda.matrix <- posterior(lda.model,topic_model_input)$topics
-    dim(lda.matrix) 
+    # lda.matrix <- posterior(lda.model,topic_model_input)$topics
+    # dim(lda.matrix) 
+    # 
+    # data <- as_tibble(t(lda.matrix))
     
-    data <- as_tibble(t(lda.matrix))
+    
 
     # write.csv2(data, file = here::here("data", "derived", "topic_model_matrix.csv"))
     # write_excel_csv2(data, here("data", "derived", "tmm.csv"), na = "NA")

### 2023-04-27 R/make_topic_model_addition.R

@@ -1,0 +1,25 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+
+#' @return
+#' @author fatal: unable to access 'C:/Users/David Jank?/Documents/.config/git/config': Invalid argument
+#' @export
+make_topic_model_addition <- function(topic_model_input_addition, topic_model_original) {
+
+    
+    new_dtm <- convert(topic_model_input_addition,to="topicmodels")
+    
+    new_topics <- posterior(topic_model_original, new_dtm)$topics
+    # dim(new_topics)
+    data <- as_tibble(t(new_topics))
+    
+
+    # write.csv2(data, file = here::here("data", "derived", "topic_model_matrix.csv"))
+    # write_excel_csv2(data, here("data", "derived", "tmm.csv"), na = "NA")
+    # save(lda.matrix, file = paste(here("data", "derived", c("topic_dist.Rdata")), sep=""))
+
+}    
+    

### 2023-05-16 _targets.Rmd
small changes and improvements

@@
                             "MatchIt",
-                            "qs"
+                            "qs",
+                            "tidyverse"
                             ))

### 2023-05-16 R/create_ids_complete.R

@@ -10,7 +10,7 @@
 create_ids_complete <- function(ids, db_path) {
 
     ids_complete <- as_tibble(ids) %>% 
-        select(vedidk_core_researcher, sup_vedidk) %>% 
+        select(vedidk_core_researcher, sup_vedidk, statni.prislusnost) %>% 
         filter(!is.na(sup_vedidk)) %>% 
         filter(!is.na(vedidk_core_researcher))
         
@@ -88,8 +88,12 @@ create_ids_complete <- function(ids, db_path) {
         
     resitele <- DBI::dbReadTable(con, "cep_investigators") %>%
         filter(kod %in% GJ$kod) %>%
-        filter(vedidk %in% ids_complete$vedidk_core_researcher) %>%
-        select(kod, vedidk)
+        select(kod, vedidk, nationality) %>% 
+        distinct() %>%
+        filter(nationality == "CZ") %>% 
+        filter(!is.na(vedidk)) %>% 
+        filter(vedidk %in% ids_complete$vedidk_core_researcher)
+    
     
     resitele_complet <- left_join(resitele, GJ, by = "kod")
     resitele_complet$vedidk <- as.integer(resitele_complet$vedidk)

### 2023-05-16 R/just_test_two.R

@@ -406,6 +406,354 @@ just_test <- function(db_path, full_indicator) {
      median(career_start_both$difference) #to colour this further, median difference is 9 years, and mean 9.3, which is both above 8
      
      
-}
+     
+     
+     
+     
+     
+     ## descriptives
+     
+     final_data$id <- seq_along(final_data$vedidk)
+     full_indicator$id <- seq_along(full_indicator$vedidk)
+     
+     
+     d <- left_join(final_data, full_indicator)
+     
+     d$treatment <- as_factor(d$treatment)
+     d$independence_timing <- as_factor(d$independence_timing)
+     
+     
+     d_before <- d %>% filter(independence_timing == "before_intervention") %>% select(-vedidk, -vedidk_treatment, -pub_table, -edgelist, -graph, -independence_timing, -sup_name, -sup_vedidk)
+     d_after <- d %>% filter(independence_timing == "after_intervention") %>% select(-vedidk, -vedidk_treatment, -pub_table, -edgelist, -graph, -independence_timing, -sup_name, -sup_vedidk)
+
+     library(tidyverse)
+     library(psych)
+     
+     table_before_0 <- d_before %>% filter(treatment == 0) %>% describe() %>% round(., digits = 3)
+     table_before_0$na_count <- colSums(is.na(d_before %>% filter(treatment == 0)))
+     table_before_1 <- d_before %>% filter(treatment == 1) %>% describe() %>% round(., digits = 3)
+     table_before_1$na_count <- colSums(is.na(d_before %>% filter(treatment == 1)))
+     table_before_2 <- d_before %>% filter(treatment == 2) %>% describe() %>% round(., digits = 3)
+     table_before_2$na_count <- colSums(is.na(d_before %>% filter(treatment == 2)))
+     
+     table_after_0 <- d_after %>% filter(treatment == 0) %>% describe() %>% round(., digits = 3)
+     table_after_0$na_count <- colSums(is.na(d_after %>% filter(treatment == 0)))
+     table_after_1 <- d_after %>% filter(treatment == 1) %>% describe() %>% round(., digits = 3)
+     table_after_1$na_count <- colSums(is.na(d_after %>% filter(treatment == 1)))
+     table_after_2 <- d_after %>% filter(treatment == 2) %>% describe() %>% round(., digits = 3)
+     table_after_2$na_count <- colSums(is.na(d_after %>% filter(treatment == 2)))
+     
+     table_before_0$na_count_total <- colSums(is.na(d_before))
[…]

### 2023-05-16 R/refine_data.R

@@ -83,5 +83,10 @@ refine_data <- function(matching, db_path, ids, sup_control) {
     d <- anti_join(a_final_data, b, by = "vedidk")
     # table(d$treatment, by =d$independence_timing)
     
+    #by this code below, I attach the cases in which no supervisor was found (i.e. cases where these people had no coauthors in theri first 5 publications) 
+    aa <- anti_join(matching, d, by = "vedidk")
+    bb <- left_join(aa, d)
 
+    cc <- rbind(d, bb)
+    
 }

### 2023-05-17 _targets.Rmd
small updates and improvements

--- 2023-04-27 _targets.Rmd
@@
                             "MatchIt",
-                            "qs"
+                            "qs",
+                            "tidyverse",
+                            "psych"
                             ))
@@
 list(
+
+    # tar_target(results,
+    #            analyse(full_indicator),
+    #            format = "qs") ,
+    # tar_target(sup_testing,
+    #            sup_test(matching, db_path, ids, sup_control, ids_complete),
+    #            format = "qs") ,
+    # 
     # tarchetypes::tar_render(article, here::here("Rmd", "article.Rmd"))

### 2023-05-17 R/calc_full_indicator.R

@@ -26,6 +26,10 @@ calc_full_indicator <- function(independent_topics) {
     independent_topics$ind_topics <- unlist(independent_topics$ind_topics)
     
     
+    independent_topics <- independent_topics %>% mutate(eig_centr = ifelse(is.na(eig_centr) & !is.na(sup_name), 0, eig_centr)) #this turns all the cases where there is a sup_name but the supervisor was not found in the authors coauthorship network (and therefore eig_centr turned NA) make it a 0, because it should be interpreted as "their independence is at max, because their supervisor is not even in their network anymore" 
+    independent_topics <- independent_topics %>% mutate(clustr = ifelse(is.na(clustr) & !is.na(sup_name), 1, clustr)) #this turns all the cases where there is a sup_name but the supervisor was not found in the authors coauthorship network (and therefore clustr turned NA) make it a 0, because it should be interpreted as "their independence is at max, because their supervisor is not even in their network anymore" 
+    
+    
     independent_topics <- independent_topics %>% 
         mutate(RII = ifelse(is.na(eig_centr) | is.na(clustr) | is.na(ind_pubs) | is.na(ind_topics), NA, ((1-eig_centr)+clustr+ind_pubs+ind_topics)/4))
     
@@ -42,6 +46,8 @@ calc_full_indicator <- function(independent_topics) {
     # 
     # c
     
+    
+    independent_topics$id <- seq_along(independent_topics$vedidk)
     
     
     d <- left_join(final_data, independent_topics)
@@ -84,35 +90,39 @@ calc_full_indicator <- function(independent_topics) {
     
     ##how many of that is because we could not find people's supervisors?
     
-    f <- d %>% filter(pub_table_empty == FALSE)
+    # f <- d %>% filter(pub_table_empty == FALSE)
+    # 
+    # sum(is.na(d$sup_name))
+    # sum(is.na(f$sup_name))
+    # 
+    # sum(is.na(d$sup_name)) / nrow(d) # this shows that X % of observations have no supervisor 
+    # 
+    # sum(is.na(f$sup_name)) / sum(is.na(d$RII)) # this shows that missing supervisors explain X % of all misssing RII scores  
+    # sum(is.na(f$sup_name)) / sum(is.na(f$RII)) # this shows that missing supervisors explain X % of all remaining misssing RII scores  
     
-    sum(is.na(d$sup_name))
-    sum(is.na(f$sup_name))
     
[…]

### 2023-06-04 _targets.Rmd
updated databasea and added ids

@@
                             "tidyverse",
-                            "psych"
+                            "psych",
+                            "arrow"
                             ))
@@
            here::here("data", "raw", "czech_sci_db.sqlite")),
+     tar_target(authors_arrow_path, here::here("data", "raw", "authors_by_pubs.arrow")),
+     tar_target(authors_arrow, arrow::read_feather(authors_arrow_path)),
+     tar_target(text_arrow_path, here::here("data", "raw", "riv_text.arrow")),
+     tar_target(text_arrow, arrow::read_feather(text_arrow_path)),
      tar_target(ids_complete, create_ids_complete(ids, db_path)),
-    tar_target(ids_complete_vector,
-               make_ids_complete_vector(ids_complete))
+     tar_target(ids_complete_vector, make_ids_complete_vector(ids_complete))
 
-    # tar_target(all_pubs,
-    #        get_all_pubs(db_path, ids_complete), 
-    #           format = "qs"),
-    # tar_target(one_author,
-    #        read_one_author(db_path, ids_complete_vector, ids_complete), 
-    #           format = "qs")
-    # 
 )
@@
 
-      tar_target(matching, match(db_path, ids, gender)),
+      tar_target(matching, match(db_path, ids, gender, authors_arrow)),
       tar_target(sup_path, here::here("data", "raw", "supervisors_control_final.csv"), format = "file"),
@@
      #          format = "qs"),
-      tar_target(final_data, refine_data(matching, db_path, ids, sup_control)),
+      tar_target(final_data, refine_data(matching, db_path, ids, sup_control, authors_arrow)),
 
@@
      tar_target(all_pubs,
-           get_all_pubs(db_path, final_data)),
+           get_all_pubs(db_path, final_data, authors_arrow, text_arrow)),
     tar_target(all_authors,
-           read_all_authors(db_path, ids_complete_vector, ids_complete, final_data, ids_full_vector)),
+           read_all_authors(db_path, ids_complete_vector, ids_complete, final_data, ids_full_vector, authors_arrow)),
      tar_target(random_pubs,
-           get_random_pubs(db_path))
+           get_random_pubs(db_path, authors_arrow, text_arrow))
 )
@@
 
-    # tar_target(edgelist,
-    #            make_edgelist(one_author),
-    #             format = "qs", pattern = map(one_author), iteration = "list"),
-    # tar_target(graph, igraph::graph_from_data_frame(edgelist, directed = FALSE), pattern = map(edgelist), iteration = "list")
     tar_target(coauthorship,
@@
 
-    # tar_target(eigen_centr,
-    #            calc_eigen_centr(graph, ids_complete, one_author, db_path),
-    #            format = "qs", pattern = map(graph, one_author), iteration = "list")
-    # 
      tar_target(eigen_centrality,
@@
 list(
-
-    #  tar_target(clustering,
-    #             calc_clustering(graph, ids_complete, one_author, db_path),
-    #            format = "qs", pattern = map(graph, one_author), iteration = "list") 
-    # #            
-    # #
 
@@
 
-     # tar_target(ind_pubs,
-     #            calc_ind_pubs(one_author, ids_complete, db_path), 
-     #            format = "qs", pattern = map(one_author),                  iteration = "list")
-     # 
    tar_target(independent_pubs,
@@
 
-     # tar_target(ind_topics,
-     #            calc_ind_topics(topic_model = NULL, one_author, ids_complete, db_path), 
-     #            format = "qs", pattern = map(one_author), iteration = "list")
-     # 
     tar_target(independent_topics,
-                comp_ind_topics(independent_pubs, topic_model, db_path))
+                comp_ind_topics(independent_pubs, topic_model, db_path, authors_arrow))
 )
@@
 
-    # tar_target(final_data,
-    #            calc_final_data(eigen_centr, clustering, ind_topics, ind_pubs, matching),
-    #            format = "qs") #,
     #  # tar_target(testing,

### 2023-06-04 R/calc_full_indicator.R

@@ -47,7 +47,7 @@ calc_full_indicator <- function(independent_topics) {
     # c
     
     
-    independent_topics$id <- seq_along(independent_topics$vedidk)
+    # independent_topics$id <- seq_along(independent_topics$vedidk)
     
     
     d <- left_join(final_data, independent_topics)

### 2023-06-04 R/calc_ind_topics.R

@@ -7,8 +7,14 @@
 #' @return
 #' @author fatal: unable to access 'C:/Users/David Jank?/Documents/.config/git/config': Invalid argument
 #' @export
-calc_ind_topics <- function(topic_model, one_author, db_path, sup_vedidk) {
+calc_ind_topics <- function(topic_model, one_author, db_path, sup_vedidk, authors_arrow) {
 
+    authors_arrow <- as.data.frame(authors_arrow)
+    con <-  DBI::dbConnect(RSQLite::SQLite(), db_path)
+    dbWriteTable(con, "authors_by_pubs", authors_arrow, overwrite = TRUE)
+    on.exit(DBI::dbDisconnect(con))
+    
+    
     # topic_model <- read.csv2(here::here("data", "derived", "tmm.csv"))
     
     # topic_model_2 <- load(paste(here::here("data", c("derivedtopic_dist.Rdata"))))

### 2023-06-04 R/comp_ind_topics.R

@@ -8,13 +8,13 @@
 #' @return
 #' @author fatal: unable to access 'C:/Users/David Jank?/Documents/.config/git/config': Invalid argument
 #' @export
-comp_ind_topics <- function(independent_pubs, topic_model, db_path) {
+comp_ind_topics <- function(independent_pubs, topic_model, db_path, authors_arrow) {
 
 
 independent_topics <-  independent_pubs %>% 
                         mutate(ind_topics = purrr::pmap(.l = list(pub_table, sup_vedidk),
                                    .f = function(first, second){
-                                       calc_ind_topics(topic_model, db_path, 
+                                       calc_ind_topics(topic_model, db_path, authors_arrow,
                                                        one_author = first, sup_vedidk = second)
                                    } ))
 

### 2023-06-04 R/match.R

@@ -8,9 +8,11 @@
 #' @return
 #' @author fatal: unable to access 'C:/Users/David Jank?/Documents/.config/git/config': Invalid argument
 #' @export
-match <- function(db_path, ids, gender) {
+match <- function(db_path, ids, gender, authors_arrow) {
 
+    authors_arrow <- as.data.frame(authors_arrow)
     con <-  DBI::dbConnect(RSQLite::SQLite(), db_path)
+    dbWriteTable(con, "authors_by_pubs", authors_arrow, overwrite = TRUE)
     on.exit(DBI::dbDisconnect(con))
     
     DBI::dbListTables(con)

### 2023-06-04 R/refine_data.R

@@ -10,7 +10,7 @@
 #' @return
 #' @author fatal: unable to access 'C:/Users/David Jank?/Documents/.config/git/config': Invalid argument
 #' @export
-refine_data <- function(matching, db_path, ids, sup_control) {
+refine_data <- function(matching, db_path, ids, sup_control, authors_arrow) {
 
    #  ids_refined <- ids %>%
    #      select(vedoucí.vedidk, vedidk_core_researcher) %>%
@@ -70,7 +70,7 @@ refine_data <- function(matching, db_path, ids, sup_control) {
         distinct() %>% 
         mutate(sup_details = purrr::pmap(.l = list(vedidk),
                                        .f = function(first){
-                                           read_sup(db_path, 
+                                           read_sup(db_path, authors_arrow, 
                                                     ids_full_vector = first)
                                        } ))
     

### 2023-06-04 article.Rmd
plain text article

---
title: "Funding programmes for early career researchers do/not influence their independence"
author: "David Janků"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(targets)
library(dplyr)
```

# Intro

Researchers’ independence from their PhD advisor is one of the criteria often used for assessing researchers for hiring, tenure and promotion (Van Arensbergen, Van der Weijden, Van den Besselaar, 2014; Moher et al, 2018), constituting one factor of research excellence.
The promise of independence is that researchers will “challenge the existing common views and open up new lines of research” (Van den Besselaar & Sandström, 2019, p.2).

An independent investigator is then defined by the US National Academies of Science (NAS) as “one who enjoys independence of thought—the freedom to define the problem of interest and to choose or develop the best strategies and approaches to address that problem–especially during the earlier career phase” (Van den Besselaar & Sandström, 2019, p.4). Such a definition does not necessarily put independence in relation to other actors (e.g. one’s PhD advisor), but only in relation to one’s own freedom and resources. However other institutions, such as European Research Council via their Starting Grants scheme (Neufeld, Huber & Wegner, 2013) think of independence in a relational manner, in terms of having one (or a few) publications without the former PhD supervisor being co-author; being PI on a grant; or being lab director or research leader.

Based on some early empirical studies (Rojko & Lužar, 2022), it seems that researchers in disciplines such as philosophy, psychology; religion, theology; social sciences; the arts, recreation, entertainment, sport; language, linguistics, literature; and geography, biography, history experience significantly higher levels of indepedence on their PhD advisor than researchers in disciplines such as science and knowledge, organization, computer science, information, documentation, librarianship, institutions, publications; mathematics, natural sciences; and applied sciences, medicine, technology. 
There is also some preliminary evidence that higher indepedence modestly correlates with number of citations aquired (Rojko & Lužar, 2022), but others argue that even the research systems with very low indepedence can create a lot of scientific impact, and thus the relationships between independence and impact might not be as clear (Gläser et al., 2021)

In recent decades, there has been a worry that researchers’ indepedence is decreasing, illustrated by increase in age at which US (biomedical) researchers received their first grant (NAS, 2005; Daniels, 2015), as well as direct measures of new reserchers becoming more depedent on their PhD advisors across almost all disciplines in Slovenia (Rojko & Lužar, 2022, table 6 on p.9). Perhaps to tackle this trend, many grant agencies decided to start awarding grants for early career researchers, usually up to 8 years after finishing their PhD. Such programmes have often explicitly stated goals of helping researchers become more indepedent, set up their own research group and open up new lines of research. The examples of such programmes could be Starting Grants by European Research Council (2022), Junior project and Junior Star by Czech Science Foundation (2020), Walter N. Benjamin Programme by DFG (2022), Innovation Research Incentives Scheme by Netherlands Organization of Scientific Research (NWO) (2021)... something from the US would be also good)

Although researcher independence seems to be important feature that is acknowledged by many actors in the research systems and that research funders try to stimulate, there hasn’t been much effort focused on quantifying this phenomenon. Some studies try to measure independence in a simple way, as a ratio of publications the given researcher produced without their supervisor divided by the total number of publications of the given researchers (e.g. Rojko & Lužar, 2022). However, such indicator could be misleading in the world of team science, and also only focuses on collaborations, not tracking whether given researcher become independent in their thinking and research topics. Van den Besselaar & Sandström (2019) therefore proposed more complex indicator for measuring researcher independence on the individual level, based on co-authorship network and topical overlaps. Their measure uses only information about publications’ characteristics (authorship and reference list) regardless of it’s impacts, unlike other alternative measures that focus solely on the impact of the independent work in terms of received citations (Dey, et al., 2021).

Since the explicit goal of many funding instruments that are being used by research funders all over the world is to help early career researchers become independent, we would like to use the newly created indicators to assess the extent, to which such programmes influence researchers independence.

H1: Researchers, who received funding from programmes aimed at funding early career researchers, will show more independence on theri PhD advisor 5 years after receiving the funding than researchers who did not receive this kind of funding.

# Method

## Sample / data

We used the database of all publications produced by researchers employed at Czech research institutions (RIV) combined with a database of all publicly funded research projects and grants in the Czech Republic (CEP), both publicly accessible at https://www.isvavai.cz/, and transformed into a single database with cleaned data, unique person and publication identifiers, and better structure (Hladik, XXX).
This allowed us to identify all researchers who received Junior Grants from the Czech Science Foundation, a funding programme that has an explicit goal to help early career researchers become independent and set up their own research groups. There were 491 projects funded from 2015 to 2020, usually 3 years long (with some being only 2 years long), where the PI must have been up to 8 years after their PhD defence (with potential extension of 2 years for each child the researcher had in that period) and the grant could contribute up to 100 % of their salary (usually, this is limited to 50 % in other funding programmes). From these 491 funded projects, we selected 348 (71 %) grants of the recipients from Czechia, since the remaining recipients were from abroad, and thus would not have their previous publications recorded in the database of researchers employed at Czech research institutions (RIV) that we used for all analyses. There were also 7 cases where one researcher received this grant two times - in these cases, we counted only the first project that was funded, reducing the number of recipients we worked with to 341.

In the second step, we manually searched for PhD advisors of these 341 researchers in the databases of theses and dissertations that cover most universities in Czechia (https://theses.cz and https://dspace.cuni.cz/). We were able to match `r nrow(tar_read(ids_complete))` researchers with a PhD advisor (69,2 % of the Czech subsample). Further, we have not managed to find a suitable matched pair for another `r nrow(tar_read(ids_complete))-nrow(tar_read("matching") %>% filter(treatment == 1) %>% distinct(vedidk))` researchers in the matching procedure, reducing our final sample to `r nrow(tar_read("matching") %>% filter(treatment == 1) %>% distinct(vedidk))`.

These researchers and their PhD advisors with their full publication history (limited to publications created at Czech institutions) created our final sample.

```{r}
head(tar_read(matching))

```

### 2023-06-06 R/calc_ind_topics.R
some errors fixed so the pipeline is operational

@@ -7,7 +7,7 @@
 #' @return
 #' @author fatal: unable to access 'C:/Users/David Jank?/Documents/.config/git/config': Invalid argument
 #' @export
-calc_ind_topics <- function(topic_model, one_author, db_path, sup_vedidk, authors_arrow) {
+calc_ind_topics <- function(topic_model, db_path, authors_arrow, one_author, sup_vedidk) {
 
     authors_arrow <- as.data.frame(authors_arrow)
     con <-  DBI::dbConnect(RSQLite::SQLite(), db_path)

### 2023-06-06 R/comp_eigen_centr.R

@@ -14,8 +14,7 @@ comp_eigen_centr <- function(coauthorship_graph) {
 eigen_centrality <-  coauthorship_graph %>% 
                         mutate(eig_centr = purrr::pmap(.l = list(graph, sup_name),
                                    .f = function(first, second){
-                                       calc_eigen_centr(db_path, 
-                                                        graph = first, one_author = second)
+                                       calc_eigen_centr(graph = first, one_author = second)
                                    } ))
 
 # eigen_centrality <- eigen_centrality %>% 

### 2023-06-08 _targets.Rmd
some errors fixed so the pipeline is operational
important edits in final_data target

@@
                             "ldatuning",
-                            "quanteda",
                             "data.table",
@@
                             "psych",
-                            "arrow"
+                            "arrow",
+                            "tarchetypes"
                             ))
@@
 
+  # tarchetypes::tar_download(ids,
+  #     urls = Sys.getenv("link_to_supervisors"),
+  #     paths = here::here("data", "raw", "supervisors.csv")),
+  # tarchetypes::tar_download(gender,
+  #     urls = Sys.getenv("link_to_gender"),
+  #     paths = here::here("data", "raw", "names4api_tagged.tsv")),
+  # tarchetypes::tar_download(authors_arrow,
+  #     urls = Sys.getenv("link_to_updated_authors"),
+  #     paths = here::here("data", "raw", "authors_by_pubs.arrow")),
+  # tarchetypes::tar_download(text_arrow,
+  #     urls = Sys.getenv("link_to_updated_texts"),
+  #     paths = here::here("data", "raw", "riv_text.arrow")),
+  #  tarchetypes::tar_download(sup_control,
+  #     urls = Sys.getenv("link_to_supervisors_control"),
+  #     paths = here::here("data", "raw", "supervisors_control_final.csv")),
+
      tar_target(ids_path, here::here("data", "raw", "supervisors.csv"), format = "file"),
@@
      tar_target(gender, read.delim(gender_path)),
-     # tar_target(gender, read.delim(here::here("data", "raw", "names4api_tagged.tsv")),
-     #          format = "qs"),
-     tar_target(db_path,
-           here::here("data", "raw", "czech_sci_db.sqlite")),
+     tar_target(db_path, here::here("data", "raw", "czech_sci_db.sqlite")),
      tar_target(authors_arrow_path, here::here("data", "raw", "authors_by_pubs.arrow")),
@@
      #          format = "qs"),
-      tar_target(final_data, refine_data(matching, db_path, ids, sup_control, authors_arrow)),
+      tar_target(final_data, refine_data(matching, db_path, ids_complete, sup_control, authors_arrow)),
 
@@
     tar_target(full_indicator,
-               calc_full_indicator(independent_topics))
+               calc_full_indicator(independent_topics, final_data))
 
@@
     # 
-    # tarchetypes::tar_render(article, here::here("Rmd", "article.Rmd"))
+    tarchetypes::tar_render(article, here::here("article.Rmd"))
 )

### 2023-06-08 article.Rmd
important edits in final_data target

@@
 library(dplyr)
+library(cobalt)
+library(knitr)
 ```
@@
 
-H1: Researchers, who received funding from programmes aimed at funding early career researchers, will show more independence on theri PhD advisor 5 years after receiving the funding than researchers who did not receive this kind of funding.
+H1: Researchers, who received funding from programmes aimed at funding early career researchers, will show more independence on their PhD advisor 5 years after receiving the funding than researchers who did not receive this kind of funding.
 
@@
 
+For the matched researchers from control groups (see the matching description below in the Analysis section), we didn't search for their supervisors manually, but rather used the "most frequent co-author of the first 5 publications" as a proxy to identify supervisors.
+Crosschecking this proxy with the actual data about supervisors we have, we found that this algorithm was able to identify supervisors correctly in about 50 % of cases (see the Attachment 1).
+Using this method, we were able to find `r (nrow(tar_read("final_data") %>% filter(treatment != 1) %>% filter(!is.na(sup_name))) / nrow(tar_read("matching") %>% filter(treatment != 1)))*100` % of the observations in the matched control groups.
+
 These researchers and their PhD advisors with their full publication history (limited to publications created at Czech institutions) created our final sample.
 
-```{r}
-head(tar_read(matching))
+## Measures
+
+*Independence*
+
+We decided to use the recently created independence indicator by Van den Besselaar & Sandström (2019), since it is based on scientific production (rather than impact) and captures the phenomena in the most complete manner.
+The indicator has 4 parts: I1: The eigenvector centrality of the supervisor in the researcher’s co-author network; I2: The clustering coefficient of the supervisor in the researcher’s co-author network; I3: The share of own papers of the researcher Pns/Pall where Pns is the number of publications of the researcher, not coauthored with the former supervisor(s) and Pall is the total number of publications of the researcher; and I4: The share of own research topics of the researcher Tns/Tall where Tns is the number of research topics of the researcher in which the former supervisor(s) is not active, and Tall is the total number of topics of the researcher.
+
+However, we have made some changes to the indicator.
+After consulting with its authors, we have changed the aggregation formula to RII = ((1- I1) + I2 + I3 + I4) / 4, since the previous formula had a small error (it weighted I4 double,, i.e.
+2*I4).
+For calculating the share of own research topics of the researcher (I4), we have also not used bibliographic coupling as originally suggested, but text-based topic modelling using publication titles and abstracts.
+Finally, the original indicator, while tracking not only collaboration independence but also topical independence, is still skewed significantly towards collaboration independence (three-quarters of the indicator measure collaboration, while only one-quarter measures topics).
+Since we consider cognitive/topical independence an important asset of this indicator, we have decided to adjust the formula a bit further and drop the I3 part, to give more weight to the cognitive/topical independence in the whole indicator.
+Throughout this paper, we will thus refer to the original indicator as RIIo, our adjusted version as RIIa and the part of the indicator measuring only the cognitive independence RIIc.
+
+*Career age*
+
+We measured researchers’ career age as the number of years since their first publication.
+
+*Discipline*
+
+We used the highest level of the OECD classification of disciplines, containing categories Natural Sciences; Engineering and Technology; Medical and Health Sciences; Agricultural Sciences; Social Sciences; Humanities.
+We chose this classification because it is widely used and also used in the dataset we worked with.
+For the matching we used the 42 sub-categories of this classification to achieve more granularity.
+
+We attributed a discipline to a given researcher based on disciplines attributed to their each publication, choosing the most frequent discipline for each author.
+
+*Interdisciplinary proportion*
+
+This measure was calculated as the ratio of publications authored by the given researcher which were not assigned to the author’s main discipline.
+
+*Number of publications*
+
+We counted all publications the given researcher produced before the intervention year (i.e.
+receiving a Junior Grant) while affiliated with the Czech institution (our database only contained publications affiliated with Czech institutions).
+We only counted publications of types: journal articles, conference proceedings, book chapters, and full books.
+
+*Number of publications in Web of Science and Scopus*
+
+We counted all publications the given researcher produced before the intervention year (i.e.
+receiving a Junior Grant) while affiliated with the Czech institution (our database only contained publications affiliated with Czech institutions), that were also linked in Web of Science or Scopus (which means they were likely published in more recognised journals).
+We only counted publications of types: journal articles, conference proceedings, book chapters, and full books.
+
+*Number of grants received prior to Junior Grant*
+
+We calculated how many (Czech) grants each researcher has received prior to the intervention year (i.e. receiving a Junior Grant).
+
+*Career age when receiving the first grant*
+
+We calculated the career age of each researcher when they received their first grant.
+
+*Gender*
+
+We used ??? table ??? to estimate the gender of each researcher.
+
+## Analysis
+
+We analysed the data in the R version 4.2.3.
+using R studio and [this code](https://github.com/david-janku/juniors).
+For the construction of the independence indicator, we used network modelling (maybe more specific?) and text-based topic modelling (maybe more specific??).
+
+For the construction of the control group, we implemented propensity matching using the package MatchIt (citation?) and matching exactly by the discipline (42 sub-categories of OECD classification), and approximately by number of publications in total, number of publications in WoS/Scopus, career age, interdisciplinary proportion, number of grants received prior to Junior Grant, career age when receiving the first grant and gender.
+All of these variables were calculated at the intervention year (i.e.
+year when the given researcher from experimental group received the Junior Grant).
+We set caliper to 0.2 standard deviations of the logit of the propensity score by recommendation of Rosenbaum and Rubin (1985b) and Austin (2011) to remove the cases where the distance between experimental and control group observation was too large.
+__This removed XXXX cases from the experimental group, leaving us with YYY matched observations__.
+The matching was done in 1:1 ratio and with replacement.
+
+We have created 2 control groups: one using the matching above and one similar but specifically containing only researchers who received their first grant (other than Junior Grant) around the same career age as researchers in our intervention group.
+That allowed us to better track the impact of any grant funding vs specifically Junior Grants funding on researchers’ independence.
+
+The difference between groups was tested using paired t-test and subsequent differences between discipline groups was tested using ANOVA post-hoc Tukey test.
+
+# Results
+
+## Descriptives
+
+### Missing data
+```{r echo=FALSE}
+d <- tar_read(full_indicator)
+na_counts <- sum(is.na(d$RII))
+na_percentage <- round((na_counts / nrow(d))*100, 1)
+
+na_sup <- round((sum(is.na(d$sup_name))/na_counts)*100, 1)
+na_pubs <- round((nrow(d %>% filter(!is.na(sup_name)) %>% filter(pub_table_empty == TRUE))/na_counts)*100, 1)
+
+na_pubs_after <- round((nrow(d %>% filter(!is.na(sup_name)) %>% filter(pub_table_empty == TRUE) %>% filter(independence_timing == "after_intervention"))/nrow(d %>% filter(!is.na(sup_name)) %>% filter(pub_table_empty == TRUE)))*100, 1)
+
+na_treatment <- nrow(d %>% filter(is.na(RII)) %>% filter(treatment == 1))
+na_control1 <- nrow(d %>% filter(is.na(RII)) %>% filter(treatment == 0))
+na_control2 <- nrow(d %>% filter(is.na(RII)) %>% filter(treatment == 2))
+
+s <- d %>% filter(is.na(RII))
+
+f_after <- d %>% filter(!is.na(RII)) %>% filter(independence_timing == "after_intervention") 
+f_before <- d %>% filter(!is.na(RII)) %>% filter(independence_timing == "before_intervention")
+
+v_after <- c(f_after$vedidk[f_after$treatment == 1 ], NA)
+v_before <- c(f_before$vedidk[f_before$treatment == 1 ], NA)
+
+r_after <- f_after %>% filter(vedidk_treatment %in% v_after)
+r_before <- f_before %>% filter(vedidk_treatment %in% v_before)
+
+v_after_control <- c(r_after$vedidk[r_after$treatment != 1 ], r_after$vedidk_treatment)
+v_before_control <- c(r_before$vedidk[r_before$treatment != 1 ], r_before$vedidk_treatment)
+
+r_after_final <- r_after %>% filter(vedidk %in% v_after_control)
+r_before_final <- r_before %>% filter(vedidk %in% v_before_control)
+
+# r_test <- r_after %>% filter(treatment != 2)
+# v_after_test <- c(r_test$vedidk[r_test$treatment != 1 ], r_test$vedidk_treatment)
+# r_test_final <- r_test %>% filter(vedidk %in% v_after_test)
+
+final_before_control1 <- nrow(r_before_final %>% filter(treatment == 0)) 
+final_before_control2 <- nrow(r_before_final %>% filter(treatment == 2))
+
+final_after_control1 <- nrow(r_after_final %>% filter(treatment == 0)) 
+final_after_control2 <- nrow(r_after_final %>% filter(treatment == 2))
+
+a <- intersect(
+    r_after_final$vedidk,
+    r_before_final$vedidk
+)
+
+all <- r_before_final %>% filter(vedidk %in% a)
 
 ```
+
+The independence indicator was not possible to calculate for `r na_counts` (`r na_percentage` % of observations).
+This is in `r na_sup` % caused by missing data about supervisors, and in `r na_pubs` % due to given researcher not having any publications in the given period (`r na_pubs_after` % of these cases are in the period after the intervention, which sometimes mean in the past few years).
+
+There are `r na_treatment` missing observations in the treatment group, `r na_control1` in the unfunded control group and  `r na_control2` in the funded control group.
+If we only keep observation that have match with non-missing values, we are left with a sample of `r final_before_control1` matched observations in unfunded control group and `r final_before_control2` matched observations in funded control group before intervention and a sample of `r final_after_control1` matched observations in unfunded control group and `r final_after_control2` matched observations in funded control group after intervention.
+
+## Matching
+
+```{r echo=FALSE}
+# Create a subset for treatment group and control group 1
+subset_1 <- (tar_read(matching)) %>% filter(treatment != 2)
+subset_2 <- (tar_read(matching)) %>% filter(treatment != 0)
+
+# Generate balance table for treatment vs control group 1
+balance_results_1 <- bal.tab(treatment ~ career_lenght + pubs_total + ws_pubs + interdisc_proportion + grants + gender, data = subset_1, disp = c("mean", "std"))
+balance_results_2 <- bal.tab(treatment ~ career_lenght + pubs_total + ws_pubs + interdisc_proportion + grants + gender, data = subset_2, disp = c("mean", "std"))
+
+# Define a function to manually extract balance statistics from bal.tab object
+extract_balance_stats <- function(bal_results) {
+  covariates <- rownames(bal_results$Balance)
+  means_treat <- bal_results$Balance$`M.1.Un`
+  means_ctrl <- bal_results$Balance$`M.0.Un`
+  diff <- bal_results$Balance$`Diff.Un`
+
+  data.frame(Covariate = covariates, 
+             Mean_Treatment = means_treat, 
+             Mean_Control = means_ctrl, 
+             Diff = diff)
+}
+
+# Extract balance stats for subset_1 and subset_2
+balance_stats_1 <- extract_balance_stats(balance_results_1)
+balance_stats_2 <- extract_balance_stats(balance_results_2)
+
+# Print tables in R Markdown
+knitr::kable(balance_stats_1, caption = "Balance Statistics: Treatment vs Control Group 1")
+knitr::kable(balance_stats_2, caption = "Balance Statistics: Treatment vs Control Group 2")
+
+```
+
+## Main results
+
+# Discussion
+
+## Limitations
+
+--> the identification of supervisors in the control group (only 50% correct)
+--> only talks about the Czech environment and considers researchers growing up and most of their careers in the Czech republic
+
+# Attachments
+
+## Identification of supervisors
+
+Data about PhD student-PhD advisor connections are usually not available.
+One must search for these connections manually on the internet, which is time consuming and not fully reliable (we were only able to find about 69 % of these connections in our treatment group).
+Therefore, we tried to come up with an alternative way of identifying supervisors from the available data: we assumed that since many researchers only start their publication career during their PhD studies, their PhD supervisors might often coauthor their first publications.
+That led us to creating an algorithm to identify the supervisor solely from the student's publication history as "the most frequent co-author of the first 5 publications".
+
+To check whether we can use "the most frequent co-author of the first 5 publications" as a proxy to identify supervisors, we have compared the supervisors identified via this method with the manually found supervisors for each researcher in our sample.
+In the treatment group of `r nrow(tar_read(ids_complete))`researchers,  118 (49 %) had their most frequent co-author same as their supervisor and 86 (36 %) had someone other than their supervisor as their most frequent co-author in their first 5 publications, and 37 (15%) had no co-author in their first 5 publications.
+In the control groups, we have manually found supervisors for `r nrow(tar_read(sup_control) %>% filter(!is.na(sup_vedidk)) %>% distinct(name_first, name_last))` researchers, and when we compared them to the supervisors suggested by the most frequent coauthor algorithm, we found that 41 (29 %) had their most frequent co-author the same as their supervisor, 80 (57 %) had someone other than their supervisor as their most frequent co-author in their first 5 publications, and 20 (14 %) had no co-author in their first 5 publications.
+
+Further, we have conducted analysis on an independent sample of researchers from Slovenia (citace Luzar??), and found that  when we filter out all researchers who have not had any publication 4 years prior to their PhD defense (1135, approx 9,5% of the sample), we see that from the remaining researchers, about 50,3 % had their supervisor as the most frequent coauthor in the 4 years prior to their PhD defense.

### 2023-06-08 R/create_ids_complete.R

@@ -112,6 +112,19 @@ create_ids_complete <- function(ids, db_path) {
     
     ids_complete <- dplyr::rename(ids_complete, sup_vedidk = sup_vedidk)
     ids_complete <- dplyr::rename(ids_complete, vedidk = vedidk_core_researcher)
+    ids_complete$sup_vedidk <- as.character(ids_complete$sup_vedidk)
+    
+    
+    control_id <-  ids_complete$sup_vedidk
+    sup_names <- dplyr::tbl(con, "authors_by_pubs") %>% # colnames()
+        dplyr::select(id_helper, vedidk) %>% 
+        filter(vedidk %in% control_id) %>% 
+        dplyr::rename(sup_name = id_helper) %>%
+        dplyr::rename(sup_vedidk = vedidk) %>%
+        dplyr::collect() %>% 
+        distinct() #tady ideálně ještě přidat část kódu která říká "pokud je tam nějaký vedidk více než jednou, vyber jeho nejčastější sup_name -> v našem vzorku ale není žádný vedidk více než jednou, takže ok
+    
+    ids_complete <- left_join(ids_complete, sup_names, by = "sup_vedidk")
      
     
 }

### 2023-06-09 _targets.Rmd
new updates

@@
 
-  # tarchetypes::tar_download(ids,
-  #     urls = Sys.getenv("link_to_supervisors"),
-  #     paths = here::here("data", "raw", "supervisors.csv")),
-  # tarchetypes::tar_download(gender,
-  #     urls = Sys.getenv("link_to_gender"),
-  #     paths = here::here("data", "raw", "names4api_tagged.tsv")),
-  # tarchetypes::tar_download(authors_arrow,
-  #     urls = Sys.getenv("link_to_updated_authors"),
-  #     paths = here::here("data", "raw", "authors_by_pubs.arrow")),
-  # tarchetypes::tar_download(text_arrow,
-  #     urls = Sys.getenv("link_to_updated_texts"),
-  #     paths = here::here("data", "raw", "riv_text.arrow")),
-  #  tarchetypes::tar_download(sup_control,
-  #     urls = Sys.getenv("link_to_supervisors_control"),
-  #     paths = here::here("data", "raw", "supervisors_control_final.csv")),
+  tarchetypes::tar_download(ids_path,
+      urls = Sys.getenv("link_to_supervisors"),
+      paths = here::here("data", "raw", "supervisors.csv")),
+  tarchetypes::tar_download(gender_path,
+      urls = Sys.getenv("link_to_gender"),
+      paths = here::here("data", "raw", "names4api_tagged.tsv")),
+  tarchetypes::tar_download(authors_arrow_path,
+      urls = Sys.getenv("link_to_updated_authors"),
+      paths = here::here("data", "raw", "authors_by_pubs.arrow")),
+  tarchetypes::tar_download(text_arrow_path,
+      urls = Sys.getenv("link_to_updated_texts"),
+      paths = here::here("data", "raw", "riv_text.arrow")),
+   tarchetypes::tar_download(sup_path,
+      urls = Sys.getenv("link_to_supervisors_control"),
+      paths = here::here("data", "raw", "supervisors_control_final.csv")),
 
-     tar_target(ids_path, here::here("data", "raw", "supervisors.csv"), format = "file"),
+     # tar_target(ids_path, here::here("data", "raw", "supervisors.csv"), format = "file"),
      tar_target(ids, read.csv2(ids_path)),
-     tar_target(gender_path, here::here("data", "raw", "names4api_tagged.tsv"), format = "file"),
+     # tar_target(gender_path, here::here("data", "raw", "names4api_tagged.tsv"), format = "file"),
      tar_target(gender, read.delim(gender_path)),
      tar_target(db_path, here::here("data", "raw", "czech_sci_db.sqlite")),
-     tar_target(authors_arrow_path, here::here("data", "raw", "authors_by_pubs.arrow")),
+     # tar_target(authors_arrow_path, here::here("data", "raw", "authors_by_pubs.arrow")),
      tar_target(authors_arrow, arrow::read_feather(authors_arrow_path)),
-     tar_target(text_arrow_path, here::here("data", "raw", "riv_text.arrow")),
+     # tar_target(text_arrow_path, here::here("data", "raw", "riv_text.arrow")),
      tar_target(text_arrow, arrow::read_feather(text_arrow_path)),
@@
       tar_target(matching, match(db_path, ids, gender, authors_arrow)),
-      tar_target(sup_path, here::here("data", "raw", "supervisors_control_final.csv"), format = "file"),
+      # tar_target(sup_path, here::here("data", "raw", "supervisors_control_final.csv"), format = "file"),
       tar_target(sup_control, read.csv2(sup_path)),

### 2023-06-09 article.Rmd
new updates

@@
 
-all <- r_before_final %>% filter(vedidk %in% a)
+all <- rbind(r_before_final, r_after_final) %>% filter(vedidk %in% a)
 
@@
 If we only keep observation that have match with non-missing values, we are left with a sample of `r final_before_control1` matched observations in unfunded control group and `r final_before_control2` matched observations in funded control group before intervention and a sample of `r final_after_control1` matched observations in unfunded control group and `r final_after_control2` matched observations in funded control group after intervention.
+
+### Before intervention
+
+```{r echo=FALSE}
+
+# assuming df is your dataframe
+df <- r_before_final
+
+# list of numeric columns. Exclude treatment column
+numeric_vars <- df %>% select(where(is.numeric)) %>% names()
+
+# descriptive stats for treatment level 0
+desc_0 <- df %>%
+  filter(treatment == 0) %>%
+  summarise(across(all_of(numeric_vars), list(mean = mean, sd = sd, min = min, max = max)))
+
+# descriptive stats for treatment level 1
+desc_1 <- df %>%
+  filter(treatment == 1) %>%
+  summarise(across(all_of(numeric_vars), list(mean = mean, sd = sd, min = min, max = max)))
+
+# descriptive stats for treatment level 2
+desc_2 <- df %>%
+  filter(treatment == 2) %>%
+  summarise(across(all_of(numeric_vars), list(mean = mean, sd = sd, min = min, max = max)))
+
+# Now you can print these as tables in your Rmd document
+
+# Print table for treatment level 0
+kable(desc_0, caption = "Descriptive statistics for treatment level 0")
+
+# Print table for treatment level 1
+kable(desc_1, caption = "Descriptive statistics for treatment level 1")
+
+# Print table for treatment level 2
+kable(desc_2, caption = "Descriptive statistics for treatment level 2")
+
+```
+
+### After intervention
+
+```{r echo=FALSE}
+d <- tar_read(full_indicator)
+na_counts <- sum(is.na(d$RII))
+
+```
 

### 2023-06-09 article.Rmd
new developments in article

--- 2023-06-08 article.Rmd
@@
 library(knitr)
+library(psych)
+library(kableExtra)
 ```
@@
 If we only keep observation that have match with non-missing values, we are left with a sample of `r final_before_control1` matched observations in unfunded control group and `r final_before_control2` matched observations in funded control group before intervention and a sample of `r final_after_control1` matched observations in unfunded control group and `r final_after_control2` matched observations in funded control group after intervention.
+
+### Before intervention
+
+```{r echo=FALSE}
+
+# assuming df is your dataframe
+df <- r_before_final
+
+# list of numeric columns. Exclude treatment column
+numeric_vars <- df %>% select(where(is.numeric)) %>% select(-weights, -funded_control, -id, -treatment_year, -career_start_year) %>% names()
+
+# descriptive stats for treatment level 1
+table_before_1 <- df %>% filter(treatment == 1) %>% select(all_of(numeric_vars)) %>% describe() %>% select(n, mean, sd, min, max) %>% round(., digits = 3)
+
+# Print table for treatment level 1
+kable(table_before_1, digits = 3, caption = "Descriptive statistics for treatment group") %>%
+  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
+
+# descriptive stats for treatment level 0
+table_before_0 <- df %>% filter(treatment == 0) %>% select(all_of(numeric_vars)) %>% describe() %>% select(n, mean, sd, min, max) %>% round(., digits = 3)
+
+# Print table for treatment level 0
+kable(table_before_0, digits = 3, caption = "Descriptive statistics for unfunded control group") %>%
+  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
+
+# descriptive stats for treatment level 2
+table_before_2 <- df %>% filter(treatment == 2) %>% select(all_of(numeric_vars)) %>% describe() %>% select(n, mean, sd, min, max) %>% round(., digits = 3)
+
+# Print table for treatment level 2
+kable(table_before_2, digits = 3, caption = "Descriptive statistics for funded control group") %>%
+  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
+
+```
+
+### After intervention
+
+```{r echo=FALSE}
+d <- tar_read(full_indicator)
+na_counts <- sum(is.na(d$RII))
+
+```
 

### 2023-06-09 _targets.Rmd
changes in tar_download

@@
       urls = Sys.getenv("link_to_updated_authors"),
-      paths = here::here("data", "raw", "authors_by_pubs.arrow")),
+      paths = here::here("data", "raw", "authors_by_pubs.arrow"),
+       mode = "wb"),
   tarchetypes::tar_download(text_arrow_path,
       urls = Sys.getenv("link_to_updated_texts"),
-      paths = here::here("data", "raw", "riv_text.arrow")),
+      paths = here::here("data", "raw", "riv_text.arrow"),
+      mode = "wb"),
    tarchetypes::tar_download(sup_path,

### 2023-06-09 article.Rmd
changes in tar_download

@@
 # Print table for treatment level 1
-kable(table_before_1, digits = 3, caption = "Descriptive statistics for treatment group") %>%
-  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
+kable(table_before_1, digits = 3, caption = "Descriptive statistics for treatment group") 
+  # %>% kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
 
@@
 kable(table_before_0, digits = 3, caption = "Descriptive statistics for unfunded control group") %>%
-  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
+  # kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
 
@@
 kable(table_before_2, digits = 3, caption = "Descriptive statistics for funded control group") %>%
-  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
+  # kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
 

### 2023-06-09 article.Rmd
visualisations added to article

--- 2023-06-09 article.Rmd
@@
 library(kableExtra)
+library(ggplot2)
 ```
@@
 d <- tar_read(full_indicator)
+d$disc_ford <- as.factor(d$disc_ford)
+
 na_counts <- sum(is.na(d$RII))
@@
 # Print table for treatment level 1
-kable(table_before_1, digits = 3, caption = "Descriptive statistics for treatment group") %>%
-  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
+kable(table_before_1, digits = 3, caption = "Descriptive statistics for treatment group") %>% kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
 
@@
 # Print table for treatment level 0
-kable(table_before_0, digits = 3, caption = "Descriptive statistics for unfunded control group") %>%
-  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
+kable(table_before_0, digits = 3, caption = "Descriptive statistics for unfunded control group") %>% kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
 
@@
 # Print table for treatment level 2
-kable(table_before_2, digits = 3, caption = "Descriptive statistics for funded control group") %>%
-  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
+kable(table_before_2, digits = 3, caption = "Descriptive statistics for funded control group") %>% kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
 
@@
 ```{r echo=FALSE}
-d <- tar_read(full_indicator)
-na_counts <- sum(is.na(d$RII))
+
+# assuming df is your dataframe
+df <- r_after_final
+
+# list of numeric columns. Exclude treatment column
+numeric_vars <- df %>% select(where(is.numeric)) %>% select(-weights, -funded_control, -id, -treatment_year, -career_start_year) %>% names()
+
+# descriptive stats for treatment level 1
+table_before_1 <- df %>% filter(treatment == 1) %>% select(all_of(numeric_vars)) %>% describe() %>% select(n, mean, sd, min, max) %>% round(., digits = 3)
+
+# Print table for treatment level 1
+kable(table_before_1, digits = 3, caption = "Descriptive statistics for treatment group") %>% kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
+
+# descriptive stats for treatment level 0
+table_before_0 <- df %>% filter(treatment == 0) %>% select(all_of(numeric_vars)) %>% describe() %>% select(n, mean, sd, min, max) %>% round(., digits = 3)
+
+# Print table for treatment level 0
+kable(table_before_0, digits = 3, caption = "Descriptive statistics for unfunded control group") %>% kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
+
+# descriptive stats for treatment level 2
+table_before_2 <- df %>% filter(treatment == 2) %>% select(all_of(numeric_vars)) %>% describe() %>% select(n, mean, sd, min, max) %>% round(., digits = 3)
+
+# Print table for treatment level 2
+kable(table_before_2, digits = 3, caption = "Descriptive statistics for funded control group") %>% kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
 
@@
 # Print tables in R Markdown
-knitr::kable(balance_stats_1, caption = "Balance Statistics: Treatment vs Control Group 1")
-knitr::kable(balance_stats_2, caption = "Balance Statistics: Treatment vs Control Group 2")
+knitr::kable(balance_stats_1, caption = "Balance Statistics: Treatment vs Control Group 1") %>% kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
+knitr::kable(balance_stats_2, caption = "Balance Statistics: Treatment vs Control Group 2") %>% kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
 
@@
 ## Main results
+
+### Before intervention
+
+Was there a difference between the treatment groups in their level of independence before the intervention?
+
+The analysis of variance (ANOVA) was used to compare the means of the three treatment groups.
+The results of the ANOVA showed that the effect of treatment was not statistically significant (F(2, 630) = 0.256, p = 0.613).
+The mean square (MS) within groups was 0.05775, which indicates that the variability within each group is relatively small.
+The MS between groups was 0.01476, which is smaller than the MS within groups, suggesting that the differences between the means of the treatment groups are small.
+The model explained only a small proportion of the total variance in the data (R-squared = 0.01).
+Sixty-five observations were deleted due to missing data.
+In conclusion, there is no evidence to suggest that the treatment has a significant effect on the outcome variable.
+However, the small effect size and the missing data should be taken into consideration when interpreting the results.
+Post-hoc test power was 0.9997622 as calculated by GPower (Faul, Erdfelder, Lang & Buchner, 2007).
+
+```{r echo=FALSE}
+set.seed(123)
+
+d_before <- r_before_final
+
+before_treatment <- aov(RII ~ treatment, data = d_before)
+summary(before_treatment)
+
+means_before_treatment <- aggregate(RII ~ treatment, data = d_before, FUN = mean)
+
+ggplot(data = means_before_treatment, aes(x = treatment, y = RII)) +
+         geom_bar(stat = "identity", position = "dodge") +
+         labs(x = "Treatment", y = "Mean RII") +
+         theme_bw()
+
+```
+
+Further, were there any differences in independence across disciplines?
+
+```{r echo=FALSE}
+set.seed(123)
+
+d_before$disc_ford <- substring(d_before$disc_ford, 0, 1)
+d_before$disc_ford <- as.factor(d_before$disc_ford)
+
+d_before$treatment <- as.factor(d_before$treatment)
+
+table(d_before$disc_ford, by = d_before$treatment)
+
+disc_before <- aov(RII ~ disc_ford, data = d_before)
+summary(disc_before)
+
+means_before_disc <- aggregate(RII ~ disc_ford, data = d_before, FUN = mean)
+
+ggplot(data = means_before_disc, aes(x = disc_ford, y = RII)) +
+         geom_bar(stat = "identity", position = "dodge") +
+         labs(x = "disc_ford", y = "Mean RII") +
+         theme_bw()
+
+```
+
+Was there any interaction between the treatment group and discipline?
+
+```{r echo=FALSE}
+set.seed(123)
+
+before_disc_interaction <- aov(RII ~ treatment*disc_ford, data = d_before)
+summary(before_disc_interaction)
+
+ means_before_disc_interaction <- aggregate(RII ~ treatment + disc_ford, data = d_before, FUN = mean)
+
+     # Plot grouped bar plot
+     ggplot(data = means_before_disc_interaction, aes(x = treatment, y = RII, fill = disc_ford)) +
+         geom_bar(stat = "identity", position = "dodge") +
+         labs(x = "Treatment", y = "Mean RII") +
+         scale_fill_discrete(name = "disc_ford") +
+         theme_bw()
+
+```
+
+### After intervention
+
+Was there a difference between the treatment groups in their level of independence after the intervention?
+
+The analysis of variance (ANOVA) was used to compare the means of the three treatment groups.
+The results of the ANOVA showed that the effect of treatment was not statistically significant (F(2, 630) = 0.256, p = 0.613).
+The mean square (MS) within groups was 0.05775, which indicates that the variability within each group is relatively small.
+The MS between groups was 0.01476, which is smaller than the MS within groups, suggesting that the differences between the means of the treatment groups are small.
+The model explained only a small proportion of the total variance in the data (R-squared = 0.01).
+Sixty-five observations were deleted due to missing data.
+In conclusion, there is no evidence to suggest that the treatment has a significant effect on the outcome variable.
+However, the small effect size and the missing data should be taken into consideration when interpreting the results.
+Post-hoc test power was 0.9997622 as calculated by GPower (Faul, Erdfelder, Lang & Buchner, 2007).
+
+```{r echo=FALSE}
+set.seed(123)
+
+d_before <- r_after_final
+
+before_treatment <- aov(RII ~ treatment, data = d_before)
+summary(before_treatment)
+
+means_before_treatment <- aggregate(RII ~ treatment, data = d_before, FUN = mean)
+
+ggplot(data = means_before_treatment, aes(x = treatment, y = RII)) +
+         geom_bar(stat = "identity", position = "dodge") +
+         labs(x = "Treatment", y = "Mean RII") +
+         theme_bw()
+
+```
+
+Further, were there any differences in independence across disciplines?
+
+```{r echo=FALSE}
+set.seed(123)
+
+d_before$disc_ford <- substring(d_before$disc_ford, 0, 1)
+d_before$disc_ford <- as.factor(d_before$disc_ford)
+
+d_before$treatment <- as.factor(d_before$treatment)
+
+table(d_before$disc_ford, by = d_before$treatment)
+
+disc_before <- aov(RII ~ disc_ford, data = d_before)
+summary(disc_before)
+
+means_before_disc <- aggregate(RII ~ disc_ford, data = d_before, FUN = mean)
+
+ggplot(data = means_before_disc, aes(x = disc_ford, y = RII)) +
+         geom_bar(stat = "identity", position = "dodge") +
+         labs(x = "disc_ford", y = "Mean RII") +
+         theme_bw()
+
+```
+
+Was there any interaction between the treatment group and discipline?
+
+```{r echo=FALSE}
+set.seed(123)
+
+before_disc_interaction <- aov(RII ~ treatment*disc_ford, data = d_before)
+summary(before_disc_interaction)
+
+ means_before_disc_interaction <- aggregate(RII ~ treatment + disc_ford, data = d_before, FUN = mean)
+
+     # Plot grouped bar plot
+     ggplot(data = means_before_disc_interaction, aes(x = treatment, y = RII, fill = disc_ford)) +
+         geom_bar(stat = "identity", position = "dodge") +
+         labs(x = "Treatment", y = "Mean RII") +
+         scale_fill_discrete(name = "disc_ford") +
+         theme_bw()
+
+```
+
+### Intervention effect
+
+```{r echo=FALSE}
+
+d <- all 
+d$treatment <- as.factor(d$treatment)
+d$independence_timing <- as.factor(d$independence_timing)
+
+interaction <- aov(RII ~ treatment * independence_timing, data = d)
+summary(interaction)
+heplots::etasq(interaction, anova = TRUE)
+
+ ###calculating r-squared - generated by chatGPT, so not sure this is correct
+
+     n <- nrow(d)
+     p <- length(coef(interaction))
+     SSresid <- sum(resid(interaction)^2)
+     SStotal <- sum((na.omit(d$RII) - mean(d$RII, na.rm = TRUE))^2)
+     R2 <- 1 - (SSresid / SStotal)
+     adjR2 <- 1 - ((1 - R2) * (n - 1) / (n - p - 1))
+
+ ### visualisations
+
+means <- aggregate(RII ~ treatment + independence_timing, data = d, FUN = mean)
+
+ ggplot(data = interaction, aes(x = treatment, y = RII, fill = independence_timing)) +
+         geom_violin(scale = "width") +
+         scale_fill_discrete(name = "Independence Timing", labels = c("After intervention", "Before intervention")) +
+         xlab("Treatment Group") +
+         ylab("RII Score") +
+         ggtitle("Violin Plot of RII Scores by Treatment and Time") +
+         theme_bw()
+
+```
 

### 2023-06-09 article.Rmd
small changes

@@
 library(targets)
+library(tidyr)
 library(dplyr)
@@
 d <- tar_read(full_indicator)
+d$disc_ford <- substring(d$disc_ford, 0, 1)
 d$disc_ford <- as.factor(d$disc_ford)
@@
 If we only keep observation that have match with non-missing values, we are left with a sample of `r final_before_control1` matched observations in unfunded control group and `r final_before_control2` matched observations in funded control group before intervention and a sample of `r final_after_control1` matched observations in unfunded control group and `r final_after_control2` matched observations in funded control group after intervention.
+
+When Looking at disciplines, we see that there are slightly more missing data in the discipline group 1 (Natural Sciences).
+
+```{r echo=FALSE}
+
+dt <- d
+dt$missing <- ifelse(is.na(dt$RII), "Missing", "Complete")
+
+# Calculate counts and proportions
+df_summary <- dt %>%
+  group_by(disc_ford, missing) %>%
+  summarise(count = n(), .groups = "drop") %>%
+  mutate(Proportion = count / sum(count)) %>%
+  pivot_wider(names_from = missing, values_from = c(count, Proportion))
+
+# Calculate Missing / (Missing + Complete) in percentages for each disc_ford
+df_summary <- df_summary %>%
+  mutate(Proportion = ifelse(!is.na(`count_Missing`) & !is.na(`count_Complete`), `count_Missing` / (`count_Missing` + `count_Complete`) * 100, NA))
+
+# If there are any NA values in the 'Proportion' column, replace them with 0
+df_summary[is.na(df_summary$Proportion)] <- 0
+
+# Remove unnecessary columns and rename the others
+df_summary <- df_summary %>%
+  select(disc_ford, count_Complete, count_Missing, Proportion) %>%
+  rename(
+    Complete = count_Complete,
+    Missing = count_Missing,
+    Proportion_Missing = Proportion
+  )
+
+# Print the updated table
+kable(df_summary, digits = 3, caption = "Counts and Proportions of Missing data by disc_ford") %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
+
+```
 
@@
 
-ggplot(data = means_before_treatment, aes(x = treatment, y = RII)) +
+ggplot(data = means_before_treatment, aes(x = treatment, y = RII, fill = treatment)) +
          geom_bar(stat = "identity", position = "dodge") +
          labs(x = "Treatment", y = "Mean RII") +
+         scale_fill_discrete(name = "treatment") +
          theme_bw()
@@
 
-ggplot(data = means_before_disc, aes(x = disc_ford, y = RII)) +
+ggplot(data = means_before_disc, aes(x = disc_ford, y = RII, fill = disc_ford)) +
          geom_bar(stat = "identity", position = "dodge") +
          labs(x = "disc_ford", y = "Mean RII") +
+         scale_fill_discrete(name = "disc_ford") +
          theme_bw()

### 2023-07-25 _targets.Rmd
new data pipeline for matching + updated parts of database

--- 2023-06-09 _targets.Rmd
@@
                             "arrow",
-                            "tarchetypes"
+                            "tarchetypes",
+                            "cobalt"
                             ))
@@
       urls = Sys.getenv("link_to_updated_authors"),
-      paths = here::here("data", "raw", "authors_by_pubs.arrow")),
+      paths = here::here("data", "raw", "authors_by_pubs.arrow"),
+       mode = "wb"),
   tarchetypes::tar_download(text_arrow_path,
       urls = Sys.getenv("link_to_updated_texts"),
-      paths = here::here("data", "raw", "riv_text.arrow")),
+      paths = here::here("data", "raw", "riv_text.arrow"),
+      mode = "wb"),
+  tarchetypes::tar_download(cep_investigators_path,
+      urls = Sys.getenv("link_to_cep_investigators"),
+      paths = here::here("data", "raw", "cep_investigators.arrow"),
+       mode = "wb"),
+  tarchetypes::tar_download(cep_details_path,
+      urls = Sys.getenv("link_to_cep_details"),
+      paths = here::here("data", "raw", "cep_details.arrow"),
+       mode = "wb"),
+  tarchetypes::tar_download(riv_details_path,
+      urls = Sys.getenv("link_to_riv_details"),
+      paths = here::here("data", "raw", "riv_details.arrow"),
+       mode = "wb"),
+  tarchetypes::tar_download(riv_authors_path,
+      urls = Sys.getenv("link_to_riv_authors"),
+      paths = here::here("data", "raw", "riv_authors.arrow"),
+       mode = "wb"),
    tarchetypes::tar_download(sup_path,
@@
      tar_target(text_arrow, arrow::read_feather(text_arrow_path)),
+     tar_target(cep_investigators_arrow, arrow::read_feather(cep_investigators_path)),
+     tar_target(cep_details_arrow, arrow::read_feather(cep_details_path)),
+     tar_target(riv_details_arrow, arrow::read_feather(riv_details_path)),
+     tar_target(riv_authors_arrow, arrow::read_feather(riv_authors_path)),
      tar_target(ids_complete, create_ids_complete(ids, db_path)),
@@
 
-      tar_target(matching, match(db_path, ids, gender, authors_arrow)),
+      tar_target(matching_data, match_data_prep(db_path, ids, gender, authors_arrow, cep_investigators_arrow, cep_details_arrow, riv_details_arrow, riv_authors_arrow)),
+      tar_target(matched_obj_unfunded, match_obj_unfunded(matching_data)), 
+      tar_target(matched_obj_funded, match_obj_funded(db_path, authors_arrow, matching_data)),
+      tar_target(matching, match_data(matched_obj_unfunded, matched_obj_funded)),
       # tar_target(sup_path, here::here("data", "raw", "supervisors_control_final.csv"), format = "file"),

### 2023-07-25 article.Rmd
new data pipeline for matching + updated parts of database

@@
 author: "David Janků"
+date: "`r Sys.Date()`"
 output: html_document
+bibliography: researcher_independence.bib
+csl: apa.csl
 ---
@@
 However, such indicator could be misleading in the world of team science, and also only focuses on collaborations, not tracking whether given researcher become independent in their thinking and research topics.
-Van den Besselaar & Sandström (2019) therefore proposed more complex indicator for measuring researcher independence on the individual level, based on co-authorship network and topical overlaps.
+[@vandenbesselaarMeasuringResearcherIndependence2019] therefore proposed more complex indicator for measuring researcher independence on the individual level, based on co-authorship network and topical overlaps.
 Their measure uses only information about publications’ characteristics (authorship and reference list) regardless of it’s impacts, unlike other alternative measures that focus solely on the impact of the independent work in terms of received citations (Dey, et al., 2021).
@@
 ```{r echo=FALSE}
-# Create a subset for treatment group and control group 1
-subset_1 <- (tar_read(matching)) %>% filter(treatment != 2)
-subset_2 <- (tar_read(matching)) %>% filter(treatment != 0)
+# # Create a subset for treatment group and control group 1
+# subset_1 <- (tar_read(matching)) %>% filter(treatment != 2)
+# subset_2 <- (tar_read(matching)) %>% filter(treatment != 0)
+# 
+# # Generate balance table for treatment vs control group 1
+# balance_results_1 <- bal.tab(treatment ~ career_lenght + pubs_total + ws_pubs + interdisc_proportion + grants + gender, data = subset_1, disp = c("mean", "std"))
+# balance_results_2 <- bal.tab(treatment ~ career_lenght + pubs_total + ws_pubs + interdisc_proportion + grants + gender, data = subset_2, disp = c("mean", "std"))
+# 
+# # Define a function to manually extract balance statistics from bal.tab object
+# extract_balance_stats <- function(bal_results) {
+#   covariates <- rownames(bal_results$Balance)
+#   means_treat <- bal_results$Balance$`M.1.Un`
+#   means_ctrl <- bal_results$Balance$`M.0.Un`
+#   diff <- bal_results$Balance$`Diff.Un`
+#   
+#   data.frame(Covariate = covariates, 
+#              Mean_Treatment = means_treat, 
+#              Mean_Control = means_ctrl, 
+#              Diff = diff)
+# }
+# 
+# # Extract balance stats for subset_1 and subset_2
+# balance_stats_1 <- extract_balance_stats(balance_results_1)
+# balance_stats_2 <- extract_balance_stats(balance_results_2)
+# 
+# # Print tables in R Markdown
+# knitr::kable(balance_stats_1, caption = "Balance Statistics: Treatment vs Control Group 1") %>% kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
+# knitr::kable(balance_stats_2, caption = "Balance Statistics: Treatment vs Control Group 2") %>% kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
 
-# Generate balance table for treatment vs control group 1
-balance_results_1 <- bal.tab(treatment ~ career_lenght + pubs_total + ws_pubs + interdisc_proportion + grants + gender, data = subset_1, disp = c("mean", "std"))
-balance_results_2 <- bal.tab(treatment ~ career_lenght + pubs_total + ws_pubs + interdisc_proportion + grants + gender, data = subset_2, disp = c("mean", "std"))
+unf_sum <- summary(matched_obj_unfunded, un = FALSE)
 
-# Define a function to manually extract balance statistics from bal.tab object
-extract_balance_stats <- function(bal_results) {
-  covariates <- rownames(bal_results$Balance)
-  means_treat <- bal_results$Balance$`M.1.Un`
-  means_ctrl <- bal_results$Balance$`M.0.Un`
-  diff <- bal_results$Balance$`Diff.Un`
+summary(matched_obj_unfunded)
 
-  data.frame(Covariate = covariates, 
-             Mean_Treatment = means_treat, 
-             Mean_Control = means_ctrl, 
-             Diff = diff)
-}
+plot(unf_sum, var.order = "unmatched")
 
-# Extract balance stats for subset_1 and subset_2
-balance_stats_1 <- extract_balance_stats(balance_results_1)
-balance_stats_2 <- extract_balance_stats(balance_results_2)
+cobalt::bal.tab(matched_obj_unfunded, un = FALSE, stats = c("m", "v", "ks"), binary = "std")
 
-# Print tables in R Markdown
-knitr::kable(balance_stats_1, caption = "Balance Statistics: Treatment vs Control Group 1") %>% kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
-knitr::kable(balance_stats_2, caption = "Balance Statistics: Treatment vs Control Group 2") %>% kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
+cobalt::love.plot(matched_obj_unfunded, binary = "std", var.order = "unmatched")
+
+fun_sum <- summary(matched_obj_funded, un = FALSE)
+
+summary(matched_obj_funded)
+
+plot(fun_sum, var.order = "unmatched")
 
@@
 Further, we have conducted analysis on an independent sample of researchers from Slovenia (citace Luzar??), and found that  when we filter out all researchers who have not had any publication 4 years prior to their PhD defense (1135, approx 9,5% of the sample), we see that from the remaining researchers, about 50,3 % had their supervisor as the most frequent coauthor in the 4 years prior to their PhD defense.
+
+# References

### 2023-07-25 R/match_obj_unfunded.R

@@ -1,0 +1,18 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param db_path
+#' @param ids
+#' @return
+#' @author fatal: unable to access 'C:/Users/David Jank?/Documents/.config/git/config': Invalid argument
+#' @export
+match_obj_unfunded <- function(matching_data) {
+
+   
+    
+    out_final <- matchit(treatment~length+pubs_total+ws_pubs+interdisc_proportion+grants+gender, method="nearest", data=matching_data, distance = "mahalanobis", ratio = 1, exact = c("disc_ford", "treatment_year"), replace = TRUE)
+    
+   
+}

### 2023-07-25 R/read_all_authors.R

@@ -30,7 +30,7 @@ new <-  matching %>%
                                        } ))
 
 
-new <- new() %>%
+new <- new %>%
     mutate(pubs_number = purrr::map_int(pub_table, function(df) {
         if (is.data.frame(df) && nrow(df) > 0) {
             return(length(unique(df$id_unique)))
@@ -39,12 +39,16 @@ new <- new() %>%
         }
     }))
 
+
+ 
 # w <- plyr::count(all_authors$pubs_number)
 # plot(w)
 
-new <- all_authors %>% filter(pubs_number >= 3)
+ new <- new %>% filter(pubs_number >= 3)
 
 # wq <- plyr::count(new$pubs_number)
 # plot(wq)
+ 
+ new
 
     }

### 2023-07-25 R/refine_data.R

@@ -65,7 +65,7 @@ refine_data <- function(matching, db_path, ids_complete, sup_control, authors_ar
    #  # # table(d$treatment, by =d$independence_timing)
    #  
     
-    new2 <- matching[1,] %>% 
+    new2 <- matching %>% 
         filter(treatment != 1) %>% 
         dplyr::select(vedidk) %>% 
         distinct() %>% 
@@ -81,12 +81,16 @@ refine_data <- function(matching, db_path, ids_complete, sup_control, authors_ar
     
     ids_complete_sup <- ids_complete %>% dplyr::select(vedidk, sup_name, sup_vedidk)
     
-    new_unnested <- rbind(new_unnested, ids_complete_sup)
+    new_unnested <- bind_rows(new_unnested, ids_complete_sup)
     
     a_final_data <- left_join(matching, new_unnested, by = "vedidk") %>% 
         filter(!is.na(sup_name))
     
-    b <- a_final_data %>% filter(!vedidk %in% vedidk_treatment) %>% filter(treatment == 1)
+    b <- a_final_data %>% 
+        group_by(subclass) %>%
+        filter(n() == 1) %>%
+        ungroup() %>%
+        filter(treatment == 1)
     d <- anti_join(a_final_data, b, by = "vedidk")
     # table(d$treatment, by =d$independence_timing)
     
@@ -94,6 +98,6 @@ refine_data <- function(matching, db_path, ids_complete, sup_control, authors_ar
     aa <- anti_join(matching, d, by = "vedidk")
     bb <- left_join(aa, d)
 
-    cc <- rbind(d, bb)
+    cc <- bind_rows(d, bb)
     
 }

### 2023-07-25 _targets.Rmd
final adjustements, added number of coauthors to the matching data

@@
                             "tarchetypes",
-                            "cobalt"
+                            "cobalt",
+                            "furrr"
                             ))

### 2023-07-25 article.Rmd
final adjustements, added number of coauthors to the matching data

@@
 
-However, we have made some changes to the indicator.
-After consulting with its authors, we have changed the aggregation formula to RII = ((1- I1) + I2 + I3 + I4) / 4, since the previous formula had a small error (it weighted I4 double,, i.e.
+However, we have made some changes to the indicator. After consulting with its authors, we have changed the aggregation formula to 
+$$RII = ((1- I1) + I2 + I3 + I4) / 4$$, since the previous formula had a small error (it weighted I4 double,, i.e.
 2*I4).
@@
 Throughout this paper, we will thus refer to the original indicator as RIIo, our adjusted version as RIIa and the part of the indicator measuring only the cognitive independence RIIc.
+
+---> popsat víc jak počítám topic model??
 
@@
 
-We used ??? table ??? to estimate the gender of each researcher.
+We used Genderize.io API to estimate the probability of perceived gender based on the first names of researchers.
+Where available, information about the nationality of researchers was included in the API call to improve accuracy.
 
@@
 year when the given researcher from experimental group received the Junior Grant).
-We set caliper to 0.2 standard deviations of the logit of the propensity score by recommendation of Rosenbaum and Rubin (1985b) and Austin (2011) to remove the cases where the distance between experimental and control group observation was too large.
-__This removed XXXX cases from the experimental group, leaving us with YYY matched observations__.
+The distance was set to "mahalanobis".
 The matching was done in 1:1 ratio and with replacement.
@@
 
+After matching, all standardized mean differences for the covariates were below 0.1 and all standardized mean differences for squares and two-way interactions between covariates were below .15, indicating adequate balance.
+__This removed XXXX cases from the experimental group, leaving us with YYY matched observations__.
+
 ```{r echo=FALSE}
@@
 
-unf_sum <- summary(matched_obj_unfunded, un = FALSE)
+unf_sum <- summary(tar_read(matched_obj_unfunded), un = TRUE)
 
-summary(matched_obj_unfunded)
+summary(tar_read(matched_obj_unfunded))
 
@@
 
-cobalt::bal.tab(matched_obj_unfunded, un = FALSE, stats = c("m", "v", "ks"), binary = "std")
+cobalt::bal.tab(tar_read(matched_obj_unfunded), un = FALSE, stats = c("m", "v", "ks"), binary = "std")
 
-cobalt::love.plot(matched_obj_unfunded, binary = "std", var.order = "unmatched")
+cobalt::love.plot(tar_read(matched_obj_unfunded), binary = "std", var.order = "adjusted")
 
-fun_sum <- summary(matched_obj_funded, un = FALSE)
+fun_sum <- summary(tar_read(matched_obj_funded), un = TRUE)
 
-summary(matched_obj_funded)
+summary(tar_read(matched_obj_funded))
 
@@
 ## Main results
+
+To estimate the treatment effect and its standard error, we fit a linear regression model with 1978 earnings as the outcome and the treatment, covariates, and their interaction as predictors and included the full matching weights in the estimation.
+The lm() function was used to fit the outcome, and the comparisons() function in the marginaleffects package was used to perform g-computation in the matched sample to estimate the ATT.
+A cluster-robust variance was used to estimate its standard error with matching stratum membership as the clustering variable.
+
+The estimated effect was XXXX (SE = XXXX, p = XXXX), indicating that the average effect of the treatment for those who received it is to increase earnings.
+
+```{r echo=FALSE}
+
+# Run regression model with interaction term
+did_model <- plm(researcher_independence ~ independence_timing * treatment + factor(subclass), 
+                 data = tar_read(full_indicator), 
+                 index = c("subclass", "independence_timing"),
+                 model = "within")
+
+# Calculate clustered standard errors
+clustered_se <- coeftest(did_model, vcov = function(x) vcovHC(x, type = "HC1", cluster = "group"))
+print(clustered_se)
+
+```
 

### 2023-07-25 R/match_data.R

@@ -43,7 +43,7 @@ match_data <- function(matched_obj_unfunded, matched_obj_funded) {
     
     full_data_1 <- rbind2(matched_data_unfunded, matched_data_funded)
     
-    #doubling data so we can calculate indepedence indicator independently from the pubs before the intevention and after the intervention
+    #doubling data so we can calculate independence indicator independently from the pubs before the intevention and after the intervention
     full_data_2 <- full_data_1 
     full_data_2$independence_timing <- "before_intervention"
     full_data_1$independence_timing <- "after_intervention"

### 2023-07-25 R/match_obj_unfunded.R

@@ -12,7 +12,7 @@ match_obj_unfunded <- function(matching_data) {
 
    
     
-    out_final <- matchit(treatment~length+pubs_total+ws_pubs+interdisc_proportion+grants+gender, method="nearest", data=matching_data, distance = "mahalanobis", ratio = 1, exact = c("disc_ford", "treatment_year"), replace = TRUE)
+    out_final <- matchit(treatment~length+pubs_total+ws_pubs+interdisc_proportion+grants+gender+total_coauthor_count, method="nearest", data=matching_data, distance = "mahalanobis", ratio = 1, exact = c("disc_ford", "treatment_year"), replace = TRUE)
     
    
 }

### 2023-07-25 R/read_all_authors.R

@@ -23,7 +23,7 @@ matching <- as_tibble(final_data)
 
 new <-  matching %>% 
         dplyr::select(id, vedidk, treatment_year, independence_timing, sup_name, sup_vedidk) %>% 
-        mutate(pub_table = purrr::pmap(.l = list(vedidk, treatment_year, independence_timing),
+        mutate(pub_table = furrr::future_pmap(.l = list(vedidk, treatment_year, independence_timing),
                                        .f = function(first, second, third){
                                            read_one_author(db_path, ids_complete_vector, ids_complete, matching, authors_arrow,
                                                                  ids_full_vector = first, intervention_year = second, timing = third)

### 2023-08-16 article.Rmd
updated database + added manually searched data for supervisors

@@
 date: "`r Sys.Date()`"
-output: html_document
+output:
+  html_document: default
+  word_document: default
 bibliography: researcher_independence.bib
@@
 Where available, information about the nationality of researchers was included in the API call to improve accuracy.
+We have also manually specified gender for 2 obrsevtation from the treatment group for which the gender was not calculated automatically.
 
@@
 
-For the construction of the control group, we implemented propensity matching using the package MatchIt (citation?) and matching exactly by the discipline (42 sub-categories of OECD classification), and approximately by number of publications in total, number of publications in WoS/Scopus, career age, interdisciplinary proportion, number of grants received prior to Junior Grant, career age when receiving the first grant and gender.
+For the construction of the control group, we implemented propensity matching using the package MatchIt (citation?) and matching exactly by the discipline (42 sub-categories of OECD classification) and treatment year, and approximately by number of publications in total, number of publications in WoS/Scopus, career age, interdisciplinary proportion, number of grants received prior to Junior Grant, career age when receiving the first grant and gender.
 All of these variables were calculated at the intervention year (i.e.
@@
 The distance was set to "mahalanobis".
-The matching was done in 1:1 ratio and with replacement.
+The matching was done in 1:3 ratio and with replacement.
+Manual search for supervisors of the matched control group observations was done by ranking the control group observation by distance from the treatment group observation and first searching for the supervisor of the closest control group observation, and if it was not possible to find it, then repeat the same for the second closest, etc...
+In the end each treatment observation was matched with exactly one control group observation which was closest but at the same time for which it was possible to identify their supervisor.
 
@@
 
+```{r echo=FALSE}
+
+removed_treatment_unfunded <- (tar_read(ids_complete) %>% distinct(vedidk) %>% nrow())-(tar_read(matching) %>% group_by(subclass) %>% filter(!any(treatment == 2)) %>%
+  ungroup() %>% filter(treatment == "1") %>% distinct(vedidk) %>% nrow())
+
+removed_treatment_funded <- (tar_read(ids_complete) %>% distinct(vedidk) %>% nrow())-(tar_read(matching) %>% group_by(subclass) %>% filter(!any(treatment == 0)) %>%
+  ungroup() %>% filter(treatment == "1") %>% distinct(vedidk) %>% nrow())
+
+unique_treatment_unfunded <- d %>% group_by(subclass) %>% filter(!any(treatment == 2)) %>% ungroup() %>% filter(treatment == "1") %>% distinct(vedidk) %>% nrow()
+
+unique_treatment_funded <- d %>% group_by(subclass) %>% filter(!any(treatment == 0)) %>%
+  ungroup() %>% filter(treatment == "1") %>% distinct(vedidk) %>% nrow()
+
+unique_control_unfunded <- d %>% filter(treatment == 0) %>% distinct(vedidk) %>% nrow()
+
+unique_control_funded <- d %>% filter(treatment == 2) %>% distinct(vedidk) %>% nrow()
+
+replaced_control_unfunded <- unique_treatment_unfunded-unique_control_unfunded
+
+replaced_control_funded <- unique_treatment_funded-unique_control_funded
+
+overlap_control <- unique_control_unfunded+unique_control_funded-(d %>% filter(treatment != 1) %>% distinct(vedidk) %>% nrow())
+
+```
+
 After matching, all standardized mean differences for the covariates were below 0.1 and all standardized mean differences for squares and two-way interactions between covariates were below .15, indicating adequate balance.
-__This removed XXXX cases from the experimental group, leaving us with YYY matched observations__.
+
+Matching process removed `r removed_treatment_unfunded` treatment observations from matching with unfunded control group and `r removed_treatment_funded` treatment observations from matching with funded control group.
+This observation was removed because the researchers had no publications prior to the year of application for the grant, which would make it not possible to calculate the independence score for them anyway.
+
+The resulting sample had `r unique_treatment_unfunded` unique treatment group observations paired with `r unique_control_unfunded` unique unfunded control group observations suggesting that `r replaced_control_unfunded` observations from unfunded control group were matched to multiple treatment group observations.
+Similarly, there were `r unique_treatment_funded` unique treatment group observations paired with `r unique_control_funded` unique funded control group observations, suggesting that `r replaced_control_funded` funded control group observations were matched to multiple treatment group observations.
+
+BTW: there is an overlap between control group observations - `r overlap_control` observations from the unfunded control group also appears in the funded control group
 
@@
 
-# Run regression model with interaction term
-did_model <- plm(researcher_independence ~ independence_timing * treatment + factor(subclass), 
-                 data = tar_read(full_indicator), 
-                 index = c("subclass", "independence_timing"),
-                 model = "within")
-
-# Calculate clustered standard errors
-clustered_se <- coeftest(did_model, vcov = function(x) vcovHC(x, type = "HC1", cluster = "group"))
-print(clustered_se)
+# # Run regression model with interaction term
+# did_model <- plm(researcher_independence ~ independence_timing * treatment + factor(subclass), 
+#                  data = tar_read(full_indicator), 
+#                  index = c("subclass", "independence_timing"),
+#                  model = "within")
+# 
+# # Calculate clustered standard errors
+# clustered_se <- coeftest(did_model, vcov = function(x) vcovHC(x, type = "HC1", cluster = "group"))
+# print(clustered_se)
 

### 2023-08-16 R/calc_ind_topics.R

@@ -7,11 +7,10 @@
 #' @return
 #' @author fatal: unable to access 'C:/Users/David Jank?/Documents/.config/git/config': Invalid argument
 #' @export
-calc_ind_topics <- function(topic_model, db_path, authors_arrow, one_author, sup_vedidk) {
+calc_ind_topics <- function(topic_model, db_path, one_author, sup_vedidk) {
 
-    authors_arrow <- as.data.frame(authors_arrow)
+    
     con <-  DBI::dbConnect(RSQLite::SQLite(), db_path)
-    dbWriteTable(con, "authors_by_pubs", authors_arrow, overwrite = TRUE)
     on.exit(DBI::dbDisconnect(con))
     
     

### 2023-08-16 R/make_ids_complete_vector.R

@@ -8,12 +8,12 @@
 #' @author fatal: unable to access 'C:/Users/David Jank?/Documents/.config/git/config': Invalid argument
 #' @export
 make_ids_complete_vector <- function(ids_complete) {
-
-  ids_complete_vector <- ids_complete$vedidk %>% 
-        as_tibble() %>% 
-        as_vector() %>% 
-        as_tibble() %>% #from here below it was added - I should check that it does change any further results 
-        distinct() %>% #here
-        as_vector()  #here
-
+    
+    
+  ids_complete_vector <- ids_complete %>% 
+        dplyr::select(vedidk) %>% 
+        as_tibble() %>%
+        distinct() %>% 
+        as_vector()
+        
 }

### 2023-08-16 R/manual_sup_search.R

@@ -1,0 +1,205 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param db_path
+#' @param ids
+#' @return
+#' @author fatal: unable to access 'C:/Users/David Jank?/Documents/.config/git/config': Invalid argument
+#' @export
+manual_sup_search <- function(db_path, matching) {
+    
+    
+    con <-  DBI::dbConnect(RSQLite::SQLite(), db_path)
+    on.exit(DBI::dbDisconnect(con))
+
+
+
+manual_sup_search <- matching %>% filter(treatment != 1) %>% dplyr::select(vedidk, disc_ford) %>% distinct()
+
+all_auth <- dplyr::tbl(con, "authors_by_pubs") %>% 
+    dplyr::collect() %>% 
+    as_tibble()
+
+
+age_pubs <- dplyr::tbl(con, "riv_disc") %>% 
+    dplyr::select(id_unique, year) %>% 
+    distinct() %>% 
+    as_tibble()
+
+age_data <- left_join(age_pubs, all_auth, by = "id_unique") %>% 
+    distinct() 
+
+career_start <- age_data %>% 
+    group_by(vedidk) %>% 
+    slice(which.min(year)) %>% 
+    ungroup() 
+
+manual_sup_search <- left_join(manual_sup_search, career_start %>% dplyr::select(vedidk, name_first, name_last, org_name), by = "vedidk")
+
+manual_sup_search <- manual_sup_search %>% 
+    mutate(theses =
+               paste0("https://theses.cz/vyhledavani/?search=",
+                      name_first, "+", name_last, "+disertační+práce"))
+    
+
+manual_sup_search <- manual_sup_search %>% 
+    mutate(dspace_cuni =
+               paste0("https://dspace.cuni.cz/discover?filtertype_1=author&filter_relational_operator_1=contains&filter_1=",
+                      name_last, "%2C+", name_first))
+
+
+manual_sup_search <- manual_sup_search %>% 
+    mutate(google =
+               paste0("https://www.google.com/search?q=",
+                      name_first, "+", name_last, "+disertační+práce"))
+
+
+
+sup_control <- read.csv2(here::here("data", "raw", "supervisors_control_final.csv")) 
[…]

### 2023-08-16 R/match_data_prep.R

@@ -8,22 +8,12 @@
 #' @return
 #' @author fatal: unable to access 'C:/Users/David Jank?/Documents/.config/git/config': Invalid argument
 #' @export
-match_data_prep <- function(db_path, ids, gender, authors_arrow, cep_investigators_arrow, cep_details_arrow, riv_details_arrow, riv_authors_arrow) {
+match_data_prep <- function(db_path, ids, gender, sup_control) {
 
-    authors_arrow <- as.data.frame(authors_arrow)
-    cep_investigators_arrow <- as.data.frame(cep_investigators_arrow)
-    cep_details_arrow <- as.data.frame(cep_details_arrow)
-    riv_details_arrow <- as.data.frame(riv_details_arrow)
-    riv_authors_arrow <- as.data.frame(riv_authors_arrow)
+    
     con <-  DBI::dbConnect(RSQLite::SQLite(), db_path)
-    dbWriteTable(con, "authors_by_pubs", authors_arrow, overwrite = TRUE)
-    dbWriteTable(con, "cep_investigators", cep_investigators_arrow, overwrite = TRUE)
-    dbWriteTable(con, "cep_details", cep_details_arrow, overwrite = TRUE)
-    dbWriteTable(con, "riv_disc", riv_details_arrow, overwrite = TRUE)
-    dbWriteTable(con, "riv_authors", riv_authors_arrow, overwrite = TRUE)
     on.exit(DBI::dbDisconnect(con))
     
-    DBI::dbListTables(con)
     
     # setting up the set of all authors
     
@@ -260,7 +250,7 @@ match_data_prep <- function(db_path, ids, gender, authors_arrow, cep_investigato
     
     
     disciplines2014 <- discipline_data %>% 
-        dplyr::select(disc_ford, vedidk, year) %>% 
+        dplyr::select(disc_ford, field, vedidk, year) %>% 
         filter(!is.na(disc_ford)) %>% 
         filter(year < 2014) %>% 
         group_by(vedidk) %>% 
@@ -389,7 +379,7 @@ match_data_prep <- function(db_path, ids, gender, authors_arrow, cep_investigato
     treatment_group <- left_join(treatment_group, nationality)
     
     ids_with_sup <- as_tibble(ids) %>% 
-        filter(!is.na(sup_vedidk)) %>%
+        filter(!is.na(sup_name_first)) %>%
         filter(!is.na(vedidk_core_researcher))
     
[…]

### 2023-08-16 R/match_obj_funded.R

@@ -8,14 +8,12 @@
 #' @return
 #' @author fatal: unable to access 'C:/Users/David Jank?/Documents/.config/git/config': Invalid argument
 #' @export
-match_obj_funded <- function(db_path, authors_arrow, matching_data) {
+match_obj_funded <- function(db_path, matching_data) {
 
-    authors_arrow <- as.data.frame(authors_arrow)
+
     con <-  DBI::dbConnect(RSQLite::SQLite(), db_path)
-    dbWriteTable(con, "authors_by_pubs", authors_arrow, overwrite = TRUE)
     on.exit(DBI::dbDisconnect(con))
     
-    DBI::dbListTables(con)
     
     # setting up the set of all authors
     
@@ -121,7 +119,7 @@ match_obj_funded <- function(db_path, authors_arrow, matching_data) {
     
     
     
-    out_funded <- matchit(treatment~length+pubs_total+ws_pubs+interdisc_proportion+grants+first_grant+gender+total_coauthor_count, method="nearest", data=final_data_funded, distance = "mahalanobis", ratio = 1, exact = c("disc_ford", "treatment_year"), replace = TRUE)
+    matched_obj_funded <- matchit(treatment~length+pubs_total+ws_pubs+interdisc_proportion+grants+first_grant+gender+total_coauthor_count, method="nearest", data=final_data_funded, distance = "mahalanobis", ratio = 1, exact = c("disc_ford", "treatment_year"), replace = TRUE)
     
    
    

### 2023-08-16 R/match_obj_unfunded.R

@@ -12,7 +12,7 @@ match_obj_unfunded <- function(matching_data) {
 
    
     
-    out_final <- matchit(treatment~length+pubs_total+ws_pubs+interdisc_proportion+grants+gender+total_coauthor_count, method="nearest", data=matching_data, distance = "mahalanobis", ratio = 1, exact = c("disc_ford", "treatment_year"), replace = TRUE)
+    matched_obj_unfunded <- matchit(treatment~length+pubs_total+ws_pubs+interdisc_proportion+grants+gender+total_coauthor_count, method="nearest", data=matching_data, distance = "mahalanobis", ratio = 1, exact = c("disc_ford", "treatment_year"), replace = TRUE)
     
    
 }

### 2023-08-22 _targets.Rmd

--- 2023-06-09 _targets.Rmd
@@
                             "arrow",
-                            "tarchetypes"
+                            "tarchetypes",
+                            "cobalt",
+                            "furrr"
                             ))
@@
       mode = "wb"),
+  tarchetypes::tar_download(cep_investigators_path,
+      urls = Sys.getenv("link_to_cep_investigators"),
+      paths = here::here("data", "raw", "cep_investigators.arrow"),
+       mode = "wb"),
+  tarchetypes::tar_download(cep_details_path,
+      urls = Sys.getenv("link_to_cep_details"),
+      paths = here::here("data", "raw", "cep_details.arrow"),
+       mode = "wb"),
+  tarchetypes::tar_download(riv_details_path,
+      urls = Sys.getenv("link_to_riv_details"),
+      paths = here::here("data", "raw", "riv_details.arrow"),
+       mode = "wb"),
+  tarchetypes::tar_download(riv_authors_path,
+      urls = Sys.getenv("link_to_riv_authors"),
+      paths = here::here("data", "raw", "riv_authors.arrow"),
+       mode = "wb"),
    tarchetypes::tar_download(sup_path,
-      urls = Sys.getenv("link_to_supervisors_control"),
-      paths = here::here("data", "raw", "supervisors_control_final.csv")),
+      urls = Sys.getenv("link_to_manual_sup_search"),
+      paths = here::here("data", "raw", "manual_sup_search.csv")),
+  tarchetypes::tar_download(sup_path_second,
+      urls = Sys.getenv("link_to_manual_sup_search_second"),
+      paths = here::here("data", "raw", "manual_sup_search_second.csv")),
 
-     # tar_target(ids_path, here::here("data", "raw", "supervisors.csv"), format = "file"),
+     # tar_target(ids_path, here::here("data", "raw", "supervisors_updated.csv"), format = "file"),
      tar_target(ids, read.csv2(ids_path)),
@@
      tar_target(gender, read.delim(gender_path)),
-     tar_target(db_path, here::here("data", "raw", "czech_sci_db.sqlite")),
-     # tar_target(authors_arrow_path, here::here("data", "raw", "authors_by_pubs.arrow")),
      tar_target(authors_arrow, arrow::read_feather(authors_arrow_path)),
-     # tar_target(text_arrow_path, here::here("data", "raw", "riv_text.arrow")),
      tar_target(text_arrow, arrow::read_feather(text_arrow_path)),
-     tar_target(ids_complete, create_ids_complete(ids, db_path)),
-     tar_target(ids_complete_vector, make_ids_complete_vector(ids_complete))
+     tar_target(cep_investigators_arrow, arrow::read_feather(cep_investigators_path)),
+     tar_target(cep_details_arrow, arrow::read_feather(cep_details_path)),
+     tar_target(riv_details_arrow, arrow::read_feather(riv_details_path)),
+     tar_target(riv_authors_arrow, arrow::read_feather(riv_authors_path)),
+     tar_target(name = db_path, 
+                command = transcribe_database(path = here::here("data",
+                                                                "raw",
+                                                                "czech_sci_db.sqlite"),
+                                              authors_arrow, 
+                                              cep_investigators_arrow,   
+                                              cep_details_arrow, 
+                                              riv_details_arrow, 
+                                              riv_authors_arrow,
+                                              text_arrow),
+                format = "file"
+                )
 
@@
 
-      tar_target(matching, match(db_path, ids, gender, authors_arrow)),
-      # tar_target(sup_path, here::here("data", "raw", "supervisors_control_final.csv"), format = "file"),
+     # tar_target(sup_path, here::here("data", "raw", "manual_sup_search.csv"), format = "file"),
       tar_target(sup_control, read.csv2(sup_path)),
 
-     # tar_target(sup_control, read.csv2(here::here("data", "raw", "supervisors_control.csv")),
-     #          format = "qs"),
-      tar_target(final_data, refine_data(matching, db_path, ids_complete, sup_control, authors_arrow)),
+      tar_target(matching_data, match_data_prep(db_path, ids, gender, sup_control)),
+      tar_target(matched_obj_unfunded, match_obj_unfunded(matching_data)), 
+      tar_target(matched_obj_funded, match_obj_funded(db_path, matching_data)),
+      tar_target(matching, match_data(matched_obj_unfunded, matched_obj_funded)),
+
+       # tar_target(sup_path_second, here::here("data", "raw", "manual_sup_search_second.csv"), format = "file"),
+      tar_target(sup_control_second, read.csv2(sup_path_second)),
+      tar_target(sup_complete, create_sup_complete(sup_control, sup_control_second, db_path, matching_data)),
+     tar_target(ids_complete, create_ids_complete(ids, db_path, matching_data)),
+     tar_target(ids_complete_vector, make_ids_complete_vector(ids_complete)),
+
+      tar_target(final_data, connect_data(matching, db_path, ids_complete, sup_complete)),
 
@@
      tar_target(all_pubs,
-           get_all_pubs(db_path, final_data, authors_arrow, text_arrow)),
+           get_all_pubs(db_path, final_data)),
     tar_target(all_authors,
-           read_all_authors(db_path, ids_complete_vector, ids_complete, final_data, ids_full_vector, authors_arrow)),
+           read_all_authors(db_path, ids_complete_vector, ids_complete, final_data, ids_full_vector)),
      tar_target(random_pubs,
-           get_random_pubs(db_path, authors_arrow, text_arrow))
+           get_random_pubs(db_path))
 )
@@
     tar_target(independent_topics,
-                comp_ind_topics(independent_pubs, topic_model, db_path, authors_arrow))
+                comp_ind_topics(independent_pubs, topic_model, db_path))
 )

### 2023-08-24 _targets.Rmd
updated pipeline

@@
      # tar_target(sup_path, here::here("data", "raw", "manual_sup_search.csv"), format = "file"),
-      tar_target(sup_control, read.csv2(sup_path)),
+      tar_target(sup_control, read.csv(sup_path)),
 
@@
        # tar_target(sup_path_second, here::here("data", "raw", "manual_sup_search_second.csv"), format = "file"),
-      tar_target(sup_control_second, read.csv2(sup_path_second)),
+      tar_target(sup_control_second, read.csv(sup_path_second)),
       tar_target(sup_complete, create_sup_complete(sup_control, sup_control_second, db_path, matching_data)),

### 2023-08-24 article.Rmd
updated pipeline

@@
 d <- tar_read(full_indicator)
-d$disc_ford <- substring(d$disc_ford, 0, 1)
 d$disc_ford <- as.factor(d$disc_ford)
@@
 na_sup <- round((sum(is.na(d$sup_name))/na_counts)*100, 1)
-na_pubs <- round((nrow(d %>% filter(!is.na(sup_name)) %>% filter(pub_table_empty == TRUE))/na_counts)*100, 1)
+na_pubs <- round((nrow(d %>% filter(!is.na(sup_name)) %>% filter(is.na(pubs_number)))/na_counts)*100, 1)
 
-na_pubs_after <- round((nrow(d %>% filter(!is.na(sup_name)) %>% filter(pub_table_empty == TRUE) %>% filter(independence_timing == "after_intervention"))/nrow(d %>% filter(!is.na(sup_name)) %>% filter(pub_table_empty == TRUE)))*100, 1)
+na_pubs_after <- round((nrow(d %>% filter(!is.na(sup_name)) %>% filter(is.na(pubs_number)) %>% filter(independence_timing == "after_intervention"))/nrow(d %>% filter(!is.na(sup_name)) %>% filter(is.na(pubs_number))))*100, 1)
 

### 2023-08-24 R/calc_full_indicator.R

@@ -50,7 +50,7 @@ calc_full_indicator <- function(independent_topics, final_data) {
     # independent_topics$id <- seq_along(independent_topics$vedidk)
     
     
-    d <- left_join(final_data, independent_topics)
+    d <- left_join(final_data, independent_topics, by = c("vedidk" = "vedidk", "treatment_year" = "treatment_year" , "independence_timing" = "independence_timing"))
     
     
     d$treatment <- as_factor(d$treatment)

### 2023-08-24 R/calc_ind_pubs.R

@@ -43,7 +43,7 @@ calc_ind_pubs <- function(one_author, sup_name) {
         filter(id_helper == c) %>% 
         select(id_unique)
     
-    ind_pubs <- anti_join(all_pubs_author, sup_pubs)
+    ind_pubs <- anti_join(all_pubs_author, sup_pubs, by = "id_unique")
        
     rpubs = nrow(ind_pubs)/nrow(all_pubs_author)
     

### 2023-08-24 R/calc_ind_topics.R

@@ -35,7 +35,16 @@ calc_ind_topics <- function(topic_model, db_path, one_author, sup_vedidk) {
     
     all_pubs_author$id_unique <- as.character(all_pubs_author$id_unique)
     
-    author_pubs_topics <- as_tibble(cbind(id_unique = names(topic_model), t(topic_model))) 
+    # author_pubs_topics <- as_tibble(cbind(id_unique = names(topic_model), t(topic_model))) 
+    
+    author_pubs_topics <- 
+        tibble::enframe(names(topic_model), name = NULL, value = "id_unique") |> 
+        bind_cols(
+            as_tibble(
+                t(topic_model),
+                .name_repair = function(x) paste0("topic_", seq_along(x))
+            )
+        )
        
     author_pubs_tp <- semi_join(author_pubs_topics, all_pubs_author, by = "id_unique") 
 
@@ -62,9 +71,7 @@ calc_ind_topics <- function(topic_model, db_path, one_author, sup_vedidk) {
             
     sup_vedidk <- sup_vedidk
     
-    con <-  DBI::dbConnect(RSQLite::SQLite(), db_path)
-    on.exit(DBI::dbDisconnect(con))
-    
+   
     sup_pubids <- dplyr::tbl(con, "authors_by_pubs") %>% #colnames()
         filter(vedidk == sup_vedidk) %>% 
         select(id_unique) %>% 
@@ -97,9 +104,14 @@ calc_ind_topics <- function(topic_model, db_path, one_author, sup_vedidk) {
     topic_model$sup_topic <- tidyr::replace_na(topic_model$sup_topic, 0)
     topic_model$author_topic <- tidyr::replace_na(topic_model$author_topic, 0)
     
+    
+    DBI::dbDisconnect(con)
+    
     topic_independence_categories = sum(ifelse(topic_model$author_topic>topic_model$sup_topic, 1, 0))/(sum(topic_model$author_topic))
     
     # table <- tibble(vedidk = vedidk_researcher, ind_topics = topic_independence_categories)
+    
+    
     
     
     # #alternativni zpusob vypoctu

### 2023-08-24 R/comp_ind_topics.R

@@ -12,7 +12,7 @@ comp_ind_topics <- function(independent_pubs, topic_model, db_path) {
 
 
 independent_topics <-  independent_pubs %>% 
-                        mutate(ind_topics = purrr::pmap(.l = list(pub_table, sup_vedidk),
+                        mutate(ind_topics = furrr::future_pmap(.l = list(pub_table, sup_vedidk),
                                    .f = function(first, second){
                                        calc_ind_topics(topic_model, db_path,
                                                        one_author = first, sup_vedidk = second)

### 2023-08-24 R/manual_sup_search.R

@@ -57,12 +57,12 @@ manual_sup_search <- manual_sup_search %>%
 
 
 
-sup_control <- read.csv2(here::here("data", "raw", "supervisors_control_final.csv")) 
-sup_control <- sup_control %>% filter(!is.na(sup_vedidk)) %>% dplyr::select(vedidk, sup_name_first, sup_name_last, sup_vedidk, sec_sup_name_first, sec_sup_name_last, sec_sup_vedidk)
-sup_control$vedidk <- as.character(sup_control$vedidk)
+sup_control2 <- read.csv2(here::here("data", "raw", "supervisors_control_final.csv")) 
+sup_control2 <- sup_control2 %>% filter(!is.na(sup_vedidk)) %>% dplyr::select(vedidk, sup_name_first, sup_name_last, sup_vedidk, sec_sup_name_first, sec_sup_name_last, sec_sup_vedidk)
+sup_control2$vedidk <- as.character(sup_control2$vedidk)
 
 
-manual_sup_search <- left_join(manual_sup_search, sup_control, by = "vedidk")
+manual_sup_search <- left_join(manual_sup_search, sup_control2, by = "vedidk")
 
 
 extra_search_sup <- anti_join(manual_sup_search, sup_control, by = "vedidk")
@@ -103,103 +103,87 @@ extra_search_sup_second <- anti_join(extra_search_sup, sup_complete, by = "vedid
 
 
 
+## extra ids search
 
-# kteří superrvisors neměli se svými studenty ani jednu publikaci? -- na ty se podívát více do hloubky
+ids_complete <- ids_complete %>% filter(!is.na(sup_name)) %>%  dplyr::select(vedidk)
 
-sup_vedidk <- dplyr::tbl(con, "authors_by_pubs") %>% 
-    dplyr::select(name_first, name_last, id_helper, vedidk) %>% 
+ids <- ids %>% mutate(across(everything(), ~replace(., . == "", NA))) %>% filter(!is.na(vedidk_core_researcher))
+
+ids$vedidk_core_researcher <- as.character(ids$vedidk_core_researcher)
+
+ids_in <- anti_join(ids, ids_complete, by = c("vedidk_core_researcher" = "vedidk")) %>% filter(statni.prislusnost == "CZ") %>% dplyr::select(vedidk_core_researcher) %>% rename(vedidk = vedidk_core_researcher) %>% distinct()
+
+con <-  DBI::dbConnect(RSQLite::SQLite(), db_path)
[…]

### 2023-08-24 R/match_data_prep.R

@@ -379,6 +379,7 @@ match_data_prep <- function(db_path, ids, gender, sup_control) {
     treatment_group <- left_join(treatment_group, nationality)
     
     ids_with_sup <- as_tibble(ids) %>% 
+        mutate(across(everything(), ~replace(., . == "", NA))) %>% 
         filter(!is.na(sup_name_first)) %>%
         filter(!is.na(vedidk_core_researcher))
     

### 2023-08-28 _targets.Rmd
added description of the code

@@
 
+Here we import all the data we work with. Data are stored on a cloud from where we download it.
+
 ```{r, engine="targets", data_import}
@@
                 format = "file"
-                )
+                ),
+     tar_target(sup_control, read.csv(sup_path)),
+     tar_target(sup_control_second, read.csv(sup_path_second))
 
@@
 
-# Matching and data preparation
+# Matching
 
-```{r, engine="targets", matching_preparation}
+Here we perform construction of control groups via mahalanobis distance matching.
+There are 2 control groups: funded, and unfunded, which have separate matching procedures, but later are combined into one dataset (target "matching") so it is easier to work with.
+
+```{r, engine="targets", matching}
 list(
-
-     # tar_target(sup_path, here::here("data", "raw", "manual_sup_search.csv"), format = "file"),
-      tar_target(sup_control, read.csv(sup_path)),
 
@@
       tar_target(matched_obj_funded, match_obj_funded(db_path, matching_data)),
-      tar_target(matching, match_data(matched_obj_unfunded, matched_obj_funded)),
+      tar_target(matching, match_data(matched_obj_unfunded, matched_obj_funded))
 
-       # tar_target(sup_path_second, here::here("data", "raw", "manual_sup_search_second.csv"), format = "file"),
-      tar_target(sup_control_second, read.csv(sup_path_second)),
+)
+```
+
+# Data preparation
+
+Here we perform author disambiguation of the manually collected names of supervisors ("sup_complete", "ids_complete") and combine these into final dataset including list of publications for each observation (in the target "all_authors").
+
+Further, we prepare the data for the construction of topic models in the targets "all_pubs" and "random_pubs".
+
+```{r, engine="targets", data_prep}
+list(
+
  tar_target(sup_complete, create_sup_complete(sup_control, sup_control_second, db_path, matching_data)),
      tar_target(ids_complete, create_ids_complete(ids, db_path, matching_data)),
-     tar_target(ids_complete_vector, make_ids_complete_vector(ids_complete)),
-
       tar_target(final_data, connect_data(matching, db_path, ids_complete, sup_complete)),
 
-     #at this point, I will need to manually search for the supervisors of the control group researchers and upload their vedidks into new ids file
-     tar_target(ids_full_vector,
-               make_ids_full_vector(matching)),
+      tar_target(all_authors,
+           read_all_authors(db_path, ids_complete, final_data)),
+
      tar_target(all_pubs,
            get_all_pubs(db_path, final_data)),
-    tar_target(all_authors,
-           read_all_authors(db_path, ids_complete_vector, ids_complete, final_data, ids_full_vector)),
      tar_target(random_pubs,
            get_random_pubs(db_path))
+
 )
@@
 # Topic model
+
+Here we construct a smaller topic model based on the randomly selected 1200 publications ("topic_model_original") from the full database of all Czech publications.
+Then we take all publications of the researchers in our sample (both treatment group and control groups, target "topic_model_input_addition") and match it onto the existing topic model ("topic_model").
+This way we limit the endogeneity of the topic model, compared to if we calculated the topic model based only on the publications of our sample researchers.
 
@@
 
+Here we construct coauthorship network for each observation in our sample, which is a precursor from which 2 parts of the independence indicator are calculated.
+
 ```{r, engine="targets", network}
@@
 
+Here we calculate first part of the independence indicator: eigenvector centrality of the PhD supervisors in the author's network.
+
 ```{r, engine="targets", RII1}
@@
 # Researcher independence indicator (RII) part 2 - clustering coefficient
+
+Here we calculate second part of the independence indicator: clustering coefficient of the PhD supervisors in the author's network.
 
@@
 
+Here we calculate third part of the independence indicator: ratio of publications without coauthorship with the author's PhD supervisor.
+
 ```{r, engine="targets", RII3}
@@
 
+Here we calculate fourth part of the independence indicator: ratio of topics that the author publishes on that their PhD supervisor does not publish on.
+
 ```{r, engine="targets", RII4}
@@
 
-# Researcher independence indicator (RII) part 4 - independent topics: alternative way via cosine similarity
+# Final indicator
 
-```{r, engine="targets", RII4_2}
-
-list(
-
-    # tar_target(ind_topics_cs,
-    #            calc_cos_sim(topic_model, two_authors), 
-    #            format = "qs")
-    # 
-)
-
-```
-
-# Final indicator
+Here we construct the final independence indicator using the parts calculated above.
 
@@
 ```
+
 # Article
+
+Here is the paper presenting results. It also contains code for figures, hypothesis testing, etc..
 
@@
 ```
-
-etc... rinse and repeat

### 2023-08-28 R/read_all_authors.R

@@ -11,8 +11,7 @@
 #' @return
 #' @author fatal: unable to access 'C:/Users/David Jank?/Documents/.config/git/config': Invalid argument
 #' @export
-read_all_authors <- function(db_path, ids_complete_vector, ids_complete,
-                             final_data, ids_full_vector) {
+read_all_authors <- function(db_path, ids_complete, final_data) {
 
 final_data <- final_data %>% 
      filter(!is.na(sup_name))
@@ -26,7 +25,7 @@ new <-  matching %>%
         distinct() %>% 
         mutate(pub_table = furrr::future_pmap(.l = list(vedidk, treatment_year, independence_timing),
                                        .f = function(first, second, third){
-                                           read_one_author(db_path, ids_complete_vector, ids_complete, matching,
+                                           read_one_author(db_path, ids_complete, matching,
                                                                  ids_full_vector = first, intervention_year = second, timing = third)
                                        } ))
 

### 2023-09-01 article.Rmd
edited results and discussion sections (though not finished yet)

@@
 library(ggplot2)
+library(lme4)
+library(lmerTest)
+library(MuMIn)
+library(ez)
+library(plm)
+
 ```
@@
 
-s <- d %>% filter(is.na(RII))
-
-f_after <- d %>% filter(!is.na(RII)) %>% filter(independence_timing == "after_intervention") 
-f_before <- d %>% filter(!is.na(RII)) %>% filter(independence_timing == "before_intervention")
-
-v_after <- c(f_after$vedidk[f_after$treatment == 1 ], NA)
-v_before <- c(f_before$vedidk[f_before$treatment == 1 ], NA)
-
-r_after <- f_after %>% filter(vedidk_treatment %in% v_after)
-r_before <- f_before %>% filter(vedidk_treatment %in% v_before)
-
-v_after_control <- c(r_after$vedidk[r_after$treatment != 1 ], r_after$vedidk_treatment)
-v_before_control <- c(r_before$vedidk[r_before$treatment != 1 ], r_before$vedidk_treatment)
-
-r_after_final <- r_after %>% filter(vedidk %in% v_after_control)
-r_before_final <- r_before %>% filter(vedidk %in% v_before_control)
+# s <- d %>% filter(is.na(RII))
+#                   
+# f_after <- d %>% filter(!is.na(RII)) %>% filter(independence_timing == "after_intervention") 
+# f_before <- d %>% filter(!is.na(RII)) %>% filter(independence_timing == "before_intervention") 
+# 
+# 
+# v_after <- c(f_after$vedidk[f_after$treatment == 1 ], NA)
+# v_before <- c(f_before$vedidk[f_before$treatment == 1 ], NA)
+# 
+# r_after <- f_after %>% filter(vedidk_treatment %in% v_after)
+# r_before <- f_before %>% filter(vedidk_treatment %in% v_before)
+# 
+# 
+# 
+# v_after_control <- c(r_after$vedidk[r_after$treatment != 1 ], r_after$vedidk_treatment)
+# v_before_control <- c(r_before$vedidk[r_before$treatment != 1 ], r_before$vedidk_treatment)
+# 
+# r_after_final <- r_after %>% filter(vedidk %in% v_after_control)
+# r_before_final <- r_before %>% filter(vedidk %in% v_before_control)
 
@@
 
-final_before_control1 <- nrow(r_before_final %>% filter(treatment == 0)) 
-final_before_control2 <- nrow(r_before_final %>% filter(treatment == 2))
+# final_before_control1 <- nrow(r_before_final %>% filter(treatment == 0)) 
+# final_before_control2 <- nrow(r_before_final %>% filter(treatment == 2))
+# 
+# 
+# final_after_control1 <- nrow(r_after_final %>% filter(treatment == 0)) 
+# final_after_control2 <- nrow(r_after_final %>% filter(treatment == 2))
 
-final_after_control1 <- nrow(r_after_final %>% filter(treatment == 0)) 
-final_after_control2 <- nrow(r_after_final %>% filter(treatment == 2))
+# a <- intersect(
+#     r_after_final$vedidk,
+#     r_before_final$vedidk
+# )
+# 
+# 
+# all <- rbind(r_before_final, r_after_final) %>% filter(vedidk %in% a)
 
-a <- intersect(
-    r_after_final$vedidk,
-    r_before_final$vedidk
-)
+filtered_by_subclass <- d %>%
+     group_by(subclass, independence_timing) %>%
+     filter(!any(is.na(RII))) %>%
+     ungroup()
 
-all <- rbind(r_before_final, r_after_final) %>% filter(vedidk %in% a)
+filtered_subclass <- nrow(filtered_by_subclass %>% distinct(subclass))
+subclass_all <- nrow(d %>% distinct(subclass))
+filtered_subclass_perc <- round((filtered_subclass/subclass_all)*100, 1)
+
+final_before_control1 <- nrow(filtered_by_subclass %>% filter(independence_timing == "before_intervention") %>% filter(treatment == 0))
+final_before_control2 <- nrow(filtered_by_subclass %>% filter(independence_timing == "before_intervention") %>% filter(treatment == 2))
+
+final_after_control1 <- nrow(filtered_by_subclass %>% filter(independence_timing == "after_intervention") %>% filter(treatment == 0))
+final_after_control2 <- nrow(filtered_by_subclass %>% filter(independence_timing == "after_intervention") %>% filter(treatment == 2))
 
@@
 There are `r na_treatment` missing observations in the treatment group, `r na_control1` in the unfunded control group and  `r na_control2` in the funded control group.
-If we only keep observation that have match with non-missing values, we are left with a sample of `r final_before_control1` matched observations in unfunded control group and `r final_before_control2` matched observations in funded control group before intervention and a sample of `r final_after_control1` matched observations in unfunded control group and `r final_after_control2` matched observations in funded control group after intervention.
+If we only keep observations that have a match with non-missing values, we are left with a sample of `r final_before_control1` matched observations in unfunded control group and `r final_before_control2` matched observations in funded control group before intervention and a sample of `r final_after_control1` matched observations in unfunded control group and `r final_after_control2` matched observations in funded control group after intervention.
 
-When Looking at disciplines, we see that there are slightly more missing data in the discipline group 1 (Natural Sciences).
+When Looking at disciplines, we see that there are slightly more missing data in Agricultural and veterinary scieces and the Humanities and the Arts.
 
@@
 df_summary <- dt %>%
-  group_by(disc_ford, missing) %>%
+  group_by(field, missing) %>%
   summarise(count = n(), .groups = "drop") %>%
@@
   pivot_wider(names_from = missing, values_from = c(count, Proportion))
+
+# If there are any NA values in the 'count_Missing' column, replace them with 0
+df_summary$count_Missing[is.na(df_summary$count_Missing)] <- 0
 
@@
 # If there are any NA values in the 'Proportion' column, replace them with 0
-df_summary[is.na(df_summary$Proportion)] <- 0
+df_summary$Proportion[is.na(df_summary$Proportion)] <- 0
 
@@
 df_summary <- df_summary %>%
-  select(disc_ford, count_Complete, count_Missing, Proportion) %>%
+  select(field, count_Complete, count_Missing, Proportion) %>%
   rename(
@@
 
+POZN: here we show data
+
 ```{r echo=FALSE}
@@
 # assuming df is your dataframe
-df <- r_before_final
+df <- filtered_by_subclass %>% filter(independence_timing == "before_intervention")
 
@@
 # assuming df is your dataframe
-df <- r_after_final
+df <- filtered_by_subclass %>% filter(independence_timing == "after_intervention")
 
@@
 
+To ascertain the differences in independence scores before and after intervention, while accounting for the treatment type, academic disciplines, and paired nature of the data, we used repeated measures ANOVA.
+This allowed us to measure the main effect of change in independence across time, across disciplines, and the main treatment effect was the interaction between treatment type and time.
+
+POZN: only for comparison:
 To estimate the treatment effect and its standard error, we fit a linear regression model with 1978 earnings as the outcome and the treatment, covariates, and their interaction as predictors and included the full matching weights in the estimation.
@@
 
+pp <- d %>%
+     group_by(subclass) %>%
+     filter(!any(is.na(RII))) %>%
+     ungroup()
+
+filtered_by_subclass_1 <- pp %>% 
+    group_by(subclass) %>% 
+    filter(!any(treatment == 2)) %>% 
+    ungroup()
+
+filtered_by_subclass_1$subclass <- as.factor(filtered_by_subclass_1$subclass)
+filtered_by_subclass_1$treatment <- as.factor(filtered_by_subclass_1$treatment)
+filtered_by_subclass_1$independence_timing <- as.factor(filtered_by_subclass_1$independence_timing)
+filtered_by_subclass_1$field <- as.factor(filtered_by_subclass_1$field)
+
+# this DiD model unfortunately doesnt work for some reason that I cannot resolve, but it is possible to calculate the same using repeated measures anova or mixes effects model, so it should be fine
+
 # # Run regression model with interaction term
-# did_model <- plm(researcher_independence ~ independence_timing * treatment + factor(subclass), 
-#                  data = tar_read(full_indicator), 
-#                  index = c("subclass", "independence_timing"),
+# did_model <- plm::plm(RII ~ independence_timing * treatment + factor(subclass),
+#                  data = filtered_by_subclass_1,
+#                  index = c("subclass"),
 #                  model = "within")
@@
 # # Calculate clustered standard errors
-# clustered_se <- coeftest(did_model, vcov = function(x) vcovHC(x, type = "HC1", cluster = "group"))
-# print(clustered_se)
+# clustered_se <- coeftest(did_model, vcov = function(x) vcovHC(x, type = "HC1", cluster = "subclass"))
+
+## here should be some assumptions tests that I will run to see whtehr it is correct, but later I will comment it so that it doesnt show in the final paper
+
+model <- lmer(RII ~ treatment * independence_timing + (1 | subclass), data = filtered_by_subclass_1)
+summary(model)
+r.squaredGLMM(model)
+
+result <- ezANOVA(data = filtered_by_subclass_1,
+                 dv = RII,
+                 wid = subclass,
+                 within = .(independence_timing),
+                 between = treatment)
+print(result)
+
+## adding disciplines:
+
+result_disc <- ezANOVA(data = filtered_by_subclass_1,
+                 dv = RII,
+                 wid = subclass,
+                 within = .(independence_timing),
+                 between = .(treatment, field))
+print(result_disc)
+
+### visualisations
+
+means <- aggregate(RII ~ treatment + independence_timing, data = filtered_by_subclass_1, FUN = mean)
+
+ ggplot(data = filtered_by_subclass_1, aes(x = treatment, y = RII, fill = independence_timing)) +
+         geom_violin(scale = "width") +
+         scale_fill_discrete(name = "Independence Timing", labels = c("Before intervention", "After intervention")) +
+         xlab("Treatment Group") +
+         ylab("RII Score") +
+         ggtitle("Violin Plot of RII Scores by Treatment and Time") +
+         theme_bw()
 
 ```
+
+In the first analysis, we examined the effects of treatment, independence_timing, and their interaction on the dependent variable, researcher independence (RII) for the treatment group and unfunded control group.
+There was a significant main effect of independence_timing on RII, F(1, 188) = 158.29, p < .001, indicating a significant change in the independence from before to after the intervention.
+The effect size (GES) for this effect was 0.075, suggesting a moderate effect.
+Importantly, there was a significant interaction effect between treatment and independence_timing on independence, F(1, 188) = 11.00, p = .001.
+This interaction suggests that the effect of the intervention on independence differed based on the treatment group.
+The effect size (GES) for this interaction was 0.006, indicating a small effect.
+
+In the subsequent analysis, we further incorporated the factor of discipline (field) to explore if there were differences across disciplines in the observed effects.
+There was a significant main effect of field on independence, F(5, 178) = 2.88, p = .016, indicating that there were significant differences in RII across the six discipline groups.
+(WHICH ARE LOW AND HIGH?) The effect size (GES) for this was 0.068, suggesting a moderate effect.
+The interaction between treatment and field was not statistically significant, F(5, 178) = 0.29, p = .920, suggesting that the effect of treatment on independence was consistent across disciplines.
+The three-way interaction among treatment, independence_timing, and field was not statistically significant, F(5, 178) = 0.51, p = .765.
+This implies that the interaction effect of treatment and independence_timing on independence remained consistent across different disciplines.
+
+POZN ON MODEL CHOICE:
+
+In Conclusion:
+
+Both the mixed-effects model and the RM-ANOVA suggest a significant interaction between the treatment and the timing of the intervention.
+This means that the effect of the intervention differed between the treatment and control groups.
+
+Both methods also indicate that the timing of the intervention (i.e., whether it's before or after) has a significant effect on the outcome RII.
+
+The models are in agreement with their primary findings, which is a good sign.
+It suggests that the treatment has a distinct effect on RII after the intervention, different from that of the control group.
+
+However, it's worth noting that while the methods reach similar conclusions, they approach the problem from different angles.
+The mixed-effects model incorporates the correlation within each subclass through its random effect, while the RM-ANOVA primarily focuses on the repeated measures nature of the data.
+Both models provide valuable insights, but the mixed-effects model might be a more robust choice for this particular dataset, given its explicit modeling of the subclass structure.
+
+My take:
+
+I understand the results of ANOVa, but dont understand the results of the mixed effects model very much. I also like that ANOVa actually provides p statistic and effect size statistic
+
+```{r echo=FALSE}
+
+filtered_by_subclass_2 <- pp %>% 
+    group_by(subclass) %>% 
+    filter(!any(treatment == 0)) %>% 
+    ungroup()
+
+filtered_by_subclass_2$subclass <- as.factor(filtered_by_subclass_2$subclass)
+filtered_by_subclass_2$treatment <- as.factor(filtered_by_subclass_2$treatment)
+filtered_by_subclass_2$independence_timing <- as.factor(filtered_by_subclass_2$independence_timing)
+filtered_by_subclass_2$field <- as.factor(filtered_by_subclass_2$field)
+
+# this DiD model unfortunately doesnt work for some reason that I cannot resolve, but it is possible to calculate the same using repeated measures anova or mixes effects model, so it should be fine
+#---> maybe if I edit the dataset so that there is only one row for each observation and it has columns RII_before and RII_after?
+------or alternatively I can also just calculate the difference directly RII_diff = after-before and then test only this difference?
+Not sure how much of a difference this would make -> I should perhaps ask chatGPT
+
+# # Run regression model with interaction term
+# did_model <- plm::plm(RII ~ independence_timing * treatment + factor(subclass),
+#                  data = filtered_by_subclass_1,
+#                  index = c("subclass"),
+#                  model = "within")
+# 
+# # Calculate clustered standard errors
+# clustered_se <- coeftest(did_model, vcov = function(x) vcovHC(x, type = "HC1", cluster = "subclass"))
+
+model2 <- lmer(RII ~ treatment * independence_timing + (1 | subclass), data = filtered_by_subclass_2)
+summary(model2)
+r.squaredGLMM(model2)
+
+result <- ezANOVA(data = filtered_by_subclass_2,
+                 dv = RII,
+                 wid = subclass,
+                 within = .(independence_timing),
+                 between = treatment)
+print(result)
+
+## adding disciplines:
+
+result_disc2 <- ezANOVA(data = filtered_by_subclass_2,
+                 dv = RII,
+                 wid = subclass,
+                 within = .(independence_timing),
+                 between = .(treatment, field))
+print(result_disc2)
+
+### visualisations
+
+means2 <- aggregate(RII ~ treatment + independence_timing, data = filtered_by_subclass_2, FUN = mean)
+
+ ggplot(data = filtered_by_subclass_2, aes(x = treatment, y = RII, fill = independence_timing)) +
+         geom_violin(scale = "width") +
+         scale_fill_discrete(name = "Independence Timing", labels = c("Before intervention", "After intervention")) +
+         xlab("Treatment Group") +
+         ylab("RII Score") +
+         ggtitle("Violin Plot of RII Scores by Treatment and Time") +
+         theme_bw()
+
+```
+
+In the second analysis, we examined the effects of treatment, independence_timing, and their interaction on the researcher independence (RII) for the treatment group and funded control group.
+Again, there was a significant main effect of time on independence (F(1, 224) = 177.37, p < 0.001), with moderate effect size (GES = 0.0938371139).
+Importantly, this time the interaction effect between treatment and time  was not significant (F(1, 224) = 0.968, p = 0.326), suggesting that funding has the same effects, regardless of its type or source.
+
+When adding disciplines into the analysis, we again found that there is a variation in independence across disciplines (WHICH ARE LOW AND HIGH?) (F(5, 214) = 3.218, p = 0.008), with a moderate effect size (GES = 0.0613437626).
+Anyway, these differences were again stable across time and treatment conditions as the interaction were not significant.
 
@@
 
+The results of this study provide important insights into the effects of funding interventions on researcher independence.
+The strongest effect we found across all control group comparison was the effect of time - over time, researchers become more independent, regardless of their access to funding or their discipline.
+The effect size for this difference is moderate (GES = 0.075) when comparing funded and unfunded groups, and moderate (GES = 0.075) when comparing the funded treatment and funded control groups.
+
+Additionally, the observed variation in independence across different disciplines underscores the importance of considering disciplinary differences, suggested by a moderate effect size (GES = 0.068).
+A moderate effect size (GES = 0.068) for the field effect emphasizes that certain disciplines might inherently have variations in RII, perhaps due to differences in practices, methodologies, or norms specific to each discipline.
+Anyway, these differences remain constant across time and funding interventions, suggesting that funding has a uniform effect on the independence across disciplines.
+
+Finally, the significant interaction between treatment and time when comparing treamtnet vs unfunded group suggests the funding has positive effect on stimulating researchers' independence.
+However, the effect size is only modest (GES = 0.006), indicating relatively small practical relevance.
+Further the insignificant interaction when comparing the treatment vs funded control group suggests that funding in this career stage has the same effect, regardless of its type or source.
+
 ## Limitations
 
---> the identification of supervisors in the control group (only 50% correct)
 --> only talks about the Czech environment and considers researchers growing up and most of their careers in the Czech republic

### 2023-09-01 R/calc_full_indicator.R

@@ -50,7 +50,7 @@ calc_full_indicator <- function(independent_topics, final_data) {
     # independent_topics$id <- seq_along(independent_topics$vedidk)
     
     
-    d <- left_join(final_data, independent_topics, by = c("vedidk" = "vedidk", "treatment_year" = "treatment_year" , "independence_timing" = "independence_timing"))
+    d <- left_join(final_data, independent_topics, by = c("vedidk" = "vedidk", "treatment_year" = "treatment_year" , "independence_timing" = "independence_timing", "sup_name" = "sup_name", "sup_vedidk" = "sup_vedidk"))
     
     
     d$treatment <- as_factor(d$treatment)

### 2023-09-05 _targets.Rmd
uploaded new data and finalized analyses in article

@@
 
-      tar_target(matching_data, match_data_prep(db_path, ids, gender, sup_control)),
+      tar_target(matching_data, match_data_prep(db_path, ids, gender, sup_control, sup_control_second)),
       tar_target(matched_obj_unfunded, match_obj_unfunded(matching_data)), 

### 2023-09-05 article.Rmd
uploaded new data and finalized analyses in article

@@
 
+##checking assumptiosn fro repeated measures ANOVA
+
+# Normality: You can check the normality of the residuals using a Q-Q plot and the Shapiro-Wilk test.
+
+model_lm <- lm(RII ~ treatment + subclass + subclass:independence_timing, data = filtered_by_subclass_1)
+
+# Check residuals from lm
+plot(resid(model_lm))
+
+#Linearity and Homoscedasticity (Equal Variances) of Residuals: If the assumptions hold, you should not see any obvious patterns or funnel shapes in the plot.
+
+plot(model_lm$fitted.values, resid(model_lm), 
+     xlab = "Fitted values", ylab = "Residuals", 
+     main = "Residuals vs. Fitted Values")
+abline(h = 0, col = "red")
+
+# Normality of Residuals: 
+qqnorm(resid(model_lm))
+qqline(resid(model_lm))
+
+shapiro.test(resid(model_lm))
+
+# Independence of Residuals: If your data has a time sequence (e.g., repeated measurements over time), then you would be concerned about the independence of residuals.
+For this, you can use the Durbin-Watson test from the car package.
+The Durbin-Watson test statistic ranges from 0 to 4.
+A value around 2 suggests no autocorrelation, while values below 1 and above 3 are cause for concern.
+
+library(car)
+durbinWatsonTest(model_lm)
+
+# Multicollinearity: Check the variance inflation factor (VIF) for each predictor. Typically, a VIF above 5-10 indicates multicollinearity.
+
+vif(model_lm)
+
+# Outliers and Influence Points: Leverage vs. studentized residuals plot can be used to identify influential points.
+
+plot(hatvalues(model_lm), rstudent(model_lm),
+     xlab = "Leverage", ylab = "Studentized Residuals",
+     main = "Residuals vs. Leverage")
+abline(h = c(-2,2), col = "red", lty = 2)
+
+# Sphericity: Use the mauchly.test function on your model. If the test is significant, then the assumption of sphericity has been violated.
+
+# mauchly.test(model_aov)
+
+# Homogeneity of Variance: Use Levene's Test. The car package offers leveneTest.
+
+library(car)
+leveneTest(RII ~ treatment, data = filtered_by_subclass_1)
+
+# Outliers:You can inspect boxplots or use Mahalanobis distance.
+
+boxplot(RII ~ treatment, data = filtered_by_subclass_1)
+
+##conducting repeated measures ANOVA
+
 result <- ezANOVA(data = filtered_by_subclass_1,
@@
 
+means_disc <- aggregate(RII ~ field, data = filtered_by_subclass_1, FUN = mean)
+
+num_disc <- filtered_by_subclass_1 %>%
+  group_by(field) %>%
+  summarise(count = n(), .groups = "drop")
+
+means_disc <- left_join(means_disc, num_disc, by = "field")
+
+# Step 1: Reorder the levels of 'field'
+means_disc$field <- with(means_disc, factor(field, levels=unique(field[order(RII)])))
+
+# Step 2: Optionally, sort the dataframe based on the reordered levels
+means_disc <- means_disc %>% arrange(field)
+
+ggplot(data = means_disc, aes(x = reorder(c(1:6), RII), y = RII, fill = field)) +
+  geom_bar(stat = "identity", position = "dodge") +
+
+  # Add the number of observations on top of the bars
+  geom_text(aes(label=count), position=position_dodge(width=0.9), vjust=-0.5) +
+
+  labs(x = "Field", y = "Mean RII") +
+  scale_fill_discrete(name = "Field") +
+  theme_bw()
+
 ```
@@
 In the first analysis, we examined the effects of treatment, independence_timing, and their interaction on the dependent variable, researcher independence (RII) for the treatment group and unfunded control group.
-There was a significant main effect of independence_timing on RII, F(1, 188) = 158.29, p < .001, indicating a significant change in the independence from before to after the intervention.
-The effect size (GES) for this effect was 0.075, suggesting a moderate effect.
-Importantly, there was a significant interaction effect between treatment and independence_timing on independence, F(1, 188) = 11.00, p = .001.
+There was a significant main effect of independence_timing on RII, F(`r result$ANOVA[2, 2]`, `r result$ANOVA[2, 3]`) = `r result$ANOVA[2, 4]`, p = `r result$ANOVA[2, 5]` indicating a significant change in the independence from before to after the intervention.
+The effect size (GES) for this effect was `r result$ANOVA[2, 7]`, suggesting a moderate effect.
+Importantly, there was a significant interaction effect between treatment and independence_timing on independence, F(`r result$ANOVA[3, 2]`, `r result$ANOVA[3, 3]`) = `r result$ANOVA[3, 4]`, p = `r result$ANOVA[3, 5]`.
 This interaction suggests that the effect of the intervention on independence differed based on the treatment group.
-The effect size (GES) for this interaction was 0.006, indicating a small effect.
+The effect size (GES) for this interaction was `r result$ANOVA[3, 7]`, indicating a small effect.
 
 In the subsequent analysis, we further incorporated the factor of discipline (field) to explore if there were differences across disciplines in the observed effects.
-There was a significant main effect of field on independence, F(5, 178) = 2.88, p = .016, indicating that there were significant differences in RII across the six discipline groups.
-(WHICH ARE LOW AND HIGH?) The effect size (GES) for this was 0.068, suggesting a moderate effect.
-The interaction between treatment and field was not statistically significant, F(5, 178) = 0.29, p = .920, suggesting that the effect of treatment on independence was consistent across disciplines.
-The three-way interaction among treatment, independence_timing, and field was not statistically significant, F(5, 178) = 0.51, p = .765.
+There was a significant main effect of field on independence, F(`r result_disc$ANOVA[2, 2]`, `r result_disc$ANOVA[2, 3]`) = `r result_disc$ANOVA[2, 4]`, p = `r result_disc$ANOVA[2, 5]`, indicating that there were significant differences in RII across the six discipline groups.
+On average, Agricultural and veterinary sciences showed lowest independence, while Social Sciences and Humanities showed almost twice as large independence, (though it is important to note that small sample might provide unstable estimates (----> i SHOULD REMOVE THEM FROM THE ANALYSIS SINCE THESE SEEM TO BE TOO FEW OBSERVATIONS --> MAYBE I SHOULD ALSO DO A SEPARATE ANOVA ONLY TAKING INTO ACCOUNT ALL DISC BEFORE INTEVENTION AND AFTER INTERVENTION SEPARATELY BUT FOR BOTH CONTROL GROUPS).
+The effect size (GES) for this was `r result_disc$ANOVA[2, 7]`, suggesting a moderate effect.
+The interaction between treatment and field was not statistically significant, F(`r result_disc$ANOVA[4, 2]`, `r result_disc$ANOVA[4, 3]`) = `r result_disc$ANOVA[4, 4]`, p = `r result_disc$ANOVA[4, 5]`, suggesting that the effect of treatment on independence was consistent across disciplines.
+The three-way interaction among treatment, independence_timing, and field was not statistically significant, F(`r result_disc$ANOVA[6, 2]`, `r result_disc$ANOVA[6, 3]`) = `r result_disc$ANOVA[6, 4]`, p = `r result_disc$ANOVA[6, 5]`.
 This implies that the interaction effect of treatment and independence_timing on independence remained consistent across different disciplines.
@@
 
-result <- ezANOVA(data = filtered_by_subclass_2,
+result2 <- ezANOVA(data = filtered_by_subclass_2,
                  dv = RII,
@@
 
-```
+means_disc2 <- aggregate(RII ~ field, data = filtered_by_subclass_2, FUN = mean)
 
-In the second analysis, we examined the effects of treatment, independence_timing, and their interaction on the researcher independence (RII) for the treatment group and funded control group.
-Again, there was a significant main effect of time on independence (F(1, 224) = 177.37, p < 0.001), with moderate effect size (GES = 0.0938371139).
-Importantly, this time the interaction effect between treatment and time  was not significant (F(1, 224) = 0.968, p = 0.326), suggesting that funding has the same effects, regardless of its type or source.
+num_disc2 <- filtered_by_subclass_2 %>%
+  group_by(field) %>%
+  summarise(count = n(), .groups = "drop")
 
-When adding disciplines into the analysis, we again found that there is a variation in independence across disciplines (WHICH ARE LOW AND HIGH?) (F(5, 214) = 3.218, p = 0.008), with a moderate effect size (GES = 0.0613437626).
-Anyway, these differences were again stable across time and treatment conditions as the interaction were not significant.
+means_disc2 <- left_join(means_disc2, num_disc2, by = "field")
 
-### Before intervention
+# Step 1: Reorder the levels of 'field'
+means_disc2$field <- with(means_disc2, factor(field, levels=unique(field[order(RII)])))
 
-Was there a difference between the treatment groups in their level of independence before the intervention?
+# Step 2: Optionally, sort the dataframe based on the reordered levels
+means_disc2 <- means_disc2 %>% arrange(field)
 
-The analysis of variance (ANOVA) was used to compare the means of the three treatment groups.
-The results of the ANOVA showed that the effect of treatment was not statistically significant (F(2, 630) = 0.256, p = 0.613).
-The mean square (MS) within groups was 0.05775, which indicates that the variability within each group is relatively small.
-The MS between groups was 0.01476, which is smaller than the MS within groups, suggesting that the differences between the means of the treatment groups are small.
-The model explained only a small proportion of the total variance in the data (R-squared = 0.01).
-Sixty-five observations were deleted due to missing data.
-In conclusion, there is no evidence to suggest that the treatment has a significant effect on the outcome variable.
-However, the small effect size and the missing data should be taken into consideration when interpreting the results.
-Post-hoc test power was 0.9997622 as calculated by GPower (Faul, Erdfelder, Lang & Buchner, 2007).
+ggplot(data = means_disc2, aes(x = reorder(c(1:6), RII), y = RII, fill = field)) +
+  geom_bar(stat = "identity", position = "dodge") +
 
-```{r echo=FALSE}
-set.seed(123)
+  # Add the number of observations on top of the bars
+  geom_text(aes(label=count), position=position_dodge(width=0.9), vjust=-0.5) +
 
-d_before <- r_before_final
-
-before_treatment <- aov(RII ~ treatment, data = d_before)
-summary(before_treatment)
-
-means_before_treatment <- aggregate(RII ~ treatment, data = d_before, FUN = mean)
-
-ggplot(data = means_before_treatment, aes(x = treatment, y = RII, fill = treatment)) +
-         geom_bar(stat = "identity", position = "dodge") +
-         labs(x = "Treatment", y = "Mean RII") +
-         scale_fill_discrete(name = "treatment") +
+  labs(x = "Field", y = "Mean RII") +
+  scale_fill_discrete(name = "Field") +
   theme_bw()
@@
 
-Further, were there any differences in independence across disciplines?
+In the second analysis, we examined the effects of treatment, independence_timing, and their interaction on the researcher independence (RII) for the treatment group and funded control group.
+Again, there was a significant main effect of time on independence (F(`r result2$ANOVA[2, 2]`, `r result2$ANOVA[2, 3]`) = `r result2$ANOVA[2, 4]`, p = `r result2$ANOVA[2, 5]`), with moderate effect size (GES = `r result2$ANOVA[2, 7]`).
+Importantly, this time the interaction effect between treatment and time  was not significant (F(`r result2$ANOVA[3, 2]`, `r result2$ANOVA[3, 3]`) = `r result2$ANOVA[3, 4]`, p = `r result2$ANOVA[3, 5]`), suggesting that funding has the same effects, regardless of its type or source.
 
-```{r echo=FALSE}
-set.seed(123)
-
-d_before$disc_ford <- substring(d_before$disc_ford, 0, 1)
-d_before$disc_ford <- as.factor(d_before$disc_ford)
-
-d_before$treatment <- as.factor(d_before$treatment)
-
-table(d_before$disc_ford, by = d_before$treatment)
-
-disc_before <- aov(RII ~ disc_ford, data = d_before)
-summary(disc_before)
-
-means_before_disc <- aggregate(RII ~ disc_ford, data = d_before, FUN = mean)
-
-ggplot(data = means_before_disc, aes(x = disc_ford, y = RII, fill = disc_ford)) +
-         geom_bar(stat = "identity", position = "dodge") +
-         labs(x = "disc_ford", y = "Mean RII") +
-         scale_fill_discrete(name = "disc_ford") +
-         theme_bw()
-
-```
-
-Was there any interaction between the treatment group and discipline?
-
-```{r echo=FALSE}
-set.seed(123)
-
-before_disc_interaction <- aov(RII ~ treatment*disc_ford, data = d_before)
-summary(before_disc_interaction)
-
- means_before_disc_interaction <- aggregate(RII ~ treatment + disc_ford, data = d_before, FUN = mean)
-
-     # Plot grouped bar plot
-     ggplot(data = means_before_disc_interaction, aes(x = treatment, y = RII, fill = disc_ford)) +
-         geom_bar(stat = "identity", position = "dodge") +
-         labs(x = "Treatment", y = "Mean RII") +
-         scale_fill_discrete(name = "disc_ford") +
-         theme_bw()
-
-```
-
-### After intervention
-
-Was there a difference between the treatment groups in their level of independence after the intervention?
-
-The analysis of variance (ANOVA) was used to compare the means of the three treatment groups.
-The results of the ANOVA showed that the effect of treatment was not statistically significant (F(2, 630) = 0.256, p = 0.613).
-The mean square (MS) within groups was 0.05775, which indicates that the variability within each group is relatively small.
-The MS between groups was 0.01476, which is smaller than the MS within groups, suggesting that the differences between the means of the treatment groups are small.
-The model explained only a small proportion of the total variance in the data (R-squared = 0.01).
-Sixty-five observations were deleted due to missing data.
-In conclusion, there is no evidence to suggest that the treatment has a significant effect on the outcome variable.
-However, the small effect size and the missing data should be taken into consideration when interpreting the results.
-Post-hoc test power was 0.9997622 as calculated by GPower (Faul, Erdfelder, Lang & Buchner, 2007).
-
-```{r echo=FALSE}
-set.seed(123)
-
-d_before <- r_after_final
-
-before_treatment <- aov(RII ~ treatment, data = d_before)
-summary(before_treatment)
-
-means_before_treatment <- aggregate(RII ~ treatment, data = d_before, FUN = mean)
-
-ggplot(data = means_before_treatment, aes(x = treatment, y = RII, fill = treatment)) +
-         geom_bar(stat = "identity", position = "dodge") +
-         labs(x = "Treatment", y = "Mean RII") +
-         scale_fill_discrete(name = "treatment") +
-         theme_bw()
-
-```
-
-Further, were there any differences in independence across disciplines?
-
-```{r echo=FALSE}
-set.seed(123)
-
-d_before$disc_ford <- substring(d_before$disc_ford, 0, 1)
-d_before$disc_ford <- as.factor(d_before$disc_ford)
-
-d_before$treatment <- as.factor(d_before$treatment)
-
-table(d_before$disc_ford, by = d_before$treatment)
-
-disc_before <- aov(RII ~ disc_ford, data = d_before)
-summary(disc_before)
-
-means_before_disc <- aggregate(RII ~ disc_ford, data = d_before, FUN = mean)
-
-ggplot(data = means_before_disc, aes(x = disc_ford, y = RII, fill = disc_ford)) +
-         geom_bar(stat = "identity", position = "dodge") +
-         labs(x = "disc_ford", y = "Mean RII") +
-         scale_fill_discrete(name = "disc_ford") +
-         theme_bw()
-
-```
-
-Was there any interaction between the treatment group and discipline?
-
-```{r echo=FALSE}
-set.seed(123)
-
-before_disc_interaction <- aov(RII ~ treatment*disc_ford, data = d_before)
-summary(before_disc_interaction)
-
- means_before_disc_interaction <- aggregate(RII ~ treatment + disc_ford, data = d_before, FUN = mean)
-
-     # Plot grouped bar plot
-     ggplot(data = means_before_disc_interaction, aes(x = treatment, y = RII, fill = disc_ford)) +
-         geom_bar(stat = "identity", position = "dodge") +
-         labs(x = "Treatment", y = "Mean RII") +
-         scale_fill_discrete(name = "disc_ford") +
-         theme_bw()
-
-```
-
-### Intervention effect
-
-```{r echo=FALSE}
-
-d <- all 
-d$treatment <- as.factor(d$treatment)
-d$independence_timing <- as.factor(d$independence_timing)
-
-interaction <- aov(RII ~ treatment * independence_timing, data = d)
-summary(interaction)
-heplots::etasq(interaction, anova = TRUE)
-
- ###calculating r-squared - generated by chatGPT, so not sure this is correct
-
-     n <- nrow(d)
-     p <- length(coef(interaction))
-     SSresid <- sum(resid(interaction)^2)
-     SStotal <- sum((na.omit(d$RII) - mean(d$RII, na.rm = TRUE))^2)
-     R2 <- 1 - (SSresid / SStotal)
-     adjR2 <- 1 - ((1 - R2) * (n - 1) / (n - p - 1))
-
- ### visualisations
-
-means <- aggregate(RII ~ treatment + independence_timing, data = d, FUN = mean)
-
- ggplot(data = interaction, aes(x = treatment, y = RII, fill = independence_timing)) +
-         geom_violin(scale = "width") +
-         scale_fill_discrete(name = "Independence Timing", labels = c("After intervention", "Before intervention")) +
-         xlab("Treatment Group") +
-         ylab("RII Score") +
-         ggtitle("Violin Plot of RII Scores by Treatment and Time") +
-         theme_bw()
-
-```
+When adding disciplines into the analysis, we again found that there is a variation in independence across disciplines (F(`r result_disc2$ANOVA[2, 2]`, `r result_disc2$ANOVA[2, 3]`) = `r result_disc2$ANOVA[2, 4]`, p = `r result_disc2$ANOVA[2, 5]`) with Agricultural and veterinary sciences again showing the lowest independence, while Social Sciences and Humanities showing largest (though it is important to note that small sample might provide unstable estimates (----> i SHOULD REMOVE THEM FROM THE ANALYSIS SINCE THESE SEEM TO BE TOO FEW OBSERVATIONS --> MAYBE I SHOULD ALSO DO A SEPARATE ANOVA ONLY TAKING INTO ACCOUNT ALL DISC BEFORE INTEVENTION AND AFTER INTERVENTION SEPARATELY BUT FOR BOTH CONTROL GROUPS), and with a moderate effect size (GES = `r result_disc2$ANOVA[2, 7]`).
+Anyway, these differences were again stable across time and treatment conditions as the interaction were not significant.
 
@@
 The strongest effect we found across all control group comparison was the effect of time - over time, researchers become more independent, regardless of their access to funding or their discipline.
-The effect size for this difference is moderate (GES = 0.075) when comparing funded and unfunded groups, and moderate (GES = 0.075) when comparing the funded treatment and funded control groups.
+The effect size for this difference is moderate when comparing funded and unfunded groups, and also moderate when comparing the funded treatment and funded control groups.
 
-Additionally, the observed variation in independence across different disciplines underscores the importance of considering disciplinary differences, suggested by a moderate effect size (GES = 0.068).
-A moderate effect size (GES = 0.068) for the field effect emphasizes that certain disciplines might inherently have variations in RII, perhaps due to differences in practices, methodologies, or norms specific to each discipline.
+Additionally, the observed variation in independence across different disciplines underscores the importance of considering disciplinary differences, suggested by a moderate effect size.
+A moderate effect size for the field effect emphasizes that certain disciplines might inherently have variations in RII, perhaps due to differences in practices, methodologies, or norms specific to each discipline.
 Anyway, these differences remain constant across time and funding interventions, suggesting that funding has a uniform effect on the independence across disciplines.
@@
 Finally, the significant interaction between treatment and time when comparing treamtnet vs unfunded group suggests the funding has positive effect on stimulating researchers' independence.
-However, the effect size is only modest (GES = 0.006), indicating relatively small practical relevance.
+However, the effect size is only modest, indicating relatively small practical relevance.
 Further the insignificant interaction when comparing the treatment vs funded control group suggests that funding in this career stage has the same effect, regardless of its type or source.

### 2023-09-13 article.Rmd
data collection complete

@@
 In the treatment group of `r nrow(tar_read(ids_complete))`researchers,  118 (49 %) had their most frequent co-author same as their supervisor and 86 (36 %) had someone other than their supervisor as their most frequent co-author in their first 5 publications, and 37 (15%) had no co-author in their first 5 publications.
-In the control groups, we have manually found supervisors for `r nrow(tar_read(sup_control) %>% filter(!is.na(sup_vedidk)) %>% distinct(name_first, name_last))` researchers, and when we compared them to the supervisors suggested by the most frequent coauthor algorithm, we found that 41 (29 %) had their most frequent co-author the same as their supervisor, 80 (57 %) had someone other than their supervisor as their most frequent co-author in their first 5 publications, and 20 (14 %) had no co-author in their first 5 publications.
+In the control groups, we have manually found supervisors for `r nrow(tar_read(sup_complete) %>% filter(!is.na(sup_vedidk)) %>% distinct(name_first, name_last))` researchers, and when we compared them to the supervisors suggested by the most frequent coauthor algorithm, we found that 41 (29 %) had their most frequent co-author the same as their supervisor, 80 (57 %) had someone other than their supervisor as their most frequent co-author in their first 5 publications, and 20 (14 %) had no co-author in their first 5 publications.
 

### 2023-09-13 R/manual_sup_search.R

@@ -8,7 +8,7 @@
 #' @return
 #' @author fatal: unable to access 'C:/Users/David Jank?/Documents/.config/git/config': Invalid argument
 #' @export
-manual_sup_search <- function(db_path, matching) {
+manual_sup_search <- function(db_path, matching, sup_control_second) {
     
     
     con <-  DBI::dbConnect(RSQLite::SQLite(), db_path)
@@ -204,6 +204,58 @@ combined <- ids %>%
   select(-sup_name_first_extra, -sup_name_last_extra)
   
 b <- combined %>% mutate(across(everything(), ~replace(., . == "", NA))) %>% filter(!is.na(sup_name_first))
+
+
+
+
+
+
+sup_control_third <- read.csv(here::here("data", "raw", "backup",  "sup_search_third.csv")) 
+
+a <- bind_rows(sup_control_first %>% dplyr::select(-Column1, -sec_sup_vedidk), sup_control_second %>% dplyr::select(-X))
+a <- bind_rows(a, sup_control_third %>% dplyr::select(-X)) %>% distinct()
+a$vedidk <- as.character(a$vedidk)
+
+final <- left_join(manual_sup_search, a, by = c("vedidk" = "vedidk", "disc_ford" = "disc_ford"))
+
+write.csv(final, file = here::here("data", "raw", "backup", "manual_sup_search_updated.csv"))
+
+
+
+
+
+
+
+sup_control_third <- read.csv2(here::here("data", "raw", "backup", "manual_sup_search_third_cleaned.csv")) 
+sup_control_second <- read.csv2(here::here("data", "raw", "backup", "manual_sup_search_second_cleaned.csv")) 
+sup_control_first <- read.csv2(here::here("data", "raw", "backup", "manual_sup_search_first_cleaned.csv")) 
+
+manual_sup_search2 <- anti_join(manual_sup_search, sup_control, by = c("vedidk" = "vedidk", "disc_ford" = "disc_ford"))
+
+final2 <- left_join(manual_sup_search2, a, by = c("vedidk" = "vedidk", "disc_ford" = "disc_ford"))
+
+write.csv(final2, file = here::here("data", "raw", "backup", "manual_sup_search_second_updated.csv"))
+
+
+
+
+
+write.csv(a, file = here::here("data", "raw", "backup", "all_control_sup.csv"))
+
[…]

### 2023-09-13 R/match_data_prep.R

@@ -1372,7 +1372,7 @@ match_data_prep <- function(db_path, ids, gender, sup_control, sup_control_secon
     
     sup_out <- sup_control %>% filter(is.na(sup_name_first))
     sup_out_second <- sup_control_second %>% filter(is.na(sup_name_first))
-    
+    # 
     final_data <- final_data %>% filter(!vedidk %in% sup_out$vedidk)
     final_data <- final_data %>% filter(!vedidk %in% sup_out_second$vedidk)
     

### 2023-09-15 article.Rmd
edited tabels for readibility

@@
 library(plm)
+library(effectsize)
+library(nlme)
 
@@
 
-When Looking at disciplines, we see that there are slightly more missing data in Agricultural and veterinary scieces and the Humanities and the Arts.
+When Looking at disciplines, we see that there are slightly more missing data in Agricultural and veterinary sciences and the Humanities and the Arts.
 
@@
 
-# assuming df is your dataframe
 df <- filtered_by_subclass %>% filter(independence_timing == "before_intervention")
+numeric_vars <- df %>% 
+  select(where(is.numeric)) %>% 
+  select(-weights, -funded_control, -id, -treatment_year, -career_start_year) %>% 
+  names()
 
-# list of numeric columns. Exclude treatment column
-numeric_vars <- df %>% select(where(is.numeric)) %>% select(-weights, -funded_control, -id, -treatment_year, -career_start_year) %>% names()
-
-# descriptive stats for treatment level 1
+# descriptive stats for each treatment level
 table_before_1 <- df %>% filter(treatment == 1) %>% select(all_of(numeric_vars)) %>% describe() %>% select(n, mean, sd, min, max) %>% round(., digits = 3)
-
-# Print table for treatment level 1
-kable(table_before_1, digits = 3, caption = "Descriptive statistics for treatment group") %>% kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
-
-# descriptive stats for treatment level 0
 table_before_0 <- df %>% filter(treatment == 0) %>% select(all_of(numeric_vars)) %>% describe() %>% select(n, mean, sd, min, max) %>% round(., digits = 3)
-
-# Print table for treatment level 0
-kable(table_before_0, digits = 3, caption = "Descriptive statistics for unfunded control group") %>% kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
-
-# descriptive stats for treatment level 2
 table_before_2 <- df %>% filter(treatment == 2) %>% select(all_of(numeric_vars)) %>% describe() %>% select(n, mean, sd, min, max) %>% round(., digits = 3)
 
-# Print table for treatment level 2
-kable(table_before_2, digits = 3, caption = "Descriptive statistics for funded control group") %>% kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
+colnames(table_before_0) <- paste0(colnames(table_before_0), "_0")
+colnames(table_before_2) <- paste0(colnames(table_before_2), "_2")
+
+combined_table_before <- cbind(table_before_1, table_before_0[, -1], table_before_2[, -1])
+
+kable(combined_table_before, 
+      digits = 3, align = "c", booktabs = TRUE) %>%
+  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
+  add_header_above(c(" " = 1, "Treatment Group" = 5, "Unfunded Control Group" = 4, "Funded Control Group" = 4))
 
@@
 
-# assuming df is your dataframe
 df <- filtered_by_subclass %>% filter(independence_timing == "after_intervention")
+numeric_vars <- df %>% 
+  select(where(is.numeric)) %>% 
+  select(-weights, -funded_control, -id, -treatment_year, -career_start_year) %>% 
+  names()
 
-# list of numeric columns. Exclude treatment column
-numeric_vars <- df %>% select(where(is.numeric)) %>% select(-weights, -funded_control, -id, -treatment_year, -career_start_year) %>% names()
+# descriptive stats for each treatment level
+table_after_1 <- df %>% filter(treatment == 1) %>% select(all_of(numeric_vars)) %>% describe() %>% select(n, mean, sd, min, max) %>% round(., digits = 3)
+table_after_0 <- df %>% filter(treatment == 0) %>% select(all_of(numeric_vars)) %>% describe() %>% select(n, mean, sd, min, max) %>% round(., digits = 3)
+table_after_2 <- df %>% filter(treatment == 2) %>% select(all_of(numeric_vars)) %>% describe() %>% select(n, mean, sd, min, max) %>% round(., digits = 3)
 
-# descriptive stats for treatment level 1
-table_before_1 <- df %>% filter(treatment == 1) %>% select(all_of(numeric_vars)) %>% describe() %>% select(n, mean, sd, min, max) %>% round(., digits = 3)
+colnames(table_after_0) <- paste0(colnames(table_after_0), "_0")
+colnames(table_after_2) <- paste0(colnames(table_after_2), "_2")
 
-# Print table for treatment level 1
-kable(table_before_1, digits = 3, caption = "Descriptive statistics for treatment group") %>% kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
+combined_table_after <- cbind(table_after_1, table_after_0[, -1], table_after_2[, -1])
 
-# descriptive stats for treatment level 0
-table_before_0 <- df %>% filter(treatment == 0) %>% select(all_of(numeric_vars)) %>% describe() %>% select(n, mean, sd, min, max) %>% round(., digits = 3)
-
-# Print table for treatment level 0
-kable(table_before_0, digits = 3, caption = "Descriptive statistics for unfunded control group") %>% kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
-
-# descriptive stats for treatment level 2
-table_before_2 <- df %>% filter(treatment == 2) %>% select(all_of(numeric_vars)) %>% describe() %>% select(n, mean, sd, min, max) %>% round(., digits = 3)
-
-# Print table for treatment level 2
-kable(table_before_2, digits = 3, caption = "Descriptive statistics for funded control group") %>% kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
+kable(combined_table_after, 
+      digits = 3, align = "c", booktabs = TRUE) %>%
+  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
+  add_header_above(c(" " = 1, "Treatment Group" = 5, "Unfunded Control Group" = 4, "Funded Control Group" = 4))
 
@@
 
-BTW: there is an overlap between control group observations - `r overlap_control` observations from the unfunded control group also appears in the funded control group
+BTW: there is an overlap between control group observations: `r overlap_control` observations from the unfunded control group also appears in the funded control group
 
@@
 
+##Unfunded group
+
 unf_sum <- summary(tar_read(matched_obj_unfunded), un = TRUE)
 
-summary(tar_read(matched_obj_unfunded))
+# summary(tar_read(matched_obj_unfunded))
+#     
+# plot(unf_sum, var.order = "unmatched")
 
-plot(unf_sum, var.order = "unmatched")
+aa <- cobalt::bal.tab(tar_read(matched_obj_unfunded), un = TRUE, stats = c("m", "v", "ks"), binary = "std")
 
-cobalt::bal.tab(tar_read(matched_obj_unfunded), un = FALSE, stats = c("m", "v", "ks"), binary = "std")
+# aa <- aa[!grepl("^disc_ford", names(aa))]
 
-cobalt::love.plot(tar_read(matched_obj_unfunded), binary = "std", var.order = "adjusted")
+# aa <- aa[!grepl("^disc_ford", names(aa$Balance))]
+
+bal_df <- aa$Balance
+
+bal_df <- bal_df[!grepl("^disc_ford", rownames(bal_df)), ]
+
+# Display the cleaned-up table with kable
+kable(bal_df, "html", caption = "Balance Statistics For Unfunded Control Group") %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
+
+aa$Balance <- bal_df
+
+cobalt::love.plot(aa, binary = "std", var.order = "adjusted")
+
+##Funded group
 
@@
 
-summary(tar_read(matched_obj_funded))
+# summary(tar_read(matched_obj_funded))
+#     
+# plot(fun_sum, var.order = "unmatched")
 
-plot(fun_sum, var.order = "unmatched")
+bb <- cobalt::bal.tab(tar_read(matched_obj_funded), un = TRUE, stats = c("m", "v", "ks"), binary = "std")
+
+# aa <- aa[!grepl("^disc_ford", names(aa))]
+
+# aa <- aa[!grepl("^disc_ford", names(aa$Balance))]
+
+bal_df_funded <- bb$Balance
+
+bal_df_funded <- bal_df_funded[!grepl("^disc_ford", rownames(bal_df_funded)), ]
+
+# Display the cleaned-up table with kable
+kable(bal_df_funded, "html", caption = "Balance Statistics For Funded Control Group") %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
+
+bb$Balance <- bal_df_funded
+
+cobalt::love.plot(bb, binary = "std", var.order = "adjusted")
 
@@
 
-POZN: only for comparison:
-To estimate the treatment effect and its standard error, we fit a linear regression model with 1978 earnings as the outcome and the treatment, covariates, and their interaction as predictors and included the full matching weights in the estimation.
+<!-- POZN: only for comparison: -->
+<!-- To estimate the treatment effect and its standard error, we fit a linear regression model with 1978 earnings as the outcome and the treatment, covariates, and their interaction as predictors and included the full matching weights in the estimation.
 The lm() function was used to fit the outcome, and the comparisons() function in the marginaleffects package was used to perform g-computation in the matched sample to estimate the ATT.
 A cluster-robust variance was used to estimate its standard error with matching stratum membership as the clustering variable.
+-->
 
-The estimated effect was XXXX (SE = XXXX, p = XXXX), indicating that the average effect of the treatment for those who received it is to increase earnings.
+<!-- The estimated effect was XXXX (SE = XXXX, p = XXXX), indicating that the average effect of the treatment for those who received it is to increase earnings. -->
 
@@
     filter(!any(treatment == 2)) %>% 
-    ungroup()
+    ungroup() %>%
+    mutate(treatment = factor(treatment, levels = c(0, 1)))
 
@@
 model <- lmer(RII ~ treatment * independence_timing + (1 | subclass), data = filtered_by_subclass_1)
-summary(model)
-r.squaredGLMM(model)
+# summary(model)
+# r.squaredGLMM(model)
 
-##checking assumptiosn fro repeated measures ANOVA
+model_no_interaction <- lmer(RII ~ treatment + independence_timing + (1 | subclass), data = filtered_by_subclass_1)
+
+RSS_no_interaction <- sum(residuals(model_no_interaction)^2)
+RSS_full <- sum(residuals(model)^2)
+delta_RSS <- RSS_no_interaction - RSS_full
+R2_interaction <- delta_RSS / RSS_no_interaction
+# print(R2_interaction)
+
+model_disc <- lmer(RII ~ treatment * independence_timing * field + 
+              (1 + independence_timing|subclass), 
+              data = filtered_by_subclass_1)
+
+# summary(model_disc)
+
+##checking assumptions fro repeated measures ANOVA
+
+result <- aov(RII ~ treatment * independence_timing + Error(subclass/independence_timing), data=filtered_by_subclass_1)
+# summary(result)
+eta_sq_result <- eta_squared(result)
 
@@
 
-model_lm <- lm(RII ~ treatment + subclass + subclass:independence_timing, data = filtered_by_subclass_1)
-
 # Check residuals from lm
-plot(resid(model_lm))
+# plot(resid(result))
 
@@
 
-plot(model_lm$fitted.values, resid(model_lm), 
-     xlab = "Fitted values", ylab = "Residuals", 
-     main = "Residuals vs. Fitted Values")
-abline(h = 0, col = "red")
+# plot(result$fitted.values, resid(result), 
+#      xlab = "Fitted values", ylab = "Residuals", 
+#      main = "Residuals vs. Fitted Values")
+# abline(h = 0, col = "red")
 
 # Normality of Residuals: 
-qqnorm(resid(model_lm))
-qqline(resid(model_lm))
-
-shapiro.test(resid(model_lm))
+# qqnorm(resid(result))
+# qqline(resid(result))
+# 
+# shapiro.test(resid(result))
 
@@
 
-library(car)
-durbinWatsonTest(model_lm)
+# library(car)
+# durbinWatsonTest(result)
 
@@
 
-vif(model_lm)
+# vif(result)
 
@@
 
-plot(hatvalues(model_lm), rstudent(model_lm),
-     xlab = "Leverage", ylab = "Studentized Residuals",
-     main = "Residuals vs. Leverage")
-abline(h = c(-2,2), col = "red", lty = 2)
+# plot(hatvalues(result), rstudent(result),
+#      xlab = "Leverage", ylab = "Studentized Residuals",
+#      main = "Residuals vs. Leverage")
+# abline(h = c(-2,2), col = "red", lty = 2)
 
@@
 
-library(car)
-leveneTest(RII ~ treatment, data = filtered_by_subclass_1)
+# library(car)
+# leveneTest(RII ~ treatment, data = filtered_by_subclass_1)
 
@@
 
-boxplot(RII ~ treatment, data = filtered_by_subclass_1)
+# boxplot(RII ~ treatment, data = filtered_by_subclass_1)
 
@@
 
-result <- ezANOVA(data = filtered_by_subclass_1,
-                 dv = RII,
-                 wid = subclass,
-                 within = .(independence_timing),
-                 between = treatment)
-print(result)
+# filtered_by_subclass_1 <- filtered_by_subclass_1 %>%
+#      group_by(vedidk, subclass) %>%  # Assuming 'id' is your current unique identifier
+#      mutate(subject_id = cur_group_id()) %>%  # This creates a unique ID for each group
+#      ungroup()
+
+# #this is preferable because it takes into account the matched nature of the data, as well as repeated measures nature of the data -> see chatGPT conversation "ANOVA `wid` parameter clarification"
+# result <- aov(RII ~ treatment * independence_timing + Error(subclass/independence_timing), data=filtered_by_subclass_1)
+# # summary(result)
+# eta_sq_result <- eta_squared(result)
+
+#this is less preferable because it takes into account only the repeated measure nature of the data, not the matched nature -> you can see that when you run this tests, there is warning that says "there were non-unique subclass values across the between-subjects variable (treatment).
+Essentially, ezANOVA detected the problem and internally "fixed" it by making subclass unique across the treatment groups, so it behaves similarly to subject_id you later created." -> this means that it effectively converts the subclass to subject_id anyway
+# result <- ezANOVA(data = filtered_by_subclass_1,
+#                  dv = RII,
+#                  wid = subclass,
+#                  within = .(independence_timing),
+#                  between = treatment)
+# # print(result)
 
@@
 
-result_disc <- ezANOVA(data = filtered_by_subclass_1,
-                 dv = RII,
-                 wid = subclass,
-                 within = .(independence_timing),
-                 between = .(treatment, field))
-print(result_disc)
+filtered_data_disc_1 <- filtered_by_subclass_1 %>%
+  group_by(field) %>%
+  filter(n() >= 10)
+
+filtered_data_disc_1 <- filtered_data_disc_1 %>%
+     group_by(vedidk, subclass) %>%  # Assuming 'id' is your current unique identifier
+     mutate(subject_id = cur_group_id()) %>%  # This creates a unique ID for each group
+     ungroup()
+
+# Calculate weights based on group size (you can adjust this based on other criteria if needed)
+group_sizes <- table(filtered_data_disc_1$field)
+max_size <- max(group_sizes)
+filtered_data_disc_1$weights <- max_size / group_sizes[filtered_data_disc_1$field]
+
+#this model addresses both unequal group sizes (via weights) and heteroscedasticity (via varIdent).
+Additionally, I've added a first-order autoregressive structure (corAR1) assuming you have repeated measures on the same subjects and to account for their paired nature (indicated by subclass/independence_timing)
+#this model directly tests whether there is a difference in disciplines - anyway it tests each discipline agains each other, so it doesnt produce the neat result of "yes, there are some significant differences between disciplines", but more nuanced version of "there is specifically difference between this and this discipline"
+
+model_gls_weighted <- gls(RII ~ field, data = filtered_data_disc_1, 
+                          weights = varIdent(form = ~ 1 | field),
+                          method = "ML",
+                          correlation = corAR1(form = ~ 1 | subject_id))
+
+# summary(model_gls_weighted)
+
+#this model below is the same as the above but with added predictors
+
+model_gls_interactions_subclass <- gls(RII ~ field * treatment * independence_timing, 
+                              data = filtered_data_disc_1, 
+                              weights = varIdent(form = ~ 1 | field),
+                              method = "ML",
+                              correlation = corAR1(form = ~ 1 | subclass/independence_timing))
+
+# summary(model_gls_interactions_subclass)
+
+#one potential strategy to get the neat result of "yes, there are some significant differences between disciplines" is following: create two similar models
+
+model_without_field <- gls(RII ~ treatment + independence_timing + treatment:independence_timing, 
+                           data = filtered_data_disc_1, 
+                           correlation = corCompSymm(form = ~ 1 | subclass/independence_timing), 
+                           method = "ML")
+
+model_with_field_main_effect <- gls(RII ~ treatment + field + independence_timing + treatment:independence_timing, 
+                                    data = filtered_data_disc_1, 
+                                    correlation = corCompSymm(form = ~ 1 | subclass/independence_timing), 
+                                    method = "ML")
+
+anova_result <- anova(model_without_field, model_with_field_main_effect)
+
+# Your result specifically shows that the model_with_field_main_effect is significantly better at explaining the variance in your response variable compared to the model_without_field.
+The p-value is extremely small (1e-04), indicating a significant main effect of "field".
+# 
+# In other words, the main effect of "field" significantly improves the model fit, suggesting that the variable "field" has a significant main effect on the response variable RII after accounting for other predictors in the model.
+
+#this model does NOT address unequal group sizes (via weights) and heteroscedasticity
+
+# result_disc <- ezANOVA(data = filtered_data_disc_1,
+#                  dv = RII,
+#                  wid = subclass,
+#                  within = .(independence_timing),
+#                  between = .(treatment, field))
+# # print(result_disc)
+
+```
+
+In the first analysis, we examined the effects of treatment, independence_timing, and their interaction on the dependent variable, researcher independence (RII) for the treatment group and unfunded control group.
+
+There was a significant main effect of independence_timing on RII, F(`r summary(result)$"Error: subclass:independence_timing"[[1]]$"Df"[1]`, `r format(summary(result)$"Error: subclass:independence_timing"[[1]]$"Df"[2])`) = `r format(summary(result)$"Error: subclass:independence_timing"[[1]]$"F value"[1], digits=2)`, p = `r format(summary(result)$"Error: subclass:independence_timing"[[1]]$"Pr(>F)"[1], digits=4)`).
+This effect accounted for approximately `r format(eta_sq_result[eta_sq_result$Parameter == "independence_timing", "Eta2_partial"] * 100, digits=2)`% of the observed variance (partial \(\eta^2 = `r eta_sq_result[eta_sq_result$Parameter == "independence_timing", "Eta2_partial"]`\), 95% CI [`r eta_sq_result[eta_sq_result$Parameter == "independence_timing", "CI_low"]`, `r eta_sq_result[eta_sq_result$Parameter == "independence_timing", "CI_high"]`]).
+
+Importantly, there was a significant interaction effect between treatment and independence_timing on independence, F(`r format(summary(result)$"Error: Within"[[1]]$"Df"[2])`, `r format(summary(result)$"Error: Within"[[1]]$"Df"[3])` = `r format(summary(result)$"Error: Within"[[1]]$"F value"[2], digits=2)`, p = `r format(summary(result)$"Error: Within"[[1]]$"Pr(>F)"[2], digits=2)`.
+This interaction effect explained about `r format(eta_sq_result[eta_sq_result$Parameter == "treatment:independence_timing", "Eta2_partial"] * 100, digits=2)`% of the variability (partial \(\eta^2 = `r eta_sq_result[eta_sq_result$Parameter == "treatment:independence_timing", "Eta2_partial"]`\), 95% CI [`r eta_sq_result[eta_sq_result$Parameter == "treatment:independence_timing", "CI_low"]`, `r eta_sq_result[eta_sq_result$Parameter == "treatment:independence_timing", "CI_high"]`]).
+
+<!-- LMM interpretation: -->
+
+<!-- In the updated analysis using a linear mixed model, we examined the effects of treatment, independence_timing, and their interaction on the dependent variable, researcher independence (RII) for the treatment group and unfunded control group.
+-->
+
+<!-- - There was a significant main effect of `independence_timing` on RII, t(`r summary(model)$coefficients[3,3]`) = `r summary(model)$coefficients[3, "t value"]`, p = `r format(summary(model)$coefficients[3,5], scientific = TRUE)`, suggesting that there was a significant change in RII from before to after intervention in the control group.
+-->
+
+<!-- - There was also a significant main effect of `treatment` on RII, t(`r summary(model)$coefficients[2,3]`) = `r summary(model)$coefficients[2, "t value"]`, p = `r format(summary(model)$coefficients[2,5], scientific = TRUE)`.
+This effect indicates a difference in RII between the control group and the treatment group before the intervention.
+-->
+
+<!-- - Importantly, there was a significant interaction effect between `treatment` and `independence_timing` on RII, t(`r summary(model)$coefficients[4,3]`) = `r summary(model)$coefficients[4, "t value"]`, p = `r format(summary(model)$coefficients[4,5], scientific = TRUE)`.
+This interaction suggests that the effect of the intervention on independence differed based on the timing of the measurement.
+The effect size for all fixed effects can be approximated using the marginal \( R^2 \) which is `r r.squaredGLMM(model)[1]`, suggesting that about `r round(r.squaredGLMM(model)[1] * 100, 1)`% of the variance in RII can be explained by the main effects in our model.
+The effect size for the interaction specifically can be computed using \( \Delta R^2 \) due to the interaction, which is `r R2_interaction`, indicating that about `r round(R2_interaction * 100, 1)`% of variance in RII is explained by the interaction between treatment and independence_timing over and above the main effects.
+-->
+
+<!-- POZN ON MODEL CHOICE: -->
+
+<!-- In Conclusion: -->
+
+<!-- Both the mixed-effects model and the RM-ANOVA suggest a significant interaction between the treatment and the timing of the intervention.
+This means that the effect of the intervention differed between the treatment and control groups.
+-->
+
+<!-- Both methods also indicate that the timing of the intervention (i.e., whether it's before or after) has a significant effect on the outcome RII. -->
+
+<!-- The models are in agreement with their primary findings, which is a good sign.
+It suggests that the treatment has a distinct effect on RII after the intervention, different from that of the control group.
+-->
+
+<!-- However, it's worth noting that while the methods reach similar conclusions, they approach the problem from different angles.
+The mixed-effects model incorporates the correlation within each subclass through its random effect, while the RM-ANOVA primarily focuses on the repeated measures nature of the data.
+Both models provide valuable insights, but the mixed-effects model might be a more robust choice for this particular dataset, given its explicit modeling of the subclass structure.
+-->
+
+<!-- My take: -->
+
+<!-- The advantage of ANOVa is that it provides information about the "average" effect of independence timing across the dataset, whereas LMM does not do that (but it could be calculated extra, by default it only shows change in time in the control group, not the treatment group, which makes the interpretation harder).
+On the other hand  -->
+<!-- None of these models work well with the disciplines by default - I could make some extra edits to make ANOVA work, but I'm unsure what the interpretation would be for LMM -->
+
+```{r echo=FALSE}
 
@@
 
- ggplot(data = filtered_by_subclass_1, aes(x = treatment, y = RII, fill = independence_timing)) +
-         geom_violin(scale = "width") +
+ # ggplot(data = filtered_by_subclass_1, aes(x = treatment, y = RII, fill = independence_timing)) +
+ #         geom_violin(scale = "width") +
+ #         scale_fill_discrete(name = "Independence Timing", labels = c("Before intervention", "After intervention")) +
+ #         xlab("Treatment Group") +
+ #         ylab("RII Score") +
+ #         ggtitle("Violin Plot of RII Scores by Treatment and Time") +
+ #         theme_bw()
+
+ # Calculate means and standard errors for plotting
+plot_data <- filtered_by_subclass_1 %>%
+  group_by(treatment, independence_timing) %>%
+  summarize(
+    mean_RII = mean(RII),
+    se_RII = sd(RII) / sqrt(n())
+  )
+
+# # Plot
+# p <- ggplot(plot_data, aes(x = independence_timing, y = mean_RII, group = treatment, color = factor(treatment))) +
+#   geom_line(aes(linetype = factor(treatment))) + 
+#   geom_point(size = 3) + 
+#   geom_errorbar(aes(ymin = mean_RII - se_RII, ymax = mean_RII + se_RII), width = 0.2) +
+#   labs(
+#     title = "Effect of Intervention on Researcher Independence Index (RII)",
+#     x = "Independence Timing",
+#     y = "Mean RII",
+#     color = "Treatment Group",
+#     linetype = "Treatment Group"
+#   ) +
+#   scale_color_manual(values = c("blue", "red"), labels = c("Control", "Treatment")) +
+#   scale_linetype_manual(values = c("dashed", "solid")) +
+#   theme_minimal()
+
+dodge_width <- 0.5
+
+combined_plot <- ggplot() +
+
+  geom_violin(data = filtered_by_subclass_1, 
+              aes(x = treatment, y = RII, fill = independence_timing), 
+              scale = "width", 
+              position = position_dodge(dodge_width)) +
+
+  geom_point(data = plot_data, 
+             aes(x = treatment, y = mean_RII, color = independence_timing), 
+             position = position_dodge(dodge_width), 
+             size = 3) +
+
+  geom_errorbar(data = plot_data, 
+                aes(x = treatment, ymin = mean_RII - se_RII, ymax = mean_RII + se_RII, color = independence_timing), 
+                position = position_dodge(dodge_width), 
+                width = 0.2) +
+
   scale_fill_discrete(name = "Independence Timing", labels = c("Before intervention", "After intervention")) +
-         xlab("Treatment Group") +
-         ylab("RII Score") +
-         ggtitle("Violin Plot of RII Scores by Treatment and Time") +
+  scale_color_manual(values = c("black", "red"), name = "Independence Timing", labels = c("Before intervention", "After intervention")) +
+
+  labs(title = "Violin Plot of RII Scores by Treatment and Time with Mean and CI Overlayed",
+       x = "Treatment Group",
+       y = "RII Score") +
   theme_bw()
 
-means_disc <- aggregate(RII ~ field, data = filtered_by_subclass_1, FUN = mean)
-
-num_disc <- filtered_by_subclass_1 %>%
-  group_by(field) %>%
-  summarise(count = n(), .groups = "drop")
-
-means_disc <- left_join(means_disc, num_disc, by = "field")
-
-# Step 1: Reorder the levels of 'field'
-means_disc$field <- with(means_disc, factor(field, levels=unique(field[order(RII)])))
-
-# Step 2: Optionally, sort the dataframe based on the reordered levels
-means_disc <- means_disc %>% arrange(field)
-
-ggplot(data = means_disc, aes(x = reorder(c(1:6), RII), y = RII, fill = field)) +
-  geom_bar(stat = "identity", position = "dodge") +
-
-  # Add the number of observations on top of the bars
-  geom_text(aes(label=count), position=position_dodge(width=0.9), vjust=-0.5) +
-
-  labs(x = "Field", y = "Mean RII") +
-  scale_fill_discrete(name = "Field") +
-  theme_bw()
+print(combined_plot)
 
@@
 
-In the first analysis, we examined the effects of treatment, independence_timing, and their interaction on the dependent variable, researcher independence (RII) for the treatment group and unfunded control group.
-There was a significant main effect of independence_timing on RII, F(`r result$ANOVA[2, 2]`, `r result$ANOVA[2, 3]`) = `r result$ANOVA[2, 4]`, p = `r result$ANOVA[2, 5]` indicating a significant change in the independence from before to after the intervention.
-The effect size (GES) for this effect was `r result$ANOVA[2, 7]`, suggesting a moderate effect.
-Importantly, there was a significant interaction effect between treatment and independence_timing on independence, F(`r result$ANOVA[3, 2]`, `r result$ANOVA[3, 3]`) = `r result$ANOVA[3, 4]`, p = `r result$ANOVA[3, 5]`.
-This interaction suggests that the effect of the intervention on independence differed based on the treatment group.
-The effect size (GES) for this interaction was `r result$ANOVA[3, 7]`, indicating a small effect.
+```{r echo=FALSE}
 
-In the subsequent analysis, we further incorporated the factor of discipline (field) to explore if there were differences across disciplines in the observed effects.
-There was a significant main effect of field on independence, F(`r result_disc$ANOVA[2, 2]`, `r result_disc$ANOVA[2, 3]`) = `r result_disc$ANOVA[2, 4]`, p = `r result_disc$ANOVA[2, 5]`, indicating that there were significant differences in RII across the six discipline groups.
-On average, Agricultural and veterinary sciences showed lowest independence, while Social Sciences and Humanities showed almost twice as large independence, (though it is important to note that small sample might provide unstable estimates (----> i SHOULD REMOVE THEM FROM THE ANALYSIS SINCE THESE SEEM TO BE TOO FEW OBSERVATIONS --> MAYBE I SHOULD ALSO DO A SEPARATE ANOVA ONLY TAKING INTO ACCOUNT ALL DISC BEFORE INTEVENTION AND AFTER INTERVENTION SEPARATELY BUT FOR BOTH CONTROL GROUPS).
-The effect size (GES) for this was `r result_disc$ANOVA[2, 7]`, suggesting a moderate effect.
-The interaction between treatment and field was not statistically significant, F(`r result_disc$ANOVA[4, 2]`, `r result_disc$ANOVA[4, 3]`) = `r result_disc$ANOVA[4, 4]`, p = `r result_disc$ANOVA[4, 5]`, suggesting that the effect of treatment on independence was consistent across disciplines.
-The three-way interaction among treatment, independence_timing, and field was not statistically significant, F(`r result_disc$ANOVA[6, 2]`, `r result_disc$ANOVA[6, 3]`) = `r result_disc$ANOVA[6, 4]`, p = `r result_disc$ANOVA[6, 5]`.
-This implies that the interaction effect of treatment and independence_timing on independence remained consistent across different disciplines.
+# means_disc <- aggregate(RII ~ field, data = filtered_by_subclass_1, FUN = mean)
+#      
+# num_disc <- filtered_by_subclass_1 %>%
+#   group_by(field) %>%
+#   summarise(count = n(), .groups = "drop")
+# 
+# means_disc <- left_join(means_disc, num_disc, by = "field") 
+# 
+# # Step 1: Reorder the levels of 'field'
+# means_disc$field <- with(means_disc, factor(field, levels=unique(field[order(RII)])))
+# 
+# # Step 2: Optionally, sort the dataframe based on the reordered levels
+# means_disc <- means_disc %>% arrange(field)
+# 
+#     
+# se_ci_data <- filtered_by_subclass_1 %>%
+#   group_by(field) %>%
+#   summarise(mean_RII = mean(RII),
+#             se_RII = sd(RII) / sqrt(n()),
+#             lower_CI = mean_RII - (1.96 * se_RII),
+#             upper_CI = mean_RII + (1.96 * se_RII), 
+#             .groups = "drop")
+# 
+# means_disc <- merge(means_disc, se_ci_data, by = "field")
+# 
+# 
+# ggplot(data = means_disc, aes(x = field, y = mean_RII, fill = field)) +
+#   geom_bar(stat = "identity", position = "dodge") +
+#   
+#   # Add error bars for confidence intervals
+#   geom_errorbar(aes(ymin = lower_CI, ymax = upper_CI), position = position_dodge(width=0.9), width=0.25) +
+#   
+#   # Add the number of observations in the middle of the bars
+#   geom_text(aes(label=count, y = mean_RII/2), position=position_dodge(width=0.9), vjust=0.5) +
+#   
+#   # Change x-axis labels and add a title
+#   scale_x_discrete(labels = seq_along(unique(means_disc$field))) + # replace with numbers
+#   labs(
+#     x = "Field", 
+#     y = "Mean RII",
+#     title = "Differences in RII across disciplines" # Replace with your desired title
+#   ) +
+#   scale_fill_discrete(name = "Field") +
+#   theme_bw()
 
-POZN ON MODEL CHOICE:
-
-In Conclusion:
-
-Both the mixed-effects model and the RM-ANOVA suggest a significant interaction between the treatment and the timing of the intervention.
-This means that the effect of the intervention differed between the treatment and control groups.
-
-Both methods also indicate that the timing of the intervention (i.e., whether it's before or after) has a significant effect on the outcome RII.
-
-The models are in agreement with their primary findings, which is a good sign.
-It suggests that the treatment has a distinct effect on RII after the intervention, different from that of the control group.
-
-However, it's worth noting that while the methods reach similar conclusions, they approach the problem from different angles.
-The mixed-effects model incorporates the correlation within each subclass through its random effect, while the RM-ANOVA primarily focuses on the repeated measures nature of the data.
-Both models provide valuable insights, but the mixed-effects model might be a more robust choice for this particular dataset, given its explicit modeling of the subclass structure.
-
-My take:
-
-I understand the results of ANOVa, but dont understand the results of the mixed effects model very much. I also like that ANOVa actually provides p statistic and effect size statistic
+```
 
@@
     filter(!any(treatment == 0)) %>% 
-    ungroup()
+    ungroup() %>%
+    mutate(treatment = as.numeric(as.character(treatment))) %>%
+    mutate(treatment = if_else(treatment == 2, 0, treatment)) %>%
+    mutate(treatment = factor(treatment, levels = c(0, 1)))
 
@@
 
-model2 <- lmer(RII ~ treatment * independence_timing + (1 | subclass), data = filtered_by_subclass_2)
-summary(model2)
-r.squaredGLMM(model2)
+# model2 <- lmer(RII ~ treatment * independence_timing + (1 | subclass), data = filtered_by_subclass_2)
+# summary(model2)
+# r.squaredGLMM(model2)
 
-result2 <- ezANOVA(data = filtered_by_subclass_2,
-                 dv = RII,
-                 wid = subclass,
-                 within = .(independence_timing),
-                 between = treatment)
-print(result)
+result2 <- aov(RII ~ treatment * independence_timing + Error(subclass/independence_timing), data=filtered_by_subclass_2)
+# summary(result)
+eta_sq_result2 <- eta_squared(result2)
+
+# result2 <- ezANOVA(data = filtered_by_subclass_2,
+#                  dv = RII,
+#                  wid = subclass,
+#                  within = .(independence_timing),
+#                  between = treatment)
+# print(result)
 
@@
 
-result_disc2 <- ezANOVA(data = filtered_by_subclass_2,
-                 dv = RII,
-                 wid = subclass,
-                 within = .(independence_timing),
-                 between = .(treatment, field))
-print(result_disc2)
+# result_disc2 <- ezANOVA(data = filtered_by_subclass_2,
+#                  dv = RII,
+#                  wid = subclass,
+#                  within = .(independence_timing),
+#                  between = .(treatment, field))
+# print(result_disc2)
+
+```
+
+In the second analysis, we examined the effects of treatment, independence_timing, and their interaction on the researcher independence (RII) for the treatment group and funded control group.
+Again, there was a significant main effect of time on independence, F(`r format(summary(result2)$"Error: subclass:independence_timing"[[1]]$"Df"[1])`, `r format(summary(result2)$"Error: subclass:independence_timing"[[1]]$"Df"[2])`) = `r format(summary(result2)$"Error: subclass:independence_timing"[[1]]$"F value"[1], digits=2)`, p = `r format(summary(result2)$"Error: subclass:independence_timing"[[1]]$"Pr(>F)"[1], digits=4)`).
+The effect accounted for approximately `r format(eta_sq_result2[eta_sq_result2$Parameter == "independence_timing", "Eta2_partial"] * 100, digits=2)`% of the observed variance (partial \(\eta^2 = `r eta_sq_result2[eta_sq_result2$Parameter == "independence_timing", "Eta2_partial"]`\), 95% CI [`r eta_sq_result2[eta_sq_result2$Parameter == "independence_timing", "CI_low"]`, `r eta_sq_result2[eta_sq_result2$Parameter == "independence_timing", "CI_high"]`]).
+
+Importantly, this time the interaction effect between treatment and time was not significant, F(`r format(summary(result2)$"Error: Within"[[1]]$"Df"[2])`, `r format(summary(result2)$"Error: Within"[[1]]$"Df"[3])`) = `r format(summary(result2)$"Error: Within"[[1]]$"F value"[2], digits=2)`, p = `r format(summary(result2)$"Error: Within"[[1]]$"Pr(>F)"[2], digits=2)`.
+This interaction effect explained about `r format(eta_sq_result2[eta_sq_result2$Parameter == "treatment:independence_timing", "Eta2_partial"] * 100, digits=2)`% of the variability (partial \(\eta^2 = `r eta_sq_result2[eta_sq_result2$Parameter == "treatment:independence_timing", "Eta2_partial"]`\), 95% CI [`r eta_sq_result2[eta_sq_result2$Parameter == "treatment:independence_timing", "CI_low"]`, `r eta_sq_result2[eta_sq_result2$Parameter == "treatment:independence_timing", "CI_high"]`]), suggesting that funding has the same effects, regardless of its type or source.
+
+```{r echo=FALSE}
 
@@
 
-means2 <- aggregate(RII ~ treatment + independence_timing, data = filtered_by_subclass_2, FUN = mean)
+plot_data2 <- filtered_by_subclass_2 %>%
+  group_by(treatment, independence_timing) %>%
+  summarize(
+    mean_RII = mean(RII),
+    se_RII = sd(RII) / sqrt(n())
+  )
 
- ggplot(data = filtered_by_subclass_2, aes(x = treatment, y = RII, fill = independence_timing)) +
-         geom_violin(scale = "width") +
+dodge_width <- 0.5
+
+combined_plot2 <- ggplot() +
+
+  geom_violin(data = filtered_by_subclass_2, 
+              aes(x = treatment, y = RII, fill = independence_timing), 
+              scale = "width", 
+              position = position_dodge(dodge_width)) +
+
+  geom_point(data = plot_data2, 
+             aes(x = treatment, y = mean_RII, color = independence_timing), 
+             position = position_dodge(dodge_width), 
+             size = 3) +
+
+  geom_errorbar(data = plot_data2, 
+                aes(x = treatment, ymin = mean_RII - se_RII, ymax = mean_RII + se_RII, color = independence_timing), 
+                position = position_dodge(dodge_width), 
+                width = 0.2) +
+
   scale_fill_discrete(name = "Independence Timing", labels = c("Before intervention", "After intervention")) +
-         xlab("Treatment Group") +
-         ylab("RII Score") +
-         ggtitle("Violin Plot of RII Scores by Treatment and Time") +
+  scale_color_manual(values = c("black", "red"), name = "Independence Timing", labels = c("Before intervention", "After intervention")) +
+
+  labs(title = "Violin Plot of RII Scores by Treatment and Time with Mean and CI Overlayed",
+       x = "Treatment Group",
+       y = "RII Score") +
   theme_bw()
 
-means_disc2 <- aggregate(RII ~ field, data = filtered_by_subclass_2, FUN = mean)
+print(combined_plot2)
 
-num_disc2 <- filtered_by_subclass_2 %>%
+# means2 <- aggregate(RII ~ treatment + independence_timing, data = filtered_by_subclass_2, FUN = mean)
+# 
+# 
+# means_disc2 <- aggregate(RII ~ field, data = filtered_by_subclass_2, FUN = mean)
+#      
+# num_disc2 <- filtered_by_subclass_2 %>%
+#   group_by(field) %>%
+#   summarise(count = n(), .groups = "drop")
+# 
+# means_disc2 <- left_join(means_disc2, num_disc2, by = "field") 
+# 
+# # Step 1: Reorder the levels of 'field'
+# means_disc2$field <- with(means_disc2, factor(field, levels=unique(field[order(RII)])))
+# 
+# # Step 2: Optionally, sort the dataframe based on the reordered levels
+# means_disc2 <- means_disc2 %>% arrange(field)
+# 
+# 
+# 
+# se_ci_data2 <- filtered_by_subclass_2 %>%
+#   group_by(field) %>%
+#   summarise(mean_RII = mean(RII),
+#             se_RII = sd(RII) / sqrt(n()),
+#             lower_CI = mean_RII - (1.96 * se_RII),
+#             upper_CI = mean_RII + (1.96 * se_RII), 
+#             .groups = "drop")
+# 
+# means_disc2 <- merge(means_disc2, se_ci_data2, by = "field")
+# 
+# 
+# ggplot(data = means_disc2, aes(x = field, y = mean_RII, fill = field)) +
+#   geom_bar(stat = "identity", position = "dodge") +
+#   
+#   # Add error bars for confidence intervals
+#   geom_errorbar(aes(ymin = lower_CI, ymax = upper_CI), position = position_dodge(width=0.9), width=0.25) +
+#   
+#   # Add the number of observations in the middle of the bars
+#   geom_text(aes(label=count, y = mean_RII/2), position=position_dodge(width=0.9), vjust=0.5) +
+#   
+#   # Change x-axis labels and add a title
+#   scale_x_discrete(labels = seq_along(unique(means_disc2$field))) + # replace with numbers
+#   labs(
+#     x = "Field", 
+#     y = "Mean RII",
+#     title = "Differences in RII across disciplines" # Replace with your desired title
+#   ) +
+#   scale_fill_discrete(name = "Field") +
+#   theme_bw()
+
+disc_data <- d %>%
+     filter(!is.na(RII)) %>% 
+     group_by(vedidk, field, RII) %>%
+     sample_n(1) %>%
+     ungroup()
+
+means_disc_complete <- aggregate(RII ~ field, data = disc_data, FUN = mean)
+
+num_disc_complete <- disc_data %>%
   group_by(field) %>%
@@
 
-means_disc2 <- left_join(means_disc2, num_disc2, by = "field")
+means_disc_complete <- left_join(means_disc_complete, num_disc_complete, by = "field")
 
 # Step 1: Reorder the levels of 'field'
-means_disc2$field <- with(means_disc2, factor(field, levels=unique(field[order(RII)])))
+means_disc_complete$field <- with(means_disc_complete, factor(field, levels=unique(field[order(RII)])))
 
 # Step 2: Optionally, sort the dataframe based on the reordered levels
-means_disc2 <- means_disc2 %>% arrange(field)
+means_disc_complete <- means_disc_complete %>% arrange(field)
 
-ggplot(data = means_disc2, aes(x = reorder(c(1:6), RII), y = RII, fill = field)) +
+se_ci_data_complete <- disc_data %>%
+  group_by(field) %>%
+  summarise(mean_RII = mean(RII),
+            se_RII = sd(RII) / sqrt(n()),
+            lower_CI = mean_RII - (1.96 * se_RII),
+            upper_CI = mean_RII + (1.96 * se_RII), 
+            .groups = "drop")
+
+means_disc_complete <- merge(means_disc_complete, se_ci_data_complete, by = "field")
+
+ggplot(data = means_disc_complete, aes(x = field, y = mean_RII, fill = field)) +
   geom_bar(stat = "identity", position = "dodge") +
 
-  # Add the number of observations on top of the bars
-  geom_text(aes(label=count), position=position_dodge(width=0.9), vjust=-0.5) +
+  # Add error bars for confidence intervals
+  geom_errorbar(aes(ymin = lower_CI, ymax = upper_CI), position = position_dodge(width=0.9), width=0.25) +
 
-  labs(x = "Field", y = "Mean RII") +
+  # Add the number of observations in the middle of the bars
+  geom_text(aes(label=count, y = mean_RII/2), position=position_dodge(width=0.9), vjust=0.5) +
+
+  # Change x-axis labels and add a title
+  scale_x_discrete(labels = seq_along(unique(means_disc_complete$field))) + # replace with numbers
+  labs(
+    x = "Field", 
+    y = "Mean RII",
+    title = "Differences in average RII across disciplines"
+  ) +
   scale_fill_discrete(name = "Field") +
@@
 
-In the second analysis, we examined the effects of treatment, independence_timing, and their interaction on the researcher independence (RII) for the treatment group and funded control group.
-Again, there was a significant main effect of time on independence (F(`r result2$ANOVA[2, 2]`, `r result2$ANOVA[2, 3]`) = `r result2$ANOVA[2, 4]`, p = `r result2$ANOVA[2, 5]`), with moderate effect size (GES = `r result2$ANOVA[2, 7]`).
-Importantly, this time the interaction effect between treatment and time  was not significant (F(`r result2$ANOVA[3, 2]`, `r result2$ANOVA[3, 3]`) = `r result2$ANOVA[3, 4]`, p = `r result2$ANOVA[3, 5]`), suggesting that funding has the same effects, regardless of its type or source.
-
-When adding disciplines into the analysis, we again found that there is a variation in independence across disciplines (F(`r result_disc2$ANOVA[2, 2]`, `r result_disc2$ANOVA[2, 3]`) = `r result_disc2$ANOVA[2, 4]`, p = `r result_disc2$ANOVA[2, 5]`) with Agricultural and veterinary sciences again showing the lowest independence, while Social Sciences and Humanities showing largest (though it is important to note that small sample might provide unstable estimates (----> i SHOULD REMOVE THEM FROM THE ANALYSIS SINCE THESE SEEM TO BE TOO FEW OBSERVATIONS --> MAYBE I SHOULD ALSO DO A SEPARATE ANOVA ONLY TAKING INTO ACCOUNT ALL DISC BEFORE INTEVENTION AND AFTER INTERVENTION SEPARATELY BUT FOR BOTH CONTROL GROUPS), and with a moderate effect size (GES = `r result_disc2$ANOVA[2, 7]`).
-Anyway, these differences were again stable across time and treatment conditions as the interaction were not significant.
-
 # Discussion
@@
 The results of this study provide important insights into the effects of funding interventions on researcher independence.
-The strongest effect we found across all control group comparison was the effect of time - over time, researchers become more independent, regardless of their access to funding or their discipline.
-The effect size for this difference is moderate when comparing funded and unfunded groups, and also moderate when comparing the funded treatment and funded control groups.
+The strongest effect we found across all control group comparison was the effect of time - over time, researchers become more independent, regardless of their access to funding or their study discipline.
+This effect explains around 60% of the variance in independence.
 
@@
 
-Finally, the significant interaction between treatment and time when comparing treamtnet vs unfunded group suggests the funding has positive effect on stimulating researchers' independence.
-However, the effect size is only modest, indicating relatively small practical relevance.
-Further the insignificant interaction when comparing the treatment vs funded control group suggests that funding in this career stage has the same effect, regardless of its type or source.
+Finally, the significant interaction between treatment and time when comparing treatment vs unfunded group suggests the funding has positive effect on stimulating researchers' independence.
+However, the effect size is only modest, explaining about 2 % of variance in independence, indicating relatively small practical relevance.
+Further, the insignificant interaction when comparing the treatment vs funded control group suggests that funding in this career stage has the same effect, regardless of its type or source.
+Interestingly, in our sample both funded groups (treatment as well as control) started with lower independence compared to unfunded control group.
+This might suggest that in the early career stages, in order to secure funding, it is needed to be more dependent on one's PhD advisor.
+
+<!-- Anyway, rather than granting funded researchers greater independence compared to the unfunded control group, it seems that the funding programme we examined sampled less independent researchers and then allowed them to catch up with the unfunded control group via providing them funding.
+-->
 

### 2023-09-22 _targets.Rmd
data collection complete
updated article

@@
      # tar_target(ids_path, here::here("data", "raw", "supervisors_updated.csv"), format = "file"),
-     tar_target(ids, read.csv2(ids_path)),
+     tar_target(ids, read.csv(ids_path)),
      # tar_target(gender_path, here::here("data", "raw", "names4api_tagged.tsv"), format = "file"),

### 2023-09-22 article.Rmd
updated article

@@
 ---
-title: "Funding programmes for early career researchers do/not influence their independence"
+title: "Funding programmes for early career researchers influence their independence"
 author: "David Janků"
@@
 output:
-  html_document: default
+  html_document:
+    df_print: paged
   word_document: default
+always_allow_html: yes
 bibliography: researcher_independence.bib
@@
 
+# Abstract
+
+Independence is important quality constituting one factor of research excellence, often used in assessments for hiring, tenure and promotion in academia [@moherAssessingScientistsHiring2018].
+From a bigger picture view, encouraging more independence might also lead to faster exploration of the cognitive map of science and thus lead to faster innovation.
+Many national research funders have created programmes specifically aimed at increasing independence of early career researchers, yet until recently, there was no quantifiable way to measure changes in independence.
+We employed recently proposed measure by @vandenbesselaarMeasuringResearcherIndependence2019 to asses whether one such funding programme by Czech Science Foundation is effective at stimulating more independence.
+We found that funding for early career researchers is effective at stimulating their independence, though the effect is relatively small (2 % of variance) and the source of funding does not matter.
+The funding also helped selected researchers to catch up with the unfunded group, rather than to outrun them.
+Additionally, we found differences in levels of independence across disciplines that were stable across time and treatment groups, with Social Sciences and Humanities showing highest independence, while Medical and Heath Sciences and Natural Sciences showing lowest independence.
+
 # Intro
 
-Researchers’ independence from their PhD advisor is one of the criteria often used for assessing researchers for hiring, tenure and promotion (Van Arensbergen, Van der Weijden, Van den Besselaar, 2014; Moher et al, 2018), constituting one factor of research excellence.
-The promise of independence is that researchers will “challenge the existing common views and open up new lines of research” (Van den Besselaar & Sandström, 2019, p.2).
-
-An independent investigator is then defined by the US National Academies of Science (NAS) as “one who enjoys independence of thought—the freedom to define the problem of interest and to choose or develop the best strategies and approaches to address that problem–especially during the earlier career phase” (Van den Besselaar & Sandström, 2019, p.4).
+Researchers’ independence from their PhD advisor is one of the criteria often used for assessing researchers for hiring, tenure and promotion (@vanarensbergenDifferentViewsScholarly2014; @moherAssessingScientistsHiring2018), constituting one factor of research excellence.
+The promise of independence is that researchers will “challenge the existing common views and open up new lines of research” (@vandenbesselaarMeasuringResearcherIndependence2019, p.2).
+
+An independent investigator is then defined by the US National Academies of Science (NAS) as “one who enjoys independence of thought—the freedom to define the problem of interest and to choose or develop the best strategies and approaches to address that problem–especially during the earlier career phase” (@vandenbesselaarMeasuringResearcherIndependence2019, p.4).
 Such a definition does not necessarily put independence in relation to other actors (e.g.
 one’s PhD advisor), but only in relation to one’s own freedom and resources.
-However other institutions, such as European Research Council via their Starting Grants scheme (Neufeld, Huber & Wegner, 2013) think of independence in a relational manner, in terms of having one (or a few) publications without the former PhD supervisor being co-author; being PI on a grant; or being lab director or research leader.
-
-Based on some early empirical studies (Rojko & Lužar, 2022), it seems that researchers in disciplines such as philosophy, psychology; religion, theology; social sciences; the arts, recreation, entertainment, sport; language, linguistics, literature; and geography, biography, history experience significantly higher levels of indepedence on their PhD advisor than researchers in disciplines such as science and knowledge, organization, computer science, information, documentation, librarianship, institutions, publications; mathematics, natural sciences; and applied sciences, medicine, technology.
-There is also some preliminary evidence that higher indepedence modestly correlates with number of citations aquired (Rojko & Lužar, 2022), but others argue that even the research systems with very low indepedence can create a lot of scientific impact, and thus the relationships between independence and impact might not be as clear (Gläser et al., 2021)
-
-In recent decades, there has been a worry that researchers’ indepedence is decreasing, illustrated by increase in age at which US (biomedical) researchers received their first grant (NAS, 2005; Daniels, 2015), as well as direct measures of new reserchers becoming more depedent on their PhD advisors across almost all disciplines in Slovenia (Rojko & Lužar, 2022, table 6 on p.9).
+However other institutions, such as European Research Council via their Starting Grants scheme (@neufeldPeerReviewbasedSelection2013) think of independence in a relational manner, in terms of having one (or a few) publications without the former PhD supervisor being co-author; being PI on a grant; or being lab director or research leader.
+
+Based on some early empirical studies @rojkoScientificPerformanceResearch2022, it seems that researchers in disciplines such as philosophy, psychology; religion, theology; social sciences; the arts, recreation, entertainment, sport; language, linguistics, literature; and geography, biography, history experience significantly higher levels of independence on their PhD advisor than researchers in disciplines such as science and knowledge, organization, computer science, information, documentation, librarianship, institutions, publications; mathematics, natural sciences; and applied sciences, medicine, technology.
+There is also some preliminary evidence that higher independence modestly correlates with number of citations acquired (@rojkoScientificPerformanceResearch2022), but others argue that even the research systems with very low independence can create a lot of scientific impact, and thus the relationships between independence and impact might not be as clear (@glaserIndependenceResearchReview2022)
+
+In recent decades, there has been a worry that researchers’ indepedence is decreasing, illustrated by increase in age at which US (biomedical) researchers received their first grant (NAS, 2005; @danielsGenerationRiskYoung2015), as well as direct measures of new researchers becoming more dependent on their PhD advisors across almost all disciplines in Slovenia (@rojkoScientificPerformanceResearch2022, table 6 on p.9).
 Perhaps to tackle this trend, many grant agencies decided to start awarding grants for early career researchers, usually up to 8 years after finishing their PhD.
-Such programmes have often explicitly stated goals of helping researchers become more indepedent, set up their own research group and open up new lines of research.
-The examples of such programmes could be Starting Grants by European Research Council (2022), Junior project and Junior Star by Czech Science Foundation (2020), Walter N.
-Benjamin Programme by DFG (2022), Innovation Research Incentives Scheme by Netherlands Organization of Scientific Research (NWO) (2021)...
+Such programmes have often explicitly stated goals of helping researchers become more independent, set up their own research group and open up new lines of research.
+The examples of such programmes could be Starting Grants by European Research Council (@StartingGrantERC), Junior project and Junior Star by Czech Science Foundation (2020), Walter N.
+Benjamin Programme by DFG (@WalterBenjaminProgramme), Innovation Research Incentives Scheme by Netherlands Organization of Scientific Research (NWO) (2021)...
 something from the US would be also good)
@@
 Some studies try to measure independence in a simple way, as a ratio of publications the given researcher produced without their supervisor divided by the total number of publications of the given researchers (e.g.
-Rojko & Lužar, 2022).
+@rojkoScientificPerformanceResearch2022).
 However, such indicator could be misleading in the world of team science, and also only focuses on collaborations, not tracking whether given researcher become independent in their thinking and research topics.
 [@vandenbesselaarMeasuringResearcherIndependence2019] therefore proposed more complex indicator for measuring researcher independence on the individual level, based on co-authorship network and topical overlaps.
-Their measure uses only information about publications’ characteristics (authorship and reference list) regardless of it’s impacts, unlike other alternative measures that focus solely on the impact of the independent work in terms of received citations (Dey, et al., 2021).
+Their measure uses only information about publications’ characteristics (authorship and reference list) regardless of it’s impacts, unlike other alternative measures that focus solely on the impact of the independent work in terms of received citations (Dey, et al., 2021, @ALISNovelMetric).
 
@@
 
-We decided to use the recently created independence indicator by Van den Besselaar & Sandström (2019), since it is based on scientific production (rather than impact) and captures the phenomena in the most complete manner.
+We decided to use the recently created independence indicator by @vandenbesselaarMeasuringResearcherIndependence2019, since it is based on scientific production (rather than impact) and captures the phenomena in the most complete manner.
 The indicator has 4 parts: I1: The eigenvector centrality of the supervisor in the researcher’s co-author network; I2: The clustering coefficient of the supervisor in the researcher’s co-author network; I3: The share of own papers of the researcher Pns/Pall where Pns is the number of publications of the researcher, not coauthored with the former supervisor(s) and Pall is the total number of publications of the researcher; and I4: The share of own research topics of the researcher Tns/Tall where Tns is the number of research topics of the researcher in which the former supervisor(s) is not active, and Tall is the total number of topics of the researcher.
@@
 However, we have made some changes to the indicator. After consulting with its authors, we have changed the aggregation formula to 
-$$RII = ((1- I1) + I2 + I3 + I4) / 4$$, since the previous formula had a small error (it weighted I4 double,, i.e.
+$$RII = ((1- I1) + I2 + I3 + I4) / 4$$ 
+since the previous formula had a small error (it weighted I4 double,, i.e.
 2*I4).
-For calculating the share of own research topics of the researcher (I4), we have also not used bibliographic coupling as originally suggested, but text-based topic modelling using publication titles and abstracts.
-Finally, the original indicator, while tracking not only collaboration independence but also topical independence, is still skewed significantly towards collaboration independence (three-quarters of the indicator measure collaboration, while only one-quarter measures topics).
+In determining the proportion of a researcher's own research topics (I4), we opted for text-based topic modeling utilizing publication titles and abstracts, diverging from the originally suggested bibliographic coupling method.
+Initially, we conducted a random sampling of 1200 publications from a set of all publications produced by researchers affiliated with Czech institutions as cataloged in the RIV database, estimated number of topics using Griffiths2004 indicator and calculated LDA topic model on this set of publications.
+Then we  compiled all publications generated by the researchers within our sample and their respective supervisors.
+We then calculated the posterior distribution of topics for this compilation, employing a pre-trained topic model.
+This way we wanted to mitigate the endogeneity of the topic modelling which would be stronger if we calculated topic model directly on the publications of our sample researchers.
+
+<!-- Finally, the original indicator, while tracking not only collaboration independence but also topical independence, is still skewed significantly towards collaboration independence (three-quarters of the indicator measure collaboration, while only one-quarter measures topics).
 Since we consider cognitive/topical independence an important asset of this indicator, we have decided to adjust the formula a bit further and drop the I3 part, to give more weight to the cognitive/topical independence in the whole indicator.
 Throughout this paper, we will thus refer to the original indicator as RIIo, our adjusted version as RIIa and the part of the indicator measuring only the cognitive independence RIIc.
-
----> popsat víc jak počítám topic model??
+-->
 
@@
 # Display the cleaned-up table with kable
-kable(bal_df, "html", caption = "Balance Statistics For Unfunded Control Group") %>%
+kable(bal_df, "pipe", caption = "Balance Statistics For Unfunded Control Group") %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
@@
 # Display the cleaned-up table with kable
-kable(bal_df_funded, "html", caption = "Balance Statistics For Funded Control Group") %>%
+kable(bal_df_funded, "pipe", caption = "Balance Statistics For Funded Control Group") %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
@@
 
+pp <- pp %>%
+     group_by(vedidk, subclass) %>%  # Assuming 'id' is your current unique identifier
+     mutate(subject_id = cur_group_id()) %>%  # This creates a unique ID for each group
+     ungroup()
+
+diff_data <- pp %>%
+  select(subject_id, independence_timing, RII) %>%
+  spread(independence_timing, RII) %>%
+  mutate(RII_diff = after_intervention - before_intervention) %>%
+  select(subject_id, RII_diff)
+
+pp <- left_join(pp, diff_data, by = "subject_id")
+
 filtered_by_subclass_1 <- pp %>% 
@@
 
-model <- lmer(RII ~ treatment * independence_timing + (1 | subclass), data = filtered_by_subclass_1)
-# summary(model)
-# r.squaredGLMM(model)
-
-model_no_interaction <- lmer(RII ~ treatment + independence_timing + (1 | subclass), data = filtered_by_subclass_1)
-
-RSS_no_interaction <- sum(residuals(model_no_interaction)^2)
-RSS_full <- sum(residuals(model)^2)
-delta_RSS <- RSS_no_interaction - RSS_full
-R2_interaction <- delta_RSS / RSS_no_interaction
-# print(R2_interaction)
-
-model_disc <- lmer(RII ~ treatment * independence_timing * field + 
-              (1 + independence_timing|subclass), 
-              data = filtered_by_subclass_1)
+# model <- lmer(RII ~ treatment * independence_timing + (1 | subclass), data = filtered_by_subclass_1)
+# # summary(model)
+# # r.squaredGLMM(model)
+# 
+# model_no_interaction <- lmer(RII ~ treatment + independence_timing + (1 | subclass), data = filtered_by_subclass_1)
+# 
+# RSS_no_interaction <- sum(residuals(model_no_interaction)^2)
+# RSS_full <- sum(residuals(model)^2)
+# delta_RSS <- RSS_no_interaction - RSS_full
+# R2_interaction <- delta_RSS / RSS_no_interaction
+# # print(R2_interaction)
+# 
+# 
+# model_disc <- lmer(RII ~ treatment * independence_timing * field + 
+#               (1 + independence_timing|subclass), 
+#               data = filtered_by_subclass_1)
 
@@
 
-filtered_data_disc_1 <- filtered_data_disc_1 %>%
-     group_by(vedidk, subclass) %>%  # Assuming 'id' is your current unique identifier
-     mutate(subject_id = cur_group_id()) %>%  # This creates a unique ID for each group
-     ungroup()
+filtered_data_disc_1$field <- droplevels(filtered_data_disc_1$field)
 
@@
 
-# summary(model_gls_interactions_subclass)
+# aa <- summary(model_gls_interactions_subclass)
 
@@
 anova_result <- anova(model_without_field, model_with_field_main_effect)
+
+model_summary <- summary(model_with_field_main_effect)
 
@@
 
+##here I calculate the interaction of filed * treatment not from the full RII score, but from RR delta, ie change in RII from before to after intervetion.
+below the results are plotted, showing that the effect of treatment on disciplines is universal, expect for social sciences where there is almost no effect.
+it also shows that almost in all cases the effect of time is positive - i.e people are getting more independent over time, in some case by quite a lot (e.g.
+0.2 in RII, which is 20 % oif the RII score)
+
+# filtered_data_disc_1 <- filtered_data_disc_1 %>% 
+#     filter(independence_timing != "after_intervention")
+# 
+# means_table_disc_1 <- filtered_data_disc_1 %>%
+#      group_by(field, treatment) %>%
+#      summarise(mean_RII = mean(RII_diff, na.rm = TRUE))
+# 
+# # Set up sum coding for "field"
+# contrasts(filtered_data_disc_1$field) <- contr.sum(levels(filtered_data_disc_1$field))
+# 
+# 
+# model_wls <- lm(RII_diff ~ field * treatment, data = filtered_data_disc_1, weights = weights)
+# summary(model_wls)
+# 
+# 
+# contrasts(filtered_data_disc_1$field)
+# 
+# # Extract the variance-covariance matrix
+# vcov_mat <- vcov(model_wls_sum_coded)
+# 
+# # Coefficient for Social Sciences
+# coef_SS <- -sum(coef(model_wls_sum_coded)[c("field1", "field2", "field3")])
+# 
+# # Variance for Social Sciences
+# var_SS <- sum(diag(vcov_mat[2:4, 2:4])) + 2*sum(vcov_mat[2,3:4]) + 2*sum(vcov_mat[3,4])
+# 
+# # Standard Error for Social Sciences
+# se_SS <- sqrt(var_SS)
+# 
+# # t-value for Social Sciences
+# t_value_SS <- coef_SS / se_SS
+# 
+# # Degrees of Freedom
+# df <- df.residual(model_wls_sum_coded)
+# 
+# # p-value for Social Sciences
+# p_value_SS <- 2 * pt(-abs(t_value_SS), df)
+# 
+# coef_SS
+# se_SS
+# t_value_SS
+# p_value_SS
+# 
+# vcov_matrix <- vcov(model_wls_sum_coded)
+# 
+# 
+# var_interaction <- vcov_matrix["treatment1", "treatment1"] + 
+#                    vcov_matrix["field1:treatment1", "field1:treatment1"] + 
+#                    vcov_matrix["field2:treatment1", "field2:treatment1"] + 
+#                    vcov_matrix["field3:treatment1", "field3:treatment1"] + 
+#                    2*(vcov_matrix["treatment1", "field1:treatment1"] + 
+#                       vcov_matrix["treatment1", "field2:treatment1"] + 
+#                       vcov_matrix["treatment1", "field3:treatment1"])
+# 
+# se_interaction <- sqrt(var_interaction)
+# 
+# t_value <- -0.01905 / se_interaction
+# 
+# df_residual <- df.residual(model_wls_sum_coded)
+# p_value <- 2 * (1 - pt(abs(t_value), df_residual))
+
+## visualise field*treatment
+
+# means_table <- filtered_by_subclass_1 %>%
+#   filter(independence_timing != "before_intervention") %>% 
+#   group_by(field, treatment) %>%
+#   summarise(mean_RII = mean(RII_diff, na.rm = TRUE))
+# 
+# sd_counts <- filtered_by_subclass_1 %>%
+#   filter(independence_timing != "before_intervention") %>% 
+#   group_by(field, treatment) %>%
+#   summarise(sd_RII = sd(RII_diff, na.rm = TRUE),
+#             n = n())
+# 
+# means_table <- merge(means_table, sd_counts, by = c("field", "treatment")) %>%
+#   mutate(se_RII = sd_RII / sqrt(n))
+# 
+# 
+# 
+# 
+# 
+# ggplot(means_table, aes(x=field, y=mean_RII, fill=treatment)) +
+#     geom_bar(stat="identity", position=position_dodge(width=0.8), width=0.7) +
+#     geom_errorbar(aes(ymin=mean_RII-se_RII, ymax=mean_RII+se_RII),
+#                   position=position_dodge(width=0.8), width=0.3) +
+#     geom_text(aes(label=n, y= 0.5 * mean_RII), # position in the middle
+#               position=position_dodge(width=0.8), vjust=0.5) + # centered vertically
+#     theme_minimal() +
+#     labs(y="Mean RII Difference", x="Field", fill="Treatment", title="Comparison of differences in RII across fields and treatment group") +
+#     theme(axis.text.x = element_text(angle = 45, hjust = 1))
+
 ```
@@
 
-<!-- LMM interpretation: -->
-
-<!-- In the updated analysis using a linear mixed model, we examined the effects of treatment, independence_timing, and their interaction on the dependent variable, researcher independence (RII) for the treatment group and unfunded control group.
--->
-
-<!-- - There was a significant main effect of `independence_timing` on RII, t(`r summary(model)$coefficients[3,3]`) = `r summary(model)$coefficients[3, "t value"]`, p = `r format(summary(model)$coefficients[3,5], scientific = TRUE)`, suggesting that there was a significant change in RII from before to after intervention in the control group.
--->
-
-<!-- - There was also a significant main effect of `treatment` on RII, t(`r summary(model)$coefficients[2,3]`) = `r summary(model)$coefficients[2, "t value"]`, p = `r format(summary(model)$coefficients[2,5], scientific = TRUE)`.
-This effect indicates a difference in RII between the control group and the treatment group before the intervention.
--->
-
-<!-- - Importantly, there was a significant interaction effect between `treatment` and `independence_timing` on RII, t(`r summary(model)$coefficients[4,3]`) = `r summary(model)$coefficients[4, "t value"]`, p = `r format(summary(model)$coefficients[4,5], scientific = TRUE)`.
-This interaction suggests that the effect of the intervention on independence differed based on the timing of the measurement.
-The effect size for all fixed effects can be approximated using the marginal \( R^2 \) which is `r r.squaredGLMM(model)[1]`, suggesting that about `r round(r.squaredGLMM(model)[1] * 100, 1)`% of the variance in RII can be explained by the main effects in our model.
-The effect size for the interaction specifically can be computed using \( \Delta R^2 \) due to the interaction, which is `r R2_interaction`, indicating that about `r round(R2_interaction * 100, 1)`% of variance in RII is explained by the interaction between treatment and independence_timing over and above the main effects.
--->
+To assess effects of study field on researcher independence, we chose GLS weighted model to account for unequal group sizes and heteroscedastic variances, while keeping the repeated measures design.
+First, we compared models with and without the field main effect and observed a notable improvement in model fit for the model where main effect of field was included.
+This suggests that there are statistically significant differences in the RII based on the field of study.
+Specifically, adding the field of study to the model resulted in a significant increase in the log-likelihood by `r anova_result$L.Ratio[2]` units (p < `r anova_result$"p-value"[2]`), emphasizing its importance as a predictor.
+Specifically, compared to the Engineering and Technology field, being in the Medical and Health Sciences field is associated with a decrease in RII by `r  coef(model_summary)["fieldMedical and Health Sciences", 1]` units, on average (p = `r coef(model_summary)["fieldMedical and Health Sciences", 4]`), while being in the Social Sciences field is associated with an increase in RII by `r coef(model_summary)["fieldSocial Sciences", 1]` units (p = `r coef(model_summary)["fieldSocial Sciences", 4]`).
+There are no statistically significant differences between Natural Sciences and Engineering and Technology.
+Humanities and Agricultural sciences categories were excluded because they had too few observations.
+The interaction between treatment and field was not statistically significant, suggesting that the effect of treatment on independence was consistent across disciplines.
+The three-way interaction among treatment, independence_timing, and field was not statistically significant.
+This implies that the interaction effect of treatment and independence_timing on independence remained consistent across different disciplines.
 
@@
 
+filtered_data_disc_2 <- filtered_by_subclass_2 %>%
+  group_by(field) %>%
+  filter(n() >= 10)
+
+filtered_data_disc_2$field <- droplevels(filtered_data_disc_2$field)
+
+# Calculate weights based on group size (you can adjust this based on other criteria if needed)
+group_sizes2 <- table(filtered_data_disc_2$field)
+max_size2 <- max(group_sizes2)
+filtered_data_disc_2$weights <- max_size2 / group_sizes2[filtered_data_disc_2$field]
+
+#this model addresses both unequal group sizes (via weights) and heteroscedasticity (via varIdent).
+Additionally, I've added a first-order autoregressive structure (corAR1) assuming you have repeated measures on the same subjects and to account for their paired nature (indicated by subclass/independence_timing)
+#this model directly tests whether there is a difference in disciplines - anyway it tests each discipline agains each other, so it doesnt produce the neat result of "yes, there are some significant differences between disciplines", but more nuanced version of "there is specifically difference between this and this discipline"
+
+model_gls_weighted2 <- gls(RII ~ field, data = filtered_data_disc_2, 
+                          weights = varIdent(form = ~ 1 | field),
+                          method = "ML",
+                          correlation = corAR1(form = ~ 1 | subject_id))
+
+# summary(model_gls_weighted2)
+
+#this model below is the same as the above but with added predictors
+
+model_gls_interactions_subclass2 <- gls(RII ~ field * treatment * independence_timing, 
+                              data = filtered_data_disc_2, 
+                              weights = varIdent(form = ~ 1 | field),
+                              method = "ML",
+                              correlation = corAR1(form = ~ 1 | subclass/independence_timing))
+
+# aa <- summary(model_gls_interactions_subclass2)
+
+#one potential strategy to get the neat result of "yes, there are some significant differences between disciplines" is following: create two similar models
+
+model_without_field2 <- gls(RII ~ treatment + independence_timing + treatment:independence_timing, 
+                           data = filtered_data_disc_2, 
+                           correlation = corCompSymm(form = ~ 1 | subclass/independence_timing), 
+                           method = "ML")
+
+model_with_field_main_effect2 <- gls(RII ~ treatment + field + independence_timing + treatment:independence_timing, 
+                                    data = filtered_data_disc_2, 
+                                    correlation = corCompSymm(form = ~ 1 | subclass/independence_timing), 
+                                    method = "ML")
+
+anova_result2 <- anova(model_without_field2, model_with_field_main_effect2)
+
+model_summary2 <- summary(model_with_field_main_effect2)
+
 ```
@@
 This interaction effect explained about `r format(eta_sq_result2[eta_sq_result2$Parameter == "treatment:independence_timing", "Eta2_partial"] * 100, digits=2)`% of the variability (partial \(\eta^2 = `r eta_sq_result2[eta_sq_result2$Parameter == "treatment:independence_timing", "Eta2_partial"]`\), 95% CI [`r eta_sq_result2[eta_sq_result2$Parameter == "treatment:independence_timing", "CI_low"]`, `r eta_sq_result2[eta_sq_result2$Parameter == "treatment:independence_timing", "CI_high"]`]), suggesting that funding has the same effects, regardless of its type or source.
+
+Same as in previous chapter, the comparison of models suggested that there are statistically significant differences in the RII based on the field of study.
+Specifically, adding the field of study to the model resulted in a significant increase in the log-likelihood by `r anova_result2$L.Ratio[2]` units (p < `r anova_result2$"p-value"[2]`), emphasizing its importance as a predictor.
+Specifically, compared to the Engineering and Technology field, being in the Medical and Health Sciences field is associated with a decrease in RII by `r  coef(model_summary2)["fieldMedical and Health Sciences", 1]` units, on average (p = `r coef(model_summary2)["fieldMedical and Health Sciences", 4]`), while being in the Social Sciences field is associated with an increase in RII by `r coef(model_summary2)["fieldSocial Sciences", 1]` units (p = `r coef(model_summary2)["fieldSocial Sciences", 4]`).
+There are no statistically significant differences between Natural Sciences and Engineering and Technology.
+Humanities and Agricultural sciences categories were excluded because they had too few observations.
+The interaction between treatment and field was not statistically significant, suggesting that the effect of treatment on independence was consistent across disciplines.
+The three-way interaction among treatment, independence_timing, and field was not statistically significant.
+This implies that the interaction effect of treatment and independence_timing on independence remained consistent across different disciplines.
 
@@
 
+# disc_data <- pp %>% 
+#     filter(independence_timing != "after_intervention")
+
 disc_data <- d %>%

### 2023-09-22 R/create_sup_complete.R

@@ -135,31 +135,47 @@ create_sup_complete <- function(sup_control, sup_control_second, db_path, matchi
     sup_rest_final <-  anti_join(sup_rest_field, sup_filtered_field, by = "vedidk.x") #už je jich jenom 6 a mám napsané v poznánmkách skoro u všech kteří supervisoři to jsou, tak to můžu asi nakódovat manuálně
     
     
-    sup_rest_final <- sup_rest_final %>% filter(vedidk.y %in% c(4672941, 5263344, 1481894, 7901410, 4766814, 3906884)) %>% 
-        dplyr::select(-disc_ford.y, -field.x, -field.y) %>% 
-        rename(disc_ford = disc_ford.x) %>% 
-        distinct()
-    
-    
-    sup_total <- rbind(sup_total, sup_rest_final)
     
     
     # disambiguation based on supervisor being older than supervisee --> based on the results, this didnt work that well
-    
-    # sup_rest_final$vedidk.x <- as.character(sup_rest_final$vedidk.x)
-    # sup_rest_final <- left_join(sup_rest_final, matching_data %>% dplyr::select(vedidk, career_start_year), by = c("vedidk.x" = "vedidk")) %>%
-    #     distinct()
-    # 
-    # sup_rest_final <- left_join(sup_rest_final, matching_data %>% dplyr::select(vedidk, career_start_year), by = c("vedidk.y" = "vedidk")) %>%
-    #     distinct()
-    # 
-    # sup_rest_final_filtered <- sup_rest_final %>% filter(career_start_year.y < career_start_year.x)
 
+    sup_rest_final$vedidk.x <- as.character(sup_rest_final$vedidk.x)
+    sup_rest_age <- left_join(sup_rest_final, matching_data %>% dplyr::select(vedidk, career_start_year), by = c("vedidk.x" = "vedidk")) %>%
+        distinct()
+
+    sup_rest_age <- left_join(sup_rest_age, matching_data %>% dplyr::select(vedidk, career_start_year), by = c("vedidk.y" = "vedidk")) %>%
+        distinct()
+
+    sup_rest_age <- sup_rest_age %>% filter(career_start_year.y < career_start_year.x)
+
+    dup_matches_age <- sup_rest_age %>%
+        group_by(vedidk.x) %>%
+        filter(n() > 1) %>%
+        ungroup()
+    
[…]

### 2023-09-30 article.Rmd
updated introduction

@@
 always_allow_html: yes
-bibliography: researcher_independence.bib
+bibliography: merged.bib
 csl: apa.csl
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
 library(targets)
@@
 
+## Intro 1: focus on the bigger picture, sociology and policy perspective
+
 Researchers’ independence from their PhD advisor is one of the criteria often used for assessing researchers for hiring, tenure and promotion (@vanarensbergenDifferentViewsScholarly2014; @moherAssessingScientistsHiring2018), constituting one factor of research excellence.
+The promise of independence is that researchers will “challenge the existing common views and open up new lines of research” (@vandenbesselaarMeasuringResearcherIndependence2019, p.2).
+
+Early career researcher independence is central to the long-lasting debate about how science progresses - whether it is indeed guided mostly by the truth and empirical evidence, or whether more social and demographic factors might play an important role.
+@hull1978 found that even more senior researchers readily updated their beliefs with the new evidence, supporting the former, though many (famously including Max Planck) observed that senior researchers were more fixed in their beliefs and new ideas were mostly brought up by the incoming early career researchers giving rise to the “science moves forward one funeral at the time” proverb.
+More recently, @azoulay2010 provided further support for the latter by investigating the effects of unexpected deaths of prominent scientists on their research fields and their collaborators' careers.
+They found a decrease in the productivity of junior collaborators and an increase in published work by young newcomers to the field rewarded by an increased citation rate.
+That suggests the sudden deaths of prominent scientists gave room for more disruptive changes in the field and for bringing new ideas and perspectives while harming the status quo holders who worked with the prominent scientists on their research agendas - a “Goliath effect”, as coined by @wang2021, p.42).
+
+/// here I can potentially talk a bit more about Inheritance of research agendas - how often does that happen, etc..///
+
+Insofar as the latter is true, in order to accelerate scientific progress, we might want to tackle this trend by supporting early career researchers to gain more independence from their PhD advisors.
+Younger researchers are already more likely to come up with new topics and ideas, as found by @packalen2019 by looking at the usage of new words in research papers.
+However, they might still feel various kinds of pressures to stick with their mentor’s research agendas and lack of opportunities to become more independent.
+In recent decades, there has been a worry that researchers’ independence is decreasing, illustrated by an increase in age at which US biomedical researchers received their first grant (NAS, 2005; @danielsGenerationRiskYoung2015), as well as direct measures of new researchers becoming more dependent on their PhD advisors across almost all disciplines in Slovenia (@rojkoScientificPerformanceResearch2022, table 6 on p.9).
+
+Perhaps to tackle this trend, many grant agencies decided to start awarding grants for early career researchers, usually up to 8 years after finishing their PhD.
+Such programmes have often explicitly stated goals of helping researchers become more independent, set up their own research group and open up new lines of research.
+The examples of such programmes could be Starting Grants by European Research Council (@StartingGrantERC), Junior project and Junior Star by Czech Science Foundation (2020), Walter N.
+Benjamin Programme by DFG (@WalterBenjaminProgramme), Innovation Research Incentives Scheme by Netherlands Organization of Scientific Research (NWO) (2021).
+
+Moreover, stimulating independence and supporting researchers to open up new lines of research is also a worthy policy goal regardless of researchers’ age.
+@rzhetsky2015 found that biomedical researchers are in practice often choosing less exploratory strategies for topic choice than would be socially optimal if we wanted to explore the cognitive map of science (or in this case chemicals) as fast as possible, and their choices become more conservative over time.
+They suggest that increased interdisciplinarity, risk-taking and the publication of experimental failures would substantially improve the speed of discovery.
+
+//// factors influencing independence////
+There are few known factors influencing the level of research independence.
+One of them is study discipline.
+Based on some early empirical studies (@rojkoScientificPerformanceResearch2022), it seems that researchers in disciplines such as philosophy, psychology; religion, theology; social sciences; the arts, recreation, entertainment, sport; language, linguistics, literature; and geography, biography, history experience significantly higher levels of independence on their PhD advisor than researchers in disciplines such as science and knowledge, organization, computer science, information, documentation, librarianship, institutions, publications; mathematics, natural sciences; and applied sciences, medicine, technology.
+
+Interestingly, there is also some evidence that the propensity to cognitive independence might be inherited and passed down from generation to generation in mentor-mentee relationships @yoshioka-kobayashi2021 - perhaps it is not only research agendas that students inherit from their advisors but also the tendency to deviate from those research agendas.
+This might also suggest that to increase junior researchers’ independence, we might want to teach their advisors to be more independent, in order to have a ripple effect down the line.
+
+Finally, there is also some preliminary evidence that higher independence modestly correlates with the number of citations acquired (@rojkoScientificPerformanceResearch2022), but others argue that even the research systems with very low independence can create a lot of scientific impact, and thus the relationships between independence and impact might not be as clear (@glaserIndependenceResearchReview2022)
+
+Although researcher independence seems to be an important feature that is acknowledged by many actors in the research systems and that research funders try to stimulate, there hasn’t been much effort focused on quantifying this phenomenon.
+Some studies try to measure independence in a simple way, as a ratio of publications the given researcher produced without their supervisor divided by the total number of publications of the given researchers (e.g.
+@rojkoScientificPerformanceResearch2022).
+However, such an indicator could be misleading in the world of team science, and also only focuses on collaborations, not tracking whether a given researcher becomes independent in their thinking and research topics.
+[@vandenbesselaarMeasuringResearcherIndependence2019] therefore proposed a more complex indicator for measuring researcher independence on the individual level, based on co-authorship network and topical overlaps.
+Their measure uses only information about publications’ characteristics (authorship and reference list) regardless of their impacts, unlike other alternative measures that focus solely on the impact of the independent work in terms of received citations (Dey, et al., 2021, @ALISNovelMetric).
+
+Since the explicit goal of many funding instruments that are being used by research funders all over the world is to help early career researchers become independent, we decided to use the newly created indicators to assess the extent, to which such programmes influence researchers' independence.
+
+## Intro 2: Perspective of “What are the effects of competitive grant funding? And looking at independence as one of such effects”
+
+///Primer of grant-making context:
+
+Grant funding mechanisms have previously been shown to stimulate productivity in terms of the number of publications, impact in terms of citations, and even scientific novelty (@wang2018, or as some authors argue rather interdisciplinarity: @fontana2020).
+In terms of researchers’ careers, obtaining grant funding was connected to significantly higher chances of career progression and obtaining a professorship (@bloch2014).
+
+///Though there is still some disagreement about the direction and magnitude of some of these effects, c.f.
+@@glaserIndependenceResearchReview2022 on novelty.
+--> here I can potentially go more in-depth into the critiques of grant funding mechanisms?
+E.g.
+spell out the critiques, such that they are strengthening the Matthews effect, they reduce novelty, etc....
+
+However, there are still several components of research excellence (see @vanarensbergenDifferentViewsScholarly2014; @moherAssessingScientistsHiring2018) that have not been investigated yet, with one having specifically important effects on researchers’ carers and development: their independence.
+Researchers’ independence from their PhD advisor is one of the criteria often used for assessing researchers for hiring, tenure and promotion (@vanarensbergenDifferentViewsScholarly2014; @moherAssessingScientistsHiring2018).
 The promise of independence is that researchers will “challenge the existing common views and open up new lines of research” (@vandenbesselaarMeasuringResearcherIndependence2019, p.2).
@@
 
-Since the explicit goal of many funding instruments that are being used by research funders all over the world is to help early career researchers become independent, we would like to use the newly created indicators to assess the extent, to which such programmes influence researchers independence.
-
-H1: Researchers, who received funding from programmes aimed at funding early career researchers, will show more independence on their PhD advisor 5 years after receiving the funding than researchers who did not receive this kind of funding.
+Since the explicit goal of many funding instruments that are being used by research funders all over the world is to help early career researchers become independent, we used the newly created indicators to assess the extent, to which such programmes influence researchers independence.
+
+H1: Researchers, who received funding from programmes aimed at funding early career researchers, will show more independence from their PhD advisors after receiving the funding than researchers who did not receive funding.
+
+H2: Researchers, who received funding from programmes aimed at funding early career researchers, will show more independence from their PhD advisors compared to similar researchers who received other types of funding at similar point in theri career.
+
+## Intro 3: focusing on support for early career researchers (and why is that important topic) and then mention the independence as one of the ways how we can test whether our support mechanisms for early stage researchers actually work
+
+Funding for early career researchers is an important topic in science funding policy discussions as it might have a significant impact on career progression of the new generations of researchers (@wright2017; @pickett2019; @vandenbesselaar2015).
+At the same time, the age of receiving a first grant has been growing significantly over the past decades (@powell2016, @christian2021).
+These trends have motivated some to create new proposals for funding agencies and other research funders in order to support early career researchers (@dewinde2021).
+Some funding agencies decided to tackle this trend by giving advantage to first-awardees and early career researchers in their usual distribution process, while others have created specific programmes designated to funding young researchers soon after their PhD.
+
+///maybe talk about other types of support that early career researchers get?
+Or maybe have another paragraph describing what does the life of early career researchers usually look like?
+(--> perhaps mentioning that the time to finish PhD gets longer and longer, people are now expected to do multiple post-docs, etc...
+--> perhaps borrow some info from Science of Science book Careers section)///
+
+It is expected, that by giving early-stage researchers funding, they will be able to develop more independence and open up new lines of research (@vandenbesselaarMeasuringResearcherIndependence2019, p.2).
+Younger researchers are already more likely to come up with new topics and ideas, as found by [@packalen2019] by looking at the usage of new words in research papers.
+However, they might still feel various kinds of pressures to stick with their mentor’s research agendas and lack of opportunities to become more independent.
+In recent decades, there has been a worry that researchers’ independence is decreasing, illustrated by increase in age at which US (biomedical) researchers received their first grant (NAS, 2005; @danielsGenerationRiskYoung2015), as well as direct measures of new researchers becoming more dependent on their PhD advisors across almost all disciplines in Slovenia (@rojkoScientificPerformanceResearch2022, table 6 on p.9).
+///talk about the balance between experience and independence??///
+
+Perhaps to tackle this trend, many grant agencies decided to start awarding grants for early career researchers, usually up to 8 years after finishing their PhD.
+Such programmes have often explicitly stated goals of helping researchers become more independent, set up their own research group and open up new lines of research.
+The examples of such programmes could be Starting Grants by European Research Council (@StartingGrantERC), Junior project and Junior Star by Czech Science Foundation (2020), Walter N.
+Benjamin Programme by DFG (@WalterBenjaminProgramme), Innovation Research Incentives Scheme by Netherlands Organization of Scientific Research (NWO) (2021)...
+something from the US would be also good)
+
+Although researcher independence seems to be important feature that is acknowledged by many actors in the research systems and that research funders try to stimulate, there hasn’t been much effort focused on quantifying this phenomenon.
+Some studies try to measure independence in a simple way, as a ratio of publications the given researcher produced without their supervisor divided by the total number of publications of the given researchers (e.g.
+@rojkoScientificPerformanceResearch2022).
+However, such indicator could be misleading in the world of team science, and also only focuses on collaborations, not tracking whether given researcher become independent in their thinking and research topics.
+[@vandenbesselaarMeasuringResearcherIndependence2019] therefore proposed more complex indicator for measuring researcher independence on the individual level, based on co-authorship network and topical overlaps.
+Their measure uses only information about publications’ characteristics (authorship and reference list) regardless of it’s impacts, unlike other alternative measures that focus solely on the impact of the independent work in terms of received citations (Dey, et al., 2021, @ALISNovelMetric).
+
+Since the explicit goal of many funding instruments that are being used by research funders all over the world is to help early career researchers become independent, we would like to use the newly created indicators to assess the extent, to which such programmes influence researchers' independence.
 
@@
 
-For the matched researchers from control groups (see the matching description below in the Analysis section), we didn't search for their supervisors manually, but rather used the "most frequent co-author of the first 5 publications" as a proxy to identify supervisors.
-Crosschecking this proxy with the actual data about supervisors we have, we found that this algorithm was able to identify supervisors correctly in about 50 % of cases (see the Attachment 1).
-Using this method, we were able to find `r (nrow(tar_read("final_data") %>% filter(treatment != 1) %>% filter(!is.na(sup_name))) / nrow(tar_read("matching") %>% filter(treatment != 1)))*100` % of the observations in the matched control groups.
+For the matched researchers from control groups see the matching description below in the Analysis section.
 
 These researchers and their PhD advisors with their full publication history (limited to publications created at Czech institutions) created our final sample.
+
+We also tested an assumption that had a hope of reducing time intensity of data collection by substitution it for algorithmic approach: using the "most frequent co-author of the first 5 publications" as a proxy to identify supervisors.
+Crosschecking this proxy with the actual data about supervisors we found manually, we found that this algorithm was able to identify supervisors correctly in about XXXXX % of cases (see the Attachment 1).
 
@@
 
+## construction of the independnece identificator
+
+Correlation of its components
+
+correlation with other stuff
+
+- test whether results for the "cognitive" part are the same as results for the "collaboration" part -> do all the tests
+
 ## Identification of supervisors

### 2023-10-01 _targets.Rmd
add method curl

@@
       urls = Sys.getenv("link_to_supervisors"),
-      paths = here::here("data", "raw", "supervisors.csv")),
+      paths = here::here("data", "raw", "supervisors.csv"),
+       mode = "wb", method = "curl"),
   tarchetypes::tar_download(gender_path,
       urls = Sys.getenv("link_to_gender"),
-      paths = here::here("data", "raw", "names4api_tagged.tsv")),
+      paths = here::here("data", "raw", "names4api_tagged.tsv"),
+       mode = "wb", method = "curl"),
   tarchetypes::tar_download(authors_arrow_path,
@@
       paths = here::here("data", "raw", "authors_by_pubs.arrow"),
-       mode = "wb"),
+       mode = "wb", method = "curl"),
   tarchetypes::tar_download(text_arrow_path,
@@
       paths = here::here("data", "raw", "riv_text.arrow"),
-      mode = "wb"),
+      mode = "wb", method = "curl"),
   tarchetypes::tar_download(cep_investigators_path,
@@
       paths = here::here("data", "raw", "cep_investigators.arrow"),
-       mode = "wb"),
+       mode = "wb", method = "curl"),
   tarchetypes::tar_download(cep_details_path,
@@
       paths = here::here("data", "raw", "cep_details.arrow"),
-       mode = "wb"),
+       mode = "wb", method = "curl"),
   tarchetypes::tar_download(riv_details_path,
@@
       paths = here::here("data", "raw", "riv_details.arrow"),
-       mode = "wb"),
+       mode = "wb", method = "curl"),
   tarchetypes::tar_download(riv_authors_path,
@@
       paths = here::here("data", "raw", "riv_authors.arrow"),
-       mode = "wb"),
+       mode = "wb", method = "curl"),
    tarchetypes::tar_download(sup_path,
       urls = Sys.getenv("link_to_manual_sup_search"),
-      paths = here::here("data", "raw", "manual_sup_search.csv")),
+      paths = here::here("data", "raw", "manual_sup_search.csv"),
+       mode = "wb", method = "curl"),
   tarchetypes::tar_download(sup_path_second,
       urls = Sys.getenv("link_to_manual_sup_search_second"),
-      paths = here::here("data", "raw", "manual_sup_search_second.csv")),
+      paths = here::here("data", "raw", "manual_sup_search_second.csv"),
+       mode = "wb", method = "curl"),
 

### 2023-10-05 _targets.Rmd
errors in data repaired (in match_data prep and read_one_author) + article updated + changes in the data infrastructure (instead of sup_control and sup_control_second now fused into one file "all_sup" and additional file "blacklist_control"

--- 2023-09-22 _targets.Rmd
@@
       paths = here::here("data", "raw", "manual_sup_search_second.csv")),
+  tarchetypes::tar_download(blacklist_path,
+      urls = Sys.getenv("link_to_blacklist_control"),
+      paths = here::here("data", "raw", "blacklist_control_after_disamb.csv")),
+  tarchetypes::tar_download(all_sup_path,
+      urls = Sys.getenv("link_to_all_sup"),
+      paths = here::here("data", "raw", "all_sup.csv")),
 
@@
      tar_target(sup_control, read.csv(sup_path)),
-     tar_target(sup_control_second, read.csv(sup_path_second))
+     tar_target(sup_control_second, read.csv(sup_path_second)),
+     tar_target(blacklist_control, read.csv(blacklist_path)),
+     tar_target(all_sup, read.csv(all_sup_path))
 
@@
 
-      tar_target(matching_data, match_data_prep(db_path, ids, gender, sup_control, sup_control_second)),
+      tar_target(matching_data, match_data_prep(db_path, ids, gender, blacklist_control)),
       tar_target(matched_obj_unfunded, match_obj_unfunded(matching_data)), 
@@
 
- tar_target(sup_complete, create_sup_complete(sup_control, sup_control_second, db_path, matching_data)),
+ tar_target(sup_complete, create_sup_complete(all_sup, db_path, matching_data)),
      tar_target(ids_complete, create_ids_complete(ids, db_path, matching_data)),
@@
 
+# Attachments and additional analyses
+
+Here we test to what extent can PhD advisors be identified algorithmically.
+
+```{r, engine="targets", attachments}
+
+list(
+
+    #  # tar_target(testing,
+    #  #           just_test(db_path),
+    #  #           format = "qs")
+
+    tar_target(sup_alg,
+               refine_data(matching, db_path, sup_complete))
+
+)
+
+```
+
 # Article

### 2023-10-05 article.Rmd
errors in data repaired (in match_data prep and read_one_author) + article updated + changes in the data infrastructure (instead of sup_control and sup_control_second now fused into one file "all_sup" and additional file "blacklist_control"

@@
 ---
-title: "Funding programmes for early career researchers influence their independence"
+title: "Funding programmes for early career researchers marginally improves their collaboration independence, but not cognitive independence"
 author: "David Janků"
@@
 In the second step, we manually searched for PhD advisors of these 341 researchers in the databases of theses and dissertations that cover most universities in Czechia (https://theses.cz and https://dspace.cuni.cz/).
-We were able to match `r nrow(tar_read(ids_complete))` researchers with a PhD advisor (69,2 % of the Czech subsample).
+We were able to match `r nrow(tar_read(ids_complete))` researchers with a PhD advisor (81 % of the Czech subsample).
 Further, we have not managed to find a suitable matched pair for another `r nrow(tar_read(ids_complete))-nrow(tar_read("matching") %>% filter(treatment == 1) %>% distinct(vedidk))` researchers in the matching procedure, reducing our final sample to `r nrow(tar_read("matching") %>% filter(treatment == 1) %>% distinct(vedidk))`.
@@
 
+To calculate this indicator, we required at least 3 publications. This led to an increased number of missing observations (see section Results -> Descriptives -> Missing data).
+
 <!-- Finally, the original indicator, while tracking not only collaboration independence but also topical independence, is still skewed significantly towards collaboration independence (three-quarters of the indicator measure collaboration, while only one-quarter measures topics).
@@
 
-POZN: here we show data
-
 ```{r echo=FALSE}
@@
   group_by(field) %>%
-  filter(n() >= 10)
+  filter(n() >= 8)
 
@@
 
-Importantly, there was a significant interaction effect between treatment and independence_timing on independence, F(`r format(summary(result)$"Error: Within"[[1]]$"Df"[2])`, `r format(summary(result)$"Error: Within"[[1]]$"Df"[3])` = `r format(summary(result)$"Error: Within"[[1]]$"F value"[2], digits=2)`, p = `r format(summary(result)$"Error: Within"[[1]]$"Pr(>F)"[2], digits=2)`.
+Importantly, there was a significant interaction effect between treatment and independence_timing on independence, F(`r format(summary(result)$"Error: Within"[[1]]$"Df"[2])`, `r format(summary(result)$"Error: Within"[[1]]$"Df"[3])`) = `r format(summary(result)$"Error: Within"[[1]]$"F value"[2], digits=2)`, p = `r format(summary(result)$"Error: Within"[[1]]$"Pr(>F)"[2], digits=2)`.
 This interaction effect explained about `r format(eta_sq_result[eta_sq_result$Parameter == "treatment:independence_timing", "Eta2_partial"] * 100, digits=2)`% of the variability (partial \(\eta^2 = `r eta_sq_result[eta_sq_result$Parameter == "treatment:independence_timing", "Eta2_partial"]`\), 95% CI [`r eta_sq_result[eta_sq_result$Parameter == "treatment:independence_timing", "CI_low"]`, `r eta_sq_result[eta_sq_result$Parameter == "treatment:independence_timing", "CI_high"]`]).
@@
 
+## Collaborative vs Cognitive Independence
+
+From the correlation matrix below, we can observe that the cognitive part of independence indicator (ind_topics) has notably lower correlation with the overall indicator (RII) and its remaining parts.
+
+```{r echo=FALSE}
+
+cor_data <- d %>% dplyr::select(RII, ind_topics, ind_pubs, clustr, eig_centr)
+
+cor_matrix <- cor(cor_data, use = "pairwise.complete.obs")
+
+# reversed_cor_matrix <- cor_matrix[rev(rownames(cor_matrix)), rev(colnames(cor_matrix))]
+
+kable(cor_matrix, format = "html", digits = 2) %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
+
+ind_top_mean_before <- d %>% 
+    filter(independence_timing == "before_intervention") %>% 
+    group_by(vedidk, ind_topics) %>%
+    sample_n(1) %>%
+    ungroup() %>%
+    summarise(mean_value = mean(ind_topics, na.rm = TRUE)) %>%
+    pull(mean_value)
+
+ind_top_mean_after <- d %>% 
+    filter(independence_timing == "after_intervention") %>% 
+    group_by(vedidk, ind_topics) %>%
+    sample_n(1) %>%
+    ungroup() %>%
+    summarise(mean_value = mean(ind_topics, na.rm = TRUE)) %>%
+    pull(mean_value)
+
+```
+
+From the violin plot it seems that the cognitive part of the indicator has lower variability than full indicator, and the differences between treatment and (unfunded) control groups are not significant.
+
+This might suggest that while funding helps early career researchers to become more independent from their PhD advisors overall, this is likely driven creating new collaboration networks, rather than "opening up new lines of research".
+That being said, the average level of cognitive (topical) independence is around `r ind_top_mean_before` (which could roughly be translated as `r round(ind_top_mean_before*100, 2)` %) even before the funding intervention and rises to about `r ind_top_mean_after` (`r round(ind_top_mean_after*100, 2)` %) in the time after the intervention.
+
+```{r echo=FALSE}
+
+### visualisations
+
+means <- aggregate(ind_topics ~ treatment + independence_timing, data = filtered_by_subclass_1, FUN = mean)
+
+ # Calculate means and standard errors for plotting
+plot_data <- filtered_by_subclass_1 %>%
+  group_by(treatment, independence_timing) %>%
+  summarize(
+    mean_ind_topics = mean(ind_topics),
+    se_ind_topics = sd(ind_topics) / sqrt(n())
+  )
+
+dodge_width <- 0.5
+
+combined_plot <- ggplot() +
+
+  geom_violin(data = filtered_by_subclass_1, 
+              aes(x = treatment, y = ind_topics, fill = independence_timing), 
+              scale = "width", 
+              position = position_dodge(dodge_width)) +
+
+  geom_point(data = plot_data, 
+             aes(x = treatment, y = mean_ind_topics, color = independence_timing), 
+             position = position_dodge(dodge_width), 
+             size = 3) +
+
+  geom_errorbar(data = plot_data, 
+                aes(x = treatment, ymin = mean_ind_topics - se_ind_topics, ymax = mean_ind_topics + se_ind_topics, color = independence_timing), 
+                position = position_dodge(dodge_width), 
+                width = 0.2) +
+
+  scale_fill_discrete(name = "Independence Timing", labels = c("Before intervention", "After intervention")) +
+  scale_color_manual(values = c("black", "red"), name = "Independence Timing", labels = c("Before intervention", "After intervention")) +
+
+  labs(title = "Violin Plot of ind_topics Scores by Treatment and Time with Mean and CI Overlayed",
+       x = "Treatment Group",
+       y = "ind_topics Score") +
+  theme_bw()
+
+print(combined_plot)
+
+```
+
+When looking at the scores of cognitive part of independence indicator, we cannot see notable differences across fields of study, unlike it case of the whole RII.
+--> SHOULD I STATISTICALLY TEST whether adding filed of study improves prediction of the id_topics? (same way as when I tested that for full RII)??
+
+```{r echo=FALSE}
+
+disc_data <- d %>%
+     group_by(vedidk, subclass) %>%  # Assuming 'id' is your current unique identifier
+     mutate(subject_id = cur_group_id()) %>%  # This creates a unique ID for each group
+     ungroup()
+
+diff_data_tp <- disc_data %>%
+  select(subject_id, independence_timing, ind_topics) %>%
+  spread(independence_timing, ind_topics) %>%
+  mutate(ind_topics_diff = after_intervention - before_intervention) %>%
+  select(subject_id, ind_topics_diff)
+
+disc_data <- left_join(disc_data, diff_data_tp, by = "subject_id")
+
+disc_data <-  disc_data %>% 
+     filter(!is.na(ind_topics)) %>%
+     group_by(vedidk, field, ind_topics) %>%
+     sample_n(1) %>%
+     ungroup()
+
+means_disc_complete <- aggregate(ind_topics ~ field, data = disc_data, FUN = mean)
+
+num_disc_complete <- disc_data %>%
+  group_by(field) %>%
+  summarise(count = n(), .groups = "drop")
+
+means_disc_complete <- left_join(means_disc_complete, num_disc_complete, by = "field")
+
+# Step 1: Reorder the levels of 'field'
+means_disc_complete$field <- with(means_disc_complete, factor(field, levels=unique(field[order(ind_topics)])))
+
+# Step 2: Optionally, sort the dataframe based on the reordered levels
+means_disc_complete <- means_disc_complete %>% arrange(field)
+
+se_ci_data_complete <- disc_data %>%
+  group_by(field) %>%
+  summarise(mean_ind_topics = mean(ind_topics),
+            se_ind_topics = sd(ind_topics) / sqrt(n()),
+            lower_CI = mean_ind_topics - (1.96 * se_ind_topics),
+            upper_CI = mean_ind_topics + (1.96 * se_ind_topics), 
+            .groups = "drop")
+
+means_disc_complete <- merge(means_disc_complete, se_ci_data_complete, by = "field")
+
+ggplot(data = means_disc_complete, aes(x = field, y = mean_ind_topics, fill = field)) +
+  geom_bar(stat = "identity", position = "dodge") +
+
+  # Add error bars for confidence intervals
+  geom_errorbar(aes(ymin = lower_CI, ymax = upper_CI), position = position_dodge(width=0.9), width=0.25) +
+
+  # Add the number of observations in the middle of the bars
+  geom_text(aes(label=count, y = mean_ind_topics/2), position=position_dodge(width=0.9), vjust=0.5) +
+
+  # Change x-axis labels and add a title
+  scale_x_discrete(labels = seq_along(unique(means_disc_complete$field))) + # replace with numbers
+  labs(
+    x = "Field", 
+    y = "Mean ind_topics",
+    title = "Differences in average ind_topics across disciplines and time"
+  ) +
+  scale_fill_discrete(name = "Field") +
+  theme_bw()
+
+disc_data_change <- disc_data %>% filter(!is.na(ind_topics_diff)) %>% 
+     group_by(vedidk, field, ind_topics_diff) %>%
+     sample_n(1) %>%
+     ungroup()
+
+means_disc_change <- aggregate(ind_topics_diff ~ field, data = disc_data_change, FUN = mean)
+
+num_disc_change <- disc_data_change %>%
+  group_by(field) %>%
+  summarise(count = n(), .groups = "drop")
+
+means_disc_change <- left_join(means_disc_change, num_disc_change, by = "field")
+
+# Step 1: Reorder the levels of 'field'
+means_disc_change$field <- with(means_disc_change, factor(field, levels=unique(field[order(ind_topics_diff)])))
+
+# Step 2: Optionally, sort the dataframe based on the reordered levels
+means_disc_change <- means_disc_change %>% arrange(field)
+
+se_ci_data_change <- disc_data_change %>%
+  group_by(field) %>%
+  summarise(mean_ind_topics_diff = mean(ind_topics_diff),
+            se_ind_topics_diff = sd(ind_topics_diff) / sqrt(n()),
+            lower_CI = mean_ind_topics_diff - (1.96 * se_ind_topics_diff),
+            upper_CI = mean_ind_topics_diff + (1.96 * se_ind_topics_diff), 
+            .groups = "drop")
+
+means_disc_change <- merge(means_disc_change, se_ci_data_change, by = "field")
+
+ggplot(data = means_disc_change, aes(x = field, y = mean_ind_topics_diff, fill = field)) +
+  geom_bar(stat = "identity", position = "dodge") +
+
+  # Add error bars for confidence intervals
+  geom_errorbar(aes(ymin = lower_CI, ymax = upper_CI), position = position_dodge(width=0.9), width=0.25) +
+
+  # Add the number of observations in the middle of the bars
+  geom_text(aes(label=count, y = mean_ind_topics_diff/2), position=position_dodge(width=0.9), vjust=0.5) +
+
+  # Change x-axis labels and add a title
+  scale_x_discrete(labels = seq_along(unique(means_disc_change$field))) + # replace with numbers
+  labs(
+    x = "Field", 
+    y = "Mean ind_topics_diff",
+    title = "Average change in cognitive independence across disciplines"
+  ) +
+  scale_fill_discrete(name = "Field") +
+  theme_bw()
+
+```
+
 # Discussion
@@
 The results of this study provide important insights into the effects of funding interventions on researcher independence.
-The strongest effect we found across all control group comparison was the effect of time - over time, researchers become more independent, regardless of their access to funding or their study discipline.
+The strongest effect we found across all control group comparisons was the effect of time - over time, researchers become more independent, regardless of their access to funding or their study discipline.
 This effect explains around 60% of the variance in independence.
@@
 Additionally, the observed variation in independence across different disciplines underscores the importance of considering disciplinary differences, suggested by a moderate effect size.
-A moderate effect size for the field effect emphasizes that certain disciplines might inherently have variations in RII, perhaps due to differences in practices, methodologies, or norms specific to each discipline.
+A moderate effect size for the field effect emphasizes that certain disciplines might inherently have variations in researchers' independence, perhaps due to differences in practices, methodologies, or norms specific to each discipline.
 Anyway, these differences remain constant across time and funding interventions, suggesting that funding has a uniform effect on the independence across disciplines.
 
-Finally, the significant interaction between treatment and time when comparing treatment vs unfunded group suggests the funding has positive effect on stimulating researchers' independence.
+Importantly, the significant interaction between treatment and time when comparing treatment vs unfunded control group suggests the funding has positive effect on stimulating researchers' independence.
 However, the effect size is only modest, explaining about 2 % of variance in independence, indicating relatively small practical relevance.
@@
 Interestingly, in our sample both funded groups (treatment as well as control) started with lower independence compared to unfunded control group.
-This might suggest that in the early career stages, in order to secure funding, it is needed to be more dependent on one's PhD advisor.
+This might suggest that in the early career stages, being more dependent on one's PhD advisor might be  beneficial (or even required) to obtain independent funding.
+
+Finally, when looking closer into the composition of the independence indicator, we found that that the main driver of the increase in independence was the collaboration part of the indicator - creating new collaboration networks - rather than the cognitive part - opening up new lines of research in which their PhD advisor is not active.
+While the level of cognitive independence is still relatively high even early on after finishing one's PhD (researchers have around 40 % of topics not shared by their PhD advisor) and increases over time, the funding does not stimulate more novelty and divergence from the portfolio of topics held by their PhD advisors.
 
@@
 
---> only talks about the Czech environment and considers researchers growing up and most of their careers in the Czech republic
+One of the main limitations of this study is that it only focuses on Czech environment - researchers growing up and spending most of their careers in the Czech Republic, only taking into account publications affiliated with Czech research institutions.
+Studies testing our results on samples from other countries, and possibly tracking international mobility would strengthen our conclusions.
+
+Further research could look more into which other factors influence researcher independence (especially the cognitive part) and how strongly compared to grant funding.
 
@@
 
-## construction of the independnece identificator
-
-Correlation of its components
-
-correlation with other stuff
-
-- test whether results for the "cognitive" part are the same as results for the "collaboration" part -> do all the tests
-
 ## Identification of supervisors
 
+```{r echo=FALSE}
+
+treatment_found_pc <- round(nrow(tar_read(final_data) %>% filter(!is.na(sup_name)) %>% filter(treatment == 1) %>% distinct(vedidk))/348*100, 2)
+
+control_found_pc <- round(nrow(tar_read(final_data) %>% filter(!is.na(sup_name)) %>% filter(treatment != 1) %>% distinct(vedidk))/nrow(tar_read(final_data) %>% filter(treatment != 1) %>% distinct(vedidk))*100, 2)
+
+treatment_match <- left_join(tar_read(final_data) %>% filter(!is.na(sup_name)), tar_read(sup_alg), by = "vedidk") %>% 
+    mutate(match = ifelse(sup_vedidk.x == sup_vedidk.y, 1, 0))
+
+match_yes <- nrow(treatment_match %>% filter(match == 1) %>% distinct(vedidk))
+match_yes_pc <- round(nrow(treatment_match %>% filter(match == 1) %>% distinct(vedidk))/nrow(treatment_match %>% distinct(vedidk))*100, 2)
+
+match_no <- nrow(treatment_match %>% filter(match == 0) %>% distinct(vedidk))
+match_no_pc <- round(nrow(treatment_match %>% filter(match == 0) %>% distinct(vedidk))/nrow(treatment_match %>% distinct(vedidk))*100, 2)
+
+match_na <- nrow(treatment_match %>% filter(is.na(match)) %>% distinct(vedidk))
+match_na_pc <- round(nrow(treatment_match %>% filter(is.na(match)) %>% distinct(vedidk))/nrow(treatment_match %>% distinct(vedidk))*100, 2)
+
+```
+
 Data about PhD student-PhD advisor connections are usually not available.
-One must search for these connections manually on the internet, which is time consuming and not fully reliable (we were only able to find about 69 % of these connections in our treatment group).
+One must search for these connections manually on the internet, which is time consuming and not fully reliable (we were only able to find about `r treatment_found_pc` % of these connections in our treatment group and `r control_found_pc`) % in control groups.
 Therefore, we tried to come up with an alternative way of identifying supervisors from the available data: we assumed that since many researchers only start their publication career during their PhD studies, their PhD supervisors might often coauthor their first publications.
@@
 To check whether we can use "the most frequent co-author of the first 5 publications" as a proxy to identify supervisors, we have compared the supervisors identified via this method with the manually found supervisors for each researcher in our sample.
-In the treatment group of `r nrow(tar_read(ids_complete))`researchers,  118 (49 %) had their most frequent co-author same as their supervisor and 86 (36 %) had someone other than their supervisor as their most frequent co-author in their first 5 publications, and 37 (15%) had no co-author in their first 5 publications.
-In the control groups, we have manually found supervisors for `r nrow(tar_read(sup_complete) %>% filter(!is.na(sup_vedidk)) %>% distinct(name_first, name_last))` researchers, and when we compared them to the supervisors suggested by the most frequent coauthor algorithm, we found that 41 (29 %) had their most frequent co-author the same as their supervisor, 80 (57 %) had someone other than their supervisor as their most frequent co-author in their first 5 publications, and 20 (14 %) had no co-author in their first 5 publications.
+Across our full sample of `r nrow(tar_read(final_data) %>% filter(!is.na(sup_name)) %>% distinct(vedidk))` researchers for whom we identified supervisors manually, `r match_yes` (`r match_yes_pc` %) had their most frequent co-author same as their supervisor and `r match_no` (`r match_no_pc` %) had someone other than their supervisor as their most frequent co-author in their first 5 publications, and `r match_na` (`r match_na_pc`%) had no co-author in their first 5 publications.
+
+---------> should I put the next paragraph here?
+If yes, I should ask Luzar whether I can publish it, show the data to reviewers and ask him how to cite him.
+(the code is at the bottom of the fuction sup_test.R)
 
@@
 
+This suggest that the algorithmic approach as we defined is not able to identify real supervisors often enough.
+Either new algorithm is needed or future studies should redefine the "supervisory role" based on other characteristics than formal supervision.
+
 # References

### 2023-10-05 R/create_sup_complete.R

@@ -7,12 +7,13 @@
 #' @return
 #' @author fatal: unable to access 'C:/Users/David Jank?/Documents/.config/git/config': Invalid argument
 #' @export
-create_sup_complete <- function(sup_control, sup_control_second, db_path, matching_data) {
+create_sup_complete <- function(all_sup, db_path, matching_data) {
     
     
-    sup_complete <- bind_rows(sup_control, sup_control_second) %>%   
+    sup_complete <- all_sup %>%   
         mutate(across(everything(), ~replace(., . == "", NA))) %>% 
-        filter(!is.na(sup_name_first)) %>% 
+        filter(!is.na(sup_name_first)) %>%
+        dplyr::select(-sup_vedidk, -sec_sup_vedidk, -ID) %>% 
         distinct() 
     
     

### 2023-10-05 R/match_data_prep.R

@@ -8,7 +8,7 @@
 #' @return
 #' @author fatal: unable to access 'C:/Users/David Jank?/Documents/.config/git/config': Invalid argument
 #' @export
-match_data_prep <- function(db_path, ids, gender, sup_control, sup_control_second) {
+match_data_prep <- function(db_path, ids, gender, blacklist_control) {
 
     
     con <-  DBI::dbConnect(RSQLite::SQLite(), db_path)
@@ -52,11 +52,13 @@ match_data_prep <- function(db_path, ids, gender, sup_control, sup_control_secon
     
     #number of wos/scopus publications up to 2014 (ie the year when the grant was awarded)
     
-    control_id <- n_pubs_types2014$id_unique
-    n_pubs_ws2014 <- dplyr::tbl(con, "riv_disc") %>% 
-        filter(id_unique %in% control_id) %>% #it doesn't really matter whether I use this filter or not - it always come with the same result which is weird
-        distinct() %>% 
-        dplyr::collect() %>% 
+    n_pubs_ws2014 <- DBI::dbReadTable(con, "riv_disc") %>%
+        dplyr::select(id_unique, utwos, eid) %>%
+        tidyr::unite(ws, c(utwos, eid), na.rm = TRUE) %>%
+        mutate(across(everything(), ~replace(., . == "", NA))) %>%
+        filter(!is.na(ws)) %>% 
+        filter(id_unique %in% n_pubs_types2014$id_unique) %>% #it doesn't really matter whether I use this filter or not - it always come with the same result which is weird
+        distinct() %>%  
         as_tibble()
     
     n_pubs_ws2014 <- left_join(n_pubs_ws2014, n_pubs_filtered2014, by = "id_unique") 
@@ -487,7 +489,11 @@ match_data_prep <- function(db_path, ids, gender, sup_control, sup_control_secon
     
     #number of wos/scopus publications up to 2015 (ie the year when the grant was awarded)
     
-    n_pubs_ws2015 <- DBI::dbReadTable(con, "riv_disc") %>% 
+    n_pubs_ws2015 <- DBI::dbReadTable(con, "riv_disc") %>%
+        dplyr::select(id_unique, utwos, eid) %>% 
+        tidyr::unite(ws, c(utwos, eid), na.rm = TRUE) %>%
+        mutate(across(everything(), ~replace(., . == "", NA))) %>%
+        filter(!is.na(ws)) %>% 
[…]

### 2023-10-05 R/read_one_author.R

@@ -48,7 +48,7 @@ read_one_author <- function(db_path, ids_complete, matching, ids_full_vector, in
      # purrr::when(matching$independence_timing == "before_intervention" ~ filter(., year <= matching$treatment_year), ~ filter(., year >= matching$treatment_year)) %>% 
      as_tibble()
      
-     one_vedidk_filtered_pubs <- if(unique(one_vedidk_filtered_pubs$independence_timing) == "before_intervention"){filter(one_vedidk_filtered_pubs, year <= intervention_year)}else{filter(one_vedidk_filtered_pubs, year >= intervention_year)}
+     one_vedidk_filtered_pubs <- if(unique(one_vedidk_filtered_pubs$independence_timing) == "before_intervention"){filter(one_vedidk_filtered_pubs, year < intervention_year)}else{filter(one_vedidk_filtered_pubs, year >= intervention_year)}
      
      
      

### 2023-10-25 _targets.Rmd
final_update, increased number of random publication sample

@@
       urls = Sys.getenv("link_to_manual_sup_search"),
-      paths = here::here("data", "raw", "manual_sup_search.csv")),
+      paths = here::here("data", "raw", "manual_sup_search_4.csv")),
   tarchetypes::tar_download(sup_path_second,
@@
 
- tar_target(sup_complete, create_sup_complete(all_sup, db_path, matching_data)),
+ tar_target(sup_complete, create_sup_complete(all_sup, sup_control, db_path, matching_data)),
      tar_target(ids_complete, create_ids_complete(ids, db_path, matching_data)),

### 2023-10-25 article.Rmd
final_update, increased number of random publication sample

@@
 
+## Intro - full
+
+To what extent is scientific progress conserved and impeded by novices mirroring seniors’ research agendas?
+Such a phenomenon is likely to occur because following tradition is usually a more beneficial and safer option for novices.
+Indeed, empirical data suggest that this strategy is chosen by a majority of researchers (@foster2015), and only a small fraction dares to deviate and explore the cognitive map of science more rapidly.
+For early career researchers specifically, partnering with already well-established seniors provides a large career boost (@li2019) and being thematically closer to their PhD as well as post-doc advisor increases the probability of continuing in academia and having more mentees later on (@lienard2018).
+However, this effect might stifle scientific progress as it leads to a slower exploration of its cognitive map (@rzhetsky2015).
+Moreover, this mirroring further strengthens the existing positions of senior faculty, making little space for disrupting the status quo and creating new perspectives.
+This was illustrated by @azoulay2010, who investigated the effects of unexpected deaths of prominent scientists in their research fields and their collaborators' careers.
+They found a decrease in the productivity of junior collaborators and an increase in published work by young newcomers in the field rewarded by an increased citation rate.
+That suggests the sudden departures of prominent scientists gave room for more disruptive changes in the field and for bringing new ideas and perspectives while harming the status quo holders who worked with the prominent scientists on their research agendas - a “Goliath effect,” as coined by @wang2021, p.42).
+
+This mirroring effect is also closely connected to the concept of academic inbreeding (@machacek2022), which focuses more on academic mobility and conservation of institutional habitus rather than specifically on the inheritance of research agendas.
+However, inbreeding is also often thought to increase dependence and decrease exploration of new ideas.
+
+As younger researchers are already more likely to come up with new topics and ideas (@packalen2019), it would be fitting to empower them and stimulate their independence so that they can “challenge the existing common views and open up new lines of research” (@vandenbesselaarMeasuringResearcherIndependence2019, p.2) and accelerate scientific progress rather than recreate the existing status quo.
+An independent investigator is then defined by the US National Academies of Science (NAS) as “one who enjoys the independence of thought—the freedom to define the problem of interest and to choose or develop the best strategies and approaches to addressing that problem–especially during the earlier career phase” (@vandenbesselaarMeasuringResearcherIndependence2019, 2019, p.4).
+Such a definition does not necessarily put independence in relation to other actors (e.g.
+one’s PhD advisor), but only in relation to one’s own freedom and resources.
+However other institutions, such as European Research Council via their Starting Grants scheme (@neufeldPeerReviewbasedSelection2013) think of independence in a relational manner, in terms of having one (or a few) publications without the former PhD supervisor being co-author; being PI on a grant; or being lab director or research leader.
+
+Developing independence is also one of the things that the system of science expects from its members - it is one of the criteria often used for assessing researchers for hiring, tenure and promotion (@vanarensbergenDifferentViewsScholarly2014; @moherAssessingScientistsHiring2018), constituting one factor of research excellence.
+Even from the perspective of scholarly output, protégés were found to “do their best work when they break from their mentor’s research topics and coauthor no more than a small portion of their overall research with their mentors” (@ma2020).
+@lienard2018 found that making a larger thematic step from the PhD advisor and finding a post-doc advisor with less similar interests was also related to increased chances of continuing in academia and having more mentees later on (although under the condition that one remains thematically close to the post-doc advisor).
+There is also some direct preliminary evidence that higher independence modestly correlates with the number of citations acquired (Rojko & Lužar, 2022), but others argue that even the research systems with very low independence can create a lot of scientific impact, and thus the relationships between independence and impact might not be as clear (Gläser et al., 2021)
+
+However, developing this independence does not go without saying.
+There are few known factors influencing the level of research independence.
+One of them is study discipline.
+Based on some early empirical studies (@rojkoScientificPerformanceResearch2022), it seems that researchers in disciplines such as philosophy, psychology; religion, theology; social sciences; the arts, recreation, entertainment, sport; language, linguistics, literature; and geography, biography, history experience significantly higher levels of independence on their PhD advisor than researchers in disciplines such as science and knowledge, organization, computer science, information, documentation, librarianship, institutions, publications; mathematics, natural sciences; and applied sciences, medicine, technology.
+
+Interestingly, there is also some evidence that the propensity to cognitive independence might be inherited and passed down from generation to generation in mentor-mentee relationships (@yoshioka-kobayashi2021) - perhaps it is not only research agendas that students inherit from their advisors but also the tendency to deviate from those research agendas.
+
+In recent decades, there has been a worry that researchers’ independence is decreasing, illustrated by an increase in the age at which researchers received their first grant (@powell2016, @christian2021; and NAS, 2005; @danielsGenerationRiskYoung2015 for US biomedical researchers specifically), as well as direct measures of new researchers becoming more dependent on their PhD advisors across almost all disciplines in Slovenia (@rojkoScientificPerformanceResearch2022, table 6 on p.9).
+These trends have motivated some to create new proposals for funding agencies and other research funders in order to support early career researchers (@dewinde2021)
+
+Perhaps to tackle this trend, many grant agencies decided to support early career researcher by funding.
+Some have decided to tackle this trend by giving advantage to first-awardees and early career researchers in their usual distribution process, while others have created specific programmes designated to funding young researchers soon, usually up to 8 years, after finishing their PhD.
+Such programmes have often explicitly stated goals of helping researchers become more independent, set up their own research groups and open up new lines of research.
+Examples of such programmes could be Starting Grants by European Research Council (@StartingGrantERC), Junior project and Junior Star by Czech Science Foundation (2020), Walter N.
+Benjamin Programme by DFG (@WalterBenjaminProgramme), Innovation Research Incentives Scheme by Netherlands Organization of Scientific Research (NWO) (2021).
+
+Grant funding mechanisms have previously been shown to stimulate productivity in terms of the number of publications and impact in terms of citations (@gallo2018; for the Czech environment specifically see @bajgar2021; notable exception is @vandenbesselaar2015, who specifically looked at funding programmes for early career researchers and found small or no effect), and even scientific novelty (@wang2018, or, as some authors argue, rather interdisciplinarity: @fontana2020).
+In terms of career progress, obtaining grant funding was connected to significantly higher chances of career progression and obtaining a professorship (@bloch2014, @vandenbesselaar2015).
+
+Funding is thus thought to be one of the mechanisms that could stimulate researchers' independence.
+However, there hasn’t been much effort focused on quantifying this phenomenon.
+Some studies try to measure independence in a simple way, as a ratio of publications the given researcher produced without their supervisor divided by the total number of publications of the given researchers (e.g.
+@rojkoScientificPerformanceResearch2022).
+However, such an indicator could be misleading in the world of team science, and also only focuses on collaborations, not tracking whether a given researcher becomes independent in their thinking and research topics.
+@vandenbesselaarMeasuringResearcherIndependence2019 therefore proposed a more complex indicator for measuring researcher independence on the individual level, based on co-authorship network and topical overlaps.
+Their measure uses only information about publications’ characteristics (authorship and reference list) regardless of their impacts, unlike other alternative measures that focus solely on the impact of the independent work in terms of received citations (Dey, et al., 2021 -> ALIS, citation need repair).
+
+Understanding the impact of early-career funding on research independence is crucial for shaping future funding policies and, ultimately, the trajectory of scientific innovation.
+This study serves as a pivotal step in quantifying that impact, providing actionable insights for funding agencies and academic institutions alike.
+
 ## Intro 1: focus on the bigger picture, sociology and policy perspective
@@
 They found a decrease in the productivity of junior collaborators and an increase in published work by young newcomers to the field rewarded by an increased citation rate.
-That suggests the sudden deaths of prominent scientists gave room for more disruptive changes in the field and for bringing new ideas and perspectives while harming the status quo holders who worked with the prominent scientists on their research agendas - a “Goliath effect”, as coined by @wang2021, p.42).
+That suggests the sudden departures of prominent scientists gave room for more disruptive changes in the field and for bringing new ideas and perspectives while harming the status quo holders who worked with the prominent scientists on their research agendas - a “Goliath effect”, as coined by @wang2021, p.42).
 
@@
 
-# Results
-
 ## Descriptives
@@
 na_control2 <- nrow(d %>% filter(is.na(RII)) %>% filter(treatment == 2))
+
+na_counts_researchers <- round(nrow(d %>% filter(!is.na(sup_name)) %>% filter(is.na(pubs_number)) %>% filter(independence_timing == "after_intervention") %>% distinct(vedidk))/nrow(d %>% filter(independence_timing == "after_intervention") %>% distinct(vedidk))*100, 1)
+
+mean_pubs_after <- d %>%
+  filter(independence_timing == "after_intervention") %>%
+  group_by(vedidk) %>%
+  summarise(pubs_number = first(pubs_number)) %>% 
+  summarise(mean_pubs_number = mean(pubs_number, na.rm = TRUE)) %>%
+  pull()
 
@@
 df <- filtered_by_subclass %>% filter(independence_timing == "after_intervention")
+df$career_length2022 <- 2022-df$career_start_year
 numeric_vars <- df %>% 
   select(where(is.numeric)) %>% 
-  select(-weights, -funded_control, -id, -treatment_year, -career_start_year) %>% 
+  select(-weights, -funded_control, -id, -treatment_year, -career_start_year, -career_length, -pubs_total, -ws_pubs, -interdisc_proportion, -grants, -total_coauthor_count, -first_grant) %>% 
   names()
@@
 
+# Move 'career_length2022' row to the top for each table
+reorder_row <- function(tbl) {
+  return(tbl[c("career_length2022", setdiff(rownames(tbl), "career_length2022")), ])
+}
+
+table_after_1 <- reorder_row(table_after_1)
+table_after_0 <- reorder_row(table_after_0)
+table_after_2 <- reorder_row(table_after_2)
+
+# Re-combine tables
 combined_table_after <- cbind(table_after_1, table_after_0[, -1], table_after_2[, -1])
@@
 ```
+
+# Results
 
@@
 
-In the first analysis, we examined the effects of treatment, independence_timing, and their interaction on the dependent variable, researcher independence (RII) for the treatment group and unfunded control group.
-
-There was a significant main effect of independence_timing on RII, F(`r summary(result)$"Error: subclass:independence_timing"[[1]]$"Df"[1]`, `r format(summary(result)$"Error: subclass:independence_timing"[[1]]$"Df"[2])`) = `r format(summary(result)$"Error: subclass:independence_timing"[[1]]$"F value"[1], digits=2)`, p = `r format(summary(result)$"Error: subclass:independence_timing"[[1]]$"Pr(>F)"[1], digits=4)`).
-This effect accounted for approximately `r format(eta_sq_result[eta_sq_result$Parameter == "independence_timing", "Eta2_partial"] * 100, digits=2)`% of the observed variance (partial \(\eta^2 = `r eta_sq_result[eta_sq_result$Parameter == "independence_timing", "Eta2_partial"]`\), 95% CI [`r eta_sq_result[eta_sq_result$Parameter == "independence_timing", "CI_low"]`, `r eta_sq_result[eta_sq_result$Parameter == "independence_timing", "CI_high"]`]).
-
-Importantly, there was a significant interaction effect between treatment and independence_timing on independence, F(`r format(summary(result)$"Error: Within"[[1]]$"Df"[2])`, `r format(summary(result)$"Error: Within"[[1]]$"Df"[3])`) = `r format(summary(result)$"Error: Within"[[1]]$"F value"[2], digits=2)`, p = `r format(summary(result)$"Error: Within"[[1]]$"Pr(>F)"[2], digits=2)`.
-This interaction effect explained about `r format(eta_sq_result[eta_sq_result$Parameter == "treatment:independence_timing", "Eta2_partial"] * 100, digits=2)`% of the variability (partial \(\eta^2 = `r eta_sq_result[eta_sq_result$Parameter == "treatment:independence_timing", "Eta2_partial"]`\), 95% CI [`r eta_sq_result[eta_sq_result$Parameter == "treatment:independence_timing", "CI_low"]`, `r eta_sq_result[eta_sq_result$Parameter == "treatment:independence_timing", "CI_high"]`]).
+In the first analysis, we examined the effects of treatment, time, and their interaction on the dependent variable, researcher independence (RII) for the treatment group and unfunded control group.
+
+There was a significant main effect of time on RII, F(`r summary(result)$"Error: subclass:independence_timing"[[1]]$"Df"[1]`, `r format(summary(result)$"Error: subclass:independence_timing"[[1]]$"Df"[2])`) = `r format(summary(result)$"Error: subclass:independence_timing"[[1]]$"F value"[1], digits=2)`, p = `r round(summary(result)$"Error: subclass:independence_timing"[[1]]$"Pr(>F)"[1], 3)`).
+This effect accounted for approximately `r format(eta_sq_result[eta_sq_result$Parameter == "independence_timing", "Eta2_partial"] * 100, digits=2)`% of the observed variance (partial \(\eta^2 = `r round(eta_sq_result[eta_sq_result$Parameter == "independence_timing", "Eta2_partial"], 3)`\), 95% CI [`r round(eta_sq_result[eta_sq_result$Parameter == "independence_timing", "CI_low"], 3)`, `r eta_sq_result[eta_sq_result$Parameter == "independence_timing", "CI_high"]`]).
+
+Importantly, there was a significant interaction effect between treatment and time on independence, F(`r format(summary(result)$"Error: Within"[[1]]$"Df"[2])`, `r format(summary(result)$"Error: Within"[[1]]$"Df"[3])`) = `r format(summary(result)$"Error: Within"[[1]]$"F value"[2], digits=2)`, p = `r format(summary(result)$"Error: Within"[[1]]$"Pr(>F)"[2], digits=2)`.
+This interaction effect explained about `r format(eta_sq_result[eta_sq_result$Parameter == "treatment:independence_timing", "Eta2_partial"] * 100, digits=2)`% of the variability (partial \(\eta^2 = `r round(eta_sq_result[eta_sq_result$Parameter == "treatment:independence_timing", "Eta2_partial"], 3)`\), 95% CI [`r eta_sq_result[eta_sq_result$Parameter == "treatment:independence_timing", "CI_low"]`, `r round(eta_sq_result[eta_sq_result$Parameter == "treatment:independence_timing", "CI_high"], 3)`]).
 
@@
 This suggests that there are statistically significant differences in the RII based on the field of study.
-Specifically, adding the field of study to the model resulted in a significant increase in the log-likelihood by `r anova_result$L.Ratio[2]` units (p < `r anova_result$"p-value"[2]`), emphasizing its importance as a predictor.
-Specifically, compared to the Engineering and Technology field, being in the Medical and Health Sciences field is associated with a decrease in RII by `r  coef(model_summary)["fieldMedical and Health Sciences", 1]` units, on average (p = `r coef(model_summary)["fieldMedical and Health Sciences", 4]`), while being in the Social Sciences field is associated with an increase in RII by `r coef(model_summary)["fieldSocial Sciences", 1]` units (p = `r coef(model_summary)["fieldSocial Sciences", 4]`).
+Specifically, adding the field of study to the model resulted in a significant increase in the log-likelihood by `r round(anova_result$L.Ratio[2], 2)` units (p < `r round(anova_result$"p-value"[2], 3)`), emphasizing its importance as a predictor.
+Specifically, compared to the Engineering and Technology field, being in the Medical and Health Sciences field is associated with a decrease in RII by `r  round(coef(model_summary)["fieldMedical and Health Sciences", 1], 2)` units, on average (p = `r round(coef(model_summary)["fieldMedical and Health Sciences", 4], 3)`), while being in the Social Sciences field is associated with an increase in RII by `r round(coef(model_summary)["fieldSocial Sciences", 1], 2)` units (p = `r round(coef(model_summary)["fieldSocial Sciences", 4], 3)`).
 There are no statistically significant differences between Natural Sciences and Engineering and Technology.
@@
 In the second analysis, we examined the effects of treatment, independence_timing, and their interaction on the researcher independence (RII) for the treatment group and funded control group.
-Again, there was a significant main effect of time on independence, F(`r format(summary(result2)$"Error: subclass:independence_timing"[[1]]$"Df"[1])`, `r format(summary(result2)$"Error: subclass:independence_timing"[[1]]$"Df"[2])`) = `r format(summary(result2)$"Error: subclass:independence_timing"[[1]]$"F value"[1], digits=2)`, p = `r format(summary(result2)$"Error: subclass:independence_timing"[[1]]$"Pr(>F)"[1], digits=4)`).
-The effect accounted for approximately `r format(eta_sq_result2[eta_sq_result2$Parameter == "independence_timing", "Eta2_partial"] * 100, digits=2)`% of the observed variance (partial \(\eta^2 = `r eta_sq_result2[eta_sq_result2$Parameter == "independence_timing", "Eta2_partial"]`\), 95% CI [`r eta_sq_result2[eta_sq_result2$Parameter == "independence_timing", "CI_low"]`, `r eta_sq_result2[eta_sq_result2$Parameter == "independence_timing", "CI_high"]`]).
+Again, there was a significant main effect of time on independence, F(`r format(summary(result2)$"Error: subclass:independence_timing"[[1]]$"Df"[1])`, `r format(summary(result2)$"Error: subclass:independence_timing"[[1]]$"Df"[2])`) = `r format(summary(result2)$"Error: subclass:independence_timing"[[1]]$"F value"[1], digits=2)`, p = `r round(summary(result2)$"Error: subclass:independence_timing"[[1]]$"Pr(>F)"[1], 3)`).
+The effect accounted for approximately `r format(eta_sq_result2[eta_sq_result2$Parameter == "independence_timing", "Eta2_partial"] * 100, digits=2)`% of the observed variance (partial \(\eta^2 = `r round(eta_sq_result2[eta_sq_result2$Parameter == "independence_timing", "Eta2_partial"], 3)`\), 95% CI [`r round(eta_sq_result2[eta_sq_result2$Parameter == "independence_timing", "CI_low"], 3)`, `r eta_sq_result2[eta_sq_result2$Parameter == "independence_timing", "CI_high"]`]).
 
 Importantly, this time the interaction effect between treatment and time was not significant, F(`r format(summary(result2)$"Error: Within"[[1]]$"Df"[2])`, `r format(summary(result2)$"Error: Within"[[1]]$"Df"[3])`) = `r format(summary(result2)$"Error: Within"[[1]]$"F value"[2], digits=2)`, p = `r format(summary(result2)$"Error: Within"[[1]]$"Pr(>F)"[2], digits=2)`.
-This interaction effect explained about `r format(eta_sq_result2[eta_sq_result2$Parameter == "treatment:independence_timing", "Eta2_partial"] * 100, digits=2)`% of the variability (partial \(\eta^2 = `r eta_sq_result2[eta_sq_result2$Parameter == "treatment:independence_timing", "Eta2_partial"]`\), 95% CI [`r eta_sq_result2[eta_sq_result2$Parameter == "treatment:independence_timing", "CI_low"]`, `r eta_sq_result2[eta_sq_result2$Parameter == "treatment:independence_timing", "CI_high"]`]), suggesting that funding has the same effects, regardless of its type or source.
+This interaction effect explained about `r format(eta_sq_result2[eta_sq_result2$Parameter == "treatment:independence_timing", "Eta2_partial"] * 100, digits=2)`% of the variability (partial \(\eta^2 = `r round(eta_sq_result2[eta_sq_result2$Parameter == "treatment:independence_timing", "Eta2_partial"], 3)`\), 95% CI [`r round(eta_sq_result2[eta_sq_result2$Parameter == "treatment:independence_timing", "CI_low"], 3)`, `r eta_sq_result2[eta_sq_result2$Parameter == "treatment:independence_timing", "CI_high"]`]), suggesting that funding has the same effects, regardless of its type or source.
 
 Same as in previous chapter, the comparison of models suggested that there are statistically significant differences in the RII based on the field of study.
-Specifically, adding the field of study to the model resulted in a significant increase in the log-likelihood by `r anova_result2$L.Ratio[2]` units (p < `r anova_result2$"p-value"[2]`), emphasizing its importance as a predictor.
-Specifically, compared to the Engineering and Technology field, being in the Medical and Health Sciences field is associated with a decrease in RII by `r  coef(model_summary2)["fieldMedical and Health Sciences", 1]` units, on average (p = `r coef(model_summary2)["fieldMedical and Health Sciences", 4]`), while being in the Social Sciences field is associated with an increase in RII by `r coef(model_summary2)["fieldSocial Sciences", 1]` units (p = `r coef(model_summary2)["fieldSocial Sciences", 4]`).
+Specifically, adding the field of study to the model resulted in a significant increase in the log-likelihood by `r round(anova_result2$L.Ratio[2], 2)` units (p < `r round(anova_result2$"p-value"[2], 3)`), emphasizing its importance as a predictor.
+Specifically, compared to the Engineering and Technology field, being in the Medical and Health Sciences field is associated with a decrease in RII by `r  round(coef(model_summary2)["fieldMedical and Health Sciences", 1], 2)` units, on average (p = `r round(coef(model_summary2)["fieldMedical and Health Sciences", 4], 3)`), while being in the Social Sciences field is associated with an increase in RII by `r round(coef(model_summary2)["fieldSocial Sciences", 1], 2)` units (p = `r round(coef(model_summary2)["fieldSocial Sciences", 4], 3)`).
 There are no statistically significant differences between Natural Sciences and Engineering and Technology.
@@
 This might suggest that while funding helps early career researchers to become more independent from their PhD advisors overall, this is likely driven creating new collaboration networks, rather than "opening up new lines of research".
-That being said, the average level of cognitive (topical) independence is around `r ind_top_mean_before` (which could roughly be translated as `r round(ind_top_mean_before*100, 2)` %) even before the funding intervention and rises to about `r ind_top_mean_after` (`r round(ind_top_mean_after*100, 2)` %) in the time after the intervention.
+That being said, the average level of cognitive (topical) independence is around `r round(ind_top_mean_before, 2)` (which could roughly be translated as `r round(ind_top_mean_before*100, 2)` %) even before the funding intervention and rises to about `r round(ind_top_mean_after, 2)` (`r round(ind_top_mean_after*100, 2)` %) in the time after the intervention.
 
@@
 
-<!-- Anyway, rather than granting funded researchers greater independence compared to the unfunded control group, it seems that the funding programme we examined sampled less independent researchers and then allowed them to catch up with the unfunded control group via providing them funding.
--->
+Given that funding for early career researchers does not have effect on stimulating their cognitive independence, does it make sense to continue providing it?
+While funding itself might not be the main driver of cognitive independence, its might still play an important role - for example, it could be a necessary thought not sufficient condition for the development of independence.
+From a common sense view, it is hard to imagine that researchers can develop much of independence while working on someone else's (often their advisor') projects.
+Moreover, funding did show to modestly stimulate creation of more independent collaborative networks, which might have a value in itself by establishing early career researchers in the scientific community and making their positions more robust.
+This would hopefully enable them to explore more rapidly later on, though that is not guaranteed.
+In any case, our results suggest that the search for factors and interventions stimulating researchers' explorative behaviour should continue.
+
+Main value of this paper is manyfold:
+- it investigated one potential factor (funding) hypothesized to stimulate researcher independence, rendering this factor unimportant, contrary to expectations
+- it confirmed there are meaningful differences in level of independence across disciplines
+- it has illuminated the magnitude of cognitive independence experienced by researchers early in their careers and its development to later stages, contributing to the discussions about tradition and innovation in research topic choice strategies and recreating status quo in science
 
@@
 
-One of the main limitations of this study is that it only focuses on Czech environment - researchers growing up and spending most of their careers in the Czech Republic, only taking into account publications affiliated with Czech research institutions.
+One of the main limitations of this study is that it only focuses on Czech environment - researchers growing up and spending most of their careers in the Czech Republic, only taking into account their publications affiliated with Czech research institutions.
 Studies testing our results on samples from other countries, and possibly tracking international mobility would strengthen our conclusions.
 
+Another potential limitation is the length of the time after the intervention.
+We have tracked the effects of funding between 2-7 years after the project started, at a point where researchers created on average `r round(mean_pubs_after, 1)` publications (while `r na_counts_researchers` % of them have created less than 3 and were deleted from this analysis).
+It might be possible that independence needs more time to develop and had we measured the effects later, we would have found stronger effects.
+
 Further research could look more into which other factors influence researcher independence (especially the cognitive part) and how strongly compared to grant funding.
+
+## Conclusion
+
+Our results showed that funding helps modestly to stimulate collaborative independence of early career researchers, but does not stimulate their cognitive independence.
+The largest effect on increase in composite independence was time - over time, researchers become more independent, regardless of their access to funding or their study discipline.
+There were also significant differences in independence level across study disciplines, where social sciences and humanities allowed for more independence than medical and health sciences and natural sciences.
+Researchers usually start with around 40 % of topics not shared by their PhD advisor early on after finishing their PhD and grow more independent over time (up to 47 % 13.5 years after their first publication).
+Search for factors and interventions stimulating researchers' cognitive independence and explorative behaviour should thus continue.
 

### 2023-10-25 article.Rmd
small changes in text

@@
 We also tested an assumption that had a hope of reducing time intensity of data collection by substitution it for algorithmic approach: using the "most frequent co-author of the first 5 publications" as a proxy to identify supervisors.
-Crosschecking this proxy with the actual data about supervisors we found manually, we found that this algorithm was able to identify supervisors correctly in about XXXXX % of cases (see the Attachment 1).
+Crosschecking this proxy with the actual data about supervisors we found manually, we found that this algorithm was able to identify supervisors correctly in about 56 % of cases (see the Attachment 1).
 
@@
 In determining the proportion of a researcher's own research topics (I4), we opted for text-based topic modeling utilizing publication titles and abstracts, diverging from the originally suggested bibliographic coupling method.
-Initially, we conducted a random sampling of 1200 publications from a set of all publications produced by researchers affiliated with Czech institutions as cataloged in the RIV database, estimated number of topics using Griffiths2004 indicator and calculated LDA topic model on this set of publications.
+Initially, we conducted a random sampling of 3000 publications from a set of all publications produced by researchers affiliated with Czech institutions as cataloged in the RIV database, estimated number of topics using Griffiths2004 indicator and calculated LDA topic model on this set of publications.
 Then we  compiled all publications generated by the researchers within our sample and their respective supervisors.
@@
 
-To calculate this indicator, we required at least 3 publications. This led to an increased number of missing observations (see section Results -> Descriptives -> Missing data).
+To calculate this indicator, we required at least 3 publications. This led to an increased number of missing observations (see section Descriptives -> Missing data).
 

### 2023-11-01 article.Rmd
changes in structure of the control groups to better match "funded" and "unfunded" terms

@@
 
-## Intro 1: focus on the bigger picture, sociology and policy perspective
-
-Researchers’ independence from their PhD advisor is one of the criteria often used for assessing researchers for hiring, tenure and promotion (@vanarensbergenDifferentViewsScholarly2014; @moherAssessingScientistsHiring2018), constituting one factor of research excellence.
-The promise of independence is that researchers will “challenge the existing common views and open up new lines of research” (@vandenbesselaarMeasuringResearcherIndependence2019, p.2).
-
-Early career researcher independence is central to the long-lasting debate about how science progresses - whether it is indeed guided mostly by the truth and empirical evidence, or whether more social and demographic factors might play an important role.
-@hull1978 found that even more senior researchers readily updated their beliefs with the new evidence, supporting the former, though many (famously including Max Planck) observed that senior researchers were more fixed in their beliefs and new ideas were mostly brought up by the incoming early career researchers giving rise to the “science moves forward one funeral at the time” proverb.
-More recently, @azoulay2010 provided further support for the latter by investigating the effects of unexpected deaths of prominent scientists on their research fields and their collaborators' careers.
-They found a decrease in the productivity of junior collaborators and an increase in published work by young newcomers to the field rewarded by an increased citation rate.
-That suggests the sudden departures of prominent scientists gave room for more disruptive changes in the field and for bringing new ideas and perspectives while harming the status quo holders who worked with the prominent scientists on their research agendas - a “Goliath effect”, as coined by @wang2021, p.42).
-
-/// here I can potentially talk a bit more about Inheritance of research agendas - how often does that happen, etc..///
-
-Insofar as the latter is true, in order to accelerate scientific progress, we might want to tackle this trend by supporting early career researchers to gain more independence from their PhD advisors.
-Younger researchers are already more likely to come up with new topics and ideas, as found by @packalen2019 by looking at the usage of new words in research papers.
-However, they might still feel various kinds of pressures to stick with their mentor’s research agendas and lack of opportunities to become more independent.
-In recent decades, there has been a worry that researchers’ independence is decreasing, illustrated by an increase in age at which US biomedical researchers received their first grant (NAS, 2005; @danielsGenerationRiskYoung2015), as well as direct measures of new researchers becoming more dependent on their PhD advisors across almost all disciplines in Slovenia (@rojkoScientificPerformanceResearch2022, table 6 on p.9).
-
-Perhaps to tackle this trend, many grant agencies decided to start awarding grants for early career researchers, usually up to 8 years after finishing their PhD.
-Such programmes have often explicitly stated goals of helping researchers become more independent, set up their own research group and open up new lines of research.
-The examples of such programmes could be Starting Grants by European Research Council (@StartingGrantERC), Junior project and Junior Star by Czech Science Foundation (2020), Walter N.
-Benjamin Programme by DFG (@WalterBenjaminProgramme), Innovation Research Incentives Scheme by Netherlands Organization of Scientific Research (NWO) (2021).
-
-Moreover, stimulating independence and supporting researchers to open up new lines of research is also a worthy policy goal regardless of researchers’ age.
-@rzhetsky2015 found that biomedical researchers are in practice often choosing less exploratory strategies for topic choice than would be socially optimal if we wanted to explore the cognitive map of science (or in this case chemicals) as fast as possible, and their choices become more conservative over time.
-They suggest that increased interdisciplinarity, risk-taking and the publication of experimental failures would substantially improve the speed of discovery.
-
-//// factors influencing independence////
-There are few known factors influencing the level of research independence.
-One of them is study discipline.
-Based on some early empirical studies (@rojkoScientificPerformanceResearch2022), it seems that researchers in disciplines such as philosophy, psychology; religion, theology; social sciences; the arts, recreation, entertainment, sport; language, linguistics, literature; and geography, biography, history experience significantly higher levels of independence on their PhD advisor than researchers in disciplines such as science and knowledge, organization, computer science, information, documentation, librarianship, institutions, publications; mathematics, natural sciences; and applied sciences, medicine, technology.
-
-Interestingly, there is also some evidence that the propensity to cognitive independence might be inherited and passed down from generation to generation in mentor-mentee relationships @yoshioka-kobayashi2021 - perhaps it is not only research agendas that students inherit from their advisors but also the tendency to deviate from those research agendas.
-This might also suggest that to increase junior researchers’ independence, we might want to teach their advisors to be more independent, in order to have a ripple effect down the line.
-
-Finally, there is also some preliminary evidence that higher independence modestly correlates with the number of citations acquired (@rojkoScientificPerformanceResearch2022), but others argue that even the research systems with very low independence can create a lot of scientific impact, and thus the relationships between independence and impact might not be as clear (@glaserIndependenceResearchReview2022)
-
-Although researcher independence seems to be an important feature that is acknowledged by many actors in the research systems and that research funders try to stimulate, there hasn’t been much effort focused on quantifying this phenomenon.
-Some studies try to measure independence in a simple way, as a ratio of publications the given researcher produced without their supervisor divided by the total number of publications of the given researchers (e.g.
-@rojkoScientificPerformanceResearch2022).
-However, such an indicator could be misleading in the world of team science, and also only focuses on collaborations, not tracking whether a given researcher becomes independent in their thinking and research topics.
-[@vandenbesselaarMeasuringResearcherIndependence2019] therefore proposed a more complex indicator for measuring researcher independence on the individual level, based on co-authorship network and topical overlaps.
-Their measure uses only information about publications’ characteristics (authorship and reference list) regardless of their impacts, unlike other alternative measures that focus solely on the impact of the independent work in terms of received citations (Dey, et al., 2021, @ALISNovelMetric).
-
-Since the explicit goal of many funding instruments that are being used by research funders all over the world is to help early career researchers become independent, we decided to use the newly created indicators to assess the extent, to which such programmes influence researchers' independence.
-
-## Intro 2: Perspective of “What are the effects of competitive grant funding? And looking at independence as one of such effects”
-
-///Primer of grant-making context:
-
-Grant funding mechanisms have previously been shown to stimulate productivity in terms of the number of publications, impact in terms of citations, and even scientific novelty (@wang2018, or as some authors argue rather interdisciplinarity: @fontana2020).
-In terms of researchers’ careers, obtaining grant funding was connected to significantly higher chances of career progression and obtaining a professorship (@bloch2014).
-
-///Though there is still some disagreement about the direction and magnitude of some of these effects, c.f.
-@@glaserIndependenceResearchReview2022 on novelty.
---> here I can potentially go more in-depth into the critiques of grant funding mechanisms?
-E.g.
-spell out the critiques, such that they are strengthening the Matthews effect, they reduce novelty, etc....
-
-However, there are still several components of research excellence (see @vanarensbergenDifferentViewsScholarly2014; @moherAssessingScientistsHiring2018) that have not been investigated yet, with one having specifically important effects on researchers’ carers and development: their independence.
-Researchers’ independence from their PhD advisor is one of the criteria often used for assessing researchers for hiring, tenure and promotion (@vanarensbergenDifferentViewsScholarly2014; @moherAssessingScientistsHiring2018).
-The promise of independence is that researchers will “challenge the existing common views and open up new lines of research” (@vandenbesselaarMeasuringResearcherIndependence2019, p.2).
-
-An independent investigator is then defined by the US National Academies of Science (NAS) as “one who enjoys independence of thought—the freedom to define the problem of interest and to choose or develop the best strategies and approaches to address that problem–especially during the earlier career phase” (@vandenbesselaarMeasuringResearcherIndependence2019, p.4).
-Such a definition does not necessarily put independence in relation to other actors (e.g.
-one’s PhD advisor), but only in relation to one’s own freedom and resources.
-However other institutions, such as European Research Council via their Starting Grants scheme (@neufeldPeerReviewbasedSelection2013) think of independence in a relational manner, in terms of having one (or a few) publications without the former PhD supervisor being co-author; being PI on a grant; or being lab director or research leader.
-
-Based on some early empirical studies @rojkoScientificPerformanceResearch2022, it seems that researchers in disciplines such as philosophy, psychology; religion, theology; social sciences; the arts, recreation, entertainment, sport; language, linguistics, literature; and geography, biography, history experience significantly higher levels of independence on their PhD advisor than researchers in disciplines such as science and knowledge, organization, computer science, information, documentation, librarianship, institutions, publications; mathematics, natural sciences; and applied sciences, medicine, technology.
-There is also some preliminary evidence that higher independence modestly correlates with number of citations acquired (@rojkoScientificPerformanceResearch2022), but others argue that even the research systems with very low independence can create a lot of scientific impact, and thus the relationships between independence and impact might not be as clear (@glaserIndependenceResearchReview2022)
-
-In recent decades, there has been a worry that researchers’ indepedence is decreasing, illustrated by increase in age at which US (biomedical) researchers received their first grant (NAS, 2005; @danielsGenerationRiskYoung2015), as well as direct measures of new researchers becoming more dependent on their PhD advisors across almost all disciplines in Slovenia (@rojkoScientificPerformanceResearch2022, table 6 on p.9).
-Perhaps to tackle this trend, many grant agencies decided to start awarding grants for early career researchers, usually up to 8 years after finishing their PhD.
-Such programmes have often explicitly stated goals of helping researchers become more independent, set up their own research group and open up new lines of research.
-The examples of such programmes could be Starting Grants by European Research Council (@StartingGrantERC), Junior project and Junior Star by Czech Science Foundation (2020), Walter N.
-Benjamin Programme by DFG (@WalterBenjaminProgramme), Innovation Research Incentives Scheme by Netherlands Organization of Scientific Research (NWO) (2021)...
-something from the US would be also good)
-
-Although researcher independence seems to be important feature that is acknowledged by many actors in the research systems and that research funders try to stimulate, there hasn’t been much effort focused on quantifying this phenomenon.
-Some studies try to measure independence in a simple way, as a ratio of publications the given researcher produced without their supervisor divided by the total number of publications of the given researchers (e.g.
-@rojkoScientificPerformanceResearch2022).
-However, such indicator could be misleading in the world of team science, and also only focuses on collaborations, not tracking whether given researcher become independent in their thinking and research topics.
-[@vandenbesselaarMeasuringResearcherIndependence2019] therefore proposed more complex indicator for measuring researcher independence on the individual level, based on co-authorship network and topical overlaps.
-Their measure uses only information about publications’ characteristics (authorship and reference list) regardless of it’s impacts, unlike other alternative measures that focus solely on the impact of the independent work in terms of received citations (Dey, et al., 2021, @ALISNovelMetric).
-
-Since the explicit goal of many funding instruments that are being used by research funders all over the world is to help early career researchers become independent, we used the newly created indicators to assess the extent, to which such programmes influence researchers independence.
-
-H1: Researchers, who received funding from programmes aimed at funding early career researchers, will show more independence from their PhD advisors after receiving the funding than researchers who did not receive funding.
-
-H2: Researchers, who received funding from programmes aimed at funding early career researchers, will show more independence from their PhD advisors compared to similar researchers who received other types of funding at similar point in theri career.
-
-## Intro 3: focusing on support for early career researchers (and why is that important topic) and then mention the independence as one of the ways how we can test whether our support mechanisms for early stage researchers actually work
-
-Funding for early career researchers is an important topic in science funding policy discussions as it might have a significant impact on career progression of the new generations of researchers (@wright2017; @pickett2019; @vandenbesselaar2015).
-At the same time, the age of receiving a first grant has been growing significantly over the past decades (@powell2016, @christian2021).
-These trends have motivated some to create new proposals for funding agencies and other research funders in order to support early career researchers (@dewinde2021).
-Some funding agencies decided to tackle this trend by giving advantage to first-awardees and early career researchers in their usual distribution process, while others have created specific programmes designated to funding young researchers soon after their PhD.
-
-///maybe talk about other types of support that early career researchers get?
-Or maybe have another paragraph describing what does the life of early career researchers usually look like?
-(--> perhaps mentioning that the time to finish PhD gets longer and longer, people are now expected to do multiple post-docs, etc...
---> perhaps borrow some info from Science of Science book Careers section)///
-
-It is expected, that by giving early-stage researchers funding, they will be able to develop more independence and open up new lines of research (@vandenbesselaarMeasuringResearcherIndependence2019, p.2).
-Younger researchers are already more likely to come up with new topics and ideas, as found by [@packalen2019] by looking at the usage of new words in research papers.
-However, they might still feel various kinds of pressures to stick with their mentor’s research agendas and lack of opportunities to become more independent.
-In recent decades, there has been a worry that researchers’ independence is decreasing, illustrated by increase in age at which US (biomedical) researchers received their first grant (NAS, 2005; @danielsGenerationRiskYoung2015), as well as direct measures of new researchers becoming more dependent on their PhD advisors across almost all disciplines in Slovenia (@rojkoScientificPerformanceResearch2022, table 6 on p.9).
-///talk about the balance between experience and independence??///
-
-Perhaps to tackle this trend, many grant agencies decided to start awarding grants for early career researchers, usually up to 8 years after finishing their PhD.
-Such programmes have often explicitly stated goals of helping researchers become more independent, set up their own research group and open up new lines of research.
-The examples of such programmes could be Starting Grants by European Research Council (@StartingGrantERC), Junior project and Junior Star by Czech Science Foundation (2020), Walter N.
-Benjamin Programme by DFG (@WalterBenjaminProgramme), Innovation Research Incentives Scheme by Netherlands Organization of Scientific Research (NWO) (2021)...
-something from the US would be also good)
-
-Although researcher independence seems to be important feature that is acknowledged by many actors in the research systems and that research funders try to stimulate, there hasn’t been much effort focused on quantifying this phenomenon.
-Some studies try to measure independence in a simple way, as a ratio of publications the given researcher produced without their supervisor divided by the total number of publications of the given researchers (e.g.
-@rojkoScientificPerformanceResearch2022).
-However, such indicator could be misleading in the world of team science, and also only focuses on collaborations, not tracking whether given researcher become independent in their thinking and research topics.
-[@vandenbesselaarMeasuringResearcherIndependence2019] therefore proposed more complex indicator for measuring researcher independence on the individual level, based on co-authorship network and topical overlaps.
-Their measure uses only information about publications’ characteristics (authorship and reference list) regardless of it’s impacts, unlike other alternative measures that focus solely on the impact of the independent work in terms of received citations (Dey, et al., 2021, @ALISNovelMetric).
-
-Since the explicit goal of many funding instruments that are being used by research funders all over the world is to help early career researchers become independent, we would like to use the newly created indicators to assess the extent, to which such programmes influence researchers' independence.
-
 # Method
@@
 
-We calculated how many (Czech) grants each researcher has received prior to the intervention year (i.e. receiving a Junior Grant).
+We calculated how many (Czech) grants each researcher has received prior and 3 years after the intervention year (i.e.
+receiving a Junior Grant).
+We did not use this variable for matching, but for filtering out control group researchers pre-matching.
 
@@
 The distance was set to "mahalanobis".
-The matching was done in 1:3 ratio and with replacement.
-Manual search for supervisors of the matched control group observations was done by ranking the control group observation by distance from the treatment group observation and first searching for the supervisor of the closest control group observation, and if it was not possible to find it, then repeat the same for the second closest, etc...
-In the end each treatment observation was matched with exactly one control group observation which was closest but at the same time for which it was possible to identify their supervisor.
-
-We have created 2 control groups: one using the matching above and one similar but specifically containing only researchers who received their first grant (other than Junior Grant) around the same career age as researchers in our intervention group.
+The matching was done in 1:1 ratio and with replacement.
+
+Using the matching algorithm, we have created 2 control groups: "Unfunded" group did not receive any grants prior to and 3 years after the treatment year.
+"Funded" group was matched based on career year at which they received their first grant, ensuring that while treatment group researchers received Junior Grant, "funded" researchers received a different grant at the same time.
 That allowed us to better track the impact of any grant funding vs specifically Junior Grants funding on researchers’ independence.
@@
 
-BTW: there is an overlap between control group observations: `r overlap_control` observations from the unfunded control group also appears in the funded control group
+There is an overlap between control group observations: `r overlap_control` observations from the unfunded control group also appears in the funded control group, showing that they did eventually received grant at the similar time as those from treatment group.
 
@@
 Specifically, adding the field of study to the model resulted in a significant increase in the log-likelihood by `r round(anova_result$L.Ratio[2], 2)` units (p < `r round(anova_result$"p-value"[2], 3)`), emphasizing its importance as a predictor.
-Specifically, compared to the Engineering and Technology field, being in the Medical and Health Sciences field is associated with a decrease in RII by `r  round(coef(model_summary)["fieldMedical and Health Sciences", 1], 2)` units, on average (p = `r round(coef(model_summary)["fieldMedical and Health Sciences", 4], 3)`), while being in the Social Sciences field is associated with an increase in RII by `r round(coef(model_summary)["fieldSocial Sciences", 1], 2)` units (p = `r round(coef(model_summary)["fieldSocial Sciences", 4], 3)`).
+Specifically, compared to the Engineering and Technology field, being in the Medical and Health Sciences field is associated with a decrease in RII by `r  round(coef(model_summary)["fieldMedical and Health Sciences", 1], 2)` units, on average (p = `r round(coef(model_summary)["fieldMedical and Health Sciences", 4], 3)`), while being in the Humanities and Arts is associated with an increase in RII by `r round(coef(model_summary)["fieldHumanities and the Arts", 1], 2)` units (p = `r round(coef(model_summary)["fieldHumanities and the Arts", 4], 3)`).
 There are no statistically significant differences between Natural Sciences and Engineering and Technology.

### 2024-01-07 _targets.Rmd
final edits

@@
 ```{r, engine="targets", data_import}
+# Set global timeout for download operations
+options(timeout = 3000) # 50 minutes
+
 list(
@@
       urls = Sys.getenv("link_to_manual_sup_search"),
-      paths = here::here("data", "raw", "manual_sup_search_4.csv")),
+      paths = here::here("data", "raw", "manual_sup_search_6.csv")),
   tarchetypes::tar_download(sup_path_second,
@@
       urls = Sys.getenv("link_to_blacklist_control"),
-      paths = here::here("data", "raw", "blacklist_control_after_disamb.csv")),
+      paths = here::here("data", "raw", "blacklist_control_final_before_disamb.csv")),
   tarchetypes::tar_download(all_sup_path,

### 2024-01-08 _targets.Rmd
update dependencies

@@
 # load libraries for make
-tar_option_set(packages = c("dplyr",
+tar_option_set(packages = c("bookdown",
+                            "dplyr",
                             "tidyr",

### 2024-01-19 article.Rmd
start edits

--- 2023-10-25 article.Rmd
@@
 ---
-title: "Funding programmes for early career researchers marginally improves their collaboration independence, but not cognitive independence"
-author: "David Janků"
-date: "`r Sys.Date()`"
-output:
-  html_document:
-    df_print: paged
-  word_document: default
-always_allow_html: yes
+title: "Mission Unaccomplished: A Funding Programme for Early Career Researchers Fails to Promote Independence"
+author:
+- name: David Janků
+  affiliation: '[1] Centre for Science, Technology, and Society
+    Studies, Institute of Philosophy, Czech Academy of Sciences; [2] Institute of Sociological Studies, Faculty of Social Sciences,
+    Charles University'
+- name: Radim Hladík
+  affiliation: '[1] Centre for Science, Technology, and Society Studies, Institute
+    of Philosophy, Czech Academy of Sciences'
+output: bookdown::html_document2
+  # pdf_document: default
+  # html_document:
+
+  # word_document: default
+  # # bookdown::pdf_document2: default
+  # bookdown::html_document2: default
+  #  df_print: paged
+  #  number_sections: true
+  # bookdown::word_document2: default
 bibliography: merged.bib
 csl: apa.csl
+---
+<!-- \doublespacing -->
+
+## Acknowledgements
+
+This work was supported by the Czech Science Foundation (project no. GJ20-01752Y, _Funded and Unfunded Research in the Czech Republic: Scientometric Analysis and Topic Modeling_).
+
+## Declaration of Interest
+
+Your declaration of interest statement here.
+
+## Corresponding Author
+
+Name: David Janků 
+Affiliation: 
+[1] Centre for Science, Technology, and Society Studies, Institute of Philosophy, Czech Academy of Sciences
+[2] Institute of Sociological Studies, Faculty of Social Sciences, Charles University
+Address: Jilská 1, 110 00, Praha 1, Czech Republic  
+E-mail: david.janku@fsv.cuni.cz
+
+\newpage
+
 ---
@@
 
-Independence is important quality constituting one factor of research excellence, often used in assessments for hiring, tenure and promotion in academia [@moherAssessingScientistsHiring2018].
-From a bigger picture view, encouraging more independence might also lead to faster exploration of the cognitive map of science and thus lead to faster innovation.
-Many national research funders have created programmes specifically aimed at increasing independence of early career researchers, yet until recently, there was no quantifiable way to measure changes in independence.
-We employed recently proposed measure by @vandenbesselaarMeasuringResearcherIndependence2019 to asses whether one such funding programme by Czech Science Foundation is effective at stimulating more independence.
-We found that funding for early career researchers is effective at stimulating their independence, though the effect is relatively small (2 % of variance) and the source of funding does not matter.
-The funding also helped selected researchers to catch up with the unfunded group, rather than to outrun them.
-Additionally, we found differences in levels of independence across disciplines that were stable across time and treatment groups, with Social Sciences and Humanities showing highest independence, while Medical and Heath Sciences and Natural Sciences showing lowest independence.
+Independence is an important factor in research excellence, often assessed for hiring, tenure and promotion in academia.
+From a macro perspective, increased independence might also lead to faster exploration of the cognitive map of science and thus accelerate innovation.
+Many national research funders have created programmes specifically aimed at increasing independence of early career researchers.
+A quantifiable measure of such programmes' impact on changes in independence has long been lacking..
+We employed a recently proposed independence indicator [@vandenbesselaarMeasuringResearcherIndependence2019] to asses whether one such funding programme operated by Czech Science Foundation succeeds at stimulating independence.
+We found that the e funding scheme designed for early career researchers is not effective at stimulating their independence.
+Regardless of the type of funding, the strongest effect on independence growth is time, explaining around 60% of the variance in independence.
+Additionally, we found differences in levels of independence across disciplines that were stable across time and treatment groups, with Social Sciences and Humanities showing highest independence, while  Agricultural and Veterinary sciences and Medical and Health Sciences showing lowest independence.
+However, these differences reflect only changes in collaboration patterns, while there were no changes in cognitive patterns across disciplines and only modest changes across time (from 40 % to 46 % of topics not shared by their PhD advisor).
+
+## Keywords
+research independence; early career researchers; project funding; mentoring; counter-factual analysis; research evaluation
 
 # Intro
-
-## Intro - full
-
-To what extent is scientific progress conserved and impeded by novices mirroring seniors’ research agendas?
-Such a phenomenon is likely to occur because following tradition is usually a more beneficial and safer option for novices.
-Indeed, empirical data suggest that this strategy is chosen by a majority of researchers (@foster2015), and only a small fraction dares to deviate and explore the cognitive map of science more rapidly.
-For early career researchers specifically, partnering with already well-established seniors provides a large career boost (@li2019) and being thematically closer to their PhD as well as post-doc advisor increases the probability of continuing in academia and having more mentees later on (@lienard2018).
-However, this effect might stifle scientific progress as it leads to a slower exploration of its cognitive map (@rzhetsky2015).
-Moreover, this mirroring further strengthens the existing positions of senior faculty, making little space for disrupting the status quo and creating new perspectives.
-This was illustrated by @azoulay2010, who investigated the effects of unexpected deaths of prominent scientists in their research fields and their collaborators' careers.
-They found a decrease in the productivity of junior collaborators and an increase in published work by young newcomers in the field rewarded by an increased citation rate.
-That suggests the sudden departures of prominent scientists gave room for more disruptive changes in the field and for bringing new ideas and perspectives while harming the status quo holders who worked with the prominent scientists on their research agendas - a “Goliath effect,” as coined by @wang2021, p.42).
-
-This mirroring effect is also closely connected to the concept of academic inbreeding (@machacek2022), which focuses more on academic mobility and conservation of institutional habitus rather than specifically on the inheritance of research agendas.
-However, inbreeding is also often thought to increase dependence and decrease exploration of new ideas.
-
-As younger researchers are already more likely to come up with new topics and ideas (@packalen2019), it would be fitting to empower them and stimulate their independence so that they can “challenge the existing common views and open up new lines of research” (@vandenbesselaarMeasuringResearcherIndependence2019, p.2) and accelerate scientific progress rather than recreate the existing status quo.
-An independent investigator is then defined by the US National Academies of Science (NAS) as “one who enjoys the independence of thought—the freedom to define the problem of interest and to choose or develop the best strategies and approaches to addressing that problem–especially during the earlier career phase” (@vandenbesselaarMeasuringResearcherIndependence2019, 2019, p.4).
-Such a definition does not necessarily put independence in relation to other actors (e.g.
-one’s PhD advisor), but only in relation to one’s own freedom and resources.
-However other institutions, such as European Research Council via their Starting Grants scheme (@neufeldPeerReviewbasedSelection2013) think of independence in a relational manner, in terms of having one (or a few) publications without the former PhD supervisor being co-author; being PI on a grant; or being lab director or research leader.
-
-Developing independence is also one of the things that the system of science expects from its members - it is one of the criteria often used for assessing researchers for hiring, tenure and promotion (@vanarensbergenDifferentViewsScholarly2014; @moherAssessingScientistsHiring2018), constituting one factor of research excellence.
-Even from the perspective of scholarly output, protégés were found to “do their best work when they break from their mentor’s research topics and coauthor no more than a small portion of their overall research with their mentors” (@ma2020).
-@lienard2018 found that making a larger thematic step from the PhD advisor and finding a post-doc advisor with less similar interests was also related to increased chances of continuing in academia and having more mentees later on (although under the condition that one remains thematically close to the post-doc advisor).
-There is also some direct preliminary evidence that higher independence modestly correlates with the number of citations acquired (Rojko & Lužar, 2022), but others argue that even the research systems with very low independence can create a lot of scientific impact, and thus the relationships between independence and impact might not be as clear (Gläser et al., 2021)
-
-However, developing this independence does not go without saying.
-There are few known factors influencing the level of research independence.
-One of them is study discipline.
-Based on some early empirical studies (@rojkoScientificPerformanceResearch2022), it seems that researchers in disciplines such as philosophy, psychology; religion, theology; social sciences; the arts, recreation, entertainment, sport; language, linguistics, literature; and geography, biography, history experience significantly higher levels of independence on their PhD advisor than researchers in disciplines such as science and knowledge, organization, computer science, information, documentation, librarianship, institutions, publications; mathematics, natural sciences; and applied sciences, medicine, technology.
-
-Interestingly, there is also some evidence that the propensity to cognitive independence might be inherited and passed down from generation to generation in mentor-mentee relationships (@yoshioka-kobayashi2021) - perhaps it is not only research agendas that students inherit from their advisors but also the tendency to deviate from those research agendas.
-
-In recent decades, there has been a worry that researchers’ independence is decreasing, illustrated by an increase in the age at which researchers received their first grant (@powell2016, @christian2021; and NAS, 2005; @danielsGenerationRiskYoung2015 for US biomedical researchers specifically), as well as direct measures of new researchers becoming more dependent on their PhD advisors across almost all disciplines in Slovenia (@rojkoScientificPerformanceResearch2022, table 6 on p.9).
-These trends have motivated some to create new proposals for funding agencies and other research funders in order to support early career researchers (@dewinde2021)
-
-Perhaps to tackle this trend, many grant agencies decided to support early career researcher by funding.
-Some have decided to tackle this trend by giving advantage to first-awardees and early career researchers in their usual distribution process, while others have created specific programmes designated to funding young researchers soon, usually up to 8 years, after finishing their PhD.
-Such programmes have often explicitly stated goals of helping researchers become more independent, set up their own research groups and open up new lines of research.
-Examples of such programmes could be Starting Grants by European Research Council (@StartingGrantERC), Junior project and Junior Star by Czech Science Foundation (2020), Walter N.
-Benjamin Programme by DFG (@WalterBenjaminProgramme), Innovation Research Incentives Scheme by Netherlands Organization of Scientific Research (NWO) (2021).
-
-Grant funding mechanisms have previously been shown to stimulate productivity in terms of the number of publications and impact in terms of citations (@gallo2018; for the Czech environment specifically see @bajgar2021; notable exception is @vandenbesselaar2015, who specifically looked at funding programmes for early career researchers and found small or no effect), and even scientific novelty (@wang2018, or, as some authors argue, rather interdisciplinarity: @fontana2020).
-In terms of career progress, obtaining grant funding was connected to significantly higher chances of career progression and obtaining a professorship (@bloch2014, @vandenbesselaar2015).
-
-Funding is thus thought to be one of the mechanisms that could stimulate researchers' independence.
-However, there hasn’t been much effort focused on quantifying this phenomenon.
-Some studies try to measure independence in a simple way, as a ratio of publications the given researcher produced without their supervisor divided by the total number of publications of the given researchers (e.g.
-@rojkoScientificPerformanceResearch2022).
-However, such an indicator could be misleading in the world of team science, and also only focuses on collaborations, not tracking whether a given researcher becomes independent in their thinking and research topics.
-@vandenbesselaarMeasuringResearcherIndependence2019 therefore proposed a more complex indicator for measuring researcher independence on the individual level, based on co-authorship network and topical overlaps.
-Their measure uses only information about publications’ characteristics (authorship and reference list) regardless of their impacts, unlike other alternative measures that focus solely on the impact of the independent work in terms of received citations (Dey, et al., 2021 -> ALIS, citation need repair).
-
-Understanding the impact of early-career funding on research independence is crucial for shaping future funding policies and, ultimately, the trajectory of scientific innovation.
-This study serves as a pivotal step in quantifying that impact, providing actionable insights for funding agencies and academic institutions alike.
 
@@
 They found a decrease in the productivity of junior collaborators and an increase in published work by young newcomers to the field rewarded by an increased citation rate.
-That suggests the sudden departures of prominent scientists gave room for more disruptive changes in the field and for bringing new ideas and perspectives while harming the status quo holders who worked with the prominent scientists on their research agendas - a “Goliath effect”, as coined by @wang2021, p.42).
+That suggests the sudden deaths of prominent scientists gave room for more disruptive changes in the field and for bringing new ideas and perspectives while harming the status quo holders who worked with the prominent scientists on their research agendas - a “Goliath effect”, as coined by @wang2021, p.42).
 
@@
 In the second step, we manually searched for PhD advisors of these 341 researchers in the databases of theses and dissertations that cover most universities in Czechia (https://theses.cz and https://dspace.cuni.cz/).
-We were able to match `r nrow(tar_read(ids_complete))` researchers with a PhD advisor (81 % of the Czech subsample).
+We were able to match `r nrow(tar_read(ids_complete))` researchers with a PhD advisor (69,2 % of the Czech subsample).
 Further, we have not managed to find a suitable matched pair for another `r nrow(tar_read(ids_complete))-nrow(tar_read("matching") %>% filter(treatment == 1) %>% distinct(vedidk))` researchers in the matching procedure, reducing our final sample to `r nrow(tar_read("matching") %>% filter(treatment == 1) %>% distinct(vedidk))`.
@@
 
-To calculate this indicator, we required at least 3 publications. This led to an increased number of missing observations (see section Results -> Descriptives -> Missing data).
-
 <!-- Finally, the original indicator, while tracking not only collaboration independence but also topical independence, is still skewed significantly towards collaboration independence (three-quarters of the indicator measure collaboration, while only one-quarter measures topics).
@@
 
+# Results
+
 ## Descriptives
@@
 na_control2 <- nrow(d %>% filter(is.na(RII)) %>% filter(treatment == 2))
-
-na_counts_researchers <- round(nrow(d %>% filter(!is.na(sup_name)) %>% filter(is.na(pubs_number)) %>% filter(independence_timing == "after_intervention") %>% distinct(vedidk))/nrow(d %>% filter(independence_timing == "after_intervention") %>% distinct(vedidk))*100, 1)
-
-mean_pubs_after <- d %>%
-  filter(independence_timing == "after_intervention") %>%
-  group_by(vedidk) %>%
-  summarise(pubs_number = first(pubs_number)) %>% 
-  summarise(mean_pubs_number = mean(pubs_number, na.rm = TRUE)) %>%
-  pull()
 
@@
 # Print the updated table
-kable(df_summary, digits = 3, caption = "Counts and Proportions of Missing data by disc_ford") %>%
+kable(df_summary, "html", digits = 3, caption = "Counts and Proportions of Missing Data by Field") %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
@@
 ### Before intervention
+
+POZN: here we show data
 
@@
 
-kable(combined_table_before, 
-      digits = 3, align = "c", booktabs = TRUE) %>%
+kable(combined_table_before, "html",
+      digits = 3, align = "c", booktabs = TRUE, caption = "Descriptives of All Groups Before Intervention") %>%
   kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
@@
 df <- filtered_by_subclass %>% filter(independence_timing == "after_intervention")
-df$career_length2022 <- 2022-df$career_start_year
 numeric_vars <- df %>% 
   select(where(is.numeric)) %>% 
-  select(-weights, -funded_control, -id, -treatment_year, -career_start_year, -career_length, -pubs_total, -ws_pubs, -interdisc_proportion, -grants, -total_coauthor_count, -first_grant) %>% 
+  select(-weights, -funded_control, -id, -treatment_year, -career_start_year) %>% 
   names()
@@
 
-# Move 'career_length2022' row to the top for each table
-reorder_row <- function(tbl) {
-  return(tbl[c("career_length2022", setdiff(rownames(tbl), "career_length2022")), ])
-}
-
-table_after_1 <- reorder_row(table_after_1)
-table_after_0 <- reorder_row(table_after_0)
-table_after_2 <- reorder_row(table_after_2)
-
-# Re-combine tables
 combined_table_after <- cbind(table_after_1, table_after_0[, -1], table_after_2[, -1])
 
-kable(combined_table_after, 
-      digits = 3, align = "c", booktabs = TRUE) %>%
+kable(combined_table_after, "html",
+      digits = 3, align = "c", booktabs = TRUE, caption = "Descriptives of All Groups After Intervention") %>%
   kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
@@
 ```
-
-# Results
 
@@
   group_by(field) %>%
-  filter(n() >= 8)
+  filter(n() >= 10)
 
@@
 
-In the first analysis, we examined the effects of treatment, time, and their interaction on the dependent variable, researcher independence (RII) for the treatment group and unfunded control group.
-
-There was a significant main effect of time on RII, F(`r summary(result)$"Error: subclass:independence_timing"[[1]]$"Df"[1]`, `r format(summary(result)$"Error: subclass:independence_timing"[[1]]$"Df"[2])`) = `r format(summary(result)$"Error: subclass:independence_timing"[[1]]$"F value"[1], digits=2)`, p = `r round(summary(result)$"Error: subclass:independence_timing"[[1]]$"Pr(>F)"[1], 3)`).
-This effect accounted for approximately `r format(eta_sq_result[eta_sq_result$Parameter == "independence_timing", "Eta2_partial"] * 100, digits=2)`% of the observed variance (partial \(\eta^2 = `r round(eta_sq_result[eta_sq_result$Parameter == "independence_timing", "Eta2_partial"], 3)`\), 95% CI [`r round(eta_sq_result[eta_sq_result$Parameter == "independence_timing", "CI_low"], 3)`, `r eta_sq_result[eta_sq_result$Parameter == "independence_timing", "CI_high"]`]).
-
-Importantly, there was a significant interaction effect between treatment and time on independence, F(`r format(summary(result)$"Error: Within"[[1]]$"Df"[2])`, `r format(summary(result)$"Error: Within"[[1]]$"Df"[3])`) = `r format(summary(result)$"Error: Within"[[1]]$"F value"[2], digits=2)`, p = `r format(summary(result)$"Error: Within"[[1]]$"Pr(>F)"[2], digits=2)`.
-This interaction effect explained about `r format(eta_sq_result[eta_sq_result$Parameter == "treatment:independence_timing", "Eta2_partial"] * 100, digits=2)`% of the variability (partial \(\eta^2 = `r round(eta_sq_result[eta_sq_result$Parameter == "treatment:independence_timing", "Eta2_partial"], 3)`\), 95% CI [`r eta_sq_result[eta_sq_result$Parameter == "treatment:independence_timing", "CI_low"]`, `r round(eta_sq_result[eta_sq_result$Parameter == "treatment:independence_timing", "CI_high"], 3)`]).
+In the first analysis, we examined the effects of treatment, independence_timing, and their interaction on the dependent variable, researcher independence (RII) for the treatment group and unfunded control group.
+
+There was a significant main effect of independence_timing on RII, F(`r summary(result)$"Error: subclass:independence_timing"[[1]]$"Df"[1]`, `r format(summary(result)$"Error: subclass:independence_timing"[[1]]$"Df"[2])`) = `r format(summary(result)$"Error: subclass:independence_timing"[[1]]$"F value"[1], digits=2)`, p = `r format(summary(result)$"Error: subclass:independence_timing"[[1]]$"Pr(>F)"[1], digits=4)`).
+This effect accounted for approximately `r format(eta_sq_result[eta_sq_result$Parameter == "independence_timing", "Eta2_partial"] * 100, digits=2)`% of the observed variance (partial \(\eta^2 = `r eta_sq_result[eta_sq_result$Parameter == "independence_timing", "Eta2_partial"]`\), 95% CI [`r eta_sq_result[eta_sq_result$Parameter == "independence_timing", "CI_low"]`, `r eta_sq_result[eta_sq_result$Parameter == "independence_timing", "CI_high"]`]).
+
+Importantly, there was a significant interaction effect between treatment and independence_timing on independence, F(`r format(summary(result)$"Error: Within"[[1]]$"Df"[2])`, `r format(summary(result)$"Error: Within"[[1]]$"Df"[3])` = `r format(summary(result)$"Error: Within"[[1]]$"F value"[2], digits=2)`, p = `r format(summary(result)$"Error: Within"[[1]]$"Pr(>F)"[2], digits=2)`.
+This interaction effect explained about `r format(eta_sq_result[eta_sq_result$Parameter == "treatment:independence_timing", "Eta2_partial"] * 100, digits=2)`% of the variability (partial \(\eta^2 = `r eta_sq_result[eta_sq_result$Parameter == "treatment:independence_timing", "Eta2_partial"]`\), 95% CI [`r eta_sq_result[eta_sq_result$Parameter == "treatment:independence_timing", "CI_low"]`, `r eta_sq_result[eta_sq_result$Parameter == "treatment:independence_timing", "CI_high"]`]).
 
@@
 This suggests that there are statistically significant differences in the RII based on the field of study.
-Specifically, adding the field of study to the model resulted in a significant increase in the log-likelihood by `r round(anova_result$L.Ratio[2], 2)` units (p < `r round(anova_result$"p-value"[2], 3)`), emphasizing its importance as a predictor.
-Specifically, compared to the Engineering and Technology field, being in the Medical and Health Sciences field is associated with a decrease in RII by `r  round(coef(model_summary)["fieldMedical and Health Sciences", 1], 2)` units, on average (p = `r round(coef(model_summary)["fieldMedical and Health Sciences", 4], 3)`), while being in the Social Sciences field is associated with an increase in RII by `r round(coef(model_summary)["fieldSocial Sciences", 1], 2)` units (p = `r round(coef(model_summary)["fieldSocial Sciences", 4], 3)`).
+Specifically, adding the field of study to the model resulted in a significant increase in the log-likelihood by `r anova_result$L.Ratio[2]` units (p < `r anova_result$"p-value"[2]`), emphasizing its importance as a predictor.
+Specifically, compared to the Engineering and Technology field, being in the Medical and Health Sciences field is associated with a decrease in RII by `r  coef(model_summary)["fieldMedical and Health Sciences", 1]` units, on average (p = `r coef(model_summary)["fieldMedical and Health Sciences", 4]`), while being in the Social Sciences field is associated with an increase in RII by `r coef(model_summary)["fieldSocial Sciences", 1]` units (p = `r coef(model_summary)["fieldSocial Sciences", 4]`).
 There are no statistically significant differences between Natural Sciences and Engineering and Technology.
@@
 In the second analysis, we examined the effects of treatment, independence_timing, and their interaction on the researcher independence (RII) for the treatment group and funded control group.
-Again, there was a significant main effect of time on independence, F(`r format(summary(result2)$"Error: subclass:independence_timing"[[1]]$"Df"[1])`, `r format(summary(result2)$"Error: subclass:independence_timing"[[1]]$"Df"[2])`) = `r format(summary(result2)$"Error: subclass:independence_timing"[[1]]$"F value"[1], digits=2)`, p = `r round(summary(result2)$"Error: subclass:independence_timing"[[1]]$"Pr(>F)"[1], 3)`).
-The effect accounted for approximately `r format(eta_sq_result2[eta_sq_result2$Parameter == "independence_timing", "Eta2_partial"] * 100, digits=2)`% of the observed variance (partial \(\eta^2 = `r round(eta_sq_result2[eta_sq_result2$Parameter == "independence_timing", "Eta2_partial"], 3)`\), 95% CI [`r round(eta_sq_result2[eta_sq_result2$Parameter == "independence_timing", "CI_low"], 3)`, `r eta_sq_result2[eta_sq_result2$Parameter == "independence_timing", "CI_high"]`]).
+Again, there was a significant main effect of time on independence, F(`r format(summary(result2)$"Error: subclass:independence_timing"[[1]]$"Df"[1])`, `r format(summary(result2)$"Error: subclass:independence_timing"[[1]]$"Df"[2])`) = `r format(summary(result2)$"Error: subclass:independence_timing"[[1]]$"F value"[1], digits=2)`, p = `r format(summary(result2)$"Error: subclass:independence_timing"[[1]]$"Pr(>F)"[1], digits=4)`).
+The effect accounted for approximately `r format(eta_sq_result2[eta_sq_result2$Parameter == "independence_timing", "Eta2_partial"] * 100, digits=2)`% of the observed variance (partial \(\eta^2 = `r eta_sq_result2[eta_sq_result2$Parameter == "independence_timing", "Eta2_partial"]`\), 95% CI [`r eta_sq_result2[eta_sq_result2$Parameter == "independence_timing", "CI_low"]`, `r eta_sq_result2[eta_sq_result2$Parameter == "independence_timing", "CI_high"]`]).
 
 Importantly, this time the interaction effect between treatment and time was not significant, F(`r format(summary(result2)$"Error: Within"[[1]]$"Df"[2])`, `r format(summary(result2)$"Error: Within"[[1]]$"Df"[3])`) = `r format(summary(result2)$"Error: Within"[[1]]$"F value"[2], digits=2)`, p = `r format(summary(result2)$"Error: Within"[[1]]$"Pr(>F)"[2], digits=2)`.
-This interaction effect explained about `r format(eta_sq_result2[eta_sq_result2$Parameter == "treatment:independence_timing", "Eta2_partial"] * 100, digits=2)`% of the variability (partial \(\eta^2 = `r round(eta_sq_result2[eta_sq_result2$Parameter == "treatment:independence_timing", "Eta2_partial"], 3)`\), 95% CI [`r round(eta_sq_result2[eta_sq_result2$Parameter == "treatment:independence_timing", "CI_low"], 3)`, `r eta_sq_result2[eta_sq_result2$Parameter == "treatment:independence_timing", "CI_high"]`]), suggesting that funding has the same effects, regardless of its type or source.
+This interaction effect explained about `r format(eta_sq_result2[eta_sq_result2$Parameter == "treatment:independence_timing", "Eta2_partial"] * 100, digits=2)`% of the variability (partial \(\eta^2 = `r eta_sq_result2[eta_sq_result2$Parameter == "treatment:independence_timing", "Eta2_partial"]`\), 95% CI [`r eta_sq_result2[eta_sq_result2$Parameter == "treatment:independence_timing", "CI_low"]`, `r eta_sq_result2[eta_sq_result2$Parameter == "treatment:independence_timing", "CI_high"]`]), suggesting that funding has the same effects, regardless of its type or source.
 
 Same as in previous chapter, the comparison of models suggested that there are statistically significant differences in the RII based on the field of study.
-Specifically, adding the field of study to the model resulted in a significant increase in the log-likelihood by `r round(anova_result2$L.Ratio[2], 2)` units (p < `r round(anova_result2$"p-value"[2], 3)`), emphasizing its importance as a predictor.
-Specifically, compared to the Engineering and Technology field, being in the Medical and Health Sciences field is associated with a decrease in RII by `r  round(coef(model_summary2)["fieldMedical and Health Sciences", 1], 2)` units, on average (p = `r round(coef(model_summary2)["fieldMedical and Health Sciences", 4], 3)`), while being in the Social Sciences field is associated with an increase in RII by `r round(coef(model_summary2)["fieldSocial Sciences", 1], 2)` units (p = `r round(coef(model_summary2)["fieldSocial Sciences", 4], 3)`).
+Specifically, adding the field of study to the model resulted in a significant increase in the log-likelihood by `r anova_result2$L.Ratio[2]` units (p < `r anova_result2$"p-value"[2]`), emphasizing its importance as a predictor.
+Specifically, compared to the Engineering and Technology field, being in the Medical and Health Sciences field is associated with a decrease in RII by `r  coef(model_summary2)["fieldMedical and Health Sciences", 1]` units, on average (p = `r coef(model_summary2)["fieldMedical and Health Sciences", 4]`), while being in the Social Sciences field is associated with an increase in RII by `r coef(model_summary2)["fieldSocial Sciences", 1]` units (p = `r coef(model_summary2)["fieldSocial Sciences", 4]`).
 There are no statistically significant differences between Natural Sciences and Engineering and Technology.
@@
 
-## Collaborative vs Cognitive Independence
-
-From the correlation matrix below, we can observe that the cognitive part of independence indicator (ind_topics) has notably lower correlation with the overall indicator (RII) and its remaining parts.
-
-```{r echo=FALSE}
-
-cor_data <- d %>% dplyr::select(RII, ind_topics, ind_pubs, clustr, eig_centr)
-
-cor_matrix <- cor(cor_data, use = "pairwise.complete.obs")
-
-# reversed_cor_matrix <- cor_matrix[rev(rownames(cor_matrix)), rev(colnames(cor_matrix))]
-
-kable(cor_matrix, format = "html", digits = 2) %>%
-  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
-
-ind_top_mean_before <- d %>% 
-    filter(independence_timing == "before_intervention") %>% 
-    group_by(vedidk, ind_topics) %>%
-    sample_n(1) %>%
-    ungroup() %>%
-    summarise(mean_value = mean(ind_topics, na.rm = TRUE)) %>%
-    pull(mean_value)
-
-ind_top_mean_after <- d %>% 
-    filter(independence_timing == "after_intervention") %>% 
-    group_by(vedidk, ind_topics) %>%
-    sample_n(1) %>%
-    ungroup() %>%
-    summarise(mean_value = mean(ind_topics, na.rm = TRUE)) %>%
-    pull(mean_value)
-
-```
-
-From the violin plot it seems that the cognitive part of the indicator has lower variability than full indicator, and the differences between treatment and (unfunded) control groups are not significant.
-
-This might suggest that while funding helps early career researchers to become more independent from their PhD advisors overall, this is likely driven creating new collaboration networks, rather than "opening up new lines of research".
-That being said, the average level of cognitive (topical) independence is around `r round(ind_top_mean_before, 2)` (which could roughly be translated as `r round(ind_top_mean_before*100, 2)` %) even before the funding intervention and rises to about `r round(ind_top_mean_after, 2)` (`r round(ind_top_mean_after*100, 2)` %) in the time after the intervention.
-
-```{r echo=FALSE}
-
-### visualisations
-
-means <- aggregate(ind_topics ~ treatment + independence_timing, data = filtered_by_subclass_1, FUN = mean)
-
- # Calculate means and standard errors for plotting
-plot_data <- filtered_by_subclass_1 %>%
-  group_by(treatment, independence_timing) %>%
-  summarize(
-    mean_ind_topics = mean(ind_topics),
-    se_ind_topics = sd(ind_topics) / sqrt(n())
-  )
-
-dodge_width <- 0.5
-
-combined_plot <- ggplot() +
-
-  geom_violin(data = filtered_by_subclass_1, 
-              aes(x = treatment, y = ind_topics, fill = independence_timing), 
-              scale = "width", 
-              position = position_dodge(dodge_width)) +
-
-  geom_point(data = plot_data, 
-             aes(x = treatment, y = mean_ind_topics, color = independence_timing), 
-             position = position_dodge(dodge_width), 
-             size = 3) +
-
-  geom_errorbar(data = plot_data, 
-                aes(x = treatment, ymin = mean_ind_topics - se_ind_topics, ymax = mean_ind_topics + se_ind_topics, color = independence_timing), 
-                position = position_dodge(dodge_width), 
-                width = 0.2) +
-
-  scale_fill_discrete(name = "Independence Timing", labels = c("Before intervention", "After intervention")) +
-  scale_color_manual(values = c("black", "red"), name = "Independence Timing", labels = c("Before intervention", "After intervention")) +
-
-  labs(title = "Violin Plot of ind_topics Scores by Treatment and Time with Mean and CI Overlayed",
-       x = "Treatment Group",
-       y = "ind_topics Score") +
-  theme_bw()
-
-print(combined_plot)
-
-```
-
-When looking at the scores of cognitive part of independence indicator, we cannot see notable differences across fields of study, unlike it case of the whole RII.
---> SHOULD I STATISTICALLY TEST whether adding filed of study improves prediction of the id_topics? (same way as when I tested that for full RII)??
-
-```{r echo=FALSE}
-
-disc_data <- d %>%
-     group_by(vedidk, subclass) %>%  # Assuming 'id' is your current unique identifier
-     mutate(subject_id = cur_group_id()) %>%  # This creates a unique ID for each group
-     ungroup()
-
-diff_data_tp <- disc_data %>%
-  select(subject_id, independence_timing, ind_topics) %>%
-  spread(independence_timing, ind_topics) %>%
-  mutate(ind_topics_diff = after_intervention - before_intervention) %>%
-  select(subject_id, ind_topics_diff)
-
-disc_data <- left_join(disc_data, diff_data_tp, by = "subject_id")
-
-disc_data <-  disc_data %>% 
-     filter(!is.na(ind_topics)) %>%
-     group_by(vedidk, field, ind_topics) %>%
-     sample_n(1) %>%
-     ungroup()
-
-means_disc_complete <- aggregate(ind_topics ~ field, data = disc_data, FUN = mean)
-
-num_disc_complete <- disc_data %>%
-  group_by(field) %>%
-  summarise(count = n(), .groups = "drop")
-
-means_disc_complete <- left_join(means_disc_complete, num_disc_complete, by = "field")
-
-# Step 1: Reorder the levels of 'field'
-means_disc_complete$field <- with(means_disc_complete, factor(field, levels=unique(field[order(ind_topics)])))
-
-# Step 2: Optionally, sort the dataframe based on the reordered levels
-means_disc_complete <- means_disc_complete %>% arrange(field)
-
-se_ci_data_complete <- disc_data %>%
-  group_by(field) %>%
-  summarise(mean_ind_topics = mean(ind_topics),
-            se_ind_topics = sd(ind_topics) / sqrt(n()),
-            lower_CI = mean_ind_topics - (1.96 * se_ind_topics),
-            upper_CI = mean_ind_topics + (1.96 * se_ind_topics), 
-            .groups = "drop")
-
-means_disc_complete <- merge(means_disc_complete, se_ci_data_complete, by = "field")
-
-ggplot(data = means_disc_complete, aes(x = field, y = mean_ind_topics, fill = field)) +
-  geom_bar(stat = "identity", position = "dodge") +
-
-  # Add error bars for confidence intervals
-  geom_errorbar(aes(ymin = lower_CI, ymax = upper_CI), position = position_dodge(width=0.9), width=0.25) +
-
-  # Add the number of observations in the middle of the bars
-  geom_text(aes(label=count, y = mean_ind_topics/2), position=position_dodge(width=0.9), vjust=0.5) +
-
-  # Change x-axis labels and add a title
-  scale_x_discrete(labels = seq_along(unique(means_disc_complete$field))) + # replace with numbers
-  labs(
-    x = "Field", 
-    y = "Mean ind_topics",
-    title = "Differences in average ind_topics across disciplines and time"
-  ) +
-  scale_fill_discrete(name = "Field") +
-  theme_bw()
-
-disc_data_change <- disc_data %>% filter(!is.na(ind_topics_diff)) %>% 
-     group_by(vedidk, field, ind_topics_diff) %>%
-     sample_n(1) %>%
-     ungroup()
-
-means_disc_change <- aggregate(ind_topics_diff ~ field, data = disc_data_change, FUN = mean)
-
-num_disc_change <- disc_data_change %>%
-  group_by(field) %>%
-  summarise(count = n(), .groups = "drop")
-
-means_disc_change <- left_join(means_disc_change, num_disc_change, by = "field")
-
-# Step 1: Reorder the levels of 'field'
-means_disc_change$field <- with(means_disc_change, factor(field, levels=unique(field[order(ind_topics_diff)])))
-
-# Step 2: Optionally, sort the dataframe based on the reordered levels
-means_disc_change <- means_disc_change %>% arrange(field)
-
-se_ci_data_change <- disc_data_change %>%
-  group_by(field) %>%
-  summarise(mean_ind_topics_diff = mean(ind_topics_diff),
-            se_ind_topics_diff = sd(ind_topics_diff) / sqrt(n()),
-            lower_CI = mean_ind_topics_diff - (1.96 * se_ind_topics_diff),
-            upper_CI = mean_ind_topics_diff + (1.96 * se_ind_topics_diff), 
-            .groups = "drop")
-
-means_disc_change <- merge(means_disc_change, se_ci_data_change, by = "field")
-
-ggplot(data = means_disc_change, aes(x = field, y = mean_ind_topics_diff, fill = field)) +
-  geom_bar(stat = "identity", position = "dodge") +
-
-  # Add error bars for confidence intervals
-  geom_errorbar(aes(ymin = lower_CI, ymax = upper_CI), position = position_dodge(width=0.9), width=0.25) +
-
-  # Add the number of observations in the middle of the bars
-  geom_text(aes(label=count, y = mean_ind_topics_diff/2), position=position_dodge(width=0.9), vjust=0.5) +
-
-  # Change x-axis labels and add a title
-  scale_x_discrete(labels = seq_along(unique(means_disc_change$field))) + # replace with numbers
-  labs(
-    x = "Field", 
-    y = "Mean ind_topics_diff",
-    title = "Average change in cognitive independence across disciplines"
-  ) +
-  scale_fill_discrete(name = "Field") +
-  theme_bw()
-
-```
-
 # Discussion
@@
 The results of this study provide important insights into the effects of funding interventions on researcher independence.
-The strongest effect we found across all control group comparisons was the effect of time - over time, researchers become more independent, regardless of their access to funding or their study discipline.
+The strongest effect we found across all control group comparison was the effect of time - over time, researchers become more independent, regardless of their access to funding or their study discipline.
 This effect explains around 60% of the variance in independence.
@@
 Additionally, the observed variation in independence across different disciplines underscores the importance of considering disciplinary differences, suggested by a moderate effect size.
-A moderate effect size for the field effect emphasizes that certain disciplines might inherently have variations in researchers' independence, perhaps due to differences in practices, methodologies, or norms specific to each discipline.
+A moderate effect size for the field effect emphasizes that certain disciplines might inherently have variations in RII, perhaps due to differences in practices, methodologies, or norms specific to each discipline.
 Anyway, these differences remain constant across time and funding interventions, suggesting that funding has a uniform effect on the independence across disciplines.
 
-Importantly, the significant interaction between treatment and time when comparing treatment vs unfunded control group suggests the funding has positive effect on stimulating researchers' independence.
+Finally, the significant interaction between treatment and time when comparing treatment vs unfunded group suggests the funding has positive effect on stimulating researchers' independence.
 However, the effect size is only modest, explaining about 2 % of variance in independence, indicating relatively small practical relevance.
@@
 Interestingly, in our sample both funded groups (treatment as well as control) started with lower independence compared to unfunded control group.
-This might suggest that in the early career stages, being more dependent on one's PhD advisor might be  beneficial (or even required) to obtain independent funding.
-
-Finally, when looking closer into the composition of the independence indicator, we found that that the main driver of the increase in independence was the collaboration part of the indicator - creating new collaboration networks - rather than the cognitive part - opening up new lines of research in which their PhD advisor is not active.
-While the level of cognitive independence is still relatively high even early on after finishing one's PhD (researchers have around 40 % of topics not shared by their PhD advisor) and increases over time, the funding does not stimulate more novelty and divergence from the portfolio of topics held by their PhD advisors.
-
-Given that funding for early career researchers does not have effect on stimulating their cognitive independence, does it make sense to continue providing it?
-While funding itself might not be the main driver of cognitive independence, its might still play an important role - for example, it could be a necessary thought not sufficient condition for the development of independence.
-From a common sense view, it is hard to imagine that researchers can develop much of independence while working on someone else's (often their advisor') projects.
-Moreover, funding did show to modestly stimulate creation of more independent collaborative networks, which might have a value in itself by establishing early career researchers in the scientific community and making their positions more robust.
-This would hopefully enable them to explore more rapidly later on, though that is not guaranteed.
-In any case, our results suggest that the search for factors and interventions stimulating researchers' explorative behaviour should continue.
-
-Main value of this paper is manyfold:
-- it investigated one potential factor (funding) hypothesized to stimulate researcher independence, rendering this factor unimportant, contrary to expectations
-- it confirmed there are meaningful differences in level of independence across disciplines
-- it has illuminated the magnitude of cognitive independence experienced by researchers early in their careers and its development to later stages, contributing to the discussions about tradition and innovation in research topic choice strategies and recreating status quo in science
+This might suggest that in the early career stages, in order to secure funding, it is needed to be more dependent on one's PhD advisor.
+
+<!-- Anyway, rather than granting funded researchers greater independence compared to the unfunded control group, it seems that the funding programme we examined sampled less independent researchers and then allowed them to catch up with the unfunded control group via providing them funding.
+-->
 
@@
 
-One of the main limitations of this study is that it only focuses on Czech environment - researchers growing up and spending most of their careers in the Czech Republic, only taking into account their publications affiliated with Czech research institutions.
-Studies testing our results on samples from other countries, and possibly tracking international mobility would strengthen our conclusions.
-
-Another potential limitation is the length of the time after the intervention.
-We have tracked the effects of funding between 2-7 years after the project started, at a point where researchers created on average `r round(mean_pubs_after, 1)` publications (while `r na_counts_researchers` % of them have created less than 3 and were deleted from this analysis).
-It might be possible that independence needs more time to develop and had we measured the effects later, we would have found stronger effects.
-
-Further research could look more into which other factors influence researcher independence (especially the cognitive part) and how strongly compared to grant funding.
-
-## Conclusion
-
-Our results showed that funding helps modestly to stimulate collaborative independence of early career researchers, but does not stimulate their cognitive independence.
-The largest effect on increase in composite independence was time - over time, researchers become more independent, regardless of their access to funding or their study discipline.
-There were also significant differences in independence level across study disciplines, where social sciences and humanities allowed for more independence than medical and health sciences and natural sciences.
-Researchers usually start with around 40 % of topics not shared by their PhD advisor early on after finishing their PhD and grow more independent over time (up to 47 % 13.5 years after their first publication).
-Search for factors and interventions stimulating researchers' cognitive independence and explorative behaviour should thus continue.
+--> only talks about the Czech environment and considers researchers growing up and most of their careers in the Czech republic
 
@@
 
+## construction of the independnece identificator
+
+Correlation of its components
+
+correlation with other stuff
+
+- test whether results for the "cognitive" part are the same as results for the "collaboration" part -> do all the tests
+
 ## Identification of supervisors
 
-```{r echo=FALSE}
-
-treatment_found_pc <- round(nrow(tar_read(final_data) %>% filter(!is.na(sup_name)) %>% filter(treatment == 1) %>% distinct(vedidk))/348*100, 2)
-
-control_found_pc <- round(nrow(tar_read(final_data) %>% filter(!is.na(sup_name)) %>% filter(treatment != 1) %>% distinct(vedidk))/nrow(tar_read(final_data) %>% filter(treatment != 1) %>% distinct(vedidk))*100, 2)
-
-treatment_match <- left_join(tar_read(final_data) %>% filter(!is.na(sup_name)), tar_read(sup_alg), by = "vedidk") %>% 
-    mutate(match = ifelse(sup_vedidk.x == sup_vedidk.y, 1, 0))
-
-match_yes <- nrow(treatment_match %>% filter(match == 1) %>% distinct(vedidk))
-match_yes_pc <- round(nrow(treatment_match %>% filter(match == 1) %>% distinct(vedidk))/nrow(treatment_match %>% distinct(vedidk))*100, 2)
-
-match_no <- nrow(treatment_match %>% filter(match == 0) %>% distinct(vedidk))
-match_no_pc <- round(nrow(treatment_match %>% filter(match == 0) %>% distinct(vedidk))/nrow(treatment_match %>% distinct(vedidk))*100, 2)
-
-match_na <- nrow(treatment_match %>% filter(is.na(match)) %>% distinct(vedidk))
-match_na_pc <- round(nrow(treatment_match %>% filter(is.na(match)) %>% distinct(vedidk))/nrow(treatment_match %>% distinct(vedidk))*100, 2)
-
-```
-
 Data about PhD student-PhD advisor connections are usually not available.
-One must search for these connections manually on the internet, which is time consuming and not fully reliable (we were only able to find about `r treatment_found_pc` % of these connections in our treatment group and `r control_found_pc`) % in control groups.
+One must search for these connections manually on the internet, which is time consuming and not fully reliable (we were only able to find about 69 % of these connections in our treatment group).
 Therefore, we tried to come up with an alternative way of identifying supervisors from the available data: we assumed that since many researchers only start their publication career during their PhD studies, their PhD supervisors might often coauthor their first publications.
@@
 To check whether we can use "the most frequent co-author of the first 5 publications" as a proxy to identify supervisors, we have compared the supervisors identified via this method with the manually found supervisors for each researcher in our sample.
-Across our full sample of `r nrow(tar_read(final_data) %>% filter(!is.na(sup_name)) %>% distinct(vedidk))` researchers for whom we identified supervisors manually, `r match_yes` (`r match_yes_pc` %) had their most frequent co-author same as their supervisor and `r match_no` (`r match_no_pc` %) had someone other than their supervisor as their most frequent co-author in their first 5 publications, and `r match_na` (`r match_na_pc`%) had no co-author in their first 5 publications.
-
----------> should I put the next paragraph here?
-If yes, I should ask Luzar whether I can publish it, show the data to reviewers and ask him how to cite him.
-(the code is at the bottom of the fuction sup_test.R)
+In the treatment group of `r nrow(tar_read(ids_complete))`researchers,  118 (49 %) had their most frequent co-author same as their supervisor and 86 (36 %) had someone other than their supervisor as their most frequent co-author in their first 5 publications, and 37 (15%) had no co-author in their first 5 publications.
+In the control groups, we have manually found supervisors for `r nrow(tar_read(sup_complete) %>% filter(!is.na(sup_vedidk)) %>% distinct(name_first, name_last))` researchers, and when we compared them to the supervisors suggested by the most frequent coauthor algorithm, we found that 41 (29 %) had their most frequent co-author the same as their supervisor, 80 (57 %) had someone other than their supervisor as their most frequent co-author in their first 5 publications, and 20 (14 %) had no co-author in their first 5 publications.
 
@@
 
-This suggest that the algorithmic approach as we defined is not able to identify real supervisors often enough.
-Either new algorithm is needed or future studies should redefine the "supervisory role" based on other characteristics than formal supervision.
-
 # References

### 2024-01-19 article_formatted.Rmd

--- 2023-11-01 article.Rmd
@@
 ---
-title: "Funding programmes for early career researchers marginally improves their collaboration independence, but not cognitive independence"
-author: "David Janků"
-date: "`r Sys.Date()`"
-output:
-  html_document:
-    df_print: paged
-  word_document: default
-always_allow_html: yes
+title: "Funding programmes for early career researchers do not improve their independence"
+author:
+- name: David Janků
+  affiliation: '[1] Institute of Sociological Studies, Faculty of Social Sciences,
+    Charles University, Czech Republic; [2] Centre for Science, Technology, and Society
+    Studies, Institute of Philosophy, Czech Academy of Sciences, Czech Republic'
+- name: Radim Hladík
+  affiliation: '[1] Centre for Science, Technology, and Society Studies, Institute
+    of Philosophy, Czech Academy of Sciences, Czech Republic'
+output: bookdown::word_document2
+always_allow_html: true
+  # pdf_document: default
+  # html_document:
+
+  # word_document: default
+  # # bookdown::pdf_document2: default
+  # bookdown::html_document2: default
+  #  df_print: paged
+  #  number_sections: true
+  # bookdown::word_document2: default
 bibliography: merged.bib
 csl: apa.csl
+---
+<!-- \doublespacing -->
+
+## Acknowledgements
+
+This work was supported by the Czech Science Foundation (project no. GJ20-01752Y, Funded and Unfunded Research in the Czech Republic: Scientometric Analysis and Topic Modeling)
+
+## Declaration of Interest
+
+Your declaration of interest statement here.
+
+## Corresponding Author
+
+Name: David Janků 
+Affiliation: 
+[1] Institute of Sociological Studies, Faculty of Social Sciences, Charles University, Czech Republic
+[2] Centre for Science, Technology, and Society Studies, Institute of Philosophy, Czech Academy of Sciences, Czech Republic  
+Address: U Kříže 661/8, Praha 5 – Jinonice  
+E-mail: david.janku@fsv.cuni.cz
+
+\newpage
+
 ---
@@
 Many national research funders have created programmes specifically aimed at increasing independence of early career researchers, yet until recently, there was no quantifiable way to measure changes in independence.
-We employed recently proposed measure by @vandenbesselaarMeasuringResearcherIndependence2019 to asses whether one such funding programme by Czech Science Foundation is effective at stimulating more independence.
-We found that funding for early career researchers is effective at stimulating their independence, though the effect is relatively small (2 % of variance) and the source of funding does not matter.
-The funding also helped selected researchers to catch up with the unfunded group, rather than to outrun them.
-Additionally, we found differences in levels of independence across disciplines that were stable across time and treatment groups, with Social Sciences and Humanities showing highest independence, while Medical and Heath Sciences and Natural Sciences showing lowest independence.
-
-# Intro
-
-## Intro - full
+We employed recently proposed measure by @vandenbesselaarMeasuringResearcherIndependence2019 to assess whether one such a funding programme by Czech Science Foundation is effective at stimulating more independence.
+We found that funding for early career researchers is not effective at stimulating their independence, regardless of the source of funding.
+The strongest effect on independence growth is time, explaining around 60% of the variance in independence.
+Additionally, we found differences in levels of independence across disciplines that were stable across time and treatment groups, with Social Sciences and Humanities showing highest independence, while  Agricultural and Veterinary sciences and Medical and Health Sciences showing lowest independence.
+However, these differences reflect only changes in collaboration patterns, while there were no changes in cognitive patterns across disciplines and only modest changes across time (from 40 % to 46 % of topics not shared by their PhD advisor).
+
+## Keywords
+research independence; early career researchers; grant funding; mentoring; counter-factual analysis; research evaluation
+
+# Introduction
 
@@
 Such a phenomenon is likely to occur because following tradition is usually a more beneficial and safer option for novices.
-Indeed, empirical data suggest that this strategy is chosen by a majority of researchers (@foster2015), and only a small fraction dares to deviate and explore the cognitive map of science more rapidly.
-For early career researchers specifically, partnering with already well-established seniors provides a large career boost (@li2019) and being thematically closer to their PhD as well as post-doc advisor increases the probability of continuing in academia and having more mentees later on (@lienard2018).
-However, this effect might stifle scientific progress as it leads to a slower exploration of its cognitive map (@rzhetsky2015).
+Indeed, empirical data suggest that this strategy is chosen by a majority of researchers [@foster2015], and only a small fraction dares to deviate and explore the cognitive map of science more rapidly.
+For early career researchers specifically, partnering with already well-established seniors provides a large career boost [@li2019] and being thematically closer to their PhD as well as their post-doc advisor increases the probability of continuing in academia and having more mentees later on [@lienard2018].
+However, this effect might stifle scientific progress as it leads to a slower exploration of its cognitive map [@rzhetsky2015].
 Moreover, this mirroring further strengthens the existing positions of senior faculty, making little space for disrupting the status quo and creating new perspectives.
@@
 They found a decrease in the productivity of junior collaborators and an increase in published work by young newcomers in the field rewarded by an increased citation rate.
-That suggests the sudden departures of prominent scientists gave room for more disruptive changes in the field and for bringing new ideas and perspectives while harming the status quo holders who worked with the prominent scientists on their research agendas - a “Goliath effect,” as coined by @wang2021, p.42).
-
-This mirroring effect is also closely connected to the concept of academic inbreeding (@machacek2022), which focuses more on academic mobility and conservation of institutional habitus rather than specifically on the inheritance of research agendas.
+That suggests the sudden departures of prominent scientists gave room for more disruptive changes in the field and for bringing new ideas and perspectives while harming the status quo holders who worked with the prominent scientists on their research agendas - a “Goliath effect,” as coined by @wang2021, p.42.
+
+This mirroring effect is also closely connected to the concept of academic inbreeding [@machacek2022], which focuses more on academic mobility and conservation of institutional habitus rather than specifically on the inheritance of research agendas.
 However, inbreeding is also often thought to increase dependence and decrease exploration of new ideas.
 
-As younger researchers are already more likely to come up with new topics and ideas (@packalen2019), it would be fitting to empower them and stimulate their independence so that they can “challenge the existing common views and open up new lines of research” (@vandenbesselaarMeasuringResearcherIndependence2019, p.2) and accelerate scientific progress rather than recreate the existing status quo.
-An independent investigator is then defined by the US National Academies of Science (NAS) as “one who enjoys the independence of thought—the freedom to define the problem of interest and to choose or develop the best strategies and approaches to addressing that problem–especially during the earlier career phase” (@vandenbesselaarMeasuringResearcherIndependence2019, 2019, p.4).
+As younger researchers are already more likely to come up with new topics and ideas [@packalen2019], it would be fitting to empower them and stimulate their independence so that they can “challenge the existing common views and open up new lines of research” [@vandenbesselaarMeasuringResearcherIndependence2019, p.2] and accelerate scientific progress rather than recreate the existing status quo.
+An independent investigator is then defined by the US National Academies of Science [@nationalresearchcouncilus2005] as “one who enjoys the independence of thought—the freedom to define the problem of interest and to choose or develop the best strategies and approaches to addressing that problem–especially during the earlier career phase” [@vandenbesselaarMeasuringResearcherIndependence2019, p.4].
 Such a definition does not necessarily put independence in relation to other actors (e.g.
 one’s PhD advisor), but only in relation to one’s own freedom and resources.
-However other institutions, such as European Research Council via their Starting Grants scheme (@neufeldPeerReviewbasedSelection2013) think of independence in a relational manner, in terms of having one (or a few) publications without the former PhD supervisor being co-author; being PI on a grant; or being lab director or research leader.
-
-Developing independence is also one of the things that the system of science expects from its members - it is one of the criteria often used for assessing researchers for hiring, tenure and promotion (@vanarensbergenDifferentViewsScholarly2014; @moherAssessingScientistsHiring2018), constituting one factor of research excellence.
-Even from the perspective of scholarly output, protégés were found to “do their best work when they break from their mentor’s research topics and coauthor no more than a small portion of their overall research with their mentors” (@ma2020).
+However other institutions, such as European Research Council via their Starting Grants scheme [@neufeldPeerReviewbasedSelection2013] think of independence in a relational manner, in terms of having one (or a few) publications without the former PhD supervisor being co-author; being PI on a grant; or being lab director or research leader.
+
+Developing independence is also one of the things that the system of science expects from its members - it is one of the criteria often used for assessing researchers for hiring, tenure and promotion [@vanarensbergenDifferentViewsScholarly2014; @moherAssessingScientistsHiring2018], constituting one factor of research excellence.
+Even from the perspective of scholarly output, protégés were found to “do their best work when they break from their mentor’s research topics and coauthor no more than a small portion of their overall research with their mentors” [@ma2020].
 @lienard2018 found that making a larger thematic step from the PhD advisor and finding a post-doc advisor with less similar interests was also related to increased chances of continuing in academia and having more mentees later on (although under the condition that one remains thematically close to the post-doc advisor).
-There is also some direct preliminary evidence that higher independence modestly correlates with the number of citations acquired (Rojko & Lužar, 2022), but others argue that even the research systems with very low independence can create a lot of scientific impact, and thus the relationships between independence and impact might not be as clear (Gläser et al., 2021)
+There is also some direct preliminary evidence that higher independence modestly correlates with the number of citations acquired [@rojkoScientificPerformanceResearch2022], but others argue that even the research systems with very low independence can create a lot of scientific impact, and thus the relationships between independence and impact might not be as clear [@glaserIndependenceResearchReview2022].
 
@@
 One of them is study discipline.
-Based on some early empirical studies (@rojkoScientificPerformanceResearch2022), it seems that researchers in disciplines such as philosophy, psychology; religion, theology; social sciences; the arts, recreation, entertainment, sport; language, linguistics, literature; and geography, biography, history experience significantly higher levels of independence on their PhD advisor than researchers in disciplines such as science and knowledge, organization, computer science, information, documentation, librarianship, institutions, publications; mathematics, natural sciences; and applied sciences, medicine, technology.
-
-Interestingly, there is also some evidence that the propensity to cognitive independence might be inherited and passed down from generation to generation in mentor-mentee relationships (@yoshioka-kobayashi2021) - perhaps it is not only research agendas that students inherit from their advisors but also the tendency to deviate from those research agendas.
-
-In recent decades, there has been a worry that researchers’ independence is decreasing, illustrated by an increase in the age at which researchers received their first grant (@powell2016, @christian2021; and NAS, 2005; @danielsGenerationRiskYoung2015 for US biomedical researchers specifically), as well as direct measures of new researchers becoming more dependent on their PhD advisors across almost all disciplines in Slovenia (@rojkoScientificPerformanceResearch2022, table 6 on p.9).
-These trends have motivated some to create new proposals for funding agencies and other research funders in order to support early career researchers (@dewinde2021)
+Based on some early empirical studies [@rojkoScientificPerformanceResearch2022], it seems that researchers in social sciences and humanities experience significantly higher levels of independence from their PhD advisor than researchers in other disciplines.
+
+Interestingly, there is also some evidence that the propensity to cognitive independence might be inherited and passed down from generation to generation in mentor-mentee relationships [@yoshioka-kobayashi2021] - perhaps it is not only research agendas that students inherit from their advisors but also the tendency to deviate from those research agendas.
+
+In recent decades, there has been a worry that researchers’ independence is decreasing, illustrated by an increase in the age at which researchers received their first grant [@powell2016; @christian2021; and @nationalresearchcouncilus2005; @danielsGenerationRiskYoung2015 for US biomedical researchers specifically], as well as direct measures of new researchers becoming more dependent on their PhD advisors across almost all disciplines in Slovenia [@rojkoScientificPerformanceResearch2022, table 6 on p.9].
+These trends have motivated some to create new proposals for funding agencies and other research funders in order to support early career researchers [@dewinde2021]
 
 Perhaps to tackle this trend, many grant agencies decided to support early career researcher by funding.
-Some have decided to tackle this trend by giving advantage to first-awardees and early career researchers in their usual distribution process, while others have created specific programmes designated to funding young researchers soon, usually up to 8 years, after finishing their PhD.
+Some have decided to address this trend by giving advantage to first-awardees and early career researchers in their usual distribution process, while others have created specific programmes dedicated to funding young researchers, typically up to 8 years after completing their PhD.
 Such programmes have often explicitly stated goals of helping researchers become more independent, set up their own research groups and open up new lines of research.
-Examples of such programmes could be Starting Grants by European Research Council (@StartingGrantERC), Junior project and Junior Star by Czech Science Foundation (2020), Walter N.
-Benjamin Programme by DFG (@WalterBenjaminProgramme), Innovation Research Incentives Scheme by Netherlands Organization of Scientific Research (NWO) (2021).
-
-Grant funding mechanisms have previously been shown to stimulate productivity in terms of the number of publications and impact in terms of citations (@gallo2018; for the Czech environment specifically see @bajgar2021; notable exception is @vandenbesselaar2015, who specifically looked at funding programmes for early career researchers and found small or no effect), and even scientific novelty (@wang2018, or, as some authors argue, rather interdisciplinarity: @fontana2020).
-In terms of career progress, obtaining grant funding was connected to significantly higher chances of career progression and obtaining a professorship (@bloch2014, @vandenbesselaar2015).
+Examples of such programmes could be Starting Grants by European Research Council [@StartingGrantERC], Junior project and Junior Star by @czechsciencefoundation2019, Walter N.
+Benjamin Programme by DFG [@WalterBenjaminProgramme], Innovation Research Incentives Scheme by Netherlands Organization of Scientific Research [@nwo2023].
+
+Grant funding mechanisms have previously been shown to stimulate productivity in terms of the number of publications and impact in terms of citations [@gallo2018; for the Czech environment specifically see @bajgar2021; notable exception is @vandenbesselaar2015, who specifically looked at funding programmes for early career researchers and found small or no effect], and even scientific novelty [@wang2018, or, as some authors argue, rather interdisciplinarity: @fontana2020].
+In terms of career progress, obtaining grant funding was connected to significantly higher chances of career progression and obtaining a professorship [@bloch2014, @vandenbesselaar2015].
 
@@
 However, there hasn’t been much effort focused on quantifying this phenomenon.
-Some studies try to measure independence in a simple way, as a ratio of publications the given researcher produced without their supervisor divided by the total number of publications of the given researchers (e.g.
-@rojkoScientificPerformanceResearch2022).
+Some studies try to measure independence in a simple way, as a ratio of publications the given researcher produced without their supervisor divided by the total number of publications of the given researchers [e.g.
+@rojkoScientificPerformanceResearch2022].
 However, such an indicator could be misleading in the world of team science, and also only focuses on collaborations, not tracking whether a given researcher becomes independent in their thinking and research topics.
 @vandenbesselaarMeasuringResearcherIndependence2019 therefore proposed a more complex indicator for measuring researcher independence on the individual level, based on co-authorship network and topical overlaps.
-Their measure uses only information about publications’ characteristics (authorship and reference list) regardless of their impacts, unlike other alternative measures that focus solely on the impact of the independent work in terms of received citations (Dey, et al., 2021 -> ALIS, citation need repair).
+Their measure uses only information about publications’ characteristics (authorship and reference list) regardless of their impacts, unlike other alternative measures that focus solely on the impact of the independent work in terms of received citations [@dey2023].
 
@@
 In the second step, we manually searched for PhD advisors of these 341 researchers in the databases of theses and dissertations that cover most universities in Czechia (https://theses.cz and https://dspace.cuni.cz/).
-We were able to match `r nrow(tar_read(ids_complete))` researchers with a PhD advisor (81 % of the Czech subsample).
-Further, we have not managed to find a suitable matched pair for another `r nrow(tar_read(ids_complete))-nrow(tar_read("matching") %>% filter(treatment == 1) %>% distinct(vedidk))` researchers in the matching procedure, reducing our final sample to `r nrow(tar_read("matching") %>% filter(treatment == 1) %>% distinct(vedidk))`.
+We were able to match `r nrow(tar_read(ids_complete) %>% filter(!is.na(sup_name)))` researchers with a PhD advisor (82 % of the Czech subsample) and find suitable matched pair from control group for each of them.
+<!-- Further, we have not managed to find a suitable matched pair for another `r nrow(tar_read(ids_complete))-nrow(tar_read("matching") %>% filter(treatment == 1) %>% distinct(vedidk))` researchers in the matching procedure, reducing our final sample to `r nrow(tar_read("matching") %>% filter(treatment == 1) %>% distinct(vedidk))`.
+-->
 
@@
 
-These researchers and their PhD advisors with their full publication history (limited to publications created at Czech institutions) created our final sample.
-
-We also tested an assumption that had a hope of reducing time intensity of data collection by substitution it for algorithmic approach: using the "most frequent co-author of the first 5 publications" as a proxy to identify supervisors.
-Crosschecking this proxy with the actual data about supervisors we found manually, we found that this algorithm was able to identify supervisors correctly in about 56 % of cases (see the Attachment 1).
+These researchers and their PhD advisors with their full publication history (limited to publications created at Czech institutions) constituted our final sample.
+
+We also tested an assumption that had a hope of reducing time intensity of data collection by substituting it with an algorithmic approach: using the "most frequent co-author of the first 5 publications" as a proxy to identify supervisors.
+Crosschecking this proxy with the actual data about supervisors we found manually showed that this algorithm was able to identify supervisors correctly in only about 56 % of cases (see the Attachments).
 
@@
 In determining the proportion of a researcher's own research topics (I4), we opted for text-based topic modeling utilizing publication titles and abstracts, diverging from the originally suggested bibliographic coupling method.
-Initially, we conducted a random sampling of 3000 publications from a set of all publications produced by researchers affiliated with Czech institutions as cataloged in the RIV database, estimated number of topics using Griffiths2004 indicator and calculated LDA topic model on this set of publications.
+Initially, we conducted a random sampling of 3000 publications from a set of all publications produced by researchers affiliated with Czech institutions as cataloged in the RIV database, estimated number of topics using Griffiths2004 indicator, and calculated LDA topic model on this set of publications.
 Then we  compiled all publications generated by the researchers within our sample and their respective supervisors.
@@
 
-To calculate this indicator, we required at least 3 publications. This led to an increased number of missing observations (see section Descriptives -> Missing data).
+To calculate this indicator, we required at least 3 publications. This led to an increased number of missing observations (see section Descriptives - Missing data).
 
@@
 
-We used the highest level of the OECD classification of disciplines, containing categories Natural Sciences; Engineering and Technology; Medical and Health Sciences; Agricultural Sciences; Social Sciences; Humanities.
-We chose this classification because it is widely used and also used in the dataset we worked with.
+We used the highest level of the OECD classification of disciplines: containing categories Natural Sciences; Engineering and Technology; Medical and Health Sciences; Agricultural Sciences; Social Sciences; Humanities.
+We chose this classification because it is widely used and also present in the dataset we worked with.
 For the matching we used the 42 sub-categories of this classification to achieve more granularity.
@@
 We used Genderize.io API to estimate the probability of perceived gender based on the first names of researchers.
-Where available, information about the nationality of researchers was included in the API call to improve accuracy.
-We have also manually specified gender for 2 obrsevtation from the treatment group for which the gender was not calculated automatically.
+We had also manually specify gender for 2 observations from the treatment group for which the gender was not calculated automatically.
 
@@
 using R studio and [this code](https://github.com/david-janku/juniors).
-For the construction of the independence indicator, we used network modelling (maybe more specific?) and text-based topic modelling (maybe more specific??).
-
-For the construction of the control group, we implemented propensity matching using the package MatchIt (citation?) and matching exactly by the discipline (42 sub-categories of OECD classification) and treatment year, and approximately by number of publications in total, number of publications in WoS/Scopus, career age, interdisciplinary proportion, number of grants received prior to Junior Grant, career age when receiving the first grant and gender.
-All of these variables were calculated at the intervention year (i.e.
+For the construction of the independence indicator, we used network modelling and text-based topic modelling.
+
+For the construction of the control group, we implemented propensity matching using the package MatchIt [@ho2011] and matching exactly by the discipline (42 sub-categories of OECD classification) and treatment year, and approximately by number of publications in total, number of publications in WoS/Scopus, career age, interdisciplinary proportion, number of grants received prior to Junior Grant, career age when receiving the first grant, and gender.
+All of these variables were calculated in the intervention year (i.e.
 year when the given researcher from experimental group received the Junior Grant).
@@
 
-The difference between groups was tested using paired t-test and subsequent differences between discipline groups was tested using ANOVA post-hoc Tukey test.
+The difference between treatment groups was tested using repeated measures ANOVA with a special error term taking into account paired nature of the data.
+The ANOVA model was specified as RII ~ treatment * independence_timing, incorporating both the main effects and the interaction between treatment and independence timing.
+A significant aspect of our ANOVA approach was the inclusion of an error term structured as Error(subclass/independence_timing).
+This error structure accounts for the nested or hierarchical nature of our data, where measurements are nested within subclasses and vary across different independence timings.
+By doing so, the model adjusts for potential within-subclass correlations and differences across independence timings.
+
+To ascertain the significance of academic field as a predictor, we constructed two additional GLS models.
+The first model included treatment, independence timing, and their interaction as predictors (treatment + independence_timing + treatment:independence_timing), while the second model added the main effect of the academic field (+ field).
+Both models employed a compound symmetry correlation structure (corCompSymm) based on subclass and independence timing, suitable for data with equal correlation between observations.
+By comparing these models, we aimed to evaluate the impact of including the academic field as a predictor on the model's explanatory power, thereby testing its statistical significance in explaining variations in RII.
 
@@
 The independence indicator was not possible to calculate for `r na_counts` (`r na_percentage` % of observations).
-This is in `r na_sup` % caused by missing data about supervisors, and in `r na_pubs` % due to given researcher not having any publications in the given period (`r na_pubs_after` % of these cases are in the period after the intervention, which sometimes mean in the past few years).
+This is in `r na_sup` % caused by missing data about supervisors, and in `r na_pubs` % due to absence of publications by the researcher during the specified period (`r na_pubs_after` % of these cases occurred post-intervention, often in the past few years).
 
@@
 
-When Looking at disciplines, we see that there are slightly more missing data in Agricultural and veterinary sciences and the Humanities and the Arts.
+From a perspective of disciplines, we see that there are slightly more missing data in Agricultural and veterinary sciences and the Humanities and the Arts.
 
@@
   rename(
+    Field = field,
     Complete = count_Complete,
@@
 # Print the updated table
-kable(df_summary, digits = 3, caption = "Counts and Proportions of Missing data by disc_ford") %>%
+kable(df_summary, digits = 3, caption = "Counts and Proportions of Missing Data by Field") %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
@@
 # descriptive stats for each treatment level
-table_before_1 <- df %>% filter(treatment == 1) %>% select(all_of(numeric_vars)) %>% describe() %>% select(n, mean, sd, min, max) %>% round(., digits = 3)
-table_before_0 <- df %>% filter(treatment == 0) %>% select(all_of(numeric_vars)) %>% describe() %>% select(n, mean, sd, min, max) %>% round(., digits = 3)
-table_before_2 <- df %>% filter(treatment == 2) %>% select(all_of(numeric_vars)) %>% describe() %>% select(n, mean, sd, min, max) %>% round(., digits = 3)
+table_before_1 <- df %>% filter(treatment == 1) %>% distinct(vedidk, .keep_all = TRUE) %>% select(all_of(numeric_vars)) %>% describe() %>% select(n, mean, sd, min, max) %>% round(., digits = 3)
+table_before_0 <- df %>% filter(treatment == 0) %>% distinct(vedidk, .keep_all = TRUE) %>% select(all_of(numeric_vars)) %>% describe() %>% select(n, mean, sd, min, max) %>% round(., digits = 3)
+table_before_2 <- df %>% filter(treatment == 2) %>% distinct(vedidk, .keep_all = TRUE) %>% select(all_of(numeric_vars)) %>% describe() %>% select(n, mean, sd, min, max) %>% round(., digits = 3)
 
@@
 
-combined_table_before <- cbind(table_before_1, table_before_0[, -1], table_before_2[, -1])
+combined_table_before <- cbind(table_before_1, table_before_0, table_before_2)
 
 kable(combined_table_before, 
-      digits = 3, align = "c", booktabs = TRUE) %>%
+      digits = 3, align = "c", booktabs = TRUE, caption = "Descriptives of All Groups Before Intervention") %>%
   kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
-  add_header_above(c(" " = 1, "Treatment Group" = 5, "Unfunded Control Group" = 4, "Funded Control Group" = 4))
+  add_header_above(c(" " = 1, "Treatment Group" = 5, "Unfunded Control Group" = 5, "Funded Control Group" = 5))
 
@@
 # descriptive stats for each treatment level
-table_after_1 <- df %>% filter(treatment == 1) %>% select(all_of(numeric_vars)) %>% describe() %>% select(n, mean, sd, min, max) %>% round(., digits = 3)
-table_after_0 <- df %>% filter(treatment == 0) %>% select(all_of(numeric_vars)) %>% describe() %>% select(n, mean, sd, min, max) %>% round(., digits = 3)
-table_after_2 <- df %>% filter(treatment == 2) %>% select(all_of(numeric_vars)) %>% describe() %>% select(n, mean, sd, min, max) %>% round(., digits = 3)
+table_after_1 <- df %>% filter(treatment == 1) %>% distinct(vedidk, .keep_all = TRUE) %>% select(all_of(numeric_vars)) %>% describe() %>% select(n, mean, sd, min, max) %>% round(., digits = 3)
+table_after_0 <- df %>% filter(treatment == 0) %>% distinct(vedidk, .keep_all = TRUE) %>% select(all_of(numeric_vars)) %>% describe() %>% select(n, mean, sd, min, max) %>% round(., digits = 3)
+table_after_2 <- df %>% filter(treatment == 2) %>% distinct(vedidk, .keep_all = TRUE) %>% select(all_of(numeric_vars)) %>% describe() %>% select(n, mean, sd, min, max) %>% round(., digits = 3)
 
@@
 # Re-combine tables
-combined_table_after <- cbind(table_after_1, table_after_0[, -1], table_after_2[, -1])
+combined_table_after <- cbind(table_after_1, table_after_0, table_after_2)
 
 kable(combined_table_after, 
-      digits = 3, align = "c", booktabs = TRUE) %>%
+      digits = 3, align = "c", booktabs = TRUE, caption = "Descriptives of All Groups After Intervention") %>%
   kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
-  add_header_above(c(" " = 1, "Treatment Group" = 5, "Unfunded Control Group" = 4, "Funded Control Group" = 4))
+  add_header_above(c(" " = 1, "Treatment Group" = 5, "Unfunded Control Group" = 5, "Funded Control Group" = 5))
 
@@
 
-```{r echo=FALSE}
+```{r echo=FALSE, fig.cap="Covariate balance table for the unfunded control group."}
 # # Create a subset for treatment group and control group 1
@@
 # Display the cleaned-up table with kable
-kable(bal_df, "pipe", caption = "Balance Statistics For Unfunded Control Group") %>%
+kable(bal_df, "pipe", caption = "Summary of Covariate Balance Post-Matching For Unfunded Control Group") %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
@@
 
+```
+
+```{r echo=FALSE, fig.cap="Covariate balance table for the funded control group."}
+
 ##Funded group
@@
 # Display the cleaned-up table with kable
-kable(bal_df_funded, "pipe", caption = "Balance Statistics For Funded Control Group") %>%
+kable(bal_df_funded, "pipe", caption = "Summary of Covariate Balance Post-Matching For Funded Control Group") %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
@@
 #   mutate(se_RII = sd_RII / sqrt(n))
-# 
 # 
@@
 This effect accounted for approximately `r format(eta_sq_result[eta_sq_result$Parameter == "independence_timing", "Eta2_partial"] * 100, digits=2)`% of the observed variance (partial \(\eta^2 = `r round(eta_sq_result[eta_sq_result$Parameter == "independence_timing", "Eta2_partial"], 3)`\), 95% CI [`r round(eta_sq_result[eta_sq_result$Parameter == "independence_timing", "CI_low"], 3)`, `r eta_sq_result[eta_sq_result$Parameter == "independence_timing", "CI_high"]`]).
-
-Importantly, there was a significant interaction effect between treatment and time on independence, F(`r format(summary(result)$"Error: Within"[[1]]$"Df"[2])`, `r format(summary(result)$"Error: Within"[[1]]$"Df"[3])`) = `r format(summary(result)$"Error: Within"[[1]]$"F value"[2], digits=2)`, p = `r format(summary(result)$"Error: Within"[[1]]$"Pr(>F)"[2], digits=2)`.
-This interaction effect explained about `r format(eta_sq_result[eta_sq_result$Parameter == "treatment:independence_timing", "Eta2_partial"] * 100, digits=2)`% of the variability (partial \(\eta^2 = `r round(eta_sq_result[eta_sq_result$Parameter == "treatment:independence_timing", "Eta2_partial"], 3)`\), 95% CI [`r eta_sq_result[eta_sq_result$Parameter == "treatment:independence_timing", "CI_low"]`, `r round(eta_sq_result[eta_sq_result$Parameter == "treatment:independence_timing", "CI_high"], 3)`]).
+However, there was no significant interaction effect between treatment and time on independence, F(`r format(summary(result)$"Error: Within"[[1]]$"Df"[2])`, `r format(summary(result)$"Error: Within"[[1]]$"Df"[3])`) = `r format(summary(result)$"Error: Within"[[1]]$"F value"[2], digits=2)`, p = `r format(summary(result)$"Error: Within"[[1]]$"Pr(>F)"[2], digits=2)` and this interaction effect explained only about `r format(eta_sq_result[eta_sq_result$Parameter == "treatment:independence_timing", "Eta2_partial"] * 100, digits=2)`% of the variability (partial \(\eta^2 = `r round(eta_sq_result[eta_sq_result$Parameter == "treatment:independence_timing", "Eta2_partial"], 3)`\), 95% CI [`r eta_sq_result[eta_sq_result$Parameter == "treatment:independence_timing", "CI_low"]`, `r round(eta_sq_result[eta_sq_result$Parameter == "treatment:independence_timing", "CI_high"], 3)`]).
 
@@
 This suggests that there are statistically significant differences in the RII based on the field of study.
-Specifically, adding the field of study to the model resulted in a significant increase in the log-likelihood by `r round(anova_result$L.Ratio[2], 2)` units (p < `r round(anova_result$"p-value"[2], 3)`), emphasizing its importance as a predictor.
-Specifically, compared to the Engineering and Technology field, being in the Medical and Health Sciences field is associated with a decrease in RII by `r  round(coef(model_summary)["fieldMedical and Health Sciences", 1], 2)` units, on average (p = `r round(coef(model_summary)["fieldMedical and Health Sciences", 4], 3)`), while being in the Humanities and Arts is associated with an increase in RII by `r round(coef(model_summary)["fieldHumanities and the Arts", 1], 2)` units (p = `r round(coef(model_summary)["fieldHumanities and the Arts", 4], 3)`).
-There are no statistically significant differences between Natural Sciences and Engineering and Technology.
-Humanities and Agricultural sciences categories were excluded because they had too few observations.
+Specifically, adding the field of study to the model resulted in a significant increase in the log-likelihood by `r round(anova_result$L.Ratio[2], 2)` units (p = `r round(anova_result$"p-value"[2], 3)`), emphasizing its importance as a predictor.
+Specifically, compared to the Agricultural and Veterinary Sciences field, being in the Social Sciences field is associated with an increase in RII by `r  round(coef(model_summary)["fieldSocial Sciences", 1], 2)` units, on average (p = `r round(coef(model_summary)["fieldSocial Sciences", 4], 3)`), as well as being in the Humanities and the Arts field (increase by `r round(coef(model_summary)["fieldHumanities and the Arts", 1], 2)` units, p = `r round(coef(model_summary)["fieldHumanities and the Arts", 4], 3)`).
+Natural Sciences, Engineering and Technology and Medical and Health Sciences were not associated with a significant increase in RII compared to Agricultural and Veterinary Sciences.
+
 The interaction between treatment and field was not statistically significant, suggesting that the effect of treatment on independence was consistent across disciplines.
@@
 
-```{r echo=FALSE}
+```{r echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Violin Plot of RII Scores by Treatment and Time with Mean and CI Overlayed for the Unfunded Control Group."}
 
@@
 
-  labs(title = "Violin Plot of RII Scores by Treatment and Time with Mean and CI Overlayed",
-       x = "Treatment Group",
+  labs(x = "Treatment Group",
        y = "RII Score") +
@@
 
-```{r echo=FALSE}
+```{r echo=FALSE, warning=FALSE, message=FALSE}
 
@@
 # means_disc <- means_disc %>% arrange(field)
-# 
 # 
@@
 
-# summary(model_gls_weighted2)
+interaction_summary <- summary(model_gls_weighted2)
 
@@
 Same as in previous chapter, the comparison of models suggested that there are statistically significant differences in the RII based on the field of study.
-Specifically, adding the field of study to the model resulted in a significant increase in the log-likelihood by `r round(anova_result2$L.Ratio[2], 2)` units (p < `r round(anova_result2$"p-value"[2], 3)`), emphasizing its importance as a predictor.
-Specifically, compared to the Engineering and Technology field, being in the Medical and Health Sciences field is associated with a decrease in RII by `r  round(coef(model_summary2)["fieldMedical and Health Sciences", 1], 2)` units, on average (p = `r round(coef(model_summary2)["fieldMedical and Health Sciences", 4], 3)`), while being in the Social Sciences field is associated with an increase in RII by `r round(coef(model_summary2)["fieldSocial Sciences", 1], 2)` units (p = `r round(coef(model_summary2)["fieldSocial Sciences", 4], 3)`).
-There are no statistically significant differences between Natural Sciences and Engineering and Technology.
-Humanities and Agricultural sciences categories were excluded because they had too few observations.
-The interaction between treatment and field was not statistically significant, suggesting that the effect of treatment on independence was consistent across disciplines.
+Specifically, adding the field of study to the model resulted in a significant increase in the log-likelihood by `r round(anova_result2$L.Ratio[2], 2)` units (p = `r round(anova_result2$"p-value"[2], 3)`), emphasizing its importance as a predictor.
+Specifically, compared to the Agricultural and Veterinary Sciences, being in the Medical and Health Sciences field is associated with an increase in RII by `r  round(coef(model_summary2)["fieldMedical and Health Sciences", 1], 2)` units (p = `r round(coef(model_summary2)["fieldMedical and Health Sciences", 4], 3)`), being in the Natural Sciences is associated with an increase in RII by `r  round(coef(model_summary2)["fieldNatural Sciences", 1], 2)` units (p = `r round(coef(model_summary2)["fieldNatural Sciences", 4], 3)`), Engineering and Technology are associated with an increase in RII by `r  round(coef(model_summary2)["fieldEngineering and Technology", 1], 2)` units (p = `r round(coef(model_summary2)["fieldEngineering and Technology", 4], 3)`), Social Sciences are associated with an increase in RII by `r round(coef(model_summary2)["fieldSocial Sciences", 1], 2)` units (p = `r round(coef(model_summary2)["fieldSocial Sciences", 4], 3)`), and Humanities and the Arts are associated with an increase in RII by `r round(coef(model_summary2)["fieldHumanities and the Arts", 1], 2)` units (p = `r round(coef(model_summary2)["fieldHumanities and the Arts", 4], 3)`).
+
 The three-way interaction among treatment, independence_timing, and field was not statistically significant.
@@
 
-```{r echo=FALSE}
+```{r echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Violin Plot of RII Scores by Treatment and Time with Mean and CI Overlayed for the Funded Control Group."}
 
@@
 # means_disc2 <- means_disc2 %>% arrange(field)
-# 
 # 
@@
 
+```
+
+```{r echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Differences in average RII across disciplines."}
+
 disc_data <- d %>%
@@
     y = "Mean RII",
-    title = "Differences in average RII across disciplines"
     ) +
@@
 
-kable(cor_matrix, format = "html", digits = 2) %>%
+kable(cor_matrix, format = "html", digits = 2, caption = "Correlation Matrix of RII indicator and its sub-parts") %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
@@
 
-```{r echo=FALSE}
+```{r echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Violin Plot of the Cognitive Part of RII Scores by Treatment and Time with Mean and CI Overlayed for the Unfunded Control Group."}
 
@@
 
-  labs(title = "Violin Plot of ind_topics Scores by Treatment and Time with Mean and CI Overlayed",
-       x = "Treatment Group",
+  labs(x = "Treatment Group",
        y = "ind_topics Score") +
@@
 
-When looking at the scores of cognitive part of independence indicator, we cannot see notable differences across fields of study, unlike it case of the whole RII.
---> SHOULD I STATISTICALLY TEST whether adding filed of study improves prediction of the id_topics? (same way as when I tested that for full RII)??
-
-```{r echo=FALSE}
+Similar pattern can be observed in differences across disciplines - while there were significant differences in full indicator scores, its cognitive part doesn't show any differences, suggesting that collaboration is the factor driving differences across fields of study.
+
+```{r echo=FALSE, fig.cap="Differences in Average Cognitive RII Scores (ind_topic) Across Disciplines and Time."}
 
@@
      ungroup()
+
+disc_data <- disc_data[!duplicated(disc_data[c("subject_id", "independence_timing")]), ]
 
@@
     y = "Mean ind_topics",
-    title = "Differences in average ind_topics across disciplines and time"
      ) +
@@
   theme_bw()
+
+```
+
+```{r echo=FALSE, fig.cap="Average Change in Cognitive RII Scores (ind_topic) Across Disciplines."}
 
@@
     y = "Mean ind_topics_diff",
-    title = "Average change in cognitive independence across disciplines"
     ) +
@@
 The results of this study provide important insights into the effects of funding interventions on researcher independence.
-The strongest effect we found across all control group comparisons was the effect of time - over time, researchers become more independent, regardless of their access to funding or their study discipline.
+We did not find a significant intervention effect of funding programmes for early career researchers, compared to no funding or other types of grant funding.
+These results suggest funding might not be an important factor in developing researcher independence.
+This is surprising finding, since many people have voiced worries about funding having strong effect either by making junior researchers more cautious and risk-averse in order to fulfill the grant conditions, limiting the novelty of their work; or by giving them more protected space where they can freely experiment and step off the traditional paths, opening new lines of research.
+Neither of these theories are supported by our findings.
+Instead, there are likely other factors influencing development of research independence more significantly.
+
+The strongest effect we found across all control group comparisons was the effect of time: over time, researchers become more independent, regardless of their access to funding or their study discipline.
 This effect explains around 60% of the variance in independence.
@@
 Additionally, the observed variation in independence across different disciplines underscores the importance of considering disciplinary differences, suggested by a moderate effect size.
-A moderate effect size for the field effect emphasizes that certain disciplines might inherently have variations in researchers' independence, perhaps due to differences in practices, methodologies, or norms specific to each discipline.
-Anyway, these differences remain constant across time and funding interventions, suggesting that funding has a uniform effect on the independence across disciplines.
-
-Importantly, the significant interaction between treatment and time when comparing treatment vs unfunded control group suggests the funding has positive effect on stimulating researchers' independence.
-However, the effect size is only modest, explaining about 2 % of variance in independence, indicating relatively small practical relevance.
-Further, the insignificant interaction when comparing the treatment vs funded control group suggests that funding in this career stage has the same effect, regardless of its type or source.
-Interestingly, in our sample both funded groups (treatment as well as control) started with lower independence compared to unfunded control group.
-This might suggest that in the early career stages, being more dependent on one's PhD advisor might be  beneficial (or even required) to obtain independent funding.
+A moderate effect size for the field effect emphasizes that certain disciplines might inherently have variations in researchers' independence, but this is driven mostly by collaboration patterns rather than cognitive patterns (e.g.
+differences in practices, methodologies, or norms specific to each discipline).
+These differences remain constant across time and funding interventions, suggesting that funding has a uniform effect on the independence across disciplines.
 
 Finally, when looking closer into the composition of the independence indicator, we found that that the main driver of the increase in independence was the collaboration part of the indicator - creating new collaboration networks - rather than the cognitive part - opening up new lines of research in which their PhD advisor is not active.
-While the level of cognitive independence is still relatively high even early on after finishing one's PhD (researchers have around 40 % of topics not shared by their PhD advisor) and increases over time, the funding does not stimulate more novelty and divergence from the portfolio of topics held by their PhD advisors.
+While the level of cognitive independence is still relatively high even early on after finishing one's PhD (researchers have around 40 % of topics not shared by their PhD advisor 8 years after their first publication) and increases over time, the funding does not stimulate more novelty and divergence from the portfolio of topics held by their PhD advisors.
 
 Given that funding for early career researchers does not have effect on stimulating their cognitive independence, does it make sense to continue providing it?
-While funding itself might not be the main driver of cognitive independence, its might still play an important role - for example, it could be a necessary thought not sufficient condition for the development of independence.
-From a common sense view, it is hard to imagine that researchers can develop much of independence while working on someone else's (often their advisor') projects.
-Moreover, funding did show to modestly stimulate creation of more independent collaborative networks, which might have a value in itself by establishing early career researchers in the scientific community and making their positions more robust.
-This would hopefully enable them to explore more rapidly later on, though that is not guaranteed.
-In any case, our results suggest that the search for factors and interventions stimulating researchers' explorative behaviour should continue.
-
-Main value of this paper is manyfold:
-- it investigated one potential factor (funding) hypothesized to stimulate researcher independence, rendering this factor unimportant, contrary to expectations
-- it confirmed there are meaningful differences in level of independence across disciplines
-- it has illuminated the magnitude of cognitive independence experienced by researchers early in their careers and its development to later stages, contributing to the discussions about tradition and innovation in research topic choice strategies and recreating status quo in science
+While funding itself might not be the main driver of cognitive independence, it might still play an important role.
+For example, it could be a necessary, though not sufficient, condition for the development of independence.
+From a common sense view, it is hard to imagine that researchers can develop much of independence while only working on someone else's (often their advisor's) projects.
+In any case, our results suggest that the search for factors and interventions stimulating researchers' exploratory behaviours should continue.
+
+Main value of this paper is manyfold.
+It investigated one potential factor (funding) hypothesized to stimulate researcher independence, rendering this factor unimportant, contrary to expectations, Further, it confirmed there are meaningful differences in level of independence across disciplines and has illuminated the magnitude of cognitive independence experienced by researchers early in their careers, including its development to later stages.
+This contributes to the discussions about tradition and innovation in research topic choice strategies and recreating status quo in science.
 
@@
 One of the main limitations of this study is that it only focuses on Czech environment - researchers growing up and spending most of their careers in the Czech Republic, only taking into account their publications affiliated with Czech research institutions.
-Studies testing our results on samples from other countries, and possibly tracking international mobility would strengthen our conclusions.
+Studies testing our results on samples from other countries, and possibly tracking international mobility, would strengthen our conclusions.
 
 Another potential limitation is the length of the time after the intervention.
-We have tracked the effects of funding between 2-7 years after the project started, at a point where researchers created on average `r round(mean_pubs_after, 1)` publications (while `r na_counts_researchers` % of them have created less than 3 and were deleted from this analysis).
+We have tracked the effects of funding between 2-7 years after the grant projects started, at a point where researchers created on average `r round(mean_pubs_after, 1)` publications (while `r na_counts_researchers` % of them have created less than 3 publications and were removed from this analysis).
 It might be possible that independence needs more time to develop and had we measured the effects later, we would have found stronger effects.
 
-Further research could look more into which other factors influence researcher independence (especially the cognitive part) and how strongly compared to grant funding.
+Further research could look into which other factors influence researcher independence (especially its cognitive part) and how strongly, compared to grant funding.
 
@@
 
-Our results showed that funding helps modestly to stimulate collaborative independence of early career researchers, but does not stimulate their cognitive independence.
-The largest effect on increase in composite independence was time - over time, researchers become more independent, regardless of their access to funding or their study discipline.
-There were also significant differences in independence level across study disciplines, where social sciences and humanities allowed for more independence than medical and health sciences and natural sciences.
-Researchers usually start with around 40 % of topics not shared by their PhD advisor early on after finishing their PhD and grow more independent over time (up to 47 % 13.5 years after their first publication).
-Search for factors and interventions stimulating researchers' cognitive independence and explorative behaviour should thus continue.
+Our results showed that funding does not help to stimulate independence of early career researchers.
+The largest effect on increase in independence was time: over time, researchers become more independent, regardless of their access to funding or their study discipline.
+There were also significant differences in independence level across study disciplines, where social sciences and humanities allowed for more independence than other disciplines.
+Researchers usually start with around 40 % of topics not shared by their PhD advisor early on after finishing their PhD and grow more independent over time (up to 47 % of independent topics 14 years after their first publication).
+Search for factors and interventions stimulating researchers' cognitive independence and exploratory behaviour should thus continue.
 
@@
 
----------> should I put the next paragraph here?
-If yes, I should ask Luzar whether I can publish it, show the data to reviewers and ask him how to cite him.
-(the code is at the bottom of the fuction sup_test.R)
-
-Further, we have conducted analysis on an independent sample of researchers from Slovenia (citace Luzar??), and found that  when we filter out all researchers who have not had any publication 4 years prior to their PhD defense (1135, approx 9,5% of the sample), we see that from the remaining researchers, about 50,3 % had their supervisor as the most frequent coauthor in the 4 years prior to their PhD defense.
-
 This suggest that the algorithmic approach as we defined is not able to identify real supervisors often enough.

### 2024-01-19 article_formatted_doc.Rmd

--- 2024-01-19 article_formatted.Rmd
@@
 ---
-<!-- \doublespacing -->
+
+**Authors:**
+
+David Janků  
+[1] Institute of Sociological Studies, Faculty of Social Sciences, Charles University, Czech Republic; 
+[2] Centre for Science, Technology, and Society Studies, Institute of Philosophy, Czech Academy of Sciences, Czech Republic
+
+Radim Hladík  
+[1] Centre for Science, Technology, and Society Studies, Institute of Philosophy, Czech Academy of Sciences, Czech Republic
 
@@
 
-Your declaration of interest statement here.
+☐ The authors declare that they have no known competing financial interests or personal relationships that could have appeared to influence the work reported in this paper.
+
+☒ The authors declare the following financial interests/personal relationships which may be considered as potential competing interests:
+
+David Janku reports a relationship with Czech Science Foundation that includes: employment.
+If there are other authors, they declare that they have no known competing financial interests or personal relationships that could have appeared to influence the work reported in this paper.
 
@@
 Name: David Janků
+
 Affiliation: 
@@
 # Print the updated table
-kable(df_summary, digits = 3, caption = "Counts and Proportions of Missing Data by Field") %>%
-  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
+kable(df_summary, format = "markdown", digits = 3, caption = "Counts and Proportions of Missing Data by Field")
 
@@
 kable(combined_table_before, 
-      digits = 3, align = "c", booktabs = TRUE, caption = "Descriptives of All Groups Before Intervention") %>%
-  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
-  add_header_above(c(" " = 1, "Treatment Group" = 5, "Unfunded Control Group" = 5, "Funded Control Group" = 5))
+      format = "markdown", digits = 3, align = "c", booktabs = TRUE, caption = "Descriptives of All Groups Before Intervention") 
+  # kableExtra::add_header_above(c(" " = 1, "Treatment Group" = 5, "Unfunded Control Group" = 5, "Funded Control Group" = 5))
 
@@
 kable(combined_table_after,
-      digits = 3, align = "c", booktabs = TRUE, caption = "Descriptives of All Groups After Intervention") %>%
-  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
-  add_header_above(c(" " = 1, "Treatment Group" = 5, "Unfunded Control Group" = 5, "Funded Control Group" = 5))
+      format = "markdown", digits = 3, align = "c", booktabs = TRUE, caption = "Descriptives of All Groups After Intervention") %>%
+  kableExtra::add_header_above(c(" " = 1, "Treatment Group" = 5, "Unfunded Control Group" = 5, "Funded Control Group" = 5))
+
+# Assuming table_after_1, table_after_0, table_after_2 are your data frames for different groups
+# 
+# # Assuming each data frame has 5 columns
+# header_columns = c("Header", rep("", 4))
+# header_1 <- data.frame(matrix(nrow = 1, ncol = 5))
+# colnames(header_1) <- header_columns
+# header_1[1, 1] <- "Treatment Group"
+# 
+# header_0 <- data.frame(matrix(nrow = 1, ncol = 5))
+# colnames(header_0) <- header_columns
+# header_0[1, 1] <- "Unfunded Control Group"
+# 
+# header_2 <- data.frame(matrix(nrow = 1, ncol = 5))
+# colnames(header_2) <- header_columns
+# header_2[1, 1] <- "Funded Control Group"
+# 
+# header_names <- colnames(table_after_1)  # Assuming all tables have the same structure
+# header_row <- setNames(data.frame(matrix(ncol = length(header_names), nrow = 1), stringsAsFactors = FALSE), header_names)
+# header_row[1, 1] <- "Your Header Title"  # Set your header title in the first column
+# 
+# combined_table_after <- rbind(header_row, table_after_1, header_row, table_after_0, header_row, table_after_2)
+# 
+# 
+# # # Assuming table_after_1, table_after_0, table_after_2 have the same column names
+# # combined_table_after <- rbind(header_1, table_after_1, 
+# #                               header_0, table_after_0, 
+# #                               header_2, table_after_2)
+# 
+# # Now create the table in R Markdown
+# knitr::kable(combined_table_after, format = "markdown", digits = 3,
+#              caption = "Descriptives of All Groups After Intervention")
+
+# # Table for Treatment Group 1
+# table_after_1_md <- knitr::kable(table_after_1, format = "markdown", 
+#                                  caption = "Treatment Group 1")
+# 
+# # Table for Unfunded Control Group
+# table_after_0_md <- knitr::kable(table_after_0, format = "markdown", 
+#                                  caption = "Unfunded Control Group")
+# 
+# # Table for Funded Control Group
+# table_after_2_md <- knitr::kable(table_after_2, format = "markdown", 
+#                                  caption = "Funded Control Group")
+#
 
@@
 # Display the cleaned-up table with kable
-kable(bal_df, "pipe", caption = "Summary of Covariate Balance Post-Matching For Unfunded Control Group") %>%
-  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
+kable(bal_df, format = "markdown", caption = "Summary of Covariate Balance Post-Matching For Unfunded Control Group", digits = 3)
 
@@
 # Display the cleaned-up table with kable
-kable(bal_df_funded, "pipe", caption = "Summary of Covariate Balance Post-Matching For Funded Control Group") %>%
-  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
+kable(bal_df_funded, format = "markdown", caption = "Summary of Covariate Balance Post-Matching For Funded Control Group", digits = 3)
 
@@
 
-kable(cor_matrix, format = "html", digits = 2, caption = "Correlation Matrix of RII indicator and its sub-parts") %>%
-  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
+kable(cor_matrix, format = "markdown", digits = 2, caption = "Correlation Matrix of RII indicator and its sub-parts")
 

### 2024-01-19 _targets.Rmd

@@
       paths = here::here("data", "raw", "riv_authors.arrow"),
-       mode = "wb"),
+       mode = "wb", method = "curl"),
    tarchetypes::tar_download(sup_path,

### 2024-01-19 article.Rmd

--- 2023-11-01 article.Rmd
@@
 ---
-title: "Funding programmes for early career researchers marginally improves their collaboration independence, but not cognitive independence"
-author: "David Janků"
-date: "`r Sys.Date()`"
-output:
-  html_document:
-    df_print: paged
-  word_document: default
-always_allow_html: yes
+title: "Mission Unaccomplished: A Funding Programme for Early Career Researchers Fails to Promote Independence"
+author:
+- name: David Janků
+  affiliation: '[1] Centre for Science, Technology, and Society
+    Studies, Institute of Philosophy, Czech Academy of Sciences; [2] Institute of Sociological Studies, Faculty of Social Sciences,
+    Charles University'
+- name: Radim Hladík
+  affiliation: '[1] Centre for Science, Technology, and Society Studies, Institute
+    of Philosophy, Czech Academy of Sciences'
+output: bookdown::word_document2
+always_allow_html: true
 bibliography: merged.bib
 csl: apa.csl
+---
+
+**Authors:**
+
+David Janků  
+[1] Institute of Sociological Studies, Faculty of Social Sciences, Charles University, Czech Republic; 
+[2] Centre for Science, Technology, and Society Studies, Institute of Philosophy, Czech Academy of Sciences, Czech Republic
+
+Radim Hladík  
+[1] Centre for Science, Technology, and Society Studies, Institute of Philosophy, Czech Academy of Sciences, Czech Republic
+
+## Acknowledgements
+
+This work was supported by the Czech Science Foundation (project no. GJ20-01752Y, _Funded and Unfunded Research in the Czech Republic: Scientometric Analysis and Topic Modeling_).
+
+## Declaration of Interest
+
+☐ The authors declare that they have no known competing financial interests or personal relationships that could have appeared to influence the work reported in this paper.
+
+☒ The authors declare the following financial interests/personal relationships which may be considered as potential competing interests:
+
+David Janku reports a relationship with the Czech Science Foundation that includes: employment.
+If there are other authors, they declare that they have no known competing financial interests or personal relationships that could have appeared to influence the work reported in this paper.
+
+## Corresponding Author
+
+Name: David Janků
+
+Affiliation: 
+[1] Centre for Science, Technology, and Society Studies, Institute of Philosophy, Czech Academy of Sciences
+[2] Institute of Sociological Studies, Faculty of Social Sciences, Charles University
+Address: Jilská 1, 110 00, Praha 1, Czech Republic  
+E-mail: david.janku@fsv.cuni.cz
+
+\newpage
+
 ---
@@
 library(nlme)
-
 ```
@@
 
-Independence is important quality constituting one factor of research excellence, often used in assessments for hiring, tenure and promotion in academia [@moherAssessingScientistsHiring2018].
-From a bigger picture view, encouraging more independence might also lead to faster exploration of the cognitive map of science and thus lead to faster innovation.
-Many national research funders have created programmes specifically aimed at increasing independence of early career researchers, yet until recently, there was no quantifiable way to measure changes in independence.
-We employed recently proposed measure by @vandenbesselaarMeasuringResearcherIndependence2019 to asses whether one such funding programme by Czech Science Foundation is effective at stimulating more independence.
-We found that funding for early career researchers is effective at stimulating their independence, though the effect is relatively small (2 % of variance) and the source of funding does not matter.
-The funding also helped selected researchers to catch up with the unfunded group, rather than to outrun them.
-Additionally, we found differences in levels of independence across disciplines that were stable across time and treatment groups, with Social Sciences and Humanities showing highest independence, while Medical and Heath Sciences and Natural Sciences showing lowest independence.
-
-# Intro
-
-## Intro - full
+Independence is an important factor in research excellence, often assessed for hiring, tenure and promotion in academia.
+From a macro perspective, increased independence might also lead to faster exploration of the cognitive map of science and thus accelerate innovation.
+Many national research funders have created programmes specifically aimed at increasing the independence of early career researchers (ECRs).
+A quantifiable measure of such programmes' impact on changes in independence has long been lacking.
+We employed a recently proposed independence indicator [@vandenbesselaarMeasuringResearcherIndependence2019], modified via topic modeling to include a cognitive dimension, to asses whether one such funding programme operated by Czech Science Foundation succeeds at stimulating independence.
+The indicator tracks overlaps between ECRs and their Ph.D. advisors' collaboration networks and topic focus.
+We found that the funding scheme designed for ECRs is not effective at fostering their independence.
+Regardless of the type of funding, the strongest effect on independence growth is time, explaining around 60% of the variance in independence.
+Additionally, we found differences in levels of independence across disciplines that were stable across time and treatment groups.
+Researchers in Social Sciences and Humanities demonstrated the highest independence scores, while those in Agricultural and Veterinary Sciences, and Medical and Health Sciences, showed the lowest.
+However, these differences were predominantly driven by changes in collaboration patterns, while there were no changes in cognitive patterns across disciplines and only modest changes across time (from 40 % to 46 % of topics not shared between ECRs and their Ph.D.
+advisors).
+
+## Keywords
+research independence; early career researchers; project funding; mentoring; counter-factual analysis; research evaluation
+
+# Introduction
 
@@
 They found a decrease in the productivity of junior collaborators and an increase in published work by young newcomers in the field rewarded by an increased citation rate.
-That suggests the sudden departures of prominent scientists gave room for more disruptive changes in the field and for bringing new ideas and perspectives while harming the status quo holders who worked with the prominent scientists on their research agendas - a “Goliath effect,” as coined by @wang2021, p.42).
-
-This mirroring effect is also closely connected to the concept of academic inbreeding (@machacek2022), which focuses more on academic mobility and conservation of institutional habitus rather than specifically on the inheritance of research agendas.
+That suggests the sudden departures of prominent scientists gave room for more disruptive changes in the field and for bringing new ideas and perspectives while harming the status quo holders who worked with the prominent scientists on their research agendas - a “Goliath effect,” as coined by @wang2021, p.42.
+
+This mirroring effect is also closely connected to the concept of academic inbreeding [@machacek2022], which focuses more on academic mobility and conservation of institutional habitus rather than specifically on the inheritance of research agendas.
 However, inbreeding is also often thought to increase dependence and decrease exploration of new ideas.
 
-As younger researchers are already more likely to come up with new topics and ideas (@packalen2019), it would be fitting to empower them and stimulate their independence so that they can “challenge the existing common views and open up new lines of research” (@vandenbesselaarMeasuringResearcherIndependence2019, p.2) and accelerate scientific progress rather than recreate the existing status quo.
-An independent investigator is then defined by the US National Academies of Science (NAS) as “one who enjoys the independence of thought—the freedom to define the problem of interest and to choose or develop the best strategies and approaches to addressing that problem–especially during the earlier career phase” (@vandenbesselaarMeasuringResearcherIndependence2019, 2019, p.4).
-Such a definition does not necessarily put independence in relation to other actors (e.g.
-one’s PhD advisor), but only in relation to one’s own freedom and resources.
-However other institutions, such as European Research Council via their Starting Grants scheme (@neufeldPeerReviewbasedSelection2013) think of independence in a relational manner, in terms of having one (or a few) publications without the former PhD supervisor being co-author; being PI on a grant; or being lab director or research leader.
-
-Developing independence is also one of the things that the system of science expects from its members - it is one of the criteria often used for assessing researchers for hiring, tenure and promotion (@vanarensbergenDifferentViewsScholarly2014; @moherAssessingScientistsHiring2018), constituting one factor of research excellence.
-Even from the perspective of scholarly output, protégés were found to “do their best work when they break from their mentor’s research topics and coauthor no more than a small portion of their overall research with their mentors” (@ma2020).
+As younger researchers are already more likely to come up with new topics and ideas [@packalen2019], it would be fitting to empower them and stimulate their independence so that they can “challenge the existing common views and open up new lines of research” [@vandenbesselaarMeasuringResearcherIndependence2019, p.2] and accelerate scientific progress rather than recreate the existing status quo.
+An independent investigator is then defined by the US National Academies of Science [@nationalresearchcouncilus2005] as “one who enjoys the independence of thought—the freedom to define the problem of interest and to choose or develop the best strategies and approaches to addressing that problem–especially during the earlier career phase” [@vandenbesselaarMeasuringResearcherIndependence2019, p.4].
+Such a definition does not necessarily put independence in relation to other actors (e.g. one’s PhD advisor), but only in relation to one’s own freedom and resources.
+However other institutions, such as European Research Council via their Starting Grants scheme [@neufeldPeerReviewbasedSelection2013] think of independence in a relational manner, in terms of having one (or a few) publications without the former PhD supervisor being co-author; being PI on a grant; or being lab director or research leader.
+
+Developing independence is also one of the things that the system of science expects from its members - it is one of the criteria often used for assessing researchers for hiring, tenure and promotion [@vanarensbergenDifferentViewsScholarly2014; @moherAssessingScientistsHiring2018], constituting one factor of research excellence.
+Even from the perspective of scholarly output, protégés were found to “do their best work when they break from their mentor’s research topics and coauthor no more than a small portion of their overall research with their mentors” [@ma2020].
 @lienard2018 found that making a larger thematic step from the PhD advisor and finding a post-doc advisor with less similar interests was also related to increased chances of continuing in academia and having more mentees later on (although under the condition that one remains thematically close to the post-doc advisor).
-There is also some direct preliminary evidence that higher independence modestly correlates with the number of citations acquired (Rojko & Lužar, 2022), but others argue that even the research systems with very low independence can create a lot of scientific impact, and thus the relationships between independence and impact might not be as clear (Gläser et al., 2021)
+There is also some direct preliminary evidence that higher independence modestly correlates with the number of citations acquired [@rojkoScientificPerformanceResearch2022], but others argue that even the research systems with very low independence can create a lot of scientific impact, and thus the relationships between independence and impact might not be as clear [@glaserIndependenceResearchReview2022].
 
@@
 
-However, we have made some changes to the indicator. After consulting with its authors, we have changed the aggregation formula to 
+However, we have made some changes to the indicator.
+After consulting with its authors, we have changed the aggregation formula to 
 $$RII = ((1- I1) + I2 + I3 + I4) / 4$$ 
-since the previous formula had a small error (it weighted I4 double,, i.e.
-2*I4).
+since the previous formula had a small error (it weighted I4 double,, i.e. 2*I4).
 In determining the proportion of a researcher's own research topics (I4), we opted for text-based topic modeling utilizing publication titles and abstracts, diverging from the originally suggested bibliographic coupling method.
-Initially, we conducted a random sampling of 3000 publications from a set of all publications produced by researchers affiliated with Czech institutions as cataloged in the RIV database, estimated number of topics using Griffiths2004 indicator and calculated LDA topic model on this set of publications.
+Initially, we conducted a random sampling of 3000 publications from a set of all publications produced by researchers affiliated with Czech institutions as cataloged in the RIV database, estimated number of topics using Griffiths2004 indicator, and calculated LDA topic model on this set of publications.
 Then we  compiled all publications generated by the researchers within our sample and their respective supervisors.
@@
 
-To calculate this indicator, we required at least 3 publications. This led to an increased number of missing observations (see section Descriptives -> Missing data).
+To calculate this indicator, we required at least 3 publications.
+This led to an increased number of missing observations (see section Descriptives - Missing data).
 
@@
 
-We calculated how many (Czech) grants each researcher has received prior and 3 years after the intervention year (i.e.
-receiving a Junior Grant).
+We calculated how many (Czech) grants each researcher has received prior and 3 years after the intervention year (i.e. receiving a Junior Grant).
 We did not use this variable for matching, but for filtering out control group researchers pre-matching.
@@
 
-We analysed the data in the R version 4.2.3.
-using R studio and [this code](https://github.com/david-janku/juniors).
-For the construction of the independence indicator, we used network modelling (maybe more specific?) and text-based topic modelling (maybe more specific??).
-
-For the construction of the control group, we implemented propensity matching using the package MatchIt (citation?) and matching exactly by the discipline (42 sub-categories of OECD classification) and treatment year, and approximately by number of publications in total, number of publications in WoS/Scopus, career age, interdisciplinary proportion, number of grants received prior to Junior Grant, career age when receiving the first grant and gender.
-All of these variables were calculated at the intervention year (i.e.
-year when the given researcher from experimental group received the Junior Grant).
+We analysed the data in the R version 4.2.3. using R studio and [this code](https://github.com/david-janku/juniors).
+For the construction of the independence indicator, we used network modelling and text-based topic modelling.
+
+For the construction of the control group, we implemented propensity matching using the package MatchIt [@ho2011] and matching exactly by the discipline (42 sub-categories of OECD classification) and treatment year, and approximately by number of publications in total, number of publications in WoS/Scopus, career age, interdisciplinary proportion, number of grants received prior to Junior Grant, career age when receiving the first grant, and gender.
+All of these variables were calculated in the intervention year (i.e. year when the given researcher from experimental group received the Junior Grant).
 The distance was set to "mahalanobis".
@@
 d$disc_ford <- as.factor(d$disc_ford)
-
 na_counts <- sum(is.na(d$RII))
 na_percentage <- round((na_counts / nrow(d))*100, 1)
-
 na_sup <- round((sum(is.na(d$sup_name))/na_counts)*100, 1)
 na_pubs <- round((nrow(d %>% filter(!is.na(sup_name)) %>% filter(is.na(pubs_number)))/na_counts)*100, 1)
-
 na_pubs_after <- round((nrow(d %>% filter(!is.na(sup_name)) %>% filter(is.na(pubs_number)) %>% filter(independence_timing == "after_intervention"))/nrow(d %>% filter(!is.na(sup_name)) %>% filter(is.na(pubs_number))))*100, 1)
-
 na_treatment <- nrow(d %>% filter(is.na(RII)) %>% filter(treatment == 1))
@@
 na_control2 <- nrow(d %>% filter(is.na(RII)) %>% filter(treatment == 2))
-
 na_counts_researchers <- round(nrow(d %>% filter(!is.na(sup_name)) %>% filter(is.na(pubs_number)) %>% filter(independence_timing == "after_intervention") %>% distinct(vedidk))/nrow(d %>% filter(independence_timing == "after_intervention") %>% distinct(vedidk))*100, 1)
-
 mean_pubs_after <- d %>%
@@
      ungroup()
-
 filtered_subclass <- nrow(filtered_by_subclass %>% distinct(subclass))
@@
 final_before_control2 <- nrow(filtered_by_subclass %>% filter(independence_timing == "before_intervention") %>% filter(treatment == 2))
-
 final_after_control1 <- nrow(filtered_by_subclass %>% filter(independence_timing == "after_intervention") %>% filter(treatment == 0))
@@
 
-When Looking at disciplines, we see that there are slightly more missing data in Agricultural and veterinary sciences and the Humanities and the Arts.
+From a perspective of disciplines, we see that there are slightly more missing data in Agricultural and veterinary sciences and the Humanities and the Arts.
 
 ```{r echo=FALSE}
-
 dt <- d
 dt$missing <- ifelse(is.na(dt$RII), "Missing", "Complete")
-
 # Calculate counts and proportions
@@
   pivot_wider(names_from = missing, values_from = c(count, Proportion))
-
 # If there are any NA values in the 'count_Missing' column, replace them with 0
 df_summary$count_Missing[is.na(df_summary$count_Missing)] <- 0
-
 # Calculate Missing / (Missing + Complete) in percentages for each disc_ford
@@
   mutate(Proportion = ifelse(!is.na(`count_Missing`) & !is.na(`count_Complete`), `count_Missing` / (`count_Missing` + `count_Complete`) * 100, NA))
-
 # If there are any NA values in the 'Proportion' column, replace them with 0
 df_summary$Proportion[is.na(df_summary$Proportion)] <- 0
-
 # Remove unnecessary columns and rename the others
@@
   )
-
 # Print the updated table
-kable(df_summary, digits = 3, caption = "Counts and Proportions of Missing data by disc_ford") %>%
-  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
+kable(df_summary, format = "markdown", digits = 3, caption = "Counts and Proportions of Missing Data by Field")
 
@@
 ```{r echo=FALSE}
-
 df <- filtered_by_subclass %>% filter(independence_timing == "before_intervention")
@@
   names()
-
 # descriptive stats for each treatment level
-table_before_1 <- df %>% filter(treatment == 1) %>% select(all_of(numeric_vars)) %>% describe() %>% select(n, mean, sd, min, max) %>% round(., digits = 3)
-table_before_0 <- df %>% filter(treatment == 0) %>% select(all_of(numeric_vars)) %>% describe() %>% select(n, mean, sd, min, max) %>% round(., digits = 3)
-table_before_2 <- df %>% filter(treatment == 2) %>% select(all_of(numeric_vars)) %>% describe() %>% select(n, mean, sd, min, max) %>% round(., digits = 3)
-
+table_before_1 <- df %>% filter(treatment == 1) %>% distinct(vedidk, .keep_all = TRUE) %>% select(all_of(numeric_vars)) %>% describe() %>% select(n, mean, sd, min, max) %>% round(., digits = 3)
+table_before_0 <- df %>% filter(treatment == 0) %>% distinct(vedidk, .keep_all = TRUE) %>% select(all_of(numeric_vars)) %>% describe() %>% select(n, mean, sd, min, max) %>% round(., digits = 3)
+table_before_2 <- df %>% filter(treatment == 2) %>% distinct(vedidk, .keep_all = TRUE) %>% select(all_of(numeric_vars)) %>% describe() %>% select(n, mean, sd, min, max) %>% round(., digits = 3)
 colnames(table_before_0) <- paste0(colnames(table_before_0), "_0")
 colnames(table_before_2) <- paste0(colnames(table_before_2), "_2")
-
-combined_table_before <- cbind(table_before_1, table_before_0[, -1], table_before_2[, -1])
-
+combined_table_before <- cbind(table_before_1, table_before_0, table_before_2)
 kable(combined_table_before, 
-      digits = 3, align = "c", booktabs = TRUE) %>%
-  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
-  add_header_above(c(" " = 1, "Treatment Group" = 5, "Unfunded Control Group" = 4, "Funded Control Group" = 4))
+      format = "markdown", digits = 3, align = "c", booktabs = TRUE, caption = "Descriptives of All Groups Before Intervention") 
+  # kableExtra::add_header_above(c(" " = 1, "Treatment Group" = 5, "Unfunded Control Group" = 5, "Funded Control Group" = 5))
 
@@
 ```{r echo=FALSE}
-
 df <- filtered_by_subclass %>% filter(independence_timing == "after_intervention")
@@
   names()
-
 # descriptive stats for each treatment level
-table_after_1 <- df %>% filter(treatment == 1) %>% select(all_of(numeric_vars)) %>% describe() %>% select(n, mean, sd, min, max) %>% round(., digits = 3)
-table_after_0 <- df %>% filter(treatment == 0) %>% select(all_of(numeric_vars)) %>% describe() %>% select(n, mean, sd, min, max) %>% round(., digits = 3)
-table_after_2 <- df %>% filter(treatment == 2) %>% select(all_of(numeric_vars)) %>% describe() %>% select(n, mean, sd, min, max) %>% round(., digits = 3)
-
+table_after_1 <- df %>% filter(treatment == 1) %>% distinct(vedidk, .keep_all = TRUE) %>% select(all_of(numeric_vars)) %>% describe() %>% select(n, mean, sd, min, max) %>% round(., digits = 3)
+table_after_0 <- df %>% filter(treatment == 0) %>% distinct(vedidk, .keep_all = TRUE) %>% select(all_of(numeric_vars)) %>% describe() %>% select(n, mean, sd, min, max) %>% round(., digits = 3)
+table_after_2 <- df %>% filter(treatment == 2) %>% distinct(vedidk, .keep_all = TRUE) %>% select(all_of(numeric_vars)) %>% describe() %>% select(n, mean, sd, min, max) %>% round(., digits = 3)
 colnames(table_after_0) <- paste0(colnames(table_after_0), "_0")
 colnames(table_after_2) <- paste0(colnames(table_after_2), "_2")
-
 # Move 'career_length2022' row to the top for each table
@@
 }
-
 table_after_1 <- reorder_row(table_after_1)
@@
 table_after_2 <- reorder_row(table_after_2)
-
 # Re-combine tables
-combined_table_after <- cbind(table_after_1, table_after_0[, -1], table_after_2[, -1])
-
+combined_table_after <- cbind(table_after_1, table_after_0, table_after_2)
 kable(combined_table_after,
-      digits = 3, align = "c", booktabs = TRUE) %>%
-  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
-  add_header_above(c(" " = 1, "Treatment Group" = 5, "Unfunded Control Group" = 4, "Funded Control Group" = 4))
+      format = "markdown", digits = 3, align = "c", booktabs = TRUE, caption = "Descriptives of All Groups After Intervention") %>%
+  kableExtra::add_header_above(c(" " = 1, "Treatment Group" = 5, "Unfunded Control Group" = 5, "Funded Control Group" = 5))
+
+# Assuming table_after_1, table_after_0, table_after_2 are your data frames for different groups
+# 
+# # Assuming each data frame has 5 columns
+# header_columns = c("Header", rep("", 4))
+# header_1 <- data.frame(matrix(nrow = 1, ncol = 5))
+# colnames(header_1) <- header_columns
+# header_1[1, 1] <- "Treatment Group"
+# 
+# header_0 <- data.frame(matrix(nrow = 1, ncol = 5))
+# colnames(header_0) <- header_columns
+# header_0[1, 1] <- "Unfunded Control Group"
+# 
+# header_2 <- data.frame(matrix(nrow = 1, ncol = 5))
+# colnames(header_2) <- header_columns
+# header_2[1, 1] <- "Funded Control Group"
+# 
+# header_names <- colnames(table_after_1)  # Assuming all tables have the same structure
+# header_row <- setNames(data.frame(matrix(ncol = length(header_names), nrow = 1), stringsAsFactors = FALSE), header_names)
+# header_row[1, 1] <- "Your Header Title"  # Set your header title in the first column
+# 
+# combined_table_after <- rbind(header_row, table_after_1, header_row, table_after_0, header_row, table_after_2)
+# 
+# 
+# # # Assuming table_after_1, table_after_0, table_after_2 have the same column names
+# # combined_table_after <- rbind(header_1, table_after_1, 
+# #                               header_0, table_after_0, 
+# #                               header_2, table_after_2)
+# 
+# # Now create the table in R Markdown
+# knitr::kable(combined_table_after, format = "markdown", digits = 3,
+#              caption = "Descriptives of All Groups After Intervention")
+
+# # Table for Treatment Group 1
+# table_after_1_md <- knitr::kable(table_after_1, format = "markdown", 
+#                                  caption = "Treatment Group 1")
+# 
+# # Table for Unfunded Control Group
+# table_after_0_md <- knitr::kable(table_after_0, format = "markdown", 
+#                                  caption = "Unfunded Control Group")
+# 
+# # Table for Funded Control Group
+# table_after_2_md <- knitr::kable(table_after_2, format = "markdown", 
+#                                  caption = "Funded Control Group")
+#
 
@@
 ```{r echo=FALSE}
-
 removed_treatment_unfunded <- (tar_read(ids_complete) %>% distinct(vedidk) %>% nrow())-(tar_read(matching) %>% group_by(subclass) %>% filter(!any(treatment == 2)) %>%
   ungroup() %>% filter(treatment == "1") %>% distinct(vedidk) %>% nrow()) 
-
 removed_treatment_funded <- (tar_read(ids_complete) %>% distinct(vedidk) %>% nrow())-(tar_read(matching) %>% group_by(subclass) %>% filter(!any(treatment == 0)) %>%
   ungroup() %>% filter(treatment == "1") %>% distinct(vedidk) %>% nrow()) 
-
 unique_treatment_unfunded <- d %>% group_by(subclass) %>% filter(!any(treatment == 2)) %>% ungroup() %>% filter(treatment == "1") %>% distinct(vedidk) %>% nrow()
-
 unique_treatment_funded <- d %>% group_by(subclass) %>% filter(!any(treatment == 0)) %>%
   ungroup() %>% filter(treatment == "1") %>% distinct(vedidk) %>% nrow()
-
 unique_control_unfunded <- d %>% filter(treatment == 0) %>% distinct(vedidk) %>% nrow()
@@
 replaced_control_unfunded <- unique_treatment_unfunded-unique_control_unfunded 
-
 replaced_control_funded <- unique_treatment_funded-unique_control_funded
@@
 unf_sum <- summary(tar_read(matched_obj_unfunded), un = TRUE)
-
 # summary(tar_read(matched_obj_unfunded))
@@
 aa <- cobalt::bal.tab(tar_read(matched_obj_unfunded), un = TRUE, stats = c("m", "v", "ks"), binary = "std")
-
 # aa <- aa[!grepl("^disc_ford", names(aa))]
-
 # aa <- aa[!grepl("^disc_ford", names(aa$Balance))]
-
 bal_df <- aa$Balance
-
 bal_df <- bal_df[!grepl("^disc_ford", rownames(bal_df)), ]
@@
 # Display the cleaned-up table with kable
-kable(bal_df, "pipe", caption = "Balance Statistics For Unfunded Control Group") %>%
-  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
+kable(bal_df, format = "markdown", caption = "Summary of Covariate Balance Post-Matching For Unfunded Control Group", digits = 3)
 
 aa$Balance <- bal_df
-
 cobalt::love.plot(aa, binary = "std", var.order = "adjusted")
 
+```
+
+```{r echo=FALSE, fig.cap="Covariate balance table for the funded control group."}
+
 ##Funded group
@@
 fun_sum <- summary(tar_read(matched_obj_funded), un = TRUE)
-
 # summary(tar_read(matched_obj_funded))
@@
 bb <- cobalt::bal.tab(tar_read(matched_obj_funded), un = TRUE, stats = c("m", "v", "ks"), binary = "std")
-
 # aa <- aa[!grepl("^disc_ford", names(aa))]
-
 # aa <- aa[!grepl("^disc_ford", names(aa$Balance))]
@@
 bal_df_funded <- bb$Balance
-
 bal_df_funded <- bal_df_funded[!grepl("^disc_ford", rownames(bal_df_funded)), ]
@@
 # Display the cleaned-up table with kable
-kable(bal_df_funded, "pipe", caption = "Balance Statistics For Funded Control Group") %>%
-  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
+kable(bal_df_funded, format = "markdown", caption = "Summary of Covariate Balance Post-Matching For Funded Control Group", digits = 3)
 
 bb$Balance <- bal_df_funded 
-
 cobalt::love.plot(bb, binary = "std", var.order = "adjusted")
@@
 ```{r echo=FALSE}
-
 pp <- d %>%
@@
      ungroup()
-
 pp <- pp %>%
@@
      ungroup()
-
 diff_data <- pp %>%
@@
   select(subject_id, RII_diff)
-
 pp <- left_join(pp, diff_data, by = "subject_id")
@@
     mutate(treatment = factor(treatment, levels = c(0, 1)))
-
 filtered_by_subclass_1$subclass <- as.factor(filtered_by_subclass_1$subclass)
@@
 filtered_by_subclass_1$field <- as.factor(filtered_by_subclass_1$field)
-
 # this DiD model unfortunately doesnt work for some reason that I cannot resolve, but it is possible to calculate the same using repeated measures anova or mixes effects model, so it should be fine
-
 # # Run regression model with interaction term
@@
 #               data = filtered_by_subclass_1)
-
 # summary(model_disc)
@@
 eta_sq_result <- eta_squared(result)
-
 # Normality: You can check the normality of the residuals using a Q-Q plot and the Shapiro-Wilk test.
-
 # Check residuals from lm
 # plot(resid(result))
-
 #Linearity and Homoscedasticity (Equal Variances) of Residuals: If the assumptions hold, you should not see any obvious patterns or funnel shapes in the plot.
-
 # plot(result$fitted.values, resid(result), 
@@
 # abline(h = 0, col = "red")
-
 # Normality of Residuals: 
@@
 A value around 2 suggests no autocorrelation, while values below 1 and above 3 are cause for concern.
-
 # library(car)
@@
 # Multicollinearity: Check the variance inflation factor (VIF) for each predictor. Typically, a VIF above 5-10 indicates multicollinearity.
-
 # vif(result)
-
 # Outliers and Influence Points: Leverage vs. studentized residuals plot can be used to identify influential points.
-
 # plot(hatvalues(result), rstudent(result),
@@
 # Sphericity: Use the mauchly.test function on your model. If the test is significant, then the assumption of sphericity has been violated.
-
 # mauchly.test(model_aov)
-
 # Homogeneity of Variance: Use Levene's Test. The car package offers leveneTest.
-
 # library(car)
 # leveneTest(RII ~ treatment, data = filtered_by_subclass_1)
-
 # Outliers:You can inspect boxplots or use Mahalanobis distance.
-
 # boxplot(RII ~ treatment, data = filtered_by_subclass_1)
@@
 ##conducting repeated measures ANOVA
-
 # filtered_by_subclass_1 <- filtered_by_subclass_1 %>%
@@
 #      ungroup()
-
 # #this is preferable because it takes into account the matched nature of the data, as well as repeated measures nature of the data -> see chatGPT conversation "ANOVA `wid` parameter clarification"
@@
 # eta_sq_result <- eta_squared(result)
-
 #this is less preferable because it takes into account only the repeated measure nature of the data, not the matched nature -> you can see that when you run this tests, there is warning that says "there were non-unique subclass values across the between-subjects variable (treatment).
@@
 ## adding disciplines:
-
 filtered_data_disc_1 <- filtered_by_subclass_1 %>%
@@
   filter(n() >= 8)
-
 filtered_data_disc_1$field <- droplevels(filtered_data_disc_1$field)
-
 # Calculate weights based on group size (you can adjust this based on other criteria if needed)
@@
 filtered_data_disc_1$weights <- max_size / group_sizes[filtered_data_disc_1$field]
-
 #this model addresses both unequal group sizes (via weights) and heteroscedasticity (via varIdent).
@@
 #this model directly tests whether there is a difference in disciplines - anyway it tests each discipline agains each other, so it doesnt produce the neat result of "yes, there are some significant differences between disciplines", but more nuanced version of "there is specifically difference between this and this discipline"
-
 model_gls_weighted <- gls(RII ~ field, data = filtered_data_disc_1, 
@@
                           correlation = corAR1(form = ~ 1 | subject_id))  
-
 # summary(model_gls_weighted)
-
 #this model below is the same as the above but with added predictors
-
 model_gls_interactions_subclass <- gls(RII ~ field * treatment * independence_timing, 
@@
                               correlation = corAR1(form = ~ 1 | subclass/independence_timing)) 
-
 # aa <- summary(model_gls_interactions_subclass)
@@
 #one potential strategy to get the neat result of "yes, there are some significant differences between disciplines" is following: create two similar models 
-
 model_without_field <- gls(RII ~ treatment + independence_timing + treatment:independence_timing, 
@@
                            method = "ML")
-
 model_with_field_main_effect <- gls(RII ~ treatment + field + independence_timing + treatment:independence_timing, 
@@
 anova_result <- anova(model_without_field, model_with_field_main_effect)
-
 model_summary <- summary(model_with_field_main_effect)
@@
 #this model does NOT address unequal group sizes (via weights) and heteroscedasticity 
-
 # result_disc <- ezANOVA(data = filtered_data_disc_1,
@@
 0.2 in RII, which is 20 % oif the RII score)
-
 # filtered_data_disc_1 <- filtered_data_disc_1 %>% 
@@
 ## visualise field*treatment
-
 # means_table <- filtered_by_subclass_1 %>%
@@
 
-```{r echo=FALSE}
-
+```{r echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Violin Plot of RII Scores by Treatment and Time with Mean and CI Overlayed for the Unfunded Control Group."}
 ### visualisations
@@
 means <- aggregate(RII ~ treatment + independence_timing, data = filtered_by_subclass_1, FUN = mean)
-
  # ggplot(data = filtered_by_subclass_1, aes(x = treatment, y = RII, fill = independence_timing)) +
@@
   )
-
 # # Plot
@@
 dodge_width <- 0.5
-
 combined_plot <- ggplot() +
@@
 
-  labs(title = "Violin Plot of RII Scores by Treatment and Time with Mean and CI Overlayed",
-       x = "Treatment Group",
+  labs(x = "Treatment Group",
        y = "RII Score") +
   theme_bw()
-
 print(combined_plot)
-
-```
-
-```{r echo=FALSE}
-
+```
+
+```{r echo=FALSE, warning=FALSE, message=FALSE}
 # means_disc <- aggregate(RII ~ field, data = filtered_by_subclass_1, FUN = mean)
@@
     mutate(treatment = factor(treatment, levels = c(0, 1)))
-
 filtered_by_subclass_2$subclass <- as.factor(filtered_by_subclass_2$subclass)
@@
 filtered_by_subclass_2$field <- as.factor(filtered_by_subclass_2$field)
-
 # this DiD model unfortunately doesnt work for some reason that I cannot resolve, but it is possible to calculate the same using repeated measures anova or mixes effects model, so it should be fine
@@
   filter(n() >= 8)
-
 filtered_data_disc_2$field <- droplevels(filtered_data_disc_2$field)
-
 # Calculate weights based on group size (you can adjust this based on other criteria if needed)
@@
 filtered_data_disc_2$weights <- max_size2 / group_sizes2[filtered_data_disc_2$field]
-
 #this model addresses both unequal group sizes (via weights) and heteroscedasticity (via varIdent).
@@
 #this model directly tests whether there is a difference in disciplines - anyway it tests each discipline agains each other, so it doesnt produce the neat result of "yes, there are some significant differences between disciplines", but more nuanced version of "there is specifically difference between this and this discipline"
-
 model_gls_weighted2 <- gls(RII ~ field, data = filtered_data_disc_2, 
@@
                           correlation = corAR1(form = ~ 1 | subject_id))  
-
-# summary(model_gls_weighted2)
-
+interaction_summary <- summary(model_gls_weighted2)
 #this model below is the same as the above but with added predictors
-
 model_gls_interactions_subclass2 <- gls(RII ~ field * treatment * independence_timing, 
@@
                               correlation = corAR1(form = ~ 1 | subclass/independence_timing)) 
-
 # aa <- summary(model_gls_interactions_subclass2)
@@
                            method = "ML")
-
 model_with_field_main_effect2 <- gls(RII ~ treatment + field + independence_timing + treatment:independence_timing, 
@@
 anova_result2 <- anova(model_without_field2, model_with_field_main_effect2)
-
 model_summary2 <- summary(model_with_field_main_effect2)
@@
 dodge_width <- 0.5
-
 combined_plot2 <- ggplot() +
@@
 
-  labs(title = "Violin Plot of RII Scores by Treatment and Time with Mean and CI Overlayed",
-       x = "Treatment Group",
+  labs(x = "Treatment Group",
        y = "RII Score") +
   theme_bw()
-
 print(combined_plot2)
@@
      ungroup()
-
 means_disc_complete <- aggregate(RII ~ field, data = disc_data, FUN = mean)
@@
   summarise(count = n(), .groups = "drop")
-
 means_disc_complete <- left_join(means_disc_complete, num_disc_complete, by = "field") 
-
 # Step 1: Reorder the levels of 'field'
 means_disc_complete$field <- with(means_disc_complete, factor(field, levels=unique(field[order(RII)])))
-
 # Step 2: Optionally, sort the dataframe based on the reordered levels
@@
             .groups = "drop")
-
 means_disc_complete <- merge(means_disc_complete, se_ci_data_complete, by = "field")
@@
 
-```{r echo=FALSE}
-
+```{r echo=FALSE, warning=FALSE, message=FALSE}
 cor_data <- d %>% dplyr::select(RII, ind_topics, ind_pubs, clustr, eig_centr)
-
 cor_matrix <- cor(cor_data, use = "pairwise.complete.obs")
-
 # reversed_cor_matrix <- cor_matrix[rev(rownames(cor_matrix)), rev(colnames(cor_matrix))]
-
-kable(cor_matrix, format = "html", digits = 2) %>%
-  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
+kable(cor_matrix, format = "markdown", digits = 2, caption = "Correlation Matrix of RII indicator and its sub-parts")
 
@@
     pull(mean_value)
-
 ind_top_mean_after <- d %>% 
@@
 
-```{r echo=FALSE}
-
+```{r echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Violin Plot of the Cognitive Part of RII Scores by Treatment and Time with Mean and CI Overlayed for the Unfunded Control Group."}
 ### visualisations
@@
 
-  labs(title = "Violin Plot of ind_topics Scores by Treatment and Time with Mean and CI Overlayed",
-       x = "Treatment Group",
+  labs(x = "Treatment Group",
        y = "ind_topics Score") +
   theme_bw()
-
 print(combined_plot)
@@
 
-When looking at the scores of cognitive part of independence indicator, we cannot see notable differences across fields of study, unlike it case of the whole RII.
---> SHOULD I STATISTICALLY TEST whether adding filed of study improves prediction of the id_topics? (same way as when I tested that for full RII)??
-
-```{r echo=FALSE}
-
+Similar pattern can be observed in differences across disciplines - while there were significant differences in full indicator scores, its cognitive part doesn't show any differences, suggesting that collaboration is the factor driving differences across fields of study.
+
+```{r echo=FALSE, fig.cap="Differences in Average Cognitive RII Scores (ind_topic) Across Disciplines and Time."}
 disc_data <- d %>%
@@
      ungroup() 
+disc_data <- disc_data[!duplicated(disc_data[c("subject_id", "independence_timing")]), ]
 
@@
   select(subject_id, ind_topics_diff)
-
 disc_data <- left_join(disc_data, diff_data_tp, by = "subject_id")
-
 disc_data <-  disc_data %>% 
@@
   summarise(count = n(), .groups = "drop")
-
 means_disc_complete <- left_join(means_disc_complete, num_disc_complete, by = "field") 
-
 # Step 1: Reorder the levels of 'field'
 means_disc_complete$field <- with(means_disc_complete, factor(field, levels=unique(field[order(ind_topics)])))
-
 # Step 2: Optionally, sort the dataframe based on the reordered levels
@@
   summarise(count = n(), .groups = "drop")
-
 means_disc_change <- left_join(means_disc_change, num_disc_change, by = "field") 
-
 # Step 1: Reorder the levels of 'field'
 means_disc_change$field <- with(means_disc_change, factor(field, levels=unique(field[order(ind_topics_diff)])))
-
 # Step 2: Optionally, sort the dataframe based on the reordered levels
@@
             .groups = "drop")
-
 means_disc_change <- merge(means_disc_change, se_ci_data_change, by = "field")
@@
 ```{r echo=FALSE}
-
 treatment_found_pc <- round(nrow(tar_read(final_data) %>% filter(!is.na(sup_name)) %>% filter(treatment == 1) %>% distinct(vedidk))/348*100, 2)
-
 control_found_pc <- round(nrow(tar_read(final_data) %>% filter(!is.na(sup_name)) %>% filter(treatment != 1) %>% distinct(vedidk))/nrow(tar_read(final_data) %>% filter(treatment != 1) %>% distinct(vedidk))*100, 2)
@@
 match_no_pc <- round(nrow(treatment_match %>% filter(match == 0) %>% distinct(vedidk))/nrow(treatment_match %>% distinct(vedidk))*100, 2)
-
 match_na <- nrow(treatment_match %>% filter(is.na(match)) %>% distinct(vedidk))

### 2024-01-23 _targets.Rmd
edits in text

--- 2024-01-08 _targets.Rmd
@@
     # 
-    tarchetypes::tar_render(article, here::here("article.Rmd"))
+    tarchetypes::tar_render(article, here::here("article_formatted_doc.Rmd"))
 )

### 2024-01-23 article_formatted.Rmd
edits in text

@@
     of Philosophy, Czech Academy of Sciences, Czech Republic'
-output: bookdown::word_document2
+output: bookdown::html_document2
 always_allow_html: true

### 2024-01-23 article_formatted_doc.Rmd
edits in text

@@
 ---
-title: "Funding programmes for early career researchers do not improve their independence"
-author:
-- name: David Janků
-  affiliation: '[1] Institute of Sociological Studies, Faculty of Social Sciences,
-    Charles University, Czech Republic; [2] Centre for Science, Technology, and Society
-    Studies, Institute of Philosophy, Czech Academy of Sciences, Czech Republic'
-- name: Radim Hladík
-  affiliation: '[1] Centre for Science, Technology, and Society Studies, Institute
-    of Philosophy, Czech Academy of Sciences, Czech Republic'
+title: "Mission Unaccomplished: A Funding Programme for Early Career Researchers Fails to Promote Independence"
 output: bookdown::word_document2
@@
 
-**Authors:**
-
-David Janků  
-[1] Institute of Sociological Studies, Faculty of Social Sciences, Charles University, Czech Republic; 
-[2] Centre for Science, Technology, and Society Studies, Institute of Philosophy, Czech Academy of Sciences, Czech Republic
-
-Radim Hladík  
+## Authors:
+- David Janků
+[1] Centre for Science, Technology, and Society Studies, Institute of Philosophy, Czech Academy of Sciences, Czech Republic; [2] Institute of Sociological Studies, Faculty of Social Sciences, Charles University, Czech Republic;
+- Radim Hladík
 [1] Centre for Science, Technology, and Society Studies, Institute of Philosophy, Czech Academy of Sciences, Czech Republic
@@
 Affiliation: 
-[1] Institute of Sociological Studies, Faculty of Social Sciences, Charles University, Czech Republic
-[2] Centre for Science, Technology, and Society Studies, Institute of Philosophy, Czech Academy of Sciences, Czech Republic  
+[1] Centre for Science, Technology, and Society Studies, Institute of Philosophy, Czech Academy of Sciences, Czech Republic
+[2] Institute of Sociological Studies, Faculty of Social Sciences, Charles University, Czech Republic  
 Address: U Kříže 661/8, Praha 5 – Jinonice  
@@
 
-Independence is important quality constituting one factor of research excellence, often used in assessments for hiring, tenure and promotion in academia [@moherAssessingScientistsHiring2018].
-From a bigger picture view, encouraging more independence might also lead to faster exploration of the cognitive map of science and thus lead to faster innovation.
-Many national research funders have created programmes specifically aimed at increasing independence of early career researchers, yet until recently, there was no quantifiable way to measure changes in independence.
-We employed recently proposed measure by @vandenbesselaarMeasuringResearcherIndependence2019 to assess whether one such a funding programme by Czech Science Foundation is effective at stimulating more independence.
-We found that funding for early career researchers is not effective at stimulating their independence, regardless of the source of funding.
-The strongest effect on independence growth is time, explaining around 60% of the variance in independence.
-Additionally, we found differences in levels of independence across disciplines that were stable across time and treatment groups, with Social Sciences and Humanities showing highest independence, while  Agricultural and Veterinary sciences and Medical and Health Sciences showing lowest independence.
-However, these differences reflect only changes in collaboration patterns, while there were no changes in cognitive patterns across disciplines and only modest changes across time (from 40 % to 46 % of topics not shared by their PhD advisor).
+Independence is an important factor in research excellence, often assessed for hiring, tenure, and promotion in academia.
+From a macro perspective, increased independence might also lead to faster exploration of the cognitive map of science and thus accelerate innovation.
+Many national research funders have created programmes specifically aimed at increasing the independence of early career researchers (ECRs).
+A quantifiable measure of such programmes' impact on changes in independence has long been lacking.
+We employed a recently proposed independence indicator [@vandenbesselaarMeasuringResearcherIndependence2019], to assess whether one such funding programme operated by Czech Science Foundation succeeds at stimulating independence.
+The indicator tracks overlaps in collaboration networks and topic focus between ECRs and their Ph.D.
+advisors.
+We found that the funding scheme designed for ECRs is not effective at fostering their independence.
+Regardless of the type of funding, the strongest effect on independence growth is time, explaining around 60% of the variance in independence.
+Additionally, we found differences in levels of independence across disciplines that were stable across time and treatment groups.
+Researchers in Social Sciences and Humanities demonstrated the highest independence scores, while those in Agricultural and Veterinary Sciences, and Medical and Health Sciences, showed the lowest.
+However, observed changes in independence across time and disciplines were caused by changes in collaboration patterns, while there were no changes in cognitive patterns across disciplines and only modest changes across time (from 40 % to 46 % of topics not shared by their PhD advisor).
 
 ## Keywords
-research independence; early career researchers; grant funding; mentoring; counter-factual analysis; research evaluation
+research independence; early career researchers; project funding; mentoring; counter-factual analysis; research evaluation
 
@@
 
-To what extent is scientific progress conserved and impeded by novices mirroring seniors’ research agendas?
+The development of an independent research agenda is important not only to the career prospects of early career researchers (ECRs) but contributes to the advancement of science as a whole.
+Independent ECRs help accelerate scientific progress and push state of the art beyond the status quo.
+They are more likely to come up with new topics and ideas [@packalen2019] and challenge commonly held views [@vandenbesselaarMeasuringResearcherIndependence2019, p.2].
+The need to cultivate research independence is a recognized objective in science policies, leading to the creation of grant programmes targeting Early Career Researchers (ECRs) by governments and funding agencies.
+Yet, the effectiveness of these financial incentives in fostering independence has not been empirically assessed.
+
+An independent investigator is defined by the US National Academies of Science [@nationalresearchcouncilus2005] as “one who enjoys the independence of thought—the freedom to define the problem of interest and to choose or develop the best strategies and approaches to addressing that problem–especially during the earlier career phase” [@vandenbesselaarMeasuringResearcherIndependence2019, p.4].
+Such a definition does not necessarily put independence in relation to other actors (e.g.
+one’s PhD advisor), but only in relation to one’s own freedom and resources.
+However, other institutions, such as European Research Council via their Starting Grants scheme [@neufeldPeerReviewbasedSelection2013], think of independence in a relational manner, in terms of having few publications without the former PhD supervisor being co-author; being PI on a grant; or being lab director or research leader.
+
+## Literature review
+
+A considerable obstacle on the road to independence is the tendency of novices to mirror the research agendas of their mentors.
+This phenomenon is common because following established traditions is often seen as a safer and more advantageous option for ECRs, despite the significant importance of independence in hiring procedures.
+Partnering with well-established seniors can provide significant career benefits [@li2019].
+Being thematically aligned with their PhD and post-doc advisors increases the likelihood of continuing in academia and having more mentees in the future [@lienard2018].
+Empirical evidence indicates that a majority of researchers choose this strategy [@foster2015].
+<!-- To what extent is scientific progress conserved and impeded by novices mirroring seniors’ research agendas?
 Such a phenomenon is likely to occur because following tradition is usually a more beneficial and safer option for novices.
@@
 For early career researchers specifically, partnering with already well-established seniors provides a large career boost [@li2019] and being thematically closer to their PhD as well as their post-doc advisor increases the probability of continuing in academia and having more mentees later on [@lienard2018].
+-->
 However, this effect might stifle scientific progress as it leads to a slower exploration of its cognitive map [@rzhetsky2015].
 Moreover, this mirroring further strengthens the existing positions of senior faculty, making little space for disrupting the status quo and creating new perspectives.
+
 This was illustrated by @azoulay2010, who investigated the effects of unexpected deaths of prominent scientists in their research fields and their collaborators' careers.
@@
 
-As younger researchers are already more likely to come up with new topics and ideas [@packalen2019], it would be fitting to empower them and stimulate their independence so that they can “challenge the existing common views and open up new lines of research” [@vandenbesselaarMeasuringResearcherIndependence2019, p.2] and accelerate scientific progress rather than recreate the existing status quo.
-An independent investigator is then defined by the US National Academies of Science [@nationalresearchcouncilus2005] as “one who enjoys the independence of thought—the freedom to define the problem of interest and to choose or develop the best strategies and approaches to addressing that problem–especially during the earlier career phase” [@vandenbesselaarMeasuringResearcherIndependence2019, p.4].
+<!-- As younger researchers are already more likely to come up with new topics and ideas [@packalen2019], it would be fitting to empower them and stimulate their independence so that they can “challenge the existing common views and open up new lines of research” [@vandenbesselaarMeasuringResearcherIndependence2019, p.2] and accelerate scientific progress rather than recreate the existing status quo.
+-->
+<!-- An independent investigator is then defined by the US National Academies of Science [@nationalresearchcouncilus2005] as “one who enjoys the independence of thought—the freedom to define the problem of interest and to choose or develop the best strategies and approaches to addressing that problem–especially during the earlier career phase” [@vandenbesselaarMeasuringResearcherIndependence2019, p.4].
 Such a definition does not necessarily put independence in relation to other actors (e.g.
 one’s PhD advisor), but only in relation to one’s own freedom and resources.
-However other institutions, such as European Research Council via their Starting Grants scheme [@neufeldPeerReviewbasedSelection2013] think of independence in a relational manner, in terms of having one (or a few) publications without the former PhD supervisor being co-author; being PI on a grant; or being lab director or research leader.
+However other institutions, such as European Research Council via their Starting Grants scheme [@neufeldPeerReviewbasedSelection2013], think of independence in a relational manner, in terms of having one (or a few) publications without the former PhD supervisor being co-author; being PI on a grant; or being lab director or research leader.
+-->
 
@@
 
+#### below is html version - comment it away if you are printing in doc
+
+# df <- filtered_by_subclass %>% filter(independence_timing == "before_intervention")
+# numeric_vars <- df %>%
+#   select(where(is.numeric)) %>%
+#   select(-weights, -funded_control, -id, -treatment_year, -career_start_year) %>%
+#   names()
+# 
+# # descriptive stats for each treatment level
+# table_before_1 <- df %>% filter(treatment == 1) %>% distinct(vedidk, .keep_all = TRUE) %>% select(all_of(numeric_vars)) %>% describe() %>% select(n, mean, sd, min, max) %>% round(., digits = 3)
+# table_before_0 <- df %>% filter(treatment == 0) %>% distinct(vedidk, .keep_all = TRUE) %>% select(all_of(numeric_vars)) %>% describe() %>% select(n, mean, sd, min, max) %>% round(., digits = 3)
+# table_before_2 <- df %>% filter(treatment == 2) %>% distinct(vedidk, .keep_all = TRUE) %>% select(all_of(numeric_vars)) %>% describe() %>% select(n, mean, sd, min, max) %>% round(., digits = 3)
+# 
+# colnames(table_before_0) <- paste0(colnames(table_before_0), "_0")
+# colnames(table_before_2) <- paste0(colnames(table_before_2), "_2")
+# 
+# combined_table_before <- cbind(table_before_1, table_before_0, table_before_2)
+# 
+# kable(combined_table_before,
+#       digits = 3, align = "c", booktabs = TRUE, caption = "Descriptives of All Groups Before Intervention") %>%
+#   kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
+#   add_header_above(c(" " = 1, "Treatment Group" = 5, "Unfunded Control Group" = 5, "Funded Control Group" = 5))
+
 ```
@@
 #
+
+#### below is html version - comment it away if you are printing in doc
+
+# df <- filtered_by_subclass %>% filter(independence_timing == "after_intervention")
+# df$career_length2022 <- 2022-df$career_start_year
+# numeric_vars <- df %>% 
+#   select(where(is.numeric)) %>% 
+#   select(-weights, -funded_control, -id, -treatment_year, -career_start_year, -career_length, -pubs_total, -ws_pubs, -interdisc_proportion, -grants, -total_coauthor_count, -first_grant) %>% 
+#   names()
+# 
+# # descriptive stats for each treatment level
+# table_after_1 <- df %>% filter(treatment == 1) %>% distinct(vedidk, .keep_all = TRUE) %>% select(all_of(numeric_vars)) %>% describe() %>% select(n, mean, sd, min, max) %>% round(., digits = 3)
+# table_after_0 <- df %>% filter(treatment == 0) %>% distinct(vedidk, .keep_all = TRUE) %>% select(all_of(numeric_vars)) %>% describe() %>% select(n, mean, sd, min, max) %>% round(., digits = 3)
+# table_after_2 <- df %>% filter(treatment == 2) %>% distinct(vedidk, .keep_all = TRUE) %>% select(all_of(numeric_vars)) %>% describe() %>% select(n, mean, sd, min, max) %>% round(., digits = 3)
+# 
+# colnames(table_after_0) <- paste0(colnames(table_after_0), "_0")
+# colnames(table_after_2) <- paste0(colnames(table_after_2), "_2")
+# 
+# # Move 'career_length2022' row to the top for each table
+# reorder_row <- function(tbl) {
+#   return(tbl[c("career_length2022", setdiff(rownames(tbl), "career_length2022")), ])
+# }
+# 
+# table_after_1 <- reorder_row(table_after_1)
+# table_after_0 <- reorder_row(table_after_0)
+# table_after_2 <- reorder_row(table_after_2)
+# 
+# # Re-combine tables
+# combined_table_after <- cbind(table_after_1, table_after_0, table_after_2)
+# 
+# kable(combined_table_after, 
+#       digits = 3, align = "c", booktabs = TRUE, caption = "Descriptives of All Groups After Intervention") %>%
+#   kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
+#   add_header_above(c(" " = 1, "Treatment Group" = 5, "Unfunded Control Group" = 5, "Funded Control Group" = 5))
 
@@
   scale_color_manual(values = c("black", "red"), name = "Independence Timing", labels = c("Before intervention", "After intervention")) +
-
-  labs(x = "Treatment Group",
+  scale_x_discrete(labels=c("Unfunded control", "Treatment")) + # This line changes the x-axis labels
+
+  labs(x = "Treatment group",
        y = "RII Score") +
@@
   scale_color_manual(values = c("black", "red"), name = "Independence Timing", labels = c("Before intervention", "After intervention")) +
-
-  labs(x = "Treatment Group",
+  scale_x_discrete(labels=c("Funded control", "Treatment")) + # This line changes the x-axis labels
+
+  labs(x = "Treatment group",
        y = "RII Score") +
@@
   scale_color_manual(values = c("black", "red"), name = "Independence Timing", labels = c("Before intervention", "After intervention")) +
+  scale_x_discrete(labels=c("Unfunded control", "Treatment")) + # This line changes the x-axis labels
 
